### 2020-05-13 paper/main.tex
Add alg II and alg IV, some minor cleanup

\input{preamble.tex}

\author{Adrian Siwiec}
\date{\today{}}
\begin{document}

\section{Notes}
\begin{itemize}
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
\end{itemize}

\section{Algorithms}
\begin{algorithm}
	\SetKwFunction{colorGraph}{\textsc{Color-Graph}}
\end{algorithm}

\input{algII.tex}

\input{algIV.tex}

\end{document}

### 2020-05-18 paper/main.tex
ALG III

@@
 	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
-	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
 	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
-	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
+	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
+	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
+	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
+	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
+	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
+	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
 	\item $[n]$  -- $\{1, \ldots, n\}$.
 	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
+	\item $a \gets b$ -- let a be equal b.
+	\item $a :\in X$ -- let a be equal to any element of $X$
+	\item $a \xor b$ -- $a$ xor $b$
 \end{itemize}
@@
 
+\input{algIII.tex}
+
 \input{algIV.tex}

### 2020-05-18 paper/algV.tex
ALG V

\begin{algorithm}
	\SetKwFunction{GoodPartitionOddH}{\textsc{Good-Partition-From-Odd-Hyperprism}}
	\Indm\nonl\GoodPartitionEvenH{$G, H, M$}\\
	\KwData{$G$ -- square-free, Berge graph containing no \LGBSK \newline
		$H = (A_1, \ldots, B_3)$  -- maximal odd hyperprism in $G$ \newline
	$M$ -- set of major neighbors of $H$}
	\KwResult{A good partition of $G$}
	\Indp

	$Z \gets \bigcup\{V(C)$ : $C$ is a component of $G \setminus \{V(H) \cup M \}$ with no attachments in $H \}$  \;

	relabel strips of $H$, so that $A_1 \setAntiComplete B_1$ and $A_2 \setAntiComplete B_2$\;
	\Assert{$C_1 \neq \emptyset, C_2 \neq \emptyset$}

	$\forall_{i \in [3]} F_i \gets \bigcup\{ V(C)$ : $C$ is a component of $G \setminus \{H \cup M \cup Z \}$ that
	attaches to $A_i \cup B_i \cup C_i$  $\}$ \;
	% $F_A \gets \bigcup \{ V(C) $ : $C$ is a component of $G \setminus \{ H \cup M \cup Z \cup F_1 \cup F_2 \cup F_3 \}$
	% that attaches to $A_1 \cup A_2 \cup A_3$  $\}$ \;

	$F_B \gets \bigcup \{ V(C) $ : $C$ is a component of $G \setminus \{ H \cup M \cup Z \cup F_1 \cup F_2 \cup F_3 \}$
	that attaches to $B_1 \cup B_2 \cup B_3$  $\}$ \;

	\TODO{$F_i, F_A, F_B$ are from algIV, make sure it is correct}

	\Assert{At least two of $A_i$ and at least two of $B_i$ are cliques}
	\Assert{$M$ is complete to at least two of $A_i$ and at least two of $B_i$}
	\Assert{$M$ is a clique}
	\Assert{For at least two $i$ : $A_i \cup M$ is a clique}
	\Assert{For at least two $j$ : $A_j \cup M$ is a clique}

	% pick any $x_1 :\in C_1, x_2 :\in C_2, a_3 :\in A_3$, so that $\tau \gets \{x_1, x_2, a_3\}$ is a triad \;

	choose $h$, so that $M \cup A_h$ and $M \cup B_h$ are cliques\;

	\If(\tcp*[h]{\TODO{make sure $h=2$ is ok}}){$h = 1 \lor h = 2$}{
		$K_1 \gets A_1$, $K_2 \gets M$, $K_3 \gets B_1$\;
		$R \gets C_1 \cup F_1 \cup Z$\;
		$L \gets G \setminus \{K_1 \cup K_2 \cup K_3 \cup R\}$ \;
		\Return $(K_1, K_2, K_3, L, R)$\;
		} \Else {
		relabel $H$ so that $M \cup A_1$ and $M \cup B_2$ are cliques\;
		$K_1 \gets B_2 \cup B_3$, $K_2 \gets M$, $K_3 \gets A_1 \cup A_3$\;
		$L \gets B_1 \cup C_1 \cup F_1 \cup F_B$\;
		$R \gets G \setminus \{K_1 \cup K_2 \cup K_3 \cup L\}$ \;
		\Return $(K_1, K_2, K_3, L, R)$\;
	}
\end{algorithm}

### 2020-05-19 paper/algVII.tex
ALG VI

\begin{algorithm}
  \SetKwFunction{FindSpecialK}{\textsc{Find-Special-K4-Strip-System}}
	\Indm\nonl\FindSpecialK{$G, J, (S, N), m$}\\
  \KwData{$G$ -- square-free, Berge graph \newline
    $J$ -- a $3$-connected graph with appearance in $G$ \newline
    $(S, N)$ -- a $J$-strip system \newline
    $m \in G \setminus (S, N)$ that is major w.r.t. some choice of rungs of $(S, N)$ but not w.r.t. $(S, N)$
  }
  \KwResult{$(S', N')$ -- A special $K_4$-strip system, or \newline
  $(S'', N'')$ -- a bigger $J$-strip system
  }
  \Indp	
\end{algorithm}

### 2020-05-19 paper/algVIII.tex
ALG VI

\unfinishedAlg[-.45cm]{
	\SetKwFunction{GrowJStrip}{\textsc{Growing-J-Strip}}
	\Indm\nonl\GrowJStrip{$G, J, (S, N)$}\\
	\KwData{$G$ -- square-free, Berge graph \newline
		$J$ -- a $3$-connected graph with appearance in $G$ \newline
		$(S, N)$ -- a $J$-strip system \newline
		\TODO{make sure def of $J$ is correct}
	}
	\KwResult{$J'$ and a maximal $J'$-strip system, or a special strip system}
	\Indp	
	$M \gets$ vertices of $G \setminus V(S, N)$ that are major on some choice of Rungs of $(S, N)$\;
	\TODO{$M$ like ALGI} 
	\If {$\exists m : m$ is not major on some choice of rungs of $(S, N)$}{
		$OUT \gets$ \FindSpecialK{$G, J, (S, N), m$} \;
		\If{$OUT$ is a special strip system}{
			\Return $OUT$ \;
		}
		\Else{
			\Return \GrowJStrip{$G, OUT$} \;
		} 
	}
	\ElseIf{$\exists F$ : $F$ is a component of $G\setminus(V(S,N) \cup M)$, 
		such that no member of $F$ is major w.r.t. $(S, N)$ 
		and set of attachments of $F$ on $H$ is not local}{
		\Assert[6.2, or actually SPGT 8.5]{}
		$F \gets$ minimal (component?) with this property\;

		\If{$\exists v \in V(J): X \subset \bigcup(S_{uv} : uv \in E(J))$}{
			$x :\in X \cap S_{uv} \setminus N_v$, for some $uv \in E(J)$\; \TODO{brackets?}
			$x' :\in X \cap S_{u'v}$, for some $u'v \in E(J), u' \neq u$\;
			\Assert{$\{x, x'\}$ is not local w.r.t. $(S,N)$}
			$L(H) \gets \forall_{i,j \in E(J)}$ choose $ij$-rung $R_{ij}$, so that $x \in V(R_{uv}), x' \in V(R_{u'v})$\;
			\Assert{$\{x, x'\}$ is not local w.r.t. $L(H)$}
			$D \gets$ a branch of $H$ with ends $d, u$: $\delta_H(d) \setminus E(D) = (X \cap E(H)) \setminus E(D)$\;
			$P \gets$ a path with ends $p_1, p_2$, so that: \nonl \;
			\pushline $p_1 \blacktriangleleft N_v \setminus N_{vu}$ and
			no other vertex of $P$ has neighbors in $N_v \setminus N_{uv}$ \nonl \;
			$p_2 - x$ and no other vertex of $P$ has neighbors in $S_{uv} \setminus N_v$ \;
			\popline
			$(S', N') \gets $ add $p_1$ to $N_v$ and $F$ to $S_{uv}$ \;
			\Return \GrowJStrip($G, J, (S',N')$)\;
		}
		\Else {
			$K \gets \{uv \in E(J) : X \cap S_{uv} \neq \emptyset \}$\;
			\Assert[SPGT 8.5.(3)]{There are two disjoint edges in $K$}
			$F$ is a vertex set of a path $\gets f_1 - \ldots - f_n$\;
			\Assert{Every choice of rungs is broad}
		}
	}
}

\continueAlg[-9cm]{
  \setcounter{AlgoLine}{18}
	\GreyIf{\transparent{.4}{$\exists F \ldots$}} {
		\GreyElse{\transparent{.4}{ //  $\nexists v \in V(J): X \subset \bigcup(S_{uv} : uv \in E(J))$}}{
			\Assert{every choice of rungs has the same traversal. (Hard to assert)} 
			$ij \gets$ the traversal edge\;
			$A_1 \gets N_i \setminus S_{ij}$, $A_2 \gets N_j \setminus S_{ij}$\;
			\Assert{$X \cap (V(S,N) \setminus S_{ij}) = A_1 \cup A_2$}
			\If{$n = 1$} {
				$(S', N') \gets$ add $f_1$ to $N_i, N_j, S_{ij}$\;
				\Return \GrowJStrip($G, J, (S',N')$)\;
			}
			\Else {
				$x_1 :\in A_1, x_2 :\in A_2$, so that $x_1$ and $x_2$ are in disjoint strips\;
				\Assert{$x_1 - f_1 \xor x_1 - f_n$}
				\If{$x_1 - f_n$}{relabel $f_1 - \ldots - f_n$ front to back}
				$(S', N') \gets$ add $f_1$ to $N_i$, $f_n$ to $N_j$ and $F$ to $S_{ij}$\;
				\Return \GrowJStrip($G, J, (S',N')$)\;
			}
		}
	}
	\Else{
		\Return $J, (S, N)$ -- a maximal $J$-strip\;
	}
}

### 2020-05-20 paper/algVII.tex
ALG VII

@@
   \Indp	
+  $X \gets N(m)$\;
+  $M \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. $(S,N)$\;
+  $M^* \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. some choice of rungs\;
+  \Assert[SPGT 8.4]{$J = K_4$}
+  $V(J) \gets [4]$\;
+  $\forall_{i\neq j \in [4]}$: choose rungs $R_{ij}, R_{ij}$, forming line graphs $L(H)$ and $L(H')$ so that $X$ 
+  saturates $L(H)$ but does not saturate $L(H')$\;
+  \Assert{$R_{ij} \neq R'_{ij} \iff \{i, j\} = [2]$}
+  $r_{ij}, r_{ji} \gets$ ends of each $R_{ij}$\;
+  $r'_{ij}, r'_{ji} \gets$ ends of each $R'_{ij}$\;
+  $\forall_{i \in [4]} T_i \gets \{r_{ij}, j \in [4] \setminus \{i\} \}$\;
+  $\forall_{i \in [4]} T'_i \gets \{r'_{ij}, j \in [4] \setminus \{i\} \}$\;
+  \Assert{$X$ has at least two members in each $T_1, \ldots T_4$}
+  \Assert{There is $T'_i$ that contains at most one member of $X$}
+  \Assert{$T_3 = T'_3, T_4 = T'_4$}
+  relabel $G$ and $J$, so that $|X \cap T_1| = 2$ and $|X \cap T'_1| = 1$\;
+  \Assert{$r_{12} \in X, r'_{12} \notin X$}
+  \Assert{$r_{13} \in X \xor r_{14} \in X$}
+  relabel $G$ and $J$, so that $r_{13} \in X, r_{14} \notin X$\;
+  \Assert[6.3.(3)]{$R_{34}$ is even and $[X \cap V(L(H'))] \setminus V(R_{34}) = \{r_{31}, r_{32}, r_{41}, r_{42} \}$}
+  \Assert[6.3.(4)]{$R_{14}$ has odd length, $r_{21} \in X$}
+  \Assert[6.3.(5)]{$R_{12}$ has length $0$, every $12$-rung has even length}
+  \Assert[6.3.(6)]{$R_{24}$ has length $0$ and $R_{23}$ has odd length}
+  \Assert[6.3.(7)]{Every $34$-rung has non-zero even length}
+  $\forall_{i \neq j \in [4]} O_{ij} \gets$ set of vertices that are not major w.r.t $L(H')$ and
+  are complete to $(T'_i \cup T'_j) \setminus R'_{ij}$\;
+  \Assert{$r_{12} = r_{21} \in O_{12}$, $m \in O_{34}$}
+  \Assert{$O_{34} = M^* \setminus M$}
+  $(S', N') \gets$ strip system obtained from $(S, N)$ by replacing $S_{12}$ with $S_{12} \setminus O_{12}$\;
+  \If{$\exists_{rung R}: $ adding $R$ to $S'_{12}$ produces enlargement of $(S, N)$}{
+    \Return $(S'', N'')$ -- an enlargement of $(S, N)$\;
+  }
+  \Else{
+    \Return $(S', N')$ -- a special $K_4$ strip system\;
+  }
 \end{algorithm}

### 2020-07-22 paper/coloringAppendix/algIV.tex
First draft of paper skeleton

\begin{algorithm}
	\SetKwFunction{GoodPartitionEvenH}{\textsc{Good-Partition-From-Even-Hyperprism}}
	\Indm\nonl\GoodPartitionEvenH{$G, H, M$}\\
	\KwData{$G$ -- square-free, Berge graph containing no \LGBSK \newline
		$H = (A_1, \ldots, B_3)$  -- maximal even hyperprism in $G$ \newline
		$M$ -- set of major neighbors of $H$}
	\KwResult{A good partition of $G$}
	\Indp	
	$Z \gets \bigcup\{V(C)$ : $C$ is a component of $G \setminus \{V(H) \cup M \}$ with no attachments in $H \}$  \;

	relabel strips of $H$, so that $M \cup A_1$ and $M \cup B_1$ are cliques \;

	$F_1 \gets \bigcup\{ V(C)$ : $C$ is a component of $G \setminus \{H \cup M \cup Z \}$ that
	attaches to $A_1 \cup B_1 \cup C_1$  $\}$ \;

	% $F_A \gets \bigcup \{ V(C) $ : $C$ is a component of $G \setminus \{ H \cup M \cup Z \cup F_1 \cup F_2 \cup F_3 \}$
	% that attaches to $A_1 \cup A_2 \cup A_3$  $\}$ \;

	% $F_B \gets \bigcup \{ V(C) $ : $C$ is a component of $G \setminus \{ H \cup M \cup Z \cup F_1 \cup F_2 \cup F_3 \}$
	% that attaches to $B_1 \cup B_2 \cup B_3$  $\}$ \;

	% \Assert{$F_1, F_2, F_3, F_A, F_B$ are pairwise anticomplete}
	% \Assert{$V(G) = H \cup M \cup Z \cup F_1 \cup F_2 \cup F_3 \cup F_a \cup F_B$}
	\Assert{$M$ is a clique}
	\Assert{$M \cup A_i$ is a clique for at least two values of $i$}
	\Assert{$M \cup B_j$ is a clique for at least two values of $j$}

	$K_1 \gets A_1$, $K_2 \gets M$, $K_3 \gets B_1$ \;
	$R \gets C_1 \cup F_1 \cup Z $ \;
	$L \gets G \setminus \{K_1 \cup K_2 \cup K_3 \cup R\}$ \;
	\Return $(K_1, K_2, K_3, L, R)$\;
\end{algorithm}

### 2020-07-22 paper/coloringAppendix/algVIa.tex
First draft of paper skeleton

\subsubsection{Notes}
\begin{itemize}
	\item $T_{uv} := N_u \cap N_v$
	\item Strip $S_{uv}$ is \emph{rich} iff $S_{uv} \setminus T_{uv} \neq \emptyset$
\end{itemize}

\begin{algorithm}
	\SetKwFunction{GoodPartitionJStrip}{\textsc{Good-Partition-From-J-Strip-System}}
	\Indm\nonl\GoodPartitionJStrip{$G, J, (S, N), M$}\\
	\KwData{$G$ -- square-free, Berge graph \newline
		$J$ -- a maximal $3$-connected graph with appearance in $G$ \newline
		$(S, N)$ -- a maximal $J$-strip system \newline
		$M$ -- a set of major vertices w.r.t. $(S, N)$
	}
	\KwResult{A good partition of $G$}
	\Indp	
	$S^*_{uv} \gets S_{uv} \cup$ $($ components of $G\setminus V(S,N)$ that attach in $S_{uv}$ only $)$\;
	$T_{uv} \gets N_u \cap N_v$\;
	\Assert{$T_{uv} \setComplete N_u \setminus N_{uv}$, $T_{uv} \setComplete N_v \setminus N_{vu}$}
	\Assert{$M \cup T_{uv}$ is a clique}
	\If{$\exists S_{uv}$ -- a rich strip in $(S,N)$} {
		\If{$\exists S_{uv}$ -- a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ and $M \cup(N_v \setminus N_{vu})$ are cliques
			}{
			$K_1 \gets N_u \setminus N_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$L \gets (S^*_{uv} \setminus T_{uv}) \cup ($ components of $G\setminus V(S, N)$ that attach only to $N_u$
			and those that attach only to $N_v$ $)$\;
			$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
		\Else{
			$S_{uv} \gets$ a rich strip in $(S, N)$, such that
			$M \cup(N_u \setminus N_{uv})$ is not a clique and $M \cup(N_v \setminus N_{vu})$ is a clique \;
			$K_1 \gets N_{uv} \setminus T_{uv}$, $K_2 \gets M \cup T_{uv}$, $K_3 \gets N_v \setminus N_{vu}$\;
			$R \gets (S^*_{uv} \setminus N_u) \cup ($ components of $G\setminus V(S,U)$ that attach only to $N_v$ $)$\;
			$L \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup R)$\;
			\Return $(K_1, K_2, K_3, L, R)$\;
		}
	}
	\Else {
		\Assert{$\forall uv \in E(J): S_{uv} = T_{uv}, S_{uv}$ is a clique}
		$S_{uv} \gets $ any strip\;
		$K_1 \gets N_u \setminus S_{uv}$, $K_2 \gets M$, $K_3 \gets N_v \setminus S_{uv}$\;
    $L \gets S^*_{uv} \cup ($ components of $G\setminus V(S,N)$ that attach only to $N_u$ and only to $N_v$ $)$\;
		$R \gets G \setminus (K_1 \cup K_2 \cup K_3 \cup L)$\;
		\Return $(K_1, K_2, K_3, L, R)$\;
	}
\end{algorithm}

### 2020-07-22 paper/main.tex
ALG V
ALG VI
ALG VIa
ALG VII
First draft of paper skeleton

--- 2020-05-13 paper/main.tex
@@
-\input{preamble.tex}
+\documentclass{article}
+
+\usepackage{appendix}
 
@@
 \begin{document}
+\begin{titlepage}
+	\begin{center}
 
-\section{Notes}
-\begin{itemize}
-	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
-	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
-	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
-	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
-	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
-	\item $[n]$  -- $\{1, \ldots, n\}$.
-	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
-\end{itemize}
+		\large
+		\textbf{Jagiellonian University}\\
+		Department of Theoretical Computer Science\\
 
-\section{Algorithms}
-\begin{algorithm}
-	\SetKwFunction{colorGraph}{\textsc{Color-Graph}}
-\end{algorithm}
+		\vspace{1.5cm}
 
-\input{algII.tex}
+		\Large
+		\textbf{Adrian Siwiec}
 
-\input{algIV.tex}
+		\vspace*{2cm}
+
+		\textbf{\LARGE Perfect Graph Recognition and Coloring}
+
+		\vspace{0.5cm}
+		\large
+
+		\vfill
+		\Large
+		Master Thesis
+
+		\vfill
+		\Large
+		Supervisor: dr inż. Krzysztof Turowski
+
+		\vspace{0.8cm}
+
+		September 2020
+
+\end{center}
+\end{titlepage}
+
+\pagebreak
+
+\begin{abstract}
+TODO
+\end{abstract}
+
+\tableofcontents
+
+\pagebreak
+
+\section{Perfect Graphs}
+Definition of perfect graphs.\\
+
+Why are they interesting (Some examples of subclasses, and problems that are solvable for perfect graphs, including recognition and coloring).\\
+
+Weak perfect graph theorem.\\
+
+Berge graphs.
+
+\subsection{Strong Perfect Graph Theorem}
+Cite the paper, brief description of the theorem.
+
+\section{Recognizing Berge Graphs}
+Cite the paper.
+
+\subsection{Recognition algorithm Overview}
+Recognizing simple structures (Diamonds, Jewels, T1, T2, T3).\\
+
+Finding and Using Half-Cleaners.\\
+
+Overview of proof of why algorithm using Half-Cleaners is correct.\\
+
+\subsection{Implementation}
+
+Anything interesting about algo/data structure?\\
+
+Optimizations - Bottlenecks in performance (next path, are vectors distinct etc).\\
+
+Validity tests - unit tests, tests of bigger parts, testing vs known answer and vs naive.
+
+\subsection{Parallelism with CUDA (?)}
+
+TODO
+
+\subsection{Experiments}
+
+Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\
+
+Description of tests used.\\
+
+Results and Corollary - almost usable algorithm.
+
+\section{Coloring Berge Graphs}
+
+\subsection{Ellipsoid method}
+
+Desctiption.\\
+
+Implementation.\\
+
+Experiments and results.\\
+
+\subsection{Combinatorial Method}
+
+Cite the paper.\\
+
+On its complexity - point to appendix for pseudo-code.
+
+\appendix
+\appendixpage
+\addappheadtotoc
+
+\section{Perfect Graph Coloring algorithm}
+TODO
 

### 2020-07-22 paper/main.tex
Introduction first draft wip

@@
 \usepackage{appendix}
+\usepackage{todonotes}
+
+\usepackage[
+	style=alphabetic
+]{biblatex}
+\addbibresource{bbl.bib}
+
+\newcommand{\TODO}{\todo[inline]}
+\newcommand\Lovasz{Lovász }
+
+% Language and typesetting notes:
+%
+% - Color, not Colour (American English)
+% - Node not a Vertex of a graph
 
@@
 \section{Perfect Graphs}
-Definition of perfect graphs.\\
+All graphs in this paper are finite, undirected and have no loops or parallel edges.
+We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$.
+\emph{Coloring} of a graph means assigning every node of a graph a color.
+A coloring is \emph{valid} iff every two nodes sharing an edge have different colors.
+An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.
 
-Why are they interesting (Some examples of subclasses, and problems that are solvable for perfect graphs, including recognition and coloring).\\
+Given a graph $G = (V,E)$ and a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$.
+A graph $G = (V,E)$ is \emph{perfect} iff for all $X \subseteq V$ we have $\chi(G[X]) = \omega(G[X])$.
 
-Weak perfect graph theorem.\\
+\TODO{Give some examples why are these interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}
 
-Berge graphs.
+Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$.
+For example a clique in a graph becomes an independent set in its complement.
+A perfect graph theorem, first conjured by Berge in 1961 \cite{CB61} and then proven by \Lovasz in 1972 \cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
+\todo{Should we give some proof of that here?}
 
 \subsection{Strong Perfect Graph Theorem}
-Cite the paper, brief description of the theorem.
+A \emph{hole} is an induced chordless cycle of length at least 4.
+An \emph{antihole} is an induced subgraph whose complement is a hole.
+A \emph{Berge} graph is a graph with no holes or antiholes of odd length.
+
+In 1961 Berge conjured that a graph is perfect iff it is Berge in what has become known as a strong perfect graph conjecture.
+In 2001 Chudnovsky et al.
+have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
 
@@
 
+% \bibliographystyle{alpha}
+\printbibliography
+
 \end{document}

### 2020-07-22 paper/main.tex
Perfect graph introduction and initial description of pyramids

@@
 \usepackage{todonotes}
+\usepackage{wrapfig}
+
+\usepackage{tikz}
+\tikzset{%
+    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
+}
 
@@
 
-Given a graph $G = (V,E)$ and a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$.
-A graph $G = (V,E)$ is \emph{perfect} iff for all $X \subseteq V$ we have $\chi(G[X]) = \omega(G[X])$.
+Given a graph $G = (V,E)$, sometimes by $V(G)$ and $E(G)$ we will denote a set of nodes and edges of $G$.
+Given a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$.
+A graph $G$ is \emph{perfect} iff for all $X \subseteq V(G)$ we have $\chi(G[X]) = \omega(G[X])$.
 
@@
 A perfect graph theorem, first conjured by Berge in 1961 \cite{CB61} and then proven by \Lovasz in 1972 \cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
-\todo{Should we give some proof of that here?}
+\todo{Should we give some proof of that here?
+Maybe based on proof in \cite{GC03}}
 
-\subsection{Strong Perfect Graph Theorem}
 A \emph{hole} is an induced chordless cycle of length at least 4.
@@
 have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
+The following overview of the proof will be based on this paper and on an article withe the same name by Cornuéjols \cite{GC03}.
+
+\subsection{Strong Perfect Graph Theorem}
+
+Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2.
+It is easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
+It is therefore clear, that if a graph is not Berge it is not perfect.
+To prove that every Berge graph is perfect is the proper part of the strong perfect graph theorem.
+
+\TODO{How long and detailed overview of the proof should we provide?}
 
 \section{Recognizing Berge Graphs}
-Cite the paper.
+
+\TODO{Cite the paper and tell this is only a short overview}
 
 \subsection{Recognition algorithm Overview}
-Recognizing simple structures (Diamonds, Jewels, T1, T2, T3).\\
+
+\TODO{Main ideas of the algorithm.}
+\TODO{First we check all on $G$, then on $\overline{G}$}
+
+\subsubsection{Simple structures}
+
+A \emph{path} in $G$ is an induced subgraph that is connected, with at least one node, no cycle and no node of degree larger than 2 (sometimes called chordless path).
+The \emph{length} of a path or a cycle is the number of edges in it.
+\todo{Should we move these definitions elsewhere?} A \emph{triangle} in a graph is a set of three pairwise adjacent nodes.
+
+\begin{wrapfigure}{r}{0.35\textwidth}
+	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
+	\node(a) at (0,0) {a};
+	\node(b1) at (-2,-6) {$b_1$};
+	\node(b2) at (0,-4.268) {$b_2$};
+	\node(b3) at (2,-6) {$b_3$};
+
+	\node(P12) at (-2/4, -6/4) {\small$P_{12}$};
+	\node(P13) at (-4/4, -12/4) {\small$P_{13}$};
+	\node(P14) at (-6/4, -18/4) {\small$P_{14}$};
+
+	\node(P32) at (2/3, -6/3) {\small$P_{32}$};
+	\node(P33) at (4/3, -12/3) {\small$P_{33}$};
+
+	\draw (b1) to (b3);
+	\draw (b1) to (b2);
+	\draw (b2) to (b3);
+
+	\draw (a) to (P12);
+	\draw (P12) to (P13);
+	\draw (P13) to (P14);
+	\draw (P14) to (b1);
+
+	\draw (a) to (P32);
+	\draw (P32) to (P33);
+	\draw (P33) to (b3);
+
+	\draw (a) to (b2);
+\end{tikzpicture}
+\caption{An example of a pyramid.}
+\end{wrapfigure}
+
+A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another node $a$, so that:
+\begin{itemize}
+	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
+	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only node in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
+	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
+\end{itemize}
+
+It is easy to see that every graph containing a pyramid contains an odd hole.
+
+\TODO{On recognition of pyramids.}
+
+Recognizing simple structures (Pyramids, Jewels, T1, T2, T3).\\
 

### 2020-07-23 paper/main.tex
Add jewel picture

@@
 \usepackage{wrapfig}
+\usepackage{intcalc}
 
@@
 }
+\usetikzlibrary{snakes}
+\usetikzlibrary{shapes.geometric}
 
@@
 
+\paragraph{Editorial notes}
+By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
+\todo{Where should we put it?}
+
 \TODO{Give some examples why are these interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}
@@
 
+\paragraph{Pyramids}
+
 A \emph{path} in $G$ is an induced subgraph that is connected, with at least one node, no cycle and no node of degree larger than 2 (sometimes called chordless path).
@@
 
-\begin{wrapfigure}{r}{0.35\textwidth}
+\begin{wrapfigure}[12]{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
@@
 
-It is easy to see that every graph containing a pyramid contains an odd hole.
+It is easy to see that every graph containing a pyramid contains an odd hole -- at least two of the paths $P_1$, $P_2$, $P_3$ will have the same parity.
 
-\TODO{On recognition of pyramids.}
+\TODO{On recognition of pyramids. Lemma 2.1 from the paper.}
+
+\paragraph{Jewels}
+
+\begin{wrapfigure}[12]{r}{0.35\textwidth}
+	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
+	\def\ngon{5}
+	\node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
+	\foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
+	%p1 - v5, p2 - v1 ...
+	\draw (p1) to (p2);
+	\draw (p2) to (p3);
+	\draw (p3) to (p4);
+	\draw (p4) to (p5);
+	\draw (p1) to (p5);
+
+  \draw[dashed] (p2) to (p5);
+  \draw[dashed] (p2) to (p4);
+	\draw[dashed] (p3) to (p5);
+
+	\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
+                       post length=0mm,pre length=0mm}}
+	\draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
+	\node[draw=none] at (0, -4.7) {$P$};
+\end{tikzpicture}
+\caption{An example of a jewel.}
+\end{wrapfigure}
+
+Five nodes $v_1, \ldots, v_5$ and a path $P$ is a \emph{jewel} iff:
+
+\begin{itemize}
+	\item $v_1, \ldots, v_5$ are distinct nodes.
+	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
+	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
+	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
+\end{itemize}
 

### 2020-07-23 paper/main.tex
Finding jewels, t1 and t2 wip

@@
 \newcommand\Lovasz{Lovász }
+\newcommand\T{\mathcal{T}}
 
@@
 \paragraph{Editorial notes}
-By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
+\begin{itemize}
+	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
 	\todo{Where should we put it?}
+	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
+	\item Given a path $P$, by $P^*$ we will denote its inside.
+\end{itemize}
 
@@
 
-\begin{wrapfigure}[12]{r}{0.35\textwidth}
+\begin{wrapfigure}[7]{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
@@
 
-Recognizing simple structures (Pyramids, Jewels, T1, T2, T3).\\
+Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required.
+This gives us a time of $O(|V|^7)$.
+We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we used this simple algorithm.
+
+\paragraph{Configurations of type $\T_1$}
+
+A configuration of type $\T_1$ is a hole of length 5.
+To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth node to complete the hole.
+See paragraph \ref{Optimizations} for more implementation details.
+
+\paragraph{Configurations of type $\T_2$} A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
+\begin{itemize}
+	\item $v_1v_2v_3v_4$ is a path in $G$.
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete nodes.
+	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
+\end{itemize}
+
+Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete nodes and its anticomponents.
+Then, for each anticomponent $X$ we check if required path $P$ exists.
 
@@
 
-Optimizations - Bottlenecks in performance (next path, are vectors distinct etc).\\
+\subsubsection{Optimizations}\label{Optimizations}
+Bottlenecks in performance (next path, are vectors distinct etc).\\
+\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
+\TODO{We used callgrind to get idea of methods crucial for time.}
+\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
+\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
+\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth node to complete the hole - much faster than iterating nodes.}
 

### 2020-07-23 paper/main.tex
T2 proof

@@
 \usepackage{intcalc}
+\usepackage{amsthm}
+\usepackage{cleveref}
 
@@
 \usetikzlibrary{shapes.geometric}
+\usetikzlibrary{positioning, fit, calc}
 
@@
 
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}{Corollary}[theorem]
+\newtheorem{lemma}[theorem]{Lemma}
+
 \newcommand{\TODO}{\todo[inline]}
@@
 \newcommand\T{\mathcal{T}}
+\crefname{lemma}{Lemma}{Lemmas}
 
@@
 
-\paragraph{Configurations of type $\T_2$} A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
+\paragraph{Configurations of type $\T_2$}
+
+\begin{wrapfigure}[15]{r}{0.35\textwidth}
+	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
+		\node(v1) at (0,0) {$v_1$};
+		\node(v2) at (1.5,0) {$v_2$};
+		\node(v3) at (3,0) {$v_3$};
+		\node(v4) at (4.5,0) {$v_4$};
+
+		\draw (v1) to (v2);
+		\draw (v2) to (v3);
+		\draw (v3) to (v4);
+
+		\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
+                       post length=0mm,pre length=0mm}}
+		\draw[decorate] (v1) to [out=90, in=180] (4.5/2, 3) to [out=0, in=90] (v4);
+		\node[draw=none] at (4.5/2, 3.5) {$P$};
+
+		\draw[dashed] (v2) to (.7,2.5);
+		\draw[dashed] (v3) to (.7,2.5);
+		\draw[dashed] (v2) to (3.8,2.5);
+		\draw[dashed] (v3) to (3.8,2.5);
+
+		\node[minimum size=4mm](x1) at (1.2, -2){};
+		\node[minimum size=4mm](x2) at (3.3, -2){};
+		\node[draw,dotted,inner sep=3pt, circle,yscale=.5, fit={(x1) (x2)},label=below:{$X$}] {};
+
+		\draw[dashed] (x1) to (x2);
+		\draw(v1) to (x1);
+		\draw(v2) to (x1);
+		\draw(v4) to (x1);
+		\draw(v1) to (x2);
+		\draw(v2) to (x2);
+		\draw(v4) to (x2);
+
+		% \draw (a) to (b2);
+\end{tikzpicture}
+\caption{An example of a $\T_2$.}
+\end{wrapfigure}
+
+A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
 \begin{itemize}
@@
 Then, for each anticomponent $X$ we check if required path $P$ exists.
+
+To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the Roussel-Rubio lemma \cite{RR01} as stated in \cite{MC05} that says:
+
+\begin{lemma}[Roussel-Rubio Lemma]\label{Roussel-Rubio}
+	Let $G$ be Berge, $X$ be an anticonnected subset of $V(G)$, $P$ be an odd path $p_1\ldots p_n$ in $G\setminus X$ with length at least 3, such that $p_1$ and $p_n$ are $X$-complete and $p_2, \ldots, p_{n-1}$ are not.
+Then:
+	\begin{itemize}
+		\item $P$ is of length at least 5 and there exist nonadjacent $x, y \in X$, such that there are exactly two edges between $x, y$ and $P^*$, namely $xp_2$ and $yp_{n-1}$,
+		\item or $P$ is of length 3 and there is an odd antipath joining internal nodes of $P$ with interior in $X$.
+	\end{itemize}
+\end{lemma}
+
+Now, we shall prove the following:
+
+\begin{lemma}
+	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
+\end{lemma}
+\begin{proof}
+	Let $(v_1, v_2, v_3, v_4, P, X)$ be a configuration of type $\T_2$. Let us assume that $G$ is not Berge and consider the following:
+	\begin{itemize}
+		\item If $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
+		\item If $P$ is of length 3.
+\todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its nodes $v_1, p_2, p_3, v_4$.
+It follows from \cref{Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
+We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
+		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
+This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
+	\end{itemize} 
+\end{proof}
 
@@
 
-Desctiption.\\
+Description.\\
 

### 2020-07-27 paper/main.tex
T3

@@
 
+\paragraph{Configurations of type $\T_3$}
+
+A configuration of type $\T_3$ is a sequence $v_1, \ldots, v_6$, $P$, $X$, such that:
+\begin{itemize}
+	\item $v_1, \ldots v_6$ are distinct nodes.
+	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges.
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete nodes, and $v_3$, $v_4$ are not $X$-complete.
+	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no node in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
+	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
+\end{itemize}
+
+\TODO{image?}
+
+The following algorithm with running time of $O(|V(G)|^6)$ checks whether $G$ contains a configuration of type $T_3$:
+
+For each triple $v_1, v_2, v_5$ of nodes such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete nodes.
+For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no node of $F'\setminus\{v_5\}$ is $X$-complete.
+Let $F$ be the union of $F'$ and the set of all $X$-complete nodes that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.
+
+Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a node $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$.
+If there is such a node $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$.
+If we exhaust our search and find none, report that graph does not contain it.
+
+To see that the algorithm below has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
+This gives us the total running time of $O(|V(G)|^6)$.
+
+We will skip the proof that each graph containing $\T_3$ is not Berge. \todo{Should we include it?} See \cite{MC05} for the proof.
+
 Finding and Using Half-Cleaners.\\

### 2020-08-03 paper/main.tex

@@
 
+\subsubsection{Amenable holes.}
+
+For a shortest odd hole $C$ in $G$, we will call a node $v \in V(G) \setminus V(C)$ $C$-\emph{major} iff the set of its neighbors in C is not contained in any 3-node path of $C$.
+An odd hole $C$ will be called \emph{clean} if no vertex is $C$-major.
+
+A hole $C$ of $G$ is \emph{amenable} iff C is a shortest odd hole in $G$ of length at least 7, and for every anticonnected set $X$ of $C$-major nodes, there is an $X$-complete edge in $C$ (an edge is $X$-complete iff both its ends are $X$-complete).
+
+The rest of the algorithm rests upon the following theorem:
+
+\begin{theorem}
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
+	\TODO{Any ideas on what else to say here? List all 9 steps?}
+\end{theorem}
+
+For a shortest odd hole $C$ in $G$, a subset $X$ of $V(G)$ is a \emph{near-cleaner for $C$} iff $X$ contains all $C$-major nodes and $X \cap V(C)$ is a subset of node set of some 3-node path of $C$.
+
 Finding and Using Half-Cleaners.\\

### 2020-08-03 code/src/nearCleaners.cpp
Tests update

@@ -33,18 +33,18 @@ bool containsOddHoleWithNearCleanerX(const Graph &G, const set<int> &sX) {
       if ((R[x3][y1].size() < n) || (R[x3][y2].size() < n)) continue;
 
       //TODO(Adrian) remove, use some code coverage tool instead
-      cout << "Interesting odd hole: " << endl;
-      cout << "sX: " << sX << endl;
-      cout << "x1: " << x1 << endl;
-      cout << "x2: " << x2 << endl;
-      cout << "x3: " << x3 << endl;
-      cout << "y1: " << y1 << endl;
-      cout << "y2: " << y2 << endl;
-      cout << "R(x1, y1): " << R[x1][y1] << endl;
-      cout << "R(x2, y1): " << R[x2][y1] << endl;
-      cout << "R(x3, y1): " << R[x3][y1] << endl;
-      cout << "R(x3, y2): " << R[x3][y2] << endl;
-      cout << G << endl;
+      // cout << "Interesting odd hole: " << endl;
+      // cout << "sX: " << sX << endl;
+      // cout << "x1: " << x1 << endl;
+      // cout << "x2: " << x2 << endl;
+      // cout << "x3: " << x3 << endl;
+      // cout << "y1: " << y1 << endl;
+      // cout << "y2: " << y2 << endl;
+      // cout << "R(x1, y1): " << R[x1][y1] << endl;
+      // cout << "R(x2, y1): " << R[x2][y1] << endl;
+      // cout << "R(x3, y1): " << R[x3][y1] << endl;
+      // cout << "R(x3, y2): " << R[x3][y2] << endl;
+      // cout << G << endl;
 
       return true;
     }

### 2020-08-03 code/src/testCommons.cpp

@@ -35,8 +35,6 @@ void printGraph(const Graph &G) {
 }
 
 Graph getRandomGraph(int size, double p) {
-  cout << "Distribution: " << p << endl;
-
   vec<vec<int>> neighbours(size);
   for (int i = 0; i < size; i++) {
     for (int j = i + 1; j < size; j++) {

### 2020-08-03 code/test/perfTest/run.sh

@@ -13,19 +13,37 @@ perfectTests=(
 )
 
 naiveTests=(
-  "small.t.in"
+  "naive.t.in"
+)
+
+perfectTestsValgrind=(
+  "perfVal.t.in"
+)
+
+naiveTestsValgrind=(
+  "smallVal.t.in"
 )
 
 for file in "${perfectTests[@]}"; do
+  echo "Running Perfect on $file"
+  $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out
+done
+
+for file in "${naiveTests[@]}"; do
+  echo "Running Naive on $file"
+  $naiveExec <$testsDir/$file >$resultsDir/$file.naive.out
+done
+
+for file in "${perfectTestsValgrind[@]}"; do
   echo "Profiling Perfect on $file"
-  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out
+  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $perfectExec <$testsDir/$file >$resultsDir/$file.Valgrind.perfect.out
   gprof2dot -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.perfect.dot
   rm $resultsDir/callgrind.tmp.out
 done
 
-for file in "${naiveTests[@]}"; do
+for file in "${naiveTestsValgrind[@]}"; do
   echo "Profiling Naive on $file"
-  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $naiveExec <$testsDir/$file >$resultsDir/$file.naive.out
+  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $naiveExec <$testsDir/$file >$resultsDir/$file.Valgrind.naive.out
   gprof2dot -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.naive.dot
   rm $resultsDir/callgrind.tmp.out
 done

### 2020-08-03 code/inc/cuCommons.h
First lines CUDA

@@ -1,0 +1,17 @@
+#include "commons.h"
+
+#include <moderngpu/context.hxx>
+#include <moderngpu/kernel_scan.hxx>
+#include <moderngpu/memory.hxx>
+using namespace mgpu;
+
+#define CUCHECK(x) CudaAssert(x, #x, __FILE__, __LINE__)
+
+struct CuGraph {
+  int n;
+  context_t &context;
+
+  int *devMatrix;
+
+  CuGraph(const Graph &G, context_t &context);
+}

### 2020-08-03 code/src/commons.cpp

@@ -404,7 +404,7 @@ vec<vec<int>> generateTuples(int size, int max) {
 }
 
 ostream &operator<<(ostream &os, Graph const &G) {
-  cout<<G.n<<endl;
+  cout << G.n << endl;
   for (int i = 0; i < G.n; i++) {
     for (int j = 0; j < G.n; j++) {
       if (G.areNeighbours(i, j))
@@ -585,7 +585,6 @@ void nextPathInPlaceInternal(const Graph &G, vec<int> &v, int len, bool isCycleO
 }
 
 void nextPathInPlace(const Graph &G, vec<int> &v, int len, bool isCycleOk, bool areChordsOk) {
-  // TODO(Adrian) faster, do not iterate over all permutations. Have a "pointer" to next neighbour in G?
   if (len <= 1) {
     throw invalid_argument("Length of next path must be at least 2");
   }

### 2020-08-03 code/src/cuCommons.cu

@@ -1,0 +1,4 @@
+#include "commons.h"
+#include "cuCommons.h"
+
+CuGraph::CuGraph(cddonst Graph &G, context_t &context) { n = G.n; }

### 2020-08-03 code/test/unitTest/cuCommons.cu

@@ -1,0 +1,12 @@
+#include "commons.h"
+#include "cuCommons.h"
+#include "testCommons.h"
+
+void testCuGraph() {
+  assert(false);
+}
+
+int main() {
+  init();
+  testCuGraph();
+}

### 2020-08-03 code/inc/colorTestCommons.h
CuGraph first draft and test

@@ -1,0 +1,6 @@
+#include "commons.h"
+
+void testColorWithStats(const Graph &G);
+void printStatsColor();
+
+bool isColoringValid(const Graph &G, const vec<int> &coloring);

### 2020-08-03 code/inc/commons.h

@@ -71,6 +71,8 @@ struct Graph {
   Graph getShuffled() const;
   Graph getLineGraph() const;
 
+  friend class CuGraph;
+
  private:
   vec<vec<int>> _neighbours;
   vec<vec<int>> _matrix;
@@ -118,8 +120,9 @@ vec<int> getCompleteVertices(const Graph &G, const vec<int> &X);
 
 // Runs dfs on a Graph G, with visited as an input-output of visited vertices. In addition action(v) will be
 // performed on each visited vertex. Each visited vertex (except start) must satisfy test predicate.
-void dfsWith(const Graph &G, vec<int> &visited, int start, function<void(int)> action,
-             function<bool(int)> test = [](int v) -> bool { return true; });
+void dfsWith(
+    const Graph &G, vec<int> &visited, int start, function<void(int)> action,
+    function<bool(int)> test = [](int v) -> bool { return true; });
 
 // Returns a vector of all components of G.
 vec<vec<int>> getComponents(const Graph &G);

### 2020-08-03 code/inc/cuCommons.h

@@ -1,11 +1,17 @@
-#include "commons.h"
+#pragma once
 
 #include <moderngpu/context.hxx>
 #include <moderngpu/kernel_scan.hxx>
 #include <moderngpu/memory.hxx>
-using namespace mgpu;
 
+#include "commons.h"
+using namespace mgpu;
+using namespace std;
+
+void CudaAssert(cudaError_t error, const char *code, const char *file, int line);
 #define CUCHECK(x) CudaAssert(x, #x, __FILE__, __LINE__)
+
+void printArray(int *dev, int n, context_t &context);
 
 struct CuGraph {
   int n;
@@ -14,4 +20,4 @@ struct CuGraph {
   int *devMatrix;
 
   CuGraph(const Graph &G, context_t &context);
-}
+};

### 2020-08-03 code/inc/nearCleaners.h

@@ -8,6 +8,8 @@
 // G should contain no pyramid or jewel.
 bool containsOddHoleWithNearCleanerX(const Graph &G, const set<int> &sX);
 
+bool cudaContainsOddHoleWithNearCleaners(const Graph &G, const set<set<int>> &Xs);
+
 bool isRelevantTriple(const Graph &G, vec<int> v);
 
 // Returns X(a, b, c) for v=[a, b, c].

### 2020-08-03 code/inc/testCommons.h

@@ -51,9 +51,6 @@ struct RaiiTimer {
 bool testWithStats(const Graph &G, bool naive);
 void printStats();
 
-void testColorWithStats(const Graph &G);
-void printStatsColor();
-
 double getDistr();
 void testGraph(const Graph &G, bool verbose);
 void testGraph(const Graph &G, bool result, bool verbose);
@@ -73,5 +70,3 @@ struct RaiiProgressBar {
 
   int getFilled(int testsDone);
 };
-
-bool isColoringValid(const Graph &G, const vec<int> &coloring);

### 2020-08-03 code/src/color.cpp

@@ -8,6 +8,7 @@ extern "C" {
 #include "theta.h"
 }
 
+
 tuple<int, int, vec<int>, vec<int>> getGraphEdges(const Graph &G, const vec<int> &isNodeRemoved) {
   vec<int> nodeStays(isNodeRemoved.size());
   for (int i = 0; i < isNodeRemoved.size(); i++) {

### 2020-08-03 code/src/colorTestCommons.cpp

@@ -1,0 +1,62 @@
+#include "colorTestCommons.h"
+
+#include <chrono>
+#include <iostream>
+
+#include "color.h"
+#include "commons.h"
+#include "testCommons.h"
+
+using namespace std::chrono;
+using std::default_random_engine;
+using std::flush;
+using std::make_pair;
+using std::normal_distribution;
+
+map<int, double> sumTimeColor;
+map<int, double> sumClockTimeColor;
+map<int, int> casesTestedColor;
+
+void testColorWithStats(const Graph &G) {
+  nanoseconds start_ns = duration_cast<nanoseconds>(system_clock::now().time_since_epoch());
+  clock_t start_clock = clock();
+
+  auto c = color(G);
+
+  nanoseconds end_ns = duration_cast<nanoseconds>(system_clock::now().time_since_epoch());
+  clock_t end_clock = clock();
+
+  double duration = (end_ns.count() - start_ns.count()) / 1e9;
+  double clock_duration = (end_clock - start_clock) / static_cast<double>(CLOCKS_PER_SEC);
+
+  assert(isColoringValid(G, c));
+
+  sumTimeColor[G.n] += duration;
+  sumClockTimeColor[G.n] += clock_duration;
+  casesTestedColor[G.n]++;
+}
+void printStatsColor() {
+  cout << "Color stats: " << endl;
+  for (auto it = sumTimeColor.begin(); it != sumTimeColor.end(); it++) {
+    int cases = casesTestedColor[it->first];
+    cout << "\tn=" << it->first << ", cases=" << cases << ", avgTime=" << it->second / cases
+         << ", parallel factor=" << sumClockTimeColor[it->first] / it->second << endl;
+  }
+}
+
+bool isColoringValid(const Graph &G, const vec<int> &coloring) {
+  if (coloring.size() != G.n) return false;
+
+  int omegaG = getOmega(G);
+  for (int c : coloring) {
+    if (c < 0 || c >= omegaG) return false;
+  }
+
+  for (int i = 0; i < G.n; i++) {
+    for (int j : G[i]) {
+      if (coloring[i] == coloring[j]) return false;
+    }
+  }
+
+  return true;
+}

### 2020-08-03 code/src/cuCommons.cu

@@ -1,4 +1,28 @@
 #include "commons.h"
 #include "cuCommons.h"
 
-CuGraph::CuGraph(cddonst Graph &G, context_t &context) { n = G.n; }
+void CudaAssert(cudaError_t error, const char *code, const char *file, int line) {
+  if (error != cudaSuccess) {
+    cerr << "Cuda error :" << code << ", " << file << ":" << error << endl;
+    exit(1);
+  }
+}
+
+void printArray(int *dev, int n, context_t &context) {
+  transform(
+      [=] MGPU_DEVICE(int i) {
+        for (int a = 0; a < n; a++) {
+          printf("%d", dev[a]);
+        }
+        printf("\n");
+      },
+      1, context);
+  context.synchronize();
+}
+
+CuGraph::CuGraph(const Graph &G, context_t &context) : n(G.n), context(context) {
+  CUCHECK(cudaMalloc((void **)&devMatrix, sizeof(int) * n * n));
+  for (int i = 0; i < n; i++) {
+    CUCHECK(cudaMemcpy(devMatrix + (i * n), G._matrix[i].data(), sizeof(int) * n, cudaMemcpyHostToDevice));
+  }
+}

### 2020-08-03 code/src/nearCleaners.cu

@@ -1,6 +1,19 @@
-#include "nearCleaners.h"
+
+#include <curand_kernel.h>
+
+#include <moderngpu/context.hxx>
+#include <moderngpu/kernel_compact.hxx>
+#include <moderngpu/kernel_mergesort.hxx>
+#include <moderngpu/kernel_reduce.hxx>
+#include <moderngpu/kernel_scan.hxx>
+#include <moderngpu/kernel_segreduce.hxx>
+#include <moderngpu/memory.hxx>
+#include <moderngpu/transform.hxx>
 #include <set>
+
 #include "commons.h"
+#include "nearCleaners.h"
+using namespace mgpu;
 
 bool containsOddHoleWithNearCleanerX(const Graph &G, const set<int> &sX) {
   auto R = allShortestPathsWithPredicate(G, [&](int v) -> bool { return sX.count(v) == 0; });
@@ -32,7 +45,7 @@ bool containsOddHoleWithNearCleanerX(const Graph &G, const set<int> &sX) {
 
       if ((R[x3][y1].size() < n) || (R[x3][y2].size() < n)) continue;
 
-      //TODO(Adrian) remove, use some code coverage tool instead
+      // TODO(Adrian) remove, use some code coverage tool instead
       // cout << "Interesting odd hole: " << endl;
       // cout << "sX: " << sX << endl;
       // cout << "x1: " << x1 << endl;
@@ -49,6 +62,13 @@ bool containsOddHoleWithNearCleanerX(const Graph &G, const set<int> &sX) {
       return true;
     }
   }
+
+  return false;
+}
+
+bool cudaContainsOddHoleWithNearCleaners(const Graph &G, const set<set<int>> &Xs) {
+  mgpu::standard_context_t context(0);
+
 
   return false;
 }

### 2020-08-03 code/src/testCommons.cpp

@@ -1,7 +1,9 @@
 #include "testCommons.h"
+
 #include <chrono>
 #include <cstdlib>
 #include <iostream>
+
 #include "color.h"
 #include "commons.h"
 #include "oddHoles.h"
@@ -253,38 +255,6 @@ void testGraph(const Graph &G, bool result, bool verbose) {
   assert(perfect == result);
 }
 
-map<int, double> sumTimeColor;
-map<int, double> sumClockTimeColor;
-map<int, int> casesTestedColor;
-
-void testColorWithStats(const Graph &G) {
-  nanoseconds start_ns = duration_cast<nanoseconds>(system_clock::now().time_since_epoch());
-  clock_t start_clock = clock();
-
-  auto c = color(G);
-
-  nanoseconds end_ns = duration_cast<nanoseconds>(system_clock::now().time_since_epoch());
-  clock_t end_clock = clock();
-
-  double duration = (end_ns.count() - start_ns.count()) / 1e9;
-  double clock_duration = (end_clock - start_clock) / static_cast<double>(CLOCKS_PER_SEC);
-
-  assert(isColoringValid(G, c));
-
-  sumTimeColor[G.n] += duration;
-  sumClockTimeColor[G.n] += clock_duration;
-  casesTestedColor[G.n]++;
-}
-
-void printStatsColor() {
-  cout << "Color stats: " << endl;
-  for (auto it = sumTimeColor.begin(); it != sumTimeColor.end(); it++) {
-    int cases = casesTestedColor[it->first];
-    cout << "\tn=" << it->first << ", cases=" << cases << ", avgTime=" << it->second / cases
-         << ", parallel factor=" << sumClockTimeColor[it->first] / it->second << endl;
-  }
-}
-
 void printTimeHumanReadable(int64_t time) {
   double s = time / static_cast<double>(CLOCKS_PER_SEC);
   int h = s / (60 * 60);
@@ -331,21 +301,4 @@ void RaiiProgressBar::update(int testsDone) {
     }
     cout << "\r" << flush;
   }
-}
-
-bool isColoringValid(const Graph &G, const vec<int> &coloring) {
-  if (coloring.size() != G.n) return false;
-
-  int omegaG = getOmega(G);
-  for (int c : coloring) {
-    if (c < 0 || c >= omegaG) return false;
-  }
-
-  for (int i = 0; i < G.n; i++) {
-    for (int j : G[i]) {
-      if (coloring[i] == coloring[j]) return false;
-    }
-  }
-
-  return true;
 }

### 2020-08-03 code/test/perfTest/run.sh

@@ -37,13 +37,13 @@ done
 for file in "${perfectTestsValgrind[@]}"; do
   echo "Profiling Perfect on $file"
   valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $perfectExec <$testsDir/$file >$resultsDir/$file.Valgrind.perfect.out
-  gprof2dot -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.perfect.dot
+  python3 $scriptDir/gprof2dot.py -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.perfect.dot
   rm $resultsDir/callgrind.tmp.out
 done
 
 for file in "${naiveTestsValgrind[@]}"; do
   echo "Profiling Naive on $file"
   valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $naiveExec <$testsDir/$file >$resultsDir/$file.Valgrind.naive.out
-  gprof2dot -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.naive.dot
+  python3 $scriptDir/gprof2dot.py -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.naive.dot
   rm $resultsDir/callgrind.tmp.out
 done

### 2020-08-03 code/test/unitTest/color.cpp

@@ -1,4 +1,6 @@
 #include "color.h"
+
+#include "colorTestCommons.h"
 #include "commons.h"
 #include "perfect.h"
 #include "testCommons.h"

### 2020-08-03 code/test/unitTest/cuCommons.cu

@@ -2,11 +2,41 @@
 #include "cuCommons.h"
 #include "testCommons.h"
 
-void testCuGraph() {
-  assert(false);
+void testCuGraph(context_t &context) {
+  Graph G = getRandomGraph(10, 0.5);
+
+  CuGraph CG(G, context);
+  assert(CG.n == 10);
+
+  int *matrix = new int[G.n * G.n];
+  for (int i = 0; i < G.n; i++) {
+    for (int j = 0; j < G.n; j++) {
+      matrix[i * G.n + j] = G.areNeighbours(i, j);
+    }
+  }
+  int *copiedToDevMatrix;
+  CUCHECK(cudaMalloc((void **)&copiedToDevMatrix, sizeof(int) * G.n * G.n));
+  CUCHECK(cudaMemcpy(copiedToDevMatrix, matrix, sizeof(int) * G.n * G.n, cudaMemcpyHostToDevice));
+
+  printArray(copiedToDevMatrix, CG.n * CG.n, context);
+  printArray(CG.devMatrix, CG.n * CG.n, context);
+
+  transform(
+      [=] MGPU_DEVICE(int i) {
+        assert(CG.n == 10);
+
+        for (int i = 0; i < CG.n; i++) {
+          for (int j = 0; j < CG.n; j++) {
+            assert(CG.devMatrix[i * CG.n + j] == copiedToDevMatrix[i * CG.n + j]);
+          }
+        }
+      },
+      1, context);
+  context.synchronize();
 }
 
 int main() {
   init();
-  testCuGraph();
+  standard_context_t context(0);
+  testCuGraph(context);
 }

### 2020-08-03 code/test/unitTest/perfect.cpp

@@ -1,5 +1,7 @@
 #include "perfect.h"
+
 #include <random>
+
 #include "commons.h"
 #include "ctime"
 #include "oddHoles.h"

### 2020-08-03 code/test/unitTest/testCommons.cpp

@@ -47,26 +47,9 @@ void testTuples() {
   assert(generateTuples(4, 3).size() == 3 * 3 * 3 * 3);
 }
 
-void testIsColoringValid() {
-  Graph G(5,
-          "\
-  .XX..\
-  X.X..\
-  XX.XX\
-  ..X.X\
-  ..XX.\
-  ");
-
-  assert(isColoringValid(G, {2, 1, 0, 2, 1}));
-  assert(!isColoringValid(G, {2, 1, 0, 2}));
-  assert(!isColoringValid(G, {2, 1, 0, 2, 3}));
-  assert(!isColoringValid(G, {1, 1, 0, 2, 3}));
-}
-
 int main() {
   init();
   testRandomGraphs();
   testGetRandomPerfect();
   testTuples();
-  testIsColoringValid();
 }

### 2020-08-08 paper/main.tex
Minor style fixes

@@
 \usepackage[
-	style=alphabetic
+	style=numeric
 ]{biblatex}
@@
 
-\paragraph{Editorial notes}
+\paragraph{Definitions and conventions}
+	\todo{Where should we put it? Should we put all definitions here, or leave them in text?}
 \begin{itemize}
 	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
-	\todo{Where should we put it?}
 	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
@@
 
-\TODO{Give some examples why are these interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}
+\TODO{Give some examples why perfect graphs are interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}
 
@@
 For example a clique in a graph becomes an independent set in its complement.
-A perfect graph theorem, first conjured by Berge in 1961 \cite{CB61} and then proven by \Lovasz in 1972 \cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
+A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
 \todo{Should we give some proof of that here?
@@
 Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2.
-It is easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
+It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
 It is therefore clear, that if a graph is not Berge it is not perfect.
@@
 
-\TODO{Cite the paper and tell this is only a short overview}
+The following is based on the paper by Maria Chudnovsky et al. \citetitle*[]{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
 
@@
 
-\TODO{Main ideas of the algorithm.}
-\TODO{First we check all on $G$, then on $\overline{G}$}
+Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple structures as a induced subgraph (\ref{SimpleStructures}).
+If they do, we output that graph is not Berge and stop.
+Else, we check if there is a near-cleaner for a shortest odd hole.(\ref{AmenableHoles}).
 
 \subsubsection{Simple structures}
+\label{SimpleStructures}
 
@@
 This gives us a time of $O(|V|^7)$.
-We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we used this simple algorithm.
+We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
 
@@
 
-\TODO{image?}
+\TODO{picture?}
 
@@
 \subsubsection{Amenable holes.}
+\label{AmenableHoles}
 
@@
 
-Finding and Using Half-Cleaners.\\
+\TODO{Finding and Using Half-Cleaners.}
 
-Overview of proof of why algorithm using Half-Cleaners is correct.\\
+\TODO{Overview of proof of why algorithm using Half-Cleaners is correct.}
 

### 2020-08-10 paper/main.tex
Pyramids

@@
 
-\begin{wrapfigure}[12]{r}{0.35\textwidth}
+\begin{wrapfigure}[14]{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
@@
 
+We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is determined by its paths $P_1$, $P_2$, $P_3$.
+
 It is easy to see that every graph containing a pyramid contains an odd hole -- at least two of the paths $P_1$, $P_2$, $P_3$ will have the same parity.
 
-\TODO{On recognition of pyramids. Lemma 2.1 from the paper.}
+We will give an algorithm finding pyramid, but first we need some additional definitions. If $K$ is a pyramid $(a, b_1, b_2, b_3, P_1, P_2, P_3)$ we say its \emph{frame} is the 10-tuple iff
+\TODO{finish it up}
+
+\subparagraph{Finding Pyramids}
+
+First, let us enumerate all 6-tuples $b_1, b_2, b_3, s_1, s_2, s_3$ such that:
+\begin{itemize}
+	\item $\{b_1, b_2, b_3\}$ is a triangle
+	\item for $1 \leq i < j \leq 3$, ${b_i, s_i}$ is disjoint from ${b_j, s_j}$ and $b_ib_j$ is the only edge between them
+	\item there is a node $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
+\end{itemize}
+
+There are $O(|V(G)|^6)$ sextuples, and it takes $O(|V(G)|)$ time to check each one. For each such sextuple we follow with the rest of the algorithm.
+
+We define $M = V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$.
+Now, for each $m \in M$, we set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
+We set $S_2$ and $S_3$ similarly.
+Then similarly we set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
+We do similar for $T_2$ and $T_3$.
+It takes $O(|V(G)|^2)$ time to calculate paths $T_i(m)$ for all $i$ and $m$.
+
+Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ and paths $P_2(m)$, $P_3(m)$ will be defined in a similar manner.
+
+If $s_1 = b_1$ let $P_1(b_1)$ be the one-node path with node $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.
+
+If $s_1 \neq b_1$, then $P_1(b_1)$ is undefined and for all $m \in M$ we will check if all the following are true:
+\begin{itemize}
+	\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
+	\item $S_1(m)$ and $T_1(m)$ both exist
+	\item $V(S_1(m) \cap T_1(m)) = \{m\}$
+	\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
+\end{itemize}
+If so, then we assign a path $s_1-S_1(m)-m-T_1(m)-b_1$ to $P_1(m)$, otherwise we let $P_1(m)$ be undefined.
+It takes $O(|V(G)|^2)$ to check this, given $m$.
+We assign $P_2$ and $P_3$ in a similar manner.
+Total time of finding all $P_i(m)$ paths for a given sextuple is $O(|V(G)|^3)$.
+
+Now we want to check if there is a triple $m_1, m_2, m_3$, so that $P_1(m_1)$, $P_2(m_2)$, $P_3(m_3)$ form a pyramid.
+A most obvious approach of enumerating them all would be too slow, so we do it carefully.
+
+For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$, $P_j(m_j)$ both exist and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
+
+We show how to find the list of all good $(1, 2)$-pairs, with similar algorithm for all other good $(i, j)$-pairs.
+For each $m_1 \in M \cup \{b_1\}$, we find the set of all $m_2$ such that $(m_1, m_2)$ is a good $(1,2)$-pair as follows.
+
+If $P_1(m_1)$ does not exist, there are no such good pairs.
+If it exists, color black the nodes of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$.
+Color all other nodes white.
+(We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black nodes.
+We do this for all $m_1$ and get a set of all $(1,2)$-good pairs.
+In similar way we calculate all good $(1,3)$-pair and $(2,3)$-pairs (in $O(|V(G)|^3)$ time).
+
+Now, we examine all triples $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$ and test whether $(m_i, m_j)$ is a good $(i, j)$-pair.
+If we find a triple such that all three pairs are good, we output that G contains a pyramid and stop.
+
+If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid.
+Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
+
+\TODO{some proofs}
 
@@
 
-\begin{wrapfigure}[7]{r}{0.35\textwidth}
+% \begin{wrapfigure}[7]{r}{0.35\textwidth}
+\begin{wrapfigure}{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
@@
 
-\begin{wrapfigure}[15]{r}{0.35\textwidth}
+% \begin{wrapfigure}[15]{r}{0.35\textwidth}
+\begin{wrapfigure}{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]

### 2020-08-11 paper/definitions.tex
Defs WIP

We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98} and extended as needed.

\begin{defn}[graph]
  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V^2$ that is of unordered pairs of $V$.
\end{defn}

\begin{wrapfigure}{r}{0.4\textwidth}
  \label{fig:examplePath}
  \centering\begin{tikzpicture}[scale=.7, simplegraph]
    \node(a) at (0, 0) {$v_1$};
    \node(b) at (2, 0) {$v_2$};
    \node(c) at (4, 0) {$v_3$};
    \node(d) at (6, 0) {$v_4$};

    \draw(a) to (b);
    \draw(b) to (c);
    \draw(c) to (d);

    \draw[dashed](a) to[in=90, out=90] (d);
    \draw[dashed](a) to[in=90, out=90] (c);
    \draw[dashed](b) to[in=90, out=90] (d);
  \end{tikzpicture}
  \caption{An example graph $G_0$}
\end{wrapfigure}

We will only consider finite graphs, that is $V$ and $E$ are always finite. If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}. An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$. Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{unordered}). If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring. If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.

Figure \ref{fig:examplePath} shows an example of a graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$. We will mark edges as solid lines on figures. Nonedges significant to the ongoing reasoning will be marked as dashed lines.

\begin{defn}[subgraph]
  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subset V$ and $E' \subset E$.
\end{defn}

\begin{defn}[induced subgraph]
  If $G' = (V', E')$ is a subgraph of $G$ and it contains \emph{all edges} of $G$ that join two vertices in $V'$, then $G'$ is said to be \emph{induced subgraph} of $G$ and is denoted $G[V']$.
\end{defn}
For example $(\{v_1, v_2, v_3\}, \{v_1v_2\})$ is \emph{not} an induced subgraph of the example graph $G_0$, while $(\{v_1, v_2, v_3\}, \{v_1v_2, v_2v_3\}) = G_0[\{v_1, v_2, v_3\}]$ is.

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_1, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.

Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we would add any edge to $G_0$ it would stop being a path (sometimes we call such an edge a \emph{chord}).

\begin{defn}[cycle]
  A \emph{cycle} is a graph $C$ of the form
  \[ V(C) = \{x_1, x_2, \ldots, x_l\},\quad E(C) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l, x_lx_1\} \]
\end{defn}

This cycle $C$ is usually denoted by $x_1x_2\ldots x_lx_1$ or $x_1 - x_2 - \ldots - x_l - x_1$. $l = |E(C)|$ is the \emph{length} of the cycle $C$.

If a path or a cycle has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.

Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle.

### 2020-08-12 paper/definitions.tex
Defs defs defs

@@
-We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98} and extended as needed.
+We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.
 
 \begin{defn}[graph]
-  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V^2$ that is of unordered pairs of $V$.
+  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V \choose 2$ that is of unordered pairs of $V$.
 \end{defn}
@@
 If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}.
+The size of the vertex set of a graph $G$ will be called the \emph{cardinality} of $G$.
+
 An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$.
@@
 
-This cycle $C$ is usually denoted by $x_1x_2\ldots x_lx_1$ or $x_1 - x_2 - \ldots - x_l - x_1$. $l = |E(C)|$ is the \emph{length} of the cycle $C$.
+This cycle $C$ is usually denoted by $x_1x_2\ldots x_lx_1$ or $x_1 - x_2 - \ldots - x_l - x_1$.
+$l = |E(C)|$ is the \emph{length} of the cycle $C$.
+Sometimes we will denote the cycle of length $l$ as $C_l$.
 
@@
 
-Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle.
+Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
+
+\begin{defn}[complement]
+  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is two vertices $x, y$ are adjacent in $\overline{G}$ iff they are not adjacent in $G$.
+\end{defn}
+
+Sometimes, we will call a complement of a member of a class $\Gamma$ an \emph{anti-
+$\Gamma$}, e.g. graph $G = (\{v_1, v_2, v_3, v_4\}, \{v_1v_3, v_2v_4\})$ is an anticycle.
+
+\begin{defn}[clique]
+  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected.
+\end{defn}
+
+Therefore an \emph{anticlique} is a graph in which there are no edges.
+We will also call anticliques \emph{independent sets}.
+In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subset V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.
+
+\begin{defn}[clique number]
+  A \emph{clique number} of a graph $G$, denoted as $\omega(G)$, is a cardinality of its largest induced clique.
+\end{defn}
+
+\begin{defn}[coloring]
+  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that for every edge $xy \in E(G)$, $c(x)$ is different from $c(y)$.
+A $k-coloring$ of $G$ (if exists) is a coloring, such that for all vertices $x \in V(G)$, $c(x) \leq k$.
+\end{defn}
+
+\begin{defn}[chromatic number]
+  A \emph{chromatic number} of a graph $G$, denoted as $\chi(G)$, is a smallest natural number $k$, for which there exists a $k$-coloring of $G$.
+\end{defn}
+
+% \begin{defn}[independent set]
+  % An \emph{independent set} or 
+% \end{defn}

### 2020-08-22 paper/definitions.tex
More defs wip

@@
 \begin{defn}[subgraph]
-  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subset V$ and $E' \subset E$.
+  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subseteq V$ and $E' \subseteq E$.
 \end{defn}
@@
 \end{defn}
-For example $(\{v_1, v_2, v_3\}, \{v_1v_2\})$ is \emph{not} an induced subgraph of the example graph $G_0$, while $(\{v_1, v_2, v_3\}, \{v_1v_2, v_2v_3\}) = G_0[\{v_1, v_2, v_3\}]$ is.
+
+Given a graph $G = (V, E)$ and a set set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.
+
+For example $(\{v_1, v_2, v_3\}, \{v_1v_2\})$ is \emph{not} an induced subgraph of the example graph $G_0$, while $(\{v_1, v_2, v_3\}, \{v_1v_2, v_2v_3\}) = G_0[\{v_1, v_2, v_3\}] = G_0 \setminus \{v_0\}$ is.
+
+\begin{defn}[$X$-completeness]
+  Given set $X \subseteq V$, vertex $v \notin X$ is \emph{$X$-complete} if it is adjacent to every node $x \in X$.
+A set $Y \subseteq V$ is $X$-complete if $X \cap Y = \emptyset$ and every node $y \in Y$ is $X$-complete.
+\end{defn}
 
@@
 
+\begin{defn}[connected graph]
+  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$. \todo{formal enough?}
+\end{defn}
+
+\begin{defn}[component]
+  A \emph{component} of a graph $G$ is its maximal connected induced subgraph.
+\end{defn}
+
 \begin{defn}[cycle]
@@
 
-If a path or a cycle has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.
+Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
 
-Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
+\begin{defn}[hole]
+  A \emph{hole} is a cycle of length at least four.
+\end{defn}
+
+If a path, a cycle or a hole has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.
 
@@
 
+\begin{defn}[anticomponent]
+  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $G$.
+\end{defn}
+
 \begin{defn}[clique]
@@
 We will also call anticliques \emph{independent sets}.
-In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subset V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.
+In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.
 
@@
 
-% \begin{defn}[independent set]
-  % An \emph{independent set} or 
-% \end{defn}
+\begin{defn}[Berge graph]
+  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole.
+\end{defn}
+
+\begin{defn}[perfect graph]
+  A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$
+\end{defn}
+
+\begin{defn}[C-major vertices]
+  Given a shortest off hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C-major$ if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
+  \TODO{a picture of this, clean odd hole, amenable hole}
+\end{defn}
+
+\begin{defn}[clean odd hole]
+  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
+\end{defn}
+
+\begin{defn}[cleaner]
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
+\end{defn}
+
+Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.
+
+\begin{defn}[near-cleaner]
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vectices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
+\end{defn}
+
+\begin{defn}[amenable odd hole]
+  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vectices there is a $X$-complete edge in $C$.
+\end{defn}

### 2020-08-22 paper/main.tex
Defs WIP
Defs defs defs
More defs wip

@@
 \usepackage{intcalc}
-\usepackage{amsthm}
+\usepackage{amsthm, amsfonts, thmtools}
 \usepackage{cleveref}
+\usepackage{floatflt}
 
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{defn}{Definition}[section]
+\renewcommand{\listtheoremname}{List of definitions}
 
@@
 
+\listoftheorems[ignoreall,show={defn}]
 \tableofcontents
@@
 
+\section{Definitions}
+\input{definitions.tex}
+
 \section{Perfect Graphs}
+
 All graphs in this paper are finite, undirected and have no loops or parallel edges.
 We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$.
-\emph{Coloring} of a graph means assigning every node of a graph a color.
+\emph{Coloring} of a graph means assigning every node\todo{node \rightarrow vertex everywhere (seems to be more common name)} of a graph a color.
 A coloring is \emph{valid} iff every two nodes sharing an edge have different colors.
@@
 
-\begin{wrapfigure}[14]{r}{0.35\textwidth}
+% \begin{floatingfigure}{0.35\textwidth}
+
+\begin{wrapfigure}{r}{0.35\textwidth}
 	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
@@
 	\draw (a) to (b2);
-\end{tikzpicture}
-\caption{An example of a pyramid.}
+\end{tikzpicture}%
+\caption{An example  of a pyramid.}%
+\vspace{-1.2cm}
+% \end{floatingfigure}
 \end{wrapfigure}
@@
 \caption{An example of a jewel.}
+\vspace{-1.5cm}
 \end{wrapfigure}
@@
 		% \draw (a) to (b2);
-\end{tikzpicture}
-\caption{An example of a $\T_2$.}
+\end{tikzpicture}%
+\caption{An example of a $\T_2$.}%
+\vspace{-1.5cm}
 \end{wrapfigure}

### 2020-08-24 paper/definitions.tex
Introduction some fixes

@@
 \begin{defn}[clique]
-  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected.
+  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique of $n$ vertices as $K_n$.
 \end{defn}
@@
 \begin{defn}[perfect graph]
+  \label{def:perfectGraph}
   A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$

### 2020-08-24 paper/main.tex
Introduction some fixes

@@
 
-All graphs in this paper are finite, undirected and have no loops or parallel edges.
-We denote the chromatic number of graph $G$ by $\chi(G)$ and the cardinality of the largest clique of $G$ by $\omega(G)$.
-\emph{Coloring} of a graph means assigning every node\todo{node \rightarrow vertex everywhere (seems to be more common name)} of a graph a color.
-A coloring is \emph{valid} iff every two nodes sharing an edge have different colors.
-An \emph{optimal} coloring (if exists) is a valid coloring using only $\omega(G)$ colors.
+Given a graph $G$, let us consider a problem of coloring it using as few colors as possible.
+If $G$ contains a clique $K$ as a subgraph, we must use at least $|V(K)|$ colors to color it.
+This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$.
+The reverse is not always true, in fact we can construct a graph with no triangle and requiring arbitrarily large numbers of colors (e.g.
+construction by Mycielski \cite{Mycielski1955}).
 
-Given a graph $G = (V,E)$, sometimes by $V(G)$ and $E(G)$ we will denote a set of nodes and edges of $G$.
-Given a set $X \subseteq V$ by $G[X]$ we will denote a graph induced on $X$.
-A graph $G$ is \emph{perfect} iff for all $X \subseteq V(G)$ we have $\chi(G[X]) = \omega(G[X])$.
+Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze?
+Not necessarily so.
+Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$.
+We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.
 
-\paragraph{Definitions and conventions}
-	\todo{Where should we put it? Should we put all definitions here, or leave them in text?}
-\begin{itemize}
-	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
-	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
-	\item Given a path $P$, by $P^*$ we will denote its inside.
-\end{itemize}
+A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal.
+The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum clique problem, and maximum independent set problem can be solved in polynomial time \cite{grotschel1993}
 
-\TODO{Give some examples why perfect graphs are interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}
-
-Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$.
-For example a clique in a graph becomes an independent set in its complement.
+\begin{theorem}{Perfect graph theorem}
 A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
@@
 Maybe based on proof in \cite{GC03}}
+\end{theorem}
 

### 2020-08-24 paper/definitions.tex
Corrections

@@
 
-\begin{defn}[connected graph]
+\begin{defn}[connected graph, subset]
   A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$. \todo{formal enough?}
+  A subset $X \subseteq V(G)$ is connected if the graph $G[X]$ is connected.
 \end{defn}
@@
 
-Sometimes, we will call a complement of a member of a class $\Gamma$ an \emph{anti-
-  $\Gamma$}, e.g. graph $G = (\{v_1, v_2, v_3, v_4\}, \{v_1v_3, v_2v_4\})$ is an anticycle.
+% Sometimes, we will call a complement of a member of a class $\Gamma$ an \emph{anti-
+% $\Gamma$}, e.g. graph $G = (\{v_1, v_2, v_3, v_4\}, \{v_1v_3, v_2v_4\})$ is an anticycle.
+
+\begin{defn}[anticonnected graph, subset]
+  A graph $G$ is anticonnected if $\overline{G}$ is connected.
+  A subset $X$ is anticonnected if $\overline{G}[X]$ is connected.
+\end{defn}
 
@@
 
-Therefore an \emph{anticlique} is a graph in which there are no edges.
-We will also call anticliques \emph{independent sets}.
+\begin{defn}[anticlique]
+  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets}. 
+\end{defn}
 In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.
@@
 \begin{defn}[Berge graph]
+  \label{def:bergeGraph}
   A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole.

### 2020-08-24 paper/main.tex
Corrections

@@
 \documentclass{article}
+\usepackage{import}
 
-\usepackage{appendix}
-\usepackage{todonotes}
-\usepackage{wrapfig}
-\usepackage{intcalc}
-\usepackage{amsthm, amsfonts, thmtools}
-\usepackage{cleveref}
-\usepackage{floatflt}
-
-\usepackage{tikz}
-\tikzset{%
-    simplegraph/.style={every node/.style={draw,circle, inner sep=0pt, minimum size=6mm}},
-}
-\usetikzlibrary{snakes}
-\usetikzlibrary{shapes.geometric}
-\usetikzlibrary{positioning, fit, calc}
-
-\usepackage[
-	style=numeric
-]{biblatex}
-\addbibresource{bbl.bib}
-
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{defn}{Definition}[section]
-\renewcommand{\listtheoremname}{List of definitions}
-
-\newcommand{\TODO}{\todo[inline]}
-\newcommand\Lovasz{Lovász }
-\newcommand\T{\mathcal{T}}
-\crefname{lemma}{Lemma}{Lemmas}
+\import{./}{preamble.tex}
 
@@
 % - Color, not Colour (American English)
-% - Node not a Vertex of a graph
 
@@
 \begin{document}
-\begin{titlepage}
-	\begin{center}
 
-		\large
-		\textbf{Jagiellonian University}\\
-		Department of Theoretical Computer Science\\
-
-		\vspace{1.5cm}
-
-		\Large
-		\textbf{Adrian Siwiec}
-
-		\vspace*{2cm}
-
-		\textbf{\LARGE Perfect Graph Recognition and Coloring}
-
-		\vspace{0.5cm}
-		\large
-
-		\vfill
-		\Large
-		Master Thesis
-
-		\vfill
-		\Large
-		Supervisor: dr inż. Krzysztof Turowski
-
-		\vspace{0.8cm}
-
-		September 2020
-
-\end{center}
-\end{titlepage}
-
+\include{titlepage}
 \pagebreak
@@
 \begin{abstract}
-TODO
+	TODOa
 \end{abstract}
@@
 
-\section{Definitions}
+\section*{Definitions}
 \input{definitions.tex}
@@
 A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal.
-The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum clique problem, and maximum independent set problem can be solved in polynomial time \cite{grotschel1993}
+The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum clique problem, and maximum independent set problem can be solved in polynomial time \cite{grotschel1993}.
 
-\begin{theorem}{Perfect graph theorem}
-A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect.
-\todo{Should we give some proof of that here?
-Maybe based on proof in \cite{GC03}}
+One of properties of perfect graphs is the \emph{perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72}.
+
+\begin{theorem}[Perfect graph theorem]
+	A graph is perfect if and only if its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}
 \end{theorem}
-
-A \emph{hole} is an induced chordless cycle of length at least 4.
-An \emph{antihole} is an induced subgraph whose complement is a hole.
-A \emph{Berge} graph is a graph with no holes or antiholes of odd length.
-
-In 1961 Berge conjured that a graph is perfect iff it is Berge in what has become known as a strong perfect graph conjecture.
-In 2001 Chudnovsky et al.
-have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
-The following overview of the proof will be based on this paper and on an article withe the same name by Cornuéjols \cite{GC03}.
 
@@
 It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
-It is therefore clear, that if a graph is not Berge it is not perfect.
-To prove that every Berge graph is perfect is the proper part of the strong perfect graph theorem.
+A graph with no odd hole and no odd antihole is called \emph{Berge} (\cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
+
+In 1961 Berge conjured that a graph is perfect iff it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture.
+In 2001 Chudnovsky et al.
+have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
+The following overview of the proof will be based on this paper and on an article with the same name by Cornuéjols \cite{GC03}.
+
+\begin{theorem}[Strong perfect graph theorem]
+	A graph is perfect if and only if it is Berge.
+\end{theorem}
 
 \TODO{How long and detailed overview of the proof should we provide?}
+\TODO{Znakomite pytanie.
+Generalnie ponieważ dowód jest drobiazgowy i trikowy, to wystarczy "z lotu ptaka" tj.
+to, co Chudnovsky i Seymour piszą w pracach popularnych i referują w wystąpieniach gościnnych typu te nagrania na YT.
+Głębiej nie ma sensu.
+Warto podkreślić, że technika dowodu i sam algorytm są zależne na dużo głębszym poziomie niż widać tj.
+ktoś mając dowód Stron Perfect Graph Theorem pewnie nie rozgryzłby algorytmu i vice versa.}
 
@@
 
-A \emph{path} in $G$ is an induced subgraph that is connected, with at least one node, no cycle and no node of degree larger than 2 (sometimes called chordless path).
-The \emph{length} of a path or a cycle is the number of edges in it.
-\todo{Should we move these definitions elsewhere?} A \emph{triangle} in a graph is a set of three pairwise adjacent nodes.
-
 % \begin{floatingfigure}{0.35\textwidth}
@@
 \begin{wrapfigure}{r}{0.35\textwidth}
-	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
-	\node(a) at (0,0) {a};
-	\node(b1) at (-2,-6) {$b_1$};
-	\node(b2) at (0,-4.268) {$b_2$};
-	\node(b3) at (2,-6) {$b_3$};
-
-	\node(P12) at (-2/4, -6/4) {\small$P_{12}$};
-	\node(P13) at (-4/4, -12/4) {\small$P_{13}$};
-	\node(P14) at (-6/4, -18/4) {\small$P_{14}$};
-
-	\node(P32) at (2/3, -6/3) {\small$P_{32}$};
-	\node(P33) at (4/3, -12/3) {\small$P_{33}$};
-
-	\draw (b1) to (b3);
-	\draw (b1) to (b2);
-	\draw (b2) to (b3);
-
-	\draw (a) to (P12);
-	\draw (P12) to (P13);
-	\draw (P13) to (P14);
-	\draw (P14) to (b1);
-
-	\draw (a) to (P32);
-	\draw (P32) to (P33);
-	\draw (P33) to (b3);
-
-	\draw (a) to (b2);
-\end{tikzpicture}%
+	\input{tikzpictures/pyramid.tex}
 	\caption{An example  of a pyramid.}%
@@
 
-A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another node $a$, so that:
+A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
 \begin{itemize}
 	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
-	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only node in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
+	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
 	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
@@
 
-We will give an algorithm finding pyramid, but first we need some additional definitions. If $K$ is a pyramid $(a, b_1, b_2, b_3, P_1, P_2, P_3)$ we say its \emph{frame} is the 10-tuple iff
+\subparagraph{Finding Pyramids}
+
+If $K$ is a pyramid $(a, b_1, b_2, b_3, P_1, P_2, P_3)$ we say its \emph{frame} is the 10-tuple iff
 \TODO{finish it up}
-
-\subparagraph{Finding Pyramids}
 
@@
 	\item for $1 \leq i < j \leq 3$, ${b_i, s_i}$ is disjoint from ${b_j, s_j}$ and $b_ib_j$ is the only edge between them
-	\item there is a node $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
+	\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
 \end{itemize}
 
-There are $O(|V(G)|^6)$ sextuples, and it takes $O(|V(G)|)$ time to check each one. For each such sextuple we follow with the rest of the algorithm.
+There are $O(|V(G)|^6)$ 6-tuples, and it takes $O(|V(G)|)$ time to check each one. For each such 6-tuple we follow with the rest of the algorithm.
 
@@
 
-If $s_1 = b_1$ let $P_1(b_1)$ be the one-node path with node $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.
+If $s_1 = b_1$ let $P_1(b_1)$ be the one-vertex path with vertex $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.
 
@@
 We assign $P_2$ and $P_3$ in a similar manner.
-Total time of finding all $P_i(m)$ paths for a given sextuple is $O(|V(G)|^3)$.
+Total time of finding all $P_i(m)$ paths for a given 6-tuple is $O(|V(G)|^3)$.
 
@@
 If $P_1(m_1)$ does not exist, there are no such good pairs.
-If it exists, color black the nodes of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$.
-Color all other nodes white.
-(We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black nodes.
+If it exists, color black the vertices of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$.
+Color all other vertices white.
+(We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black vertices.
 We do this for all $m_1$ and get a set of all $(1,2)$-good pairs.
@@
 \begin{wrapfigure}{r}{0.35\textwidth}
-	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
-	\def\ngon{5}
-	\node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
-	\foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
-	%p1 - v5, p2 - v1 ...
-	\draw (p1) to (p2);
-	\draw (p2) to (p3);
-	\draw (p3) to (p4);
-	\draw (p4) to (p5);
-	\draw (p1) to (p5);
-
-  \draw[dashed] (p2) to (p5);
-  \draw[dashed] (p2) to (p4);
-	\draw[dashed] (p3) to (p5);
-
-	\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
-                       post length=0mm,pre length=0mm}}
-	\draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
-	\node[draw=none] at (0, -4.7) {$P$};
-\end{tikzpicture}
+	\input{tikzpictures/jewel.tex}
 	\caption{An example of a jewel.}
@@
 
-Five nodes $v_1, \ldots, v_5$ and a path $P$ is a \emph{jewel} iff:
+Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} iff:
 
 \begin{itemize}
-	\item $v_1, \ldots, v_5$ are distinct nodes.
+	\item $v_1, \ldots, v_5$ are distinct vertices.
 	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
@@
 A configuration of type $\T_1$ is a hole of length 5.
-To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth node to complete the hole.
+To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole.
 See paragraph \ref{Optimizations} for more implementation details.
@@
 \begin{wrapfigure}{r}{0.35\textwidth}
-	\centering\begin{tikzpicture}[scale=0.7,simplegraph]
-		\node(v1) at (0,0) {$v_1$};
-		\node(v2) at (1.5,0) {$v_2$};
-		\node(v3) at (3,0) {$v_3$};
-		\node(v4) at (4.5,0) {$v_4$};
-
-		\draw (v1) to (v2);
-		\draw (v2) to (v3);
-		\draw (v3) to (v4);
-
-		\tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
-                       post length=0mm,pre length=0mm}}
-		\draw[decorate] (v1) to [out=90, in=180] (4.5/2, 3) to [out=0, in=90] (v4);
-		\node[draw=none] at (4.5/2, 3.5) {$P$};
-
-		\draw[dashed] (v2) to (.7,2.5);
-		\draw[dashed] (v3) to (.7,2.5);
-		\draw[dashed] (v2) to (3.8,2.5);
-		\draw[dashed] (v3) to (3.8,2.5);
-
-		\node[minimum size=4mm](x1) at (1.2, -2){};
-		\node[minimum size=4mm](x2) at (3.3, -2){};
-		\node[draw,dotted,inner sep=3pt, circle,yscale=.5, fit={(x1) (x2)},label=below:{$X$}] {};
-
-		\draw[dashed] (x1) to (x2);
-		\draw(v1) to (x1);
-		\draw(v2) to (x1);
-		\draw(v4) to (x1);
-		\draw(v1) to (x2);
-		\draw(v2) to (x2);
-		\draw(v4) to (x2);
-
-		% \draw (a) to (b2);
-\end{tikzpicture}%
+	\input{tikzpictures/t2.tex}
 	\caption{An example of a $\T_2$.}%
@@
 
-A configuration of type $\T_2$ is a six $(v_1, v_2, v_3, v_4, P, X)$, such that:
+A configuration of type $\T_2$ is a tuple $(v_1, v_2, v_3, v_4, P, X)$, such that:
 \begin{itemize}
 	\item $v_1v_2v_3v_4$ is a path in $G$.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete nodes.
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete vertices.
 	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
@@
 
-Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete nodes and its anticomponents.
+Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete vertices and its anticomponents.
 Then, for each anticomponent $X$ we check if required path $P$ exists.
 
-To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the Roussel-Rubio lemma \cite{RR01} as stated in \cite{MC05} that says:
+To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the following Roussel-Rubio lemma:
 
-\begin{lemma}[Roussel-Rubio Lemma]\label{Roussel-Rubio}
+\begin{lemma}[Roussel-Rubio Lemma \cite{RR01,MC05}]\label{lem:Roussel-Rubio}
 	Let $G$ be Berge, $X$ be an anticonnected subset of $V(G)$, $P$ be an odd path $p_1\ldots p_n$ in $G\setminus X$ with length at least 3, such that $p_1$ and $p_n$ are $X$-complete and $p_2, \ldots, p_{n-1}$ are not.
@@
 		\item $P$ is of length at least 5 and there exist nonadjacent $x, y \in X$, such that there are exactly two edges between $x, y$ and $P^*$, namely $xp_2$ and $yp_{n-1}$,
-		\item or $P$ is of length 3 and there is an odd antipath joining internal nodes of $P$ with interior in $X$.
+		\item or $P$ is of length 3 and there is an odd antipath joining internal vertices of $P$ with interior in $X$.
 	\end{itemize}
+	\TODO{We may use this lemma quite often, might want to provide proof if so.}
 \end{lemma}
@@
 		\item If $P$ is of length 3.
-\todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its nodes $v_1, p_2, p_3, v_4$.
-It follows from \cref{Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
+\todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$.
+It follows from \cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
 We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
-		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
+		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
 This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
@@
 \begin{itemize}
-	\item $v_1, \ldots v_6$ are distinct nodes.
+	\item $v_1, \ldots v_6$ are distinct vertices.
 	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete nodes, and $v_3$, $v_4$ are not $X$-complete.
-	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no node in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete.
+	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
 	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
@@
 
-\TODO{picture?}
+\TODO{picture!}
 
@@
 
-For each triple $v_1, v_2, v_5$ of nodes such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete nodes.
-For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no node of $F'\setminus\{v_5\}$ is $X$-complete.
-Let $F$ be the union of $F'$ and the set of all $X$-complete nodes that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.
+For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices.
+For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
+Let $F$ be the union of $F'$ and the set of all $X$-complete vertices that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.
 
-Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a node $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$.
-If there is such a node $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$.
+Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$.
+If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$.
 If we exhaust our search and find none, report that graph does not contain it.
@@
 
-We will skip the proof that each graph containing $\T_3$ is not Berge. \todo{Should we include it?} See \cite{MC05} for the proof.
+We will skip the proof that each graph containing $\T_3$ is not Berge. See paragraph 6.7 of \cite{MC05} for the proof.
 
@@
 
-For a shortest odd hole $C$ in $G$, we will call a node $v \in V(G) \setminus V(C)$ $C$-\emph{major} iff the set of its neighbors in C is not contained in any 3-node path of $C$.
-An odd hole $C$ will be called \emph{clean} if no vertex is $C$-major.
-
-A hole $C$ of $G$ is \emph{amenable} iff C is a shortest odd hole in $G$ of length at least 7, and for every anticonnected set $X$ of $C$-major nodes, there is an $X$-complete edge in $C$ (an edge is $X$-complete iff both its ends are $X$-complete).
-
-The rest of the algorithm rests upon the following theorem:
-
 \begin{theorem}
@@
 	\TODO{Any ideas on what else to say here? List all 9 steps?}
+	\TODO{Dobre pytanie. Te 9 kroków to da się zawrzeć w 1-2 zdaniach każde? Jeśli nie, to tylko napisałbym ogólnikowo, że "jest sekwencja kroków, która to robi, tu jest odnośnik"}
 \end{theorem}
 
-For a shortest odd hole $C$ in $G$, a subset $X$ of $V(G)$ is a \emph{near-cleaner for $C$} iff $X$ contains all $C$-major nodes and $X \cap V(C)$ is a subset of node set of some 3-node path of $C$.
-
-\TODO{Finding and Using Half-Cleaners.}
+\TODO{Finding and Using near-cleaners.}
 
@@
 \TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
-\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth node to complete the hole - much faster than iterating nodes.}
+\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth vertex to complete the hole - much faster than iterating vertices.}
 

### 2020-08-24 paper/tikzpictures/jewel.tex
Corrections

\centering\begin{tikzpicture}[scale=0.7,simplegraph]
  \def\ngon{5}
  \node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
  \foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{5}+1$};}
  %p1 - v5, p2 - v1 ...
  \draw (p1) to (p2);
  \draw (p2) to (p3);
  \draw (p3) to (p4);
  \draw (p4) to (p5);
  \draw (p1) to (p5);

  \draw[dashed] (p2) to (p5);
  \draw[dashed] (p2) to (p4);
  \draw[dashed] (p3) to (p5);

  \tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
        post length=0mm,pre length=0mm}}
  \draw[decorate] (p2) to [out=-100, in=180] (0, -5) to [out=0, in=-80] (p5);
  \node[draw=none] at (0, -4.7) {$P$};
\end{tikzpicture}

### 2020-08-24 paper/tikzpictures/t2.tex
Corrections

\centering\begin{tikzpicture}[scale=0.7,simplegraph]
  \node(v1) at (0,0) {$v_1$};
  \node(v2) at (1.5,0) {$v_2$};
  \node(v3) at (3,0) {$v_3$};
  \node(v4) at (4.5,0) {$v_4$};

  \draw (v1) to (v2);
  \draw (v2) to (v3);
  \draw (v3) to (v4);

  \tikzset{decoration={snake,amplitude=.6mm,segment length=6mm,
        post length=0mm,pre length=0mm}}
  \draw[decorate] (v1) to [out=90, in=180] (4.5/2, 3) to [out=0, in=90] (v4);
  \node[draw=none] at (4.5/2, 3.5) {$P$};

  \draw[dashed] (v2) to (.7,2.5);
  \draw[dashed] (v3) to (.7,2.5);
  \draw[dashed] (v2) to (3.8,2.5);
  \draw[dashed] (v3) to (3.8,2.5);

  \node[minimum size=4mm](x1) at (1.2, -2){};
  \node[minimum size=4mm](x2) at (3.3, -2){};
  \node[draw,dotted,inner sep=3pt, circle,yscale=.5, fit={(x1) (x2)},label=below:{$X$}] {};

  \draw[dashed] (x1) to (x2);
  \draw(v1) to (x1);
  \draw(v2) to (x1);
  \draw(v4) to (x1);
  \draw(v1) to (x2);
  \draw(v2) to (x2);
  \draw(v4) to (x2);

  % \draw (a) to (b2);
\end{tikzpicture}%

### 2020-08-24 paper/tikzpictures/t3.tex
T3 pic

\centering\begin{tikzpicture}[scale=.7,simplegraph]
  \def\ngon{6}
  \node[regular polygon,regular polygon sides=\ngon,minimum size=3cm, draw=none] (p) {};
  \foreach\x in {1,...,\ngon}{\node[] (p\x) at (p.corner \x){$v_\the\numexpr\intcalcMod{\x+3}{6}+1$};}

  \draw (p3) to (p4);
  \draw (p5) to (p6);
  \draw (p3) to (p6);
  \draw (p4) to (p5);
  \draw (p5) to (p1);
  \draw (p6) to (p2);

  \draw[dashed] (p3) to (p5);
  \draw[dashed] (p4) to (p6);
  \draw[dashed] (p3) to (p1);
  \draw[dashed] (p4) to (p1);
  \draw[dashed] (p3) to (p2);
  \draw[dashed] (p4) to (p2);
  \draw[dashed] (p6) to (p1);

  \node[minimum size=4mm](x1) at (-1, -4.5){};
  \node[minimum size=4mm](x2) at (1, -4.5){};
  \node[draw,dotted,inner sep=3pt, circle,yscale=.5, fit={(x1) (x2)},label=below:{$X$}] {};

  \draw[dashed] (x1) to (x2);

  \draw (p3) to[out=-90] (x1);
  \draw (p3) to[out=-90, in=150] (x2);

  \draw (p4) to (x1);
  \draw (p4) to (x2);

  \draw (p1) to[out=0, in=0] (x1);
  \draw (p1) to[out=0, in=0] (x2);

  \draw[dashed] (p5) to (x1);
  \draw[dashed] (p6) to (x2);

  \tikzset{decoration={snake,amplitude=.6mm,segment length=4mm,
        post length=0mm,pre length=0mm}}
  \draw[decorate] (p1) to [out=90, in=0] (0, 4) to [out=180, in=90] (p2);
  \node[draw=none] at (0, 4.5) {$P$};

  \draw[dashed] (p4) to (0, 4.1);
  \draw[dashed] (x2) [out=100, in=-90] to (0, 4.1);
\end{tikzpicture}%

### 2020-08-24 paper/main.tex
T3 pic
Near cleaners wip

@@
 \subparagraph{Finding Pyramids}
-
-If $K$ is a pyramid $(a, b_1, b_2, b_3, P_1, P_2, P_3)$ we say its \emph{frame} is the 10-tuple iff
-\TODO{finish it up}
 
@@
 
+\begin{wrapfigure}{r}{0.35\textwidth}
+	\input{tikzpictures/t3.tex}
+	\caption{An example of a $\T_3$.}%
+	\vspace{-1.5cm}
+\end{wrapfigure}
+
 A configuration of type $\T_3$ is a sequence $v_1, \ldots, v_6$, $P$, $X$, such that:
@@
 \end{itemize}
-
-\TODO{picture!}
 
@@
 \begin{theorem}
+	\label{thm:amenableHoles}
 	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
-	\TODO{Any ideas on what else to say here? List all 9 steps?}
-	\TODO{Dobre pytanie. Te 9 kroków to da się zawrzeć w 1-2 zdaniach każde? Jeśli nie, to tylko napisałbym ogólnikowo, że "jest sekwencja kroków, która to robi, tu jest odnośnik"}
+	% \TODO{Any ideas on what else to say here? List all 9 steps?}
+	% \TODO{Dobre pytanie. Te 9 kroków to da się zawrzeć w 1-2 zdaniach każde? Jeśli nie, to tylko napisałbym ogólnikowo, że "jest sekwencja kroków, która to robi, tu jest odnośnik"}
 \end{theorem}
+
+The proof of this theorem is quite technical and we will not discuss it here. See section 8 of \cite{MC05} for the proof.
+
+With \cref{thm:amenableHoles} we can describe the rest of the algorithm.
+
+\begin{alg}[List possible near cleners, 5.1 of \cite{MC05}]
+	Input: A graph $G$ containing no simple bad structure \todo{define this somewhere}, and a subset $X \subseteq V(G)$.
+	Output: Determines one of the following:
+	\begin{itemize}
+		\item $G$ has an odd hole
+		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
+	\end{itemize}
+\end{alg}
+\begin{algtext}
+	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$.
+If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.
+
+	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
+	\begin{itemize}
+		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
+		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say)
+		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
+	\end{itemize}
+\end{algtext}
 

### 2020-08-24 paper/main.tex
Amenable holes wip

@@
 
-\begin{alg}[List possible near cleners, 5.1 of \cite{MC05}]
+\begin{alg}[List possible near cleaners, 9.2 of \cite{MC05}]
+	\label{alg:listNearCleaners}
+	Input: A graph $G$.
+
+	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
+\end{alg}
+\begin{algtext}
+	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
+
+	Given a relevant triple $(a, b, c)$ we can compute the following:
+	\begin{itemize}
+		\item $r(a,b,c) \leftarrow$~the cardinality of the largest anticomponent of $N(a, b)$, that contains a nonneibhbor of $c$, or 0, if $c$ is $N(a, b)$-complete.
+		\item $Y(a,b,c) \leftarrow$~the union of all anticomponents of $N(a, b)$ that have cardinality strictly greater than $r(a, b, c)$.
+		\item $W(a, b, c) \leftarrow$~the anticomponent of $N(a,b) \cup \{c\}$ that contains $c$.
+		\item $Z(a, b, c) \leftarrow$~the set of all $Y(a, b, c) \cup W(a,b,c)$-complete vertices.
+		\item $X(a, b, c) \leftarrow$~$Y(a,b,c) \cup Z(a,b,c)$.
+	\end{itemize}
+
+	For every two adjacent vertices $u, v$ compute the set $N(u, v)$ and list all such sets.
+	For each relevant triple $(a,b,c)$ compute the set $X(a,b,c)$ and list all such sets.
+
+	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
+\end{algtext}
+
+To proove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.
+
+\begin{theorem}[9.1 of \cite{MC05}]
+	\label{thm:91}
+	Let $C$ be a shortest odd hole in $G$, with length at least 7. Then there is a relevant triple $(a, b, c)$ of vertices such that
+	\begin{itemize}
+		\item the set of all $C$-major vertices not in $X(a, b, c)$ is anticonnected
+		\item $X(a, b, c) \cap V(C)$ is a subset of the vertex set of some 3-vertex path of $C$.
+	\end{itemize}
+\end{theorem}
+\begin{proof}
+	\TODO{do we want it here? 1-2 pages long}
+\end{proof}
+
+Let us suppose that $C$ is an amenable hole in $G$.
+By \cref{thm:91}, there is a relevant triple $(a, b, c)$ satisfying that theorem.
+Let $T$ be the set of all $C$-major vertices not in $X(a,b,c)$.
+From \cref{thm:91} we get that $T$ is anticonnected.
+Since $C$ is amenable, there is an edge $uv$ of $C$ that is $T$-complete, and therefore $T \subseteq N(u, v)$.
+But then $N(u, v) \cup X(a, b, c)$ is a near-cleaner for $C$.
+Therefore the output of the \cref{alg:listNearCleaners} is correct.
+
+\begin{alg}[Test possible near clener, 5.1 of \cite{MC05}]
 	Input: A graph $G$ containing no simple bad structure \todo{define this somewhere}, and a subset $X \subseteq V(G)$.
-	Output: Determines one of the following:
+
+	\noindent Output: Determines one of the following:
 	\begin{itemize}

### 2020-08-24 paper/main.tex
Move from article to report

@@
-\documentclass{article}
+\documentclass{report}
 \usepackage{import}
@@
 
-\section*{Definitions}
+\chapter*{Definitions}
 \input{definitions.tex}
 
-\section{Perfect Graphs}
+\chapter{Perfect Graphs}
 
@@
 
-\subsection{Strong Perfect Graph Theorem}
+\section{Strong Perfect Graph Theorem}
 
@@
 
-\section{Recognizing Berge Graphs}
+\chapter{Recognizing Berge Graphs}
 
@@
 
-\subsection{Recognition algorithm Overview}
+\section{Recognition algorithm Overview}
 
@@
 
-\subsubsection{Simple structures}
+\subsection{Simple structures}
 \label{SimpleStructures}
 
-\paragraph{Pyramids}
+\subsubsection{Pyramids}
 
@@
 
-\subparagraph{Finding Pyramids}
+\paragraph{Finding Pyramids}
 
@@
 
-\paragraph{Jewels}
+\subsubsection{Jewels}
 
@@
 
-\paragraph{Configurations of type $\T_1$}
+\subsubsection{Configurations of type $\T_1$}
 
@@
 To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole.
-See paragraph \ref{Optimizations} for more implementation details.
+See \cref{Optimizations} for more implementation details.
 
-\paragraph{Configurations of type $\T_2$}
+\subsubsection{Configurations of type $\T_2$}
 
@@
 
-\paragraph{Configurations of type $\T_3$}
+\subsubsection{Configurations of type $\T_3$}
 
@@
 
-We will skip the proof that each graph containing $\T_3$ is not Berge. See paragraph 6.7 of \cite{MC05} for the proof.
+We will skip the proof that each graph containing $\T_3$ is not Berge. See section 6.7 of \cite{MC05} for the proof.
 
-\subsubsection{Amenable holes.}
+\subsection{Amenable holes.}
 \label{AmenableHoles}
@@
 
-\subsection{Implementation}
+\section{Implementation}
 
@@
 
-\subsubsection{Optimizations}\label{Optimizations}
+\subsection{Optimizations}\label{Optimizations}
 Bottlenecks in performance (next path, are vectors distinct etc).\\
@@
 
-\subsection{Parallelism with CUDA (?)}
+\section{Parallelism with CUDA (?)}
 
@@
 
-\subsection{Experiments}
+\section{Experiments}
 
@@
 
-\section{Coloring Berge Graphs}
+\chapter{Coloring Berge Graphs}
 
-\subsection{Ellipsoid method}
+\section{Ellipsoid method}
 
@@
 
-\subsection{Combinatorial Method}
+\section{Combinatorial Method}
 
@@
 
-\section{Perfect Graph Coloring algorithm}
+\chapter{Perfect Graph Coloring algorithm}
 TODO

### 2020-08-25 paper/main.tex
Some reorganization, testing near cleaner wip

--- 2020-08-24 paper/main.tex
@@
 
-\section*{Definitions}
+\chapter*{Definitions}
 \input{definitions.tex}
 
-\section{Perfect Graphs}
+\chapter{Perfect Graphs}
+\input{perfectGraphs.tex}
 
-Given a graph $G$, let us consider a problem of coloring it using as few colors as possible.
-If $G$ contains a clique $K$ as a subgraph, we must use at least $|V(K)|$ colors to color it.
-This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$.
-The reverse is not always true, in fact we can construct a graph with no triangle and requiring arbitrarily large numbers of colors (e.g.
-construction by Mycielski \cite{Mycielski1955}).
+\chapter{Recognizing Berge Graphs}
 
-Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze?
-Not necessarily so.
-Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$.
-We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.
-
-A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal.
-The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum clique problem, and maximum independent set problem can be solved in polynomial time \cite{grotschel1993}.
-
-One of properties of perfect graphs is the \emph{perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72}.
-
-\begin{theorem}[Perfect graph theorem]
-	A graph is perfect if and only if its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}
-\end{theorem}
-
-\subsection{Strong Perfect Graph Theorem}
-
-Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2.
-It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
-A graph with no odd hole and no odd antihole is called \emph{Berge} (\cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
-
-In 1961 Berge conjured that a graph is perfect iff it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture.
-In 2001 Chudnovsky et al.
-have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
-The following overview of the proof will be based on this paper and on an article with the same name by Cornuéjols \cite{GC03}.
-
-\begin{theorem}[Strong perfect graph theorem]
-	A graph is perfect if and only if it is Berge.
-\end{theorem}
-
-\TODO{How long and detailed overview of the proof should we provide?}
-\TODO{Znakomite pytanie.
-Generalnie ponieważ dowód jest drobiazgowy i trikowy, to wystarczy "z lotu ptaka" tj.
-to, co Chudnovsky i Seymour piszą w pracach popularnych i referują w wystąpieniach gościnnych typu te nagrania na YT.
-Głębiej nie ma sensu.
-Warto podkreślić, że technika dowodu i sam algorytm są zależne na dużo głębszym poziomie niż widać tj.
-ktoś mając dowód Stron Perfect Graph Theorem pewnie nie rozgryzłby algorytmu i vice versa.}
-
-\section{Recognizing Berge Graphs}
-
-The following is based on the paper by Maria Chudnovsky et al. \citetitle*[]{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
-
-\subsection{Recognition algorithm Overview}
-
-Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple structures as a induced subgraph (\ref{SimpleStructures}).
-If they do, we output that graph is not Berge and stop.
-Else, we check if there is a near-cleaner for a shortest odd hole.(\ref{AmenableHoles}).
-
-\subsubsection{Simple structures}
-\label{SimpleStructures}
-
-\paragraph{Pyramids}
-
-% \begin{floatingfigure}{0.35\textwidth}
-
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/pyramid.tex}
-	\caption{An example  of a pyramid.}%
-	\vspace{-1.2cm}
-	% \end{floatingfigure}
-\end{wrapfigure}
-
-A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
-\begin{itemize}
-	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
-	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
-	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
-\end{itemize}
-
-We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is determined by its paths $P_1$, $P_2$, $P_3$.
-
-It is easy to see that every graph containing a pyramid contains an odd hole -- at least two of the paths $P_1$, $P_2$, $P_3$ will have the same parity.
-
-\subparagraph{Finding Pyramids}
-
-First, let us enumerate all 6-tuples $b_1, b_2, b_3, s_1, s_2, s_3$ such that:
-\begin{itemize}
-	\item $\{b_1, b_2, b_3\}$ is a triangle
-	\item for $1 \leq i < j \leq 3$, ${b_i, s_i}$ is disjoint from ${b_j, s_j}$ and $b_ib_j$ is the only edge between them
-	\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
-\end{itemize}
-
-There are $O(|V(G)|^6)$ 6-tuples, and it takes $O(|V(G)|)$ time to check each one. For each such 6-tuple we follow with the rest of the algorithm.
-
-We define $M = V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$.
-Now, for each $m \in M$, we set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
-We set $S_2$ and $S_3$ similarly.
-Then similarly we set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
-We do similar for $T_2$ and $T_3$.
-It takes $O(|V(G)|^2)$ time to calculate paths $T_i(m)$ for all $i$ and $m$.
-
-Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ and paths $P_2(m)$, $P_3(m)$ will be defined in a similar manner.
-
-If $s_1 = b_1$ let $P_1(b_1)$ be the one-vertex path with vertex $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.
-
-If $s_1 \neq b_1$, then $P_1(b_1)$ is undefined and for all $m \in M$ we will check if all the following are true:
-\begin{itemize}
-	\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
-	\item $S_1(m)$ and $T_1(m)$ both exist
-	\item $V(S_1(m) \cap T_1(m)) = \{m\}$
-	\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
-\end{itemize}
-If so, then we assign a path $s_1-S_1(m)-m-T_1(m)-b_1$ to $P_1(m)$, otherwise we let $P_1(m)$ be undefined.
-It takes $O(|V(G)|^2)$ to check this, given $m$.
-We assign $P_2$ and $P_3$ in a similar manner.
-Total time of finding all $P_i(m)$ paths for a given 6-tuple is $O(|V(G)|^3)$.
-
-Now we want to check if there is a triple $m_1, m_2, m_3$, so that $P_1(m_1)$, $P_2(m_2)$, $P_3(m_3)$ form a pyramid.
-A most obvious approach of enumerating them all would be too slow, so we do it carefully.
-
-For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$, $P_j(m_j)$ both exist and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
-
-We show how to find the list of all good $(1, 2)$-pairs, with similar algorithm for all other good $(i, j)$-pairs.
-For each $m_1 \in M \cup \{b_1\}$, we find the set of all $m_2$ such that $(m_1, m_2)$ is a good $(1,2)$-pair as follows.
-
-If $P_1(m_1)$ does not exist, there are no such good pairs.
-If it exists, color black the vertices of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$.
-Color all other vertices white.
-(We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black vertices.
-We do this for all $m_1$ and get a set of all $(1,2)$-good pairs.
-In similar way we calculate all good $(1,3)$-pair and $(2,3)$-pairs (in $O(|V(G)|^3)$ time).
-
-Now, we examine all triples $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$ and test whether $(m_i, m_j)$ is a good $(i, j)$-pair.
-If we find a triple such that all three pairs are good, we output that G contains a pyramid and stop.
-
-If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid.
-Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
-
-\TODO{some proofs}
-
-\paragraph{Jewels}
-
-% \begin{wrapfigure}[7]{r}{0.35\textwidth}
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/jewel.tex}
-	\caption{An example of a jewel.}
-	\vspace{-1.5cm}
-\end{wrapfigure}
-
-Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} iff:
-
-\begin{itemize}
-	\item $v_1, \ldots, v_5$ are distinct vertices.
-	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
-	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
-	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
-\end{itemize}
-
-Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required.
-This gives us a time of $O(|V|^7)$.
-We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
-
-\paragraph{Configurations of type $\T_1$}
-
-A configuration of type $\T_1$ is a hole of length 5.
-To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole.
-See paragraph \ref{Optimizations} for more implementation details.
-
-\paragraph{Configurations of type $\T_2$}
-
-% \begin{wrapfigure}[15]{r}{0.35\textwidth}
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/t2.tex}
-	\caption{An example of a $\T_2$.}%
-	\vspace{-1.5cm}
-\end{wrapfigure}
-
-A configuration of type $\T_2$ is a tuple $(v_1, v_2, v_3, v_4, P, X)$, such that:
-\begin{itemize}
-	\item $v_1v_2v_3v_4$ is a path in $G$.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete vertices.
-	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
-\end{itemize}
-
-Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete vertices and its anticomponents.
-Then, for each anticomponent $X$ we check if required path $P$ exists.
-
-To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the following Roussel-Rubio lemma:
-
-\begin{lemma}[Roussel-Rubio Lemma \cite{RR01,MC05}]\label{lem:Roussel-Rubio}
-	Let $G$ be Berge, $X$ be an anticonnected subset of $V(G)$, $P$ be an odd path $p_1\ldots p_n$ in $G\setminus X$ with length at least 3, such that $p_1$ and $p_n$ are $X$-complete and $p_2, \ldots, p_{n-1}$ are not.
-Then:
-	\begin{itemize}
-		\item $P$ is of length at least 5 and there exist nonadjacent $x, y \in X$, such that there are exactly two edges between $x, y$ and $P^*$, namely $xp_2$ and $yp_{n-1}$,
-		\item or $P$ is of length 3 and there is an odd antipath joining internal vertices of $P$ with interior in $X$.
-	\end{itemize}
-	\TODO{We may use this lemma quite often, might want to provide proof if so.}
-\end{lemma}
-
-Now, we shall prove the following:
-
-\begin{lemma}
-	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
-\end{lemma}
-\begin{proof}
-	Let $(v_1, v_2, v_3, v_4, P, X)$ be a configuration of type $\T_2$. Let us assume that $G$ is not Berge and consider the following:
-	\begin{itemize}
-		\item If $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
-		\item If $P$ is of length 3.
-\todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$.
-It follows from \cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
-We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
-		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
-This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
-	\end{itemize}
-\end{proof}
-
-\paragraph{Configurations of type $\T_3$}
-
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/t3.tex}
-	\caption{An example of a $\T_3$.}%
-	\vspace{-1.5cm}
-\end{wrapfigure}
-
-A configuration of type $\T_3$ is a sequence $v_1, \ldots, v_6$, $P$, $X$, such that:
-\begin{itemize}
-	\item $v_1, \ldots v_6$ are distinct vertices.
-	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete.
-	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
-	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
-\end{itemize}
-
-The following algorithm with running time of $O(|V(G)|^6)$ checks whether $G$ contains a configuration of type $T_3$:
-
-For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices.
-For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
-Let $F$ be the union of $F'$ and the set of all $X$-complete vertices that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.
-
-Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$.
-If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$.
-If we exhaust our search and find none, report that graph does not contain it.
-
-To see that the algorithm below has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
-This gives us the total running time of $O(|V(G)|^6)$.
-
-We will skip the proof that each graph containing $\T_3$ is not Berge. See paragraph 6.7 of \cite{MC05} for the proof.
-
-\subsubsection{Amenable holes.}
-\label{AmenableHoles}
-
-\begin{theorem}
-	\label{thm:amenableHoles}
-	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
-	% \TODO{Any ideas on what else to say here? List all 9 steps?}
-	% \TODO{Dobre pytanie. Te 9 kroków to da się zawrzeć w 1-2 zdaniach każde? Jeśli nie, to tylko napisałbym ogólnikowo, że "jest sekwencja kroków, która to robi, tu jest odnośnik"}
-\end{theorem}
-
-The proof of this theorem is quite technical and we will not discuss it here. See section 8 of \cite{MC05} for the proof.
-
-With \cref{thm:amenableHoles} we can describe the rest of the algorithm.
-
-\begin{alg}[List possible near cleners, 5.1 of \cite{MC05}]
-	Input: A graph $G$ containing no simple bad structure \todo{define this somewhere}, and a subset $X \subseteq V(G)$.
-	Output: Determines one of the following:
-	\begin{itemize}
-		\item $G$ has an odd hole
-		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
-	\end{itemize}
-\end{alg}
-\begin{algtext}
-	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$.
-If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.
-
-	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
-	\begin{itemize}
-		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
-		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say)
-		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
-	\end{itemize}
-\end{algtext}
-
-\TODO{Finding and Using near-cleaners.}
-
-\TODO{Overview of proof of why algorithm using Half-Cleaners is correct.}
-
-\subsection{Implementation}
+\section{Implementation}
 

### 2020-08-25 paper/perfectGraphs.tex
Some reorganization, testing near cleaner wip

Given a graph $G$, let us consider a problem of coloring it using as few colors as possible. If $G$ contains a clique $K$ as a subgraph, we must use at least $|V(K)|$ colors to color it. This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$. The reverse is not always true, in fact we can construct a graph with no triangle and requiring arbitrarily large numbers of colors (e.g. construction by Mycielski \cite{Mycielski1955}).

Do graphs that admit coloring using only $\omega(G)$ color are "simpler" to further analyze? Not necessarily so. Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$. We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.

A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal. The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures some of the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum (weighted) clique problem, and maximum (weighted) independent set problem can be solved in polynomial time \cite{grotschel1993}. Other classical NP-complete problems are still NP-complete in perfect graphs e.g. Hamiltonian path \cite{Mller1996}, maximum cut problem \cite{Bodlaender1994} or dominating set problem \cite{Dewdney81}. \todo{all theese citations are about subclasses e.g. biparite graphs. Should we mention some subclasses?}

The most fundamental problem -- the problem of recognizing perfect graphs -- was open since its posing in 1961 until recently. Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge (\cref{def:bergeGraph}) and an algorithm for recognizing Berge graphs in polynomial time (\cref{sec:recognizingBerge}).

The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72}.

\begin{theorem}[Perfect graph theorem]
	A graph is perfect if and only if its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}
\end{theorem}

\section{Strong Perfect Graph Theorem}
\label{sec:SPGT}

Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2. It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$. A graph with no odd hole and no odd antihole is called \emph{Berge} (\cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.

In 1961 Berge conjured that a graph is perfect iff it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture. In 2001 Chudnovsky et al. have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}. The following overview of the proof will be based on this paper and on an article with the same name by Cornuéjols \cite{GC03}.

\begin{theorem}[Strong perfect graph theorem]
	A graph is perfect if and only if it is Berge.
\end{theorem}

\TODO{How long and detailed overview of the proof should we provide?}
\TODO{Znakomite pytanie. Generalnie ponieważ dowód jest drobiazgowy i trikowy, to wystarczy "z lotu ptaka" tj. to, co Chudnovsky i Seymour piszą w pracach popularnych i referują w wystąpieniach gościnnych typu te nagrania na YT. Głębiej nie ma sensu. Warto podkreślić, że technika dowodu i sam algorytm są zależne na dużo głębszym poziomie niż widać tj. ktoś mając dowód Stron Perfect Graph Theorem pewnie nie rozgryzłby algorytmu i vice versa.}

\section{Recognizing Berge Graphs}
\label{sec:recognizingBerge}

The following is based on the paper by Maria Chudnovsky et al. \citetitle*[]{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.

Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple structures as a induced subgraph (\ref{SimpleStructures}). If they do, we output that graph is not Berge and stop. Else, we check if there is a near-cleaner for a shortest odd hole (\ref{AmenableHoles}).

\subsection{Simple structures}
\label{SimpleStructures}

\subsubsection{Pyramids}

% \begin{floatingfigure}{0.35\textwidth}

\begin{wrapfigure}{r}{0.35\textwidth}
	\input{tikzpictures/pyramid.tex}
	\caption{An example  of a pyramid.}%
	\vspace{-1.2cm}
	% \end{floatingfigure}
\end{wrapfigure}

A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
\begin{itemize}
	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
\end{itemize}

We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is determined by its paths $P_1$, $P_2$, $P_3$.

It is easy to see that every graph containing a pyramid contains an odd hole -- at least two of the paths $P_1$, $P_2$, $P_3$ will have the same parity.

\paragraph{Finding Pyramids}

First, let us enumerate all 6-tuples $b_1, b_2, b_3, s_1, s_2, s_3$ such that:
\begin{itemize}
	\item $\{b_1, b_2, b_3\}$ is a triangle
	\item for $1 \leq i < j \leq 3$, ${b_i, s_i}$ is disjoint from ${b_j, s_j}$ and $b_ib_j$ is the only edge between them
	\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
\end{itemize}

There are $O(|V(G)|^6)$ 6-tuples, and it takes $O(|V(G)|)$ time to check each one. For each such 6-tuple we follow with the rest of the algorithm.

We define $M = V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$. Now, for each $m \in M$, we set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists. We set $S_2$ and $S_3$ similarly. Then similarly we set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists. We do similar for $T_2$ and $T_3$. It takes $O(|V(G)|^2)$ time to calculate paths $T_i(m)$ for all $i$ and $m$.

Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ and paths $P_2(m)$, $P_3(m)$ will be defined in a similar manner.

If $s_1 = b_1$ let $P_1(b_1)$ be the one-vertex path with vertex $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.

If $s_1 \neq b_1$, then $P_1(b_1)$ is undefined and for all $m \in M$ we will check if all the following are true:
\begin{itemize}
	\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
	\item $S_1(m)$ and $T_1(m)$ both exist
	\item $V(S_1(m) \cap T_1(m)) = \{m\}$
	\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
\end{itemize}
If so, then we assign a path $s_1-S_1(m)-m-T_1(m)-b_1$ to $P_1(m)$, otherwise we let $P_1(m)$ be undefined. It takes $O(|V(G)|^2)$ to check this, given $m$. We assign $P_2$ and $P_3$ in a similar manner. Total time of finding all $P_i(m)$ paths for a given 6-tuple is $O(|V(G)|^3)$.

Now we want to check if there is a triple $m_1, m_2, m_3$, so that $P_1(m_1)$, $P_2(m_2)$, $P_3(m_3)$ form a pyramid. A most obvious approach of enumerating them all would be too slow, so we do it carefully.

For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$, $P_j(m_j)$ both exist and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.

We show how to find the list of all good $(1, 2)$-pairs, with similar algorithm for all other good $(i, j)$-pairs. For each $m_1 \in M \cup \{b_1\}$, we find the set of all $m_2$ such that $(m_1, m_2)$ is a good $(1,2)$-pair as follows.

If $P_1(m_1)$ does not exist, there are no such good pairs. If it exists, color black the vertices of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$. Color all other vertices white. (We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black vertices. We do this for all $m_1$ and get a set of all $(1,2)$-good pairs. In similar way we calculate all good $(1,3)$-pair and $(2,3)$-pairs (in $O(|V(G)|^3)$ time).

Now, we examine all triples $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$ and test whether $(m_i, m_j)$ is a good $(i, j)$-pair. If we find a triple such that all three pairs are good, we output that G contains a pyramid and stop.

If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid. Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.

\TODO{some proofs}

\subsubsection{Jewels}

% \begin{wrapfigure}[7]{r}{0.35\textwidth}
\begin{wrapfigure}{r}{0.35\textwidth}
	\input{tikzpictures/jewel.tex}
	\caption{An example of a jewel.}
	\vspace{-1.5cm}
\end{wrapfigure}

Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} iff:

\begin{itemize}
	\item $v_1, \ldots, v_5$ are distinct vertices.
	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
\end{itemize}

Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required. This gives us a time of $O(|V|^7)$. We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.

\subsubsection{Configurations of type $\T_1$}

A configuration of type $\T_1$ is a hole of length 5. To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole. See \cref{Optimizations} for more implementation details.

\subsubsection{Configurations of type $\T_2$}

% \begin{wrapfigure}[15]{r}{0.35\textwidth}
\begin{wrapfigure}{r}{0.35\textwidth}
	\input{tikzpictures/t2.tex}
	\caption{An example of a $\T_2$.}%
	\vspace{-1.5cm}
\end{wrapfigure}

A configuration of type $\T_2$ is a tuple $(v_1, v_2, v_3, v_4, P, X)$, such that:
\begin{itemize}
	\item $v_1v_2v_3v_4$ is a path in $G$.
	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete vertices.
	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
\end{itemize}

Checking if configuration of type $\T_2$ exists in our graph is straightforward: we enumerate all paths $v_1\ldots v_4$, calculate set of all $\{v_1, v_2, v_4\}$-complete vertices and its anticomponents. Then, for each anticomponent $X$ we check if required path $P$ exists.

To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the following Roussel-Rubio lemma:

\begin{lemma}[Roussel-Rubio Lemma \cite{RR01,MC05}]\label{lem:Roussel-Rubio}
	Let $G$ be Berge, $X$ be an anticonnected subset of $V(G)$, $P$ be an odd path $p_1\ldots p_n$ in $G\setminus X$ with length at least 3, such that $p_1$ and $p_n$ are $X$-complete and $p_2, \ldots, p_{n-1}$ are not. Then:
	\begin{itemize}
		\item $P$ is of length at least 5 and there exist nonadjacent $x, y \in X$, such that there are exactly two edges between $x, y$ and $P^*$, namely $xp_2$ and $yp_{n-1}$,
		\item or $P$ is of length 3 and there is an odd antipath joining internal vertices of $P$ with interior in $X$.
	\end{itemize}
	\TODO{We may use this lemma quite often, might want to provide proof if so.}
\end{lemma}

Now, we shall prove the following:

\begin{lemma}
	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
\end{lemma}
\begin{proof}
	Let $(v_1, v_2, v_3, v_4, P, X)$ be a configuration of type $\T_2$. Let us assume that $G$ is not Berge and consider the following:
	\begin{itemize}
		\item If $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
		\item If $P$ is of length 3. \todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$. It follows from \cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$. We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$. This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
	\end{itemize}
\end{proof}

\subsubsection{Configurations of type $\T_3$}

\begin{wrapfigure}{r}{0.35\textwidth}
	\input{tikzpictures/t3.tex}
	\caption{An example of a $\T_3$.}%
	\vspace{-1.5cm}
\end{wrapfigure}

A configuration of type $\T_3$ is a sequence $v_1, \ldots, v_6$, $P$, $X$, such that:
\begin{itemize}
	\item $v_1, \ldots v_6$ are distinct vertices.
	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges.
	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete.
	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
\end{itemize}

The following algorithm with running time of $O(|V(G)|^6)$ checks whether $G$ contains a configuration of type $T_3$:

For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices. For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete. Let $F$ be the union of $F'$ and the set of all $X$-complete vertices that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.

Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$. If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$. If we exhaust our search and find none, report that graph does not contain it.

To see that the algorithm below has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn. This gives us the total running time of $O(|V(G)|^6)$.

We will skip the proof that each graph containing $\T_3$ is not Berge. See section6 6.7 of \cite{MC05} for the proof.

\subsection{Amenable holes.}
\label{AmenableHoles}

\begin{theorem}
	\label{thm:amenableHoles}
	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
	% \TODO{Any ideas on what else to say here? List all 9 steps?}
	% \TODO{Dobre pytanie. Te 9 kroków to da się zawrzeć w 1-2 zdaniach każde? Jeśli nie, to tylko napisałbym ogólnikowo, że "jest sekwencja kroków, która to robi, tu jest odnośnik"}
\end{theorem}

The proof of this theorem is quite technical and we will not discuss it here. See section 8 of \cite{MC05} for the proof.

With \cref{thm:amenableHoles} we can describe the rest of the algorithm.

\begin{alg}[List possible near cleaners, 9.2 of \cite{MC05}]
	\label{alg:listNearCleaners}
	Input: A graph $G$.

	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
\end{alg}
\begin{algtext}
	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.

	Given a relevant triple $(a, b, c)$ we can compute the following:
	\begin{itemize}
		\item $r(a,b,c) \leftarrow$~the cardinality of the largest anticomponent of $N(a, b)$, that contains a nonneibhbor of $c$, or 0, if $c$ is $N(a, b)$-complete.
		\item $Y(a,b,c) \leftarrow$~the union of all anticomponents of $N(a, b)$ that have cardinality strictly greater than $r(a, b, c)$.
		\item $W(a, b, c) \leftarrow$~the anticomponent of $N(a,b) \cup \{c\}$ that contains $c$.
		\item $Z(a, b, c) \leftarrow$~the set of all $Y(a, b, c) \cup W(a,b,c)$-complete vertices.
		\item $X(a, b, c) \leftarrow$~$Y(a,b,c) \cup Z(a,b,c)$.
	\end{itemize}

	For every two adjacent vertices $u, v$ compute the set $N(u, v)$ and list all such sets.
	For each relevant triple $(a,b,c)$ compute the set $X(a,b,c)$ and list all such sets.

	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
\end{algtext}

To proove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.

\begin{theorem}[9.1 of \cite{MC05}]
	\label{thm:91}
	Let $C$ be a shortest odd hole in $G$, with length at least 7. Then there is a relevant triple $(a, b, c)$ of vertices such that
	\begin{itemize}
		\item the set of all $C$-major vertices not in $X(a, b, c)$ is anticonnected
		\item $X(a, b, c) \cap V(C)$ is a subset of the vertex set of some 3-vertex path of $C$.
	\end{itemize}
\end{theorem}
\begin{proof}
	\TODO{do we want it here? 1-2 pages long}
\end{proof}

Let us suppose that $C$ is an amenable hole in $G$. By \cref{thm:91}, there is a relevant triple $(a, b, c)$ satisfying that theorem. Let $T$ be the set of all $C$-major vertices not in $X(a,b,c)$. From \cref{thm:91} we get that $T$ is anticonnected. Since $C$ is amenable, there is an edge $uv$ of $C$ that is $T$-complete, and therefore $T \subseteq N(u, v)$. But then $N(u, v) \cup X(a, b, c)$ is a near-cleaner for $C$. Therefore the output of the \cref{alg:listNearCleaners} is correct.

\begin{alg}[Test possible near clener, 5.1 of \cite{MC05}]
	\label{alg:testNearCleaner}
	Input: A graph $G$ containing no simple bad structure \todo{define this somewhere}, and a subset $X \subseteq V(G)$.

	\noindent Output: Determines one of the following:
	\begin{itemize}
		\item $G$ has an odd hole
		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
	\end{itemize}
\end{alg}
\begin{algtext}
	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$. If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.

	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
	\begin{itemize}
		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say)
		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
	\end{itemize}

	If there is such a choice of $x_1$, $x_2$, $x_3$, $y_1$ then we output that there is an odd hole. If not, we report that there is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
\end{algtext}

Below we will proove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one. The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.

\begin{proof}
	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying the three conditions in the \cref{alg:testNearCleaner} and let $y_2$ and $n$ be defined as in there. We claim that $G$ contains an odd hole.

	Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$. From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$. Also, from the definition of $y_1$, $y_1 \notin X$.
\end{proof}

### 2020-08-25 paper/perfectGraphs.tex
Near cleaner proof

@@
 
+\begin{wrapfigure}{r}{0.35\textwidth}
+	\input{tikzpictures/nearCleanerFound.tex}
+	\caption{An odd hole is found}%
+	\vspace{-0.5cm}
+\end{wrapfigure}
+
 Below we will proove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
@@
 Also, from the definition of $y_1$, $y_1 \notin X$.
+
+	Since $r(x_1, y_1) = r(x_2, y_1) - 1$ and since $x_1$, $x_2$ are nonadjacent it follows that $x_2$ does not belong to $R(x_1, y_1)$ and $x_1$ does not belong to $R(x_2, y_1)$.
+Since $r(x_3, y_1), r(x_3, y_2) \geq n (= r(x_1, y_2))$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
+Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.
+
+	We claim first that the insides of paths $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertices.
+For suppose that there are $2 \leq i \leq n-1$ and $2 \leq j \leq n$ that $p_i = q_j$.
+Then the subpaths of these two paths between $p_i$, $y_1$ are both subpaths of the shortest paths, and therefore have the same length, that is $j=i+1$.
+So $p_1-\ldots-p_1-q_{j+1}-\ldots-q_n$ contains a path between $x_1$, $y_2$ of length $\leq n-2$, contradicting that $r(x_1, y_2) = n$.
+So $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertex except $y_1$.
+
+	If there are no edges between $R(x_1, y_1) \setminus y_1$ and $R(x_2, y_1) \setminus y_1$ then the union of these two paths and a path $x_1-x_3-x_2$ form an odd hole, so the answer is correct.
+
+	Suppose that $p_iq_j$ is an edge for some $1\leq i \leq n-1$ and $1 \leq j \leq n$.
+We claim $i \geq j$.
+If $j = 1$ this is clear so let us assume $j > 1$.
+Then there is a path between $x_1$, $y_2$ within $\{p_1, \ldots , p_i, q_j, \ldots q_n\}$ which has length $\leq n-j+1$ and has no internal vertex in $X$ (since $j > 1$); and since $r(x_1, y_2) = n$, it follows that $n-j+i \geq n$, that is, $i \geq j$ as claimed.
+
+	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$.
+But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, that is $j \geq i$.
+So we get $i=j$.
+Let us choose $i$ minumum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
 \end{proof}

### 2020-08-25 paper/coloringBergeGraphs.tex
Coloring

\section{Coloring Perfect Graphs}

A natural problem for perfect graphs is a problem of coloring them. In 1988 Martin Grötschel et al. published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}. We consider it in section \cref{sec:ellipsoidMethod}. Hovewer due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.

There has been much progress on the quest of finding a more classical algorithm coloring perfect graphs, without the use of ellipsoid method (see \cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this. \todo{better wording of this paragraph}

\subsection{Ellipsoid method}
\label{sec:ellipsoidMethod}

\subsubsection{\Lovasz number}
\TODO{background, definition}

\begin{theorem}[\Lovasz "sandwich theorem"]
  For any graph $G$:
  $$ \omega(G) \leq \vartheta(\overline{G}) \leq \chi(G) $$
\end{theorem}

Because in perfect graphs $\omega(G) = \chi(G)$, we get $\omega(G) = \vartheta(G) = \chi(G)$.

\subsubsection{Computing \boldmath$\vartheta$}
\TODO{TODO}

\subsubsection{Maximum cardinality stable set}

\TODO{cite the paper on using theta to color.}

Given graph $G$, recall that stability number of $G$ is equal clique number of the complement of $G$. This gives us a way to compute $\alpha(G)$ for any perfect graph $G$.

In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$.

We will now show how to find a stable set in $G$ of size $\alpha(G)$.

\begin{alg}[maximum cardinality stable set in a perfect graph]
  \label{alg:maxStableSet}
  Input: A perfect graph $G = (V, E)$.

  \noindent Output: A maximum cardinality stable set in $G$.
\end{alg}
\begin{algtext}
  Let $v_1, \ldots v_n$ be an ordering of vertices of $G$. We will construct a sequence of induced subgraphs $G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_n$, so that $G_n$ is a required stable set.

  Let $G_0 \leftarrow G$. Then, for each $i \geq 1$, compute $\alpha(G_{i-1} \setminus v_i)$. If $\alpha(G_{i-1} \setminus v_i) = \alpha(G)$, then set $G_i \leftarrow G_{i-1} \setminus \{v_i\}$, else set $G_i \leftarrow G_{i-1}$.

  Return $G_n$.
\end{algtext}

Let us proove that $G_n$ is indeed a stable set. Suppose otherwise and let $v_iv_j$ be an edge in $G_n$ with $i < j$ and $i$ minimal. But then $\alpha(G_{i-1} \setminus v_i) = \alpha(G_{i-1}) = \alpha(G)$ so by our construction $v_i$ is not in $G_i$ and $v_iv_j$ is not an edge of $G_n$. Therefore there are no edges in $G_n$.

Because at every step we have $\alpha(G_i) = \alpha(G_{i-1})$, therefore $\alpha(G_n) = \alpha(G)$, so $G_n$ is required maximum cardinality stable set.

The running time of \cref{alg:maxStableSet} is polynomial, because we construct $n$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.

Given a weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ in the following manner. Create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ iff the nodes $v$, $u$ are adjacent in $G$. Then calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen. We will use this technique later on.

\subsubsection{Stable set intersecting all maximum cardinality cliques}
Next, let us show how to find a stable set intersecting all the maximum cardinality cliques of $G$.

\begin{alg}
  \label{alg:ssIntersectingCliques}
  Input: A perfect graph $G = (V, E)$.

  \noindent Output: A stable set which intersects all the maximum cardinality cliques of $G$.
\end{alg}
\begin{algtext}
  We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$.

  Let $Q_1 \leftarrow$ a maximum cardinality clique of $G$. We calculate this by running \cref{alg:maxStableSet} on $\overline{G}$.

  Now suppose $Q_1, \ldots, Q_t$ have been found. We show how to calculate $Q_{t+1}$ or see that we are done.

  Let us define a weight function $w : V \rightarrow \mathbb{N}$, so that for $v \in V$, $w(v)$ is equal to the number of cliques $Q_1, \ldots Q_t$ that contain $v$.

  Assign $S \leftarrow$ the maximum $w$-weighted stable set, as described in a remark to \cref{alg:maxStableSet}. It is easy to see that $S$ has weight $t$, which means that $S$ meets each of $Q_1, \ldots Q_t$.

  If $\omega(G \setminus S) < \omega(G)$, then $S$ meets all the maximum cardinality cliques in G so we return $S$. Otherwise we find a maximum cardinality clique in $G \setminus S$ (it will be of size $\omega(G)$, because $\omega(G \setminus S) = \omega(G)$), add it to our list as $Q_{t+1}$ and continue with longer list.

\end{algtext}

There are at most $|V|$ maximum cardinality cliques in $G$. Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(V^2)$ and running \cref{alg:maxStableSet} on it. Therefore total running time is polynomial.

\subsubsection{Minimum coloring}

\begin{alg}
  \label{alg:minColoring}
  Input: A perfect graph $G = (V, E)$.

  \noindent Output: A coloring of $G$ using $\chi(G)$ colors.
\end{alg}
\begin{algtext}
  If $G$ is equal to its maximum cardinality stable set, color all verces one color and return.

  Else find $S$ intersecting all maximum cardinality cliques of $G$ (\cref{alg:ssIntersectingCliques}). Color recursively all vertices of $G \setminus S$ with $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors and all vertices of $S$ with one additional color.
\end{algtext}

We will call recursion at most $O(|V|)$ times, each step of recursion is polynomial in time. Therefore the running time of \cref{alg:minColoring} is polynomial.

\subsection{Classical algorithms}
\label{sec:classicalColoring}

### 2020-08-26 paper/coloringBergeGraphs.tex
Ellipsoid method description heavy wip

@@
 \label{sec:ellipsoidMethod}
+
+\subsubsection{Background}
+
+\begin{wrapfigure}{r}{0.35\textwidth}
+  \label{fig:c5}
+	\input{tikzpictures/c5.tex}
+	\caption{Example noisy channel}%
+	% \vspace{-0.5cm}
+	% \end{floatingfigure}
+\end{wrapfigure}
+
+Let us first discuss the background in which perfect graphs first arose.
+Suppose we have a noisy communication channel in which certain signal values can be confused with others.
+For instance, suppose our channel has five discrete signal values, represented as 0, 1, 2, 3, 4.
+However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
+This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) with in which vertices correspond to signal values and two vertices are connected iff values they represent can be confused.
+
+We are interested in transission without possibility of confusion.
+In other words, we are interested in the Shannon capacity of the channel modeled by a graph \cite{Lovasz1979}.
+For this example it is possible for two values to be transmited without ambiguity e.g.
+values 1 and 4, which allows us to communicate $2^n$ bits of information in $n$ steps.
+But we could do better, for example we could communicate five two-step codewords e.g.
+"00", "12", "24", "43", "31".
+Each pair of these codewords includes at least one position where its values differ by two or more modulo 5, which allows the recipent to distinguish them without confusion.
+This allows us to send $5^{n / 2}$ bits of information in $n$ steps, or effectively send $(5^{n/2})^{1/n} = \sqrt{5}$ bits per step.
+
+Such methods provide a lower bound on the Shannon capacity of a graph
 

### 2020-08-26 paper/perfectGraphs.tex
Ellipsoid method description heavy wip

@@
 
+Perfect graphs are interesting not only because of their theoretical properties, but they are also used in other areas of study e.g.
+integrality of polyhedra \cite{Chvtal1975, Chudnovsky2003}, radio channel assignment problem \cite{McDiarmid99, McDiarmid2000} and appear in the theory of Shannon capacity of a graph \cite{Lovasz1979}.
+Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
+We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ellipsoidMethod}.
+
+\section{Strong Perfect Graph Theorem}
+\label{sec:SPGT}
+
 The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72}.
@@
 \end{theorem}
-
-\section{Strong Perfect Graph Theorem}
-\label{sec:SPGT}
 

### 2020-08-26 paper/coloringBergeGraphs.tex
Lovasz Theta number

@@
 
-\subsection{Ellipsoid method}
+\subsection{Information theory background}
 \label{sec:ellipsoidMethod}
 
-\subsubsection{Background}
+\subsubsection{Shannon Capacity of a graph}
+
+The polynomial technique of coloring perfect graphs known so far arose in the field of semidefinite programming.
+Semidefinite programs are linear programs over the cones of semi-definite matrice.
+The connection of coloring graphs and the cones of semi-definite matrices might be surprising, so let us take a brief digression into the field of information theory, where we will see the connection more clearly.
+Also, this is the background which motivated Berge to introduce perfect graphs \cite{Chudnovsky2003}.
 
@@
 	% \vspace{-0.5cm}
-	% \end{floatingfigure}
 \end{wrapfigure}
 
-Let us first discuss the background in which perfect graphs first arose.
 Suppose we have a noisy communication channel in which certain signal values can be confused with others.
@@
 
-We are interested in transission without possibility of confusion.
-In other words, we are interested in the Shannon capacity of the channel modeled by a graph \cite{Lovasz1979}.
+We are interested in transmission without possibility of confusion.
 For this example it is possible for two values to be transmited without ambiguity e.g.
-values 1 and 4, which allows us to communicate $2^n$ bits of information in $n$ steps.
+values 1 and 4, which allows us to send $2^n$ non-confoundable messages in $n$ steps.
 But we could do better, for example we could communicate five two-step codewords e.g.
@@
 Each pair of these codewords includes at least one position where its values differ by two or more modulo 5, which allows the recipent to distinguish them without confusion.
-This allows us to send $5^{n / 2}$ bits of information in $n$ steps, or effectively send $(5^{n/2})^{1/n} = \sqrt{5}$ bits per step.
+This allows us to send $5^{n / 2}$ non-confoundable messages in $n$ steps.
 
-Such methods provide a lower bound on the Shannon capacity of a graph
+Let us be more precise.
+Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in G(V)^k$ of lenght $k$ are non-confoundable iff there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
+We are interested in the maximum rate at which we can reliably transmit information (the \emph{Shannon capacity} of the channel defined by $G$) For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$.
+
+To describe longer messages we indroduce \emph{Strong Product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ iff $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
+Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ -- which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission.
+So, we can define the Shannon capacity of the channel defined by $G$ as $\Theta(G) = \sup\limits_k \sqrt[k]{\alpha(G^k)}$.
+
+Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs (polynomial or not).
+If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$.
+Let us now turn into search for some usable upper bound.
 
 \subsubsection{\Lovasz number}
-\TODO{background, definition}
+
+The following introduction of what has become known as \emph{\Lovasz number} is based on excellent lecture notes by \Lovasz \cite{Lovasz95}. \todo{rewrite this so its not blatantly copied.}
+
+For a channel defined by graph $C_5$ using five messages of length 2 gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\alpha(C_5^2)$).
+
+Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length \todo{picture}.
+Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90°.
+This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
+We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.
+
+It turns out, that we can obtain a similar representation of the nodes of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^3k$, so that any two non-adjacent nodes are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}).
+Moreover, we still get $e_1^\intercal v_i = 5^{-k/4}$ for every $i \in V(C_5^k)$ (the proof is quite technical and we omit it here).
+
+If $S$ is any stable set in $C_5^k$, then $\{v_i, i \in S\}$ is a set of mutually orthogonal unit vectors so we get 
+$$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq |e_1|^2 = 1$$ 
+(if $v_i$ formed a basis then this inequality would be an equality).
+
+On the other hand each term on the left hand side is $5^{-1/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
+Thus we get $\alpha(C_5^k) \leq 5 ^{k/2}$ and $\Theta(C_5) = \sqrt{5}$.
+
+This method extends to any graph $G$ in place of $C_5$.
+All we have to do is find a orthogonal representation that will give us the best bound.
+So, we can define the \emph{\Lovasz number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
+$$\vartheta(G) = \min\limits_{c,U} \max\limits_{i\in V} \frac{1}{(c^\intercal u_i)^2},$$
+
+where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is a orthogonal representation of $G$.
+But how can we construct an optimum (or even good) orthogonal representation?
+It turns out that it can be computed in polynomial time using semidefinite optimization.
+
+\subsection{Computing \boldmath$\vartheta$}
+
+\TODO{TODO}
+
+\subsection{Coloring perfect graph using ellipsoid method}
 
@@
 
-\subsubsection{Computing \boldmath$\vartheta$}
 \TODO{TODO}
@@
 Next, let us show how to find a stable set intersecting all the maximum cardinality cliques of $G$. 
-
 \begin{alg}

### 2020-08-26 paper/definitions.tex
Amenable holes wip
Coloring
Lovasz Theta number

@@
+\TODO{Run proofreader on all text (temporarily disabled because it slowed down IDE)}
+
 We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.
@@
 If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring.
+By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge.
 If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.
@@
 
+\begin{defn}[clique number]
+  A \emph{clique number} of a graph $G$, denoted as $\omega(G)$, is a cardinality of its largest induced clique.
+\end{defn}
+
 \begin{defn}[anticlique]
@@
 
-\begin{defn}[clique number]
-  A \emph{clique number} of a graph $G$, denoted as $\omega(G)$, is a cardinality of its largest induced clique.
+\begin{defn}[stability number]
+  A \emph{stability number} of a graph $G$, denoted as $\alpha(G)$, is a cardinality of its largest induced stable set.
 \end{defn}

### 2020-08-27 paper/coloringBergeGraphs.tex
Minor fixes

@@
 We consider it in section \cref{sec:ellipsoidMethod}.
-Hovewer due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
+However due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
 
@@
 The polynomial technique of coloring perfect graphs known so far arose in the field of semidefinite programming.
-Semidefinite programs are linear programs over the cones of semi-definite matrice.
+Semidefinite programs are linear programs over the cones of semi-definite matrices.
 The connection of coloring graphs and the cones of semi-definite matrices might be surprising, so let us take a brief digression into the field of information theory, where we will see the connection more clearly.
@@
 However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
-This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) with in which vertices correspond to signal values and two vertices are connected iff values they represent can be confused.
+This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected iff values they represent can be confused.
 
 We are interested in transmission without possibility of confusion.
-For this example it is possible for two values to be transmited without ambiguity e.g.
+For this example it is possible for two values to be transmitted without ambiguity e.g.
 values 1 and 4, which allows us to send $2^n$ non-confoundable messages in $n$ steps.
@@
 "00", "12", "24", "43", "31".
-Each pair of these codewords includes at least one position where its values differ by two or more modulo 5, which allows the recipent to distinguish them without confusion.
+Each pair of these codewords includes at least one position where its values differ by two or more modulo 5, which allows the recipient to distinguish them without confusion.
 This allows us to send $5^{n / 2}$ non-confoundable messages in $n$ steps.
@@
 Let us be more precise.
-Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in G(V)^k$ of lenght $k$ are non-confoundable iff there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
-We are interested in the maximum rate at which we can reliably transmit information (the \emph{Shannon capacity} of the channel defined by $G$) For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$.
+Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in G(V)^k$ of length $k$ are non-confoundable iff there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
+We are interested in the maximum rate at which we can reliably transmit information (the \emph{Shannon capacity} of the channel defined by $G$).
 
-To describe longer messages we indroduce \emph{Strong Product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ iff $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
+For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$.
+To describe longer messages we use \emph{Strong Product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ iff $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
 Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ -- which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission.
@@
 
-If $S$ is any stable set in $C_5^k$, then $\{v_i, i \in S\}$ is a set of mutually orthogonal unit vectors so we get 
+If $S$ is any stable set in $C_5^k$, then $\{v_i, i \in S\}$ is a set of mutually orthogonal unit vectors so we get \todo{why?}
 $$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq |e_1|^2 = 1$$ 
@@
 where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is a orthogonal representation of $G$.
-But how can we construct an optimum (or even good) orthogonal representation?
-It turns out that it can be computed in polynomial time using semidefinite optimization.
+
+Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on Shannon capacity of the graph.
+However, these two equal in some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" \cref{thm:sandwich}.
+
+But how can we construct an optimum (or even good) orthogonal representation? It turns out that it can be computed in polynomial time using semidefinite optimization.
 
@@
 
-\subsection{Coloring perfect graph using ellipsoid method}
-
 \begin{theorem}[\Lovasz "sandwich theorem"]
+  \label{thm:sandwich}
   For any graph $G$:
@@
 
+\subsection{Coloring perfect graph using ellipsoid method}
 \subsubsection{Maximum cardinality stable set}
@@
 
-Let us proove that $G_n$ is indeed a stable set.
+Let us prove that $G_n$ is indeed a stable set.
 Suppose otherwise and let $v_iv_j$ be an edge in $G_n$ with $i < j$ and $i$ minimal.
@@
 \begin{algtext}
-  If $G$ is equal to its maximum cardinality stable set, color all verces one color and return.
+  If $G$ is equal to its maximum cardinality stable set, color all vertices one color and return.
 

### 2020-08-27 paper/definitions.tex
Minor fixes

@@
 \begin{defn}[near-cleaner]
-  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vectices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
 \end{defn}
@@
 \begin{defn}[amenable odd hole]
-  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vectices there is a $X$-complete edge in $C$.
+  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
 \end{defn}

### 2020-09-01 paper/perfectGraphs.tex

@@
 
-To proove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.
+To prove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.
 
@@
 
-Below we will proove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
+Below we will prove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
 The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.
@@
 So we get $i=j$.
-Let us choose $i$ minumum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
+Let us choose $i$ minimum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
 \end{proof}
+
+\subsection{Summary}
+
+\TODO{todo?}

### 2020-09-01 paper/tikzpictures/nearCleanerFound.tex

\centering\begin{tikzpicture}[scale=0.7,simplegraph]
  \node(x1) at (0,0) {$x_1$};
  \node(x3) at (1.5,0) {$x_3$};
  \node(x2) at (3,0) {$x_2$};

  \node (y1) at (.6, 3) {$y_1$};
  \node (y2) at (2.4, 3) {$y_2$};

  \draw (x1) to (x3);
  \draw (x2) to (x3);

  \tikzset{decoration={snake,amplitude=.6mm,segment length=4mm,
        post length=0mm,pre length=0mm}}
  \draw[decorate, color=c1] (x1) to (y1);
  \draw[decorate, color=c2] (x2) to (y2);
  \draw[color=c2] (y1) to (y2);

  \node[draw=none, color=c2] at (3.8, 2.5) {$R(x_2, y_1)$};
  \node[draw=none, color=c1] at (1.4, 1.5) {\small$R(x_1, y_1)$};

  \node[draw=none, minimum size=4mm](inx1) at (.8, -1.1){};
  \node[draw=none, minimum size=4mm](inx2) at (2.2, -1.1){};
  \node[draw,inner sep=3pt, circle,yscale=.5, fit={(inx1) (inx2)},label=below:{$X$}] {};
  \node[draw,dotted,inner sep=5pt, circle,yscale=.5, fit={(inx1) (inx2) (x3) (x1) (x2)}] {};

  % \draw[dashed] (x1) to (x2);
  % \draw(v1) to (x1);
  % \draw(v2) to (x1);
  % \draw(v4) to (x1);
  % \draw(v1) to (x2);
  % \draw(v2) to (x2);
  % \draw(v4) to (x2);

  % \draw (a) to (b2);
\end{tikzpicture}%

### 2020-09-01 paper/implementation.tex
Implementation WIP

\TODO{link to repo}

\section{Berge graphs recognition}

The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case. Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\cref{sec:Optimizations}) make a very big difference and make it usable -- or at least much more usable than na\"ive algorithm could be. Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with good results (\cref{sec:CUDA}).

\TODO{Anything interesting about algo/data structure?}

\subsection{Optimizations}
\label{sec:Optimizations}

When implementing a complicated algorithm that has a time complexity of $O(n^9)$ optimizations can be both crucial and difficult to implement. There is not a single code path that takes up all the running time -- or at lest there isn't one from theoretical point of view. Therefore a tool for inspecting running time bottlenecks is needed. We used Valgrind's tool called \emph{callgrind} \cite{callgrind}.

Callgrind is a profiling tool that records the call history of a program and presents it as a call-graph. When profiling a program, event counts (data reads, cache misses etc.) are attributed directly to the function that they occurred in. In addition to that, the costs are propagated to functions upwards the call stack. For example, say internal function $worker$ consumes most of programs running time. It is called from $run1$ and $run2$, with $run2$ calls taking twice as much time. $run1$ and $run2$ are in turn called from main. Total attribution of $worker$ would be nearly 100\%, of $run1$ about 33\% and of $run2$ about 66\%. The contribution of main would also be near 100\%. We used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.

\TODO{example of a call graph?}

\TODO{callgrind}
\TODO{first result to best result gains (like: we are 20x faster than what first comes to mind)}
\TODO{regenerate speedup results to make sure what the gains were}

\subsubsection{Generating paths}

\TODO{we also optimize na\"ive, in fact it makes a bigger difference there.}
A major part of Berge recognition algorithm is spent on enumerating all possible paths of given length -- this is done either to find a hole by itself, find a simple structure or check a possible near cleaner for amenable odd hole. Therefore a quick method for generating paths, a problem that could seem trivial at first, is a crucial part to optimize and we give it much attention.

First of all, there are many methods for generating all possible paths to choose from. We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no chords), but this would be too slow and render our algorithm unusable.

We notice that nowhere in the algorithm we need all the paths at once. It would suffice for us to have a path, check if it has the properties we further require of it and then proceed to generate next path (in some ordering of paths). Therefore, we need a method that receives a path on the input (or a special flag indicating it should generate first path) and returns next path in some order (or a first path, or a code signaling all paths have been generated). As this method will be used many, many times we require of it to work in place with constant additional space.

With those requirements defined a simplest algorithm would be to implement a sort of a "counter" with base of $|V(G)|$. In short: we take a path on a input, increment its last vertex until it is a neighbor of one before last vertex. Then we check if generated sequence is a path (all vertices unique and no chords). If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process. If still no path is found, we increment vertices closer to beginning of the path, until all a path is found or we check all candidates.

This method is significantly faster than simply enumerating all combinations, but still leaves a problem of generating paths a main bottleneck of our algorithm (in our preliminary test it took about 70\% of running time for graphs with $|V(G)| = 10$ and growing with bigger graphs.

But we can do much better with some care and better data structure. For a given graph we create a data structure that suits best the goal of generating paths. Instead of having for each vertex a list of its neighbors we create data structure that will allow us to generate a candidate for next path in amortized $O(1)$ time.

We have an array $first$ in which for each vertex is written its first neighbor on its neighbors list, and an array $next$ of size $|V(G)|^2$ where for each pair of vertices $a, b$ if $a$ and $b$ are connected, there is written a neighbor of $a$ that is next after $b$ in a neighbors list of $a$ (or a flag indicating $b$ is $a$'s last neighbor). Then, say our input is a path $v = v_1, \ldots v_k$. If $next[v_{k-1}][v_k]$ exists we change $v_k$ to $next[v_{k-1}][v_k]$ and return $v$. If it indicated that $v_k$ is $v_{k-1}$'s last neighbor, we set $v_{k-1}$ to $next[v_{k-2}][v_{k-1}]$ and then $v_k$ to $first[v_{k-1}]$ (or we go further back, if all neighbors of $v_{k-2}$ are done).

This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of 20x\todo{check this}, with much bigger speedup for na\"ive algorithm (around TODOx).

\paragraph{Array unique}

For each path candidate we call a subroutine to determine whether all vertices in it are unique. As this subroutine could be called many times for generating a single path, its optimization is very important.

A theoretically optimal solution in general would be to have a hashing set of vertices. For each vertex in a path candidate, we check if it is already in a set. If it is, return that not all vertices are unique, else add it to the set.

In our use case, a few optimizations can be made. First, we don't need a hashing set. We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there. Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this. Second, we notice that we don't need to create this array for each call of $unique$ procedure. Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called $unique$ method. For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique. Else we set $stamp[v_i] = counter$. When returning from the $unique$ method we increment $counter$.

This optimization alone is crucial for performance. In our testing, all calls of $unique$ took abour 70\% of total running time of the algorithm. After using static $stamp$ array, it fell to 5.2\%. The overall speedup of the algorithm was about 6x. \todo{check if for sure it didn't use path speedup} The speedup of na\"ive algorithm was even greater -- about 20x.

\paragraph{Other uses for path generation}
\label{sec:usesGeneration}

Because of a good performance of our optimized algorithm for generating paths use it whenever possible. It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the algorithm. For example, when searching for Jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a Jewel. This proved to be much faster than generating vertices that don't have forbidden chords one by one. We use the same algorithm for generating starting vertices for a possible $T_2$ and $T_3$.

\subsection{Correctness Testing}

\subsubsection{Unit tests}

In an algorithm this complex, debugging can be difficult and time consuming, so we used extensive unit testing and principles of test driven development to make sure that the program results are correct.

Whole algorithm was divided into subroutines used in many places. One of such subroutines is a path generation algorithm described above (\cref{sec:usesGeneration}). There are many other generalized methods we implemented: checking if a set of vertices is $X$-complete, getting a set of components of a graph, creating a induced graph or finding a shortest path, such that each internal vertex satisfies a predicate. Each of those and many more methods have unit tests that check their general use and edge cases. This allowed us to debug very effectively and have complex algorithms be simple to analyze.

In addition to correctness checking, extensive unit test suite allowed us to optimize our algorithm and test different subroutines with ease, without fear of introducing bugs.

\subsubsection{End to end tests}

In addition to unit tests, we employ a range of end to end tests, that check the final answer of the algorithm. We compare answer to the na\"ive algorithm's answer and also to the result of the algorithm on CUDA (\cref{sec:CUDA}).

Also, we test the algorithm on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof. In addition to that, a test on all perfect graphs up to a size of 10\todo{update to 11?} was performed -- we used \cite{graphRepo} as a source of perfect graphs.

We also test on graphs that we know are not perfect: we generate them by generating an odd hole and adding it with some edges to a random graph.

In total over 100 \todo{update the munber}cpu-hours of end to end tests were performed without any errors.

\subsection{Parallelism with CUDA (?)}
\label{sec:CUDA}

\TODO{a section?}
\TODO{CUDA background}
\TODO{moderngpu - allows us to run simple transforms}

We posed a question if it would be profitable to use GPU for this problem. On one hand the graphs we are working on are small and our time complexity so large that a speedup from massively parallel architecture could be profitable. On the other the algorithm is complex and not easy to parallelise. Therefore we decided to implement whole na\"ive algorithm and most time consuming parts of the CCLSV\todo{a good name for it?} algorithm.

\subsubsection{Na\"ive parallelisation}

Na\"ive algorithm is very simple -- generate all possible odd hole candidates, check if any of them is an odd hole and repeat for the complement. But its parallelisation is not trivial.

The biggest problem of implementing na\"ive algorithm is in splitting the work between CUDA threads. This is very important because while GPU is faster when all its cores are working efficiently, single core performance is much slower than CPU. But it is not obvious how to split the work.

Our first attempt was to switch our slightly more sophisticated way of generating paths (\cref{sec:usesGeneration}) in favor of generating all combinations. We could code a prefix of a combination as a number (we use combinations with repetitions for simplicity). This would give us $|V(G)|^k$ codes for all prefixes of length $k$. Then each CUDA thread would process its part of all codes: for each code it would first check if the encoded prefix is a valid path and then generate all path candidates with that prefix. This approach has two problems: it doesn't split the work evenly enough and it does too much unneeded work (only a few prefix codes are valid). Still, implementing it on GPU gives us a program with speeds comparable to na\"ive CPU algorithm after all optimizations.

A better approach is to generate all paths of some length $k$ on CPU (using algorithm described in \cref{sec:usesGeneration}), copy them on GPU and have each thread process them as described above. This is superior to the previous algorithm in utilizing GPU -- each prefix takes similar time to process. We also even out the work done by each thread by having single thread process multiple prefixes. But it puts much more strain on the CPU -- it has to generate all valid prefixes. Here we used experiments to determine best value of $k$ (it was 7 for graphs of $n < 15$ \todo{check} and 6 for larger). This yields an algorithm that beats CPU na\"ive by a factor of 50x. \todo{check}.

\subsubsection{CCLSV parallelisation}

To identify parts of CCLSV to implement, we used callgrind and found potential bottlenecks. The initial tests showed that with growing size of a graph some parts take more and more relative time. Because of callgrind's slow execution times compared to just running the program, we used manual timers for bigger tests. Using this method we identified testing all possible near-cleaners (\cref{alg:testNearCleaner}) as the biggest bottleneck for larger graphs. We considered two approaches: run whole \cref{alg:testNearCleaner} on a single CUDA core, testing multiple $X$s in parallel, or parallelize \cref{alg:testNearCleaner} itself and run it on one $X$ at a time. It turned out that second approach is better and much simpler.

Let us recall the \cref{alg:testNearCleaner}. It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole. We will parallelise the work after calculating $R$. Let us notice, that for all $X$s all 3-vertex paths are the same. We calculate them beforehand \todo{do it also in CPU} \todo{acutally do this}. Then each thread receives a 3-vertex path and an additional vertex and performs the required checks. This is almost perfect scenario for GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.

It turns out that this optimization alone speeds up \cref{alg:testNearCleaner} almost 30x \todo{check} on bigger tests, which gives us a speedup of about 5x \todo{check} for overall algorithm.

\TODO{implement other CUDA opts and describe them}

\subsection{Experiments}

Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\

Description of tests used.\\

Results and Corollary - almost usable algorithm.

\section{Coloring Berge Graphs}

\subsection{Ellipsoid method}

Description.\\

Implementation.\\

Experiments and results.\\

\subsection{Combinatorial Method}

Cite the paper.\\

On its complexity - point to appendix for pseudo-code.

### 2020-09-01 paper/main.tex
Implementation WIP

@@
 \input{perfectGraphs.tex}
+\input{coloringBergeGraphs.tex}
 
-\chapter{Recognizing Berge Graphs}
-
-\section{Implementation}
-
-Anything interesting about algo/data structure?\\
-
-\subsection{Optimizations}\label{Optimizations}
-Bottlenecks in performance (next path, are vectors distinct etc).\\
-\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
-\TODO{We used callgrind to get idea of methods crucial for time.}
-\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
-\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
-\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth vertex to complete the hole - much faster than iterating vertices.}
-
-Validity tests - unit tests, tests of bigger parts, testing vs known answer and vs naive.
-
-\section{Parallelism with CUDA (?)}
-
-TODO
-
-\section{Experiments}
-
-Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\
-
-Description of tests used.\\
-
-Results and Corollary - almost usable algorithm.
-
-\chapter{Coloring Berge Graphs}
-
-\section{Ellipsoid method}
-
-Description.\\
-
-Implementation.\\
-
-Experiments and results.\\
-
-\section{Combinatorial Method}
-
-Cite the paper.\\
-
-On its complexity - point to appendix for pseudo-code.
+\chapter{Implementation}
+\input{implementation.tex}
 

### 2020-09-02 code/src/testCommons.cpp
Plots heavy WIP

@@ -171,7 +171,7 @@ double RaiiTimer::getElapsedSeconds() {
 map<tuple<algos, bool, int>, double> sumTime;
 // map<pair<int, bool>, double> sumClockTime;
 map<tuple<algos, bool, int>, int> casesTested;
-string algo_names[] = {"Perfect     ", "Naive       ", "CUDA Naive  ", "Cuda Perfect"};
+string algo_names[] = {"Perfect", "Naive", "CUDA Naive", "Cuda Perfect"};
 
 // map<pair<int, bool>, double> sumTimeNaive;
 // map<pair<int, bool>, double> sumClockTimeNaive;

### 2020-09-02 code/test/cuPerfTest/cuPerfectNaive.cu

@@ -28,8 +28,6 @@ int main() {
   random_shuffle(Gs.begin(), Gs.end());
 
   {
-    cout << "N=" << n << endl;
-
     RaiiProgressBar bar(Gs.size());
 
     for (int i = 0; i < Gs.size(); i++) {

### 2020-09-02 code/test/cuPerfTest/naive.cpp

@@ -26,8 +26,6 @@ int main() {
   random_shuffle(Gs.begin(), Gs.end());
 
   {
-    cout << "N=" << n << endl;
-
     RaiiProgressBar bar(Gs.size());
 
     for (int i = 0; i < Gs.size(); i++) {

### 2020-09-02 code/test/cuPerfTest/run.sh

@@ -23,25 +23,25 @@ benchTests=(
   "bench.t.in"
 )
 
-for file in "${benchTests[@]}"; do
-  echo "Running CuPerfect on $file"
-  $cuPerfectExec <$testsDir/$file >$resultsDir/$file.cuPerfect.out.csv
-done
-
-# for file in "${perfectTests[@]}"; do
-#   echo "Running Perfect on $file"
-#   $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out.csv
-# done
-
-# for file in "${perfectTests[@]}"; do
+# for file in "${benchTests[@]}"; do
 #   echo "Running CuPerfect on $file"
 #   $cuPerfectExec <$testsDir/$file >$resultsDir/$file.cuPerfect.out.csv
 # done
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running CuPerfectNaive on $file"
-#   $cuPerfectNaiveExec <$testsDir/$file >$resultsDir/$file.cuPerfectNaive.out.csv
-# done
+for file in "${perfectTests[@]}"; do
+  echo "Running Perfect on $file"
+  $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out.csv
+done
+
+for file in "${perfectTests[@]}"; do
+  echo "Running CuPerfect on $file"
+  $cuPerfectExec <$testsDir/$file >$resultsDir/$file.cuPerfect.out.csv
+done
+
+for file in "${perfectTests[@]}"; do
+  echo "Running CuPerfectNaive on $file"
+  $cuPerfectNaiveExec <$testsDir/$file >$resultsDir/$file.cuPerfectNaive.out.csv
+done
 
 
 # for file in "${naiveTests[@]}"; do

### 2020-09-02 code/test/plot.py

@@ -1,0 +1,487 @@
+# coding: utf-8
+
+# usePgf = True
+usePgf = False
+
+import matplotlib as mpl
+if usePgf:
+    mpl.use('pgf')
+else:
+    mpl.use('Agg')
+
+
+from cycler import cycler
+import re
+import io
+import os
+import sys
+import csv
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter
+import matplotlib.ticker as ticker
+import matplotlib.patches as patches
+import numpy as np
+
+plt.rcParams.update({'pgf.texsystem': 'pdflatex', 'font.family': 'serif', 'pgf.rcfonts': False, })
+
+csv_N = 'n'
+csv_result = 'result'
+csv_algo = 'algorithm'
+csv_overall = 'Overall'
+csv_numRuns = 'num_runs'
+csv_simpleStructures = 'Simple Structures'
+csv_getNearCleaners = 'Get Near Cleaners'
+csv_testNCShortestPaths = 'Test NC Shortest Paths'
+csv_gpuCopyR = 'GPU Test NC Copy R'
+csv_gpuWork = 'GPU Test NC work'
+csv_testNCRest = 'Test NC Rest'
+
+
+csv_ints = []
+csv_ints.extend([csv_N, csv_result, csv_numRuns])
+csv_floats = []
+csv_floats.extend([csv_overall, csv_simpleStructures, csv_getNearCleaners, csv_testNCShortestPaths, csv_gpuCopyR, csv_gpuWork, csv_testNCRest])
+
+csv_detailed_fields = [csv_simpleStructures, csv_getNearCleaners, csv_testNCShortestPaths, csv_gpuCopyR, csv_gpuWork, csv_testNCRest]
+
+# csv_detailed_fields = [csv_BFS, csv_spanning_tree,
+#                        csv_list_rank, csv_distance_parent, csv_find_bridges, csv_naive_bridges]
+
+hatches = ['++', '**', 'oo', '----', '||', '..']
+algo_colors = {"Cuda Perfect": "#377eb8", "Perfect": "#ff7f00"}
+algo_markers = {"Cuda Perfect": ".", "Perfect": "x"}
+
+algo_labels = {"Cuda Perfect": "GPU Perfect", "Perfect": "Perfect",
+#  "naive": u"GPU Naïve", "CPU Inlabel": "CPU Inlabel",
[…]

### 2020-09-02 code/inc/commons.h
Serious opt naive

@@ -73,6 +73,8 @@ struct Graph {
   Graph getShuffled() const;
   Graph getLineGraph() const;
 
+  void printOut() const;
+
   friend class CuGraph;
 
  private:
@@ -148,8 +150,12 @@ void nextTupleInPlace(vec<int> &v, int max);
 
 // Returns whether v is a path in G. A path must have all vertices distinct, and edges only between neighbors.
 // If isCycleOk a cycle is also considered a path e.g. [1,2,3,4] if 1-4 is an edge
-bool isAPath(const Graph &G, const vec<int> &v, bool isCycleOk = false, bool areChordsOk = false);
+bool isAPath(const Graph &G, const vec<int> &v, bool isCycleOk = false, bool areChordsOk = false,
+             bool holeRequired = false);
+
+bool isHole(const Graph &G, const vec<int> &v);
 
 // Returns (in &v) next path of length len in G (in some order). If v is empty returns first path. If v is
 // the last path returns empty vec. Iterating from empty vector to empty vector gives all paths of length len.
-void nextPathInPlace(const Graph &G, vec<int> &v, int len, bool isCycleOk = false, bool areChordsOk = false);
+void nextPathInPlace(const Graph &G, vec<int> &v, int len, bool isCycleOk = false, bool areChordsOk = false,
+                     bool holeRequired = false);

### 2020-09-02 code/inc/oddHoles.h

@@ -3,7 +3,6 @@
 #include <tuple>
 #include "commons.h"
 
-bool isHole(const Graph &G, const vec<int> &v);
 // Checks whether graph contains hole of the given size. If not, empty vector is returned.
 vec<int> findHoleOfSize(const Graph &G, int size);
 bool constainsHoleOfSize(const Graph &G, int size);

### 2020-09-02 code/inc/testCommons.h

@@ -23,8 +23,8 @@ using std::map;
 using namespace std::chrono;
 
 // Whether to run big tests. These take more time.
-const bool bigTests = false;  // TODO(Adrian) make bigTests big again (perf)
-// const bool bigTests = true;
+// const bool bigTests = false;  // TODO(Adrian) make bigTests big again (perf)
+const bool bigTests = true;
 const int _max_threads_to_run = 10000;
 
 bool probTrue(double p);

### 2020-09-02 code/src/commons.cpp

@@ -403,6 +403,19 @@ vec<vec<int>> generateTuples(int size, int max) {
   return ret;
 }
 
+void Graph::printOut() const {
+  cout << n << endl;
+  for (int i = 0; i < n; i++) {
+    for (int j = 0; j < n; j++) {
+      if (areNeighbours(i, j))
+        cout << "X";
+      else
+        cout << ".";
+    }
+    cout << endl;
+  }
+}
+
 ostream &operator<<(ostream &os, Graph const &G) {
   cout << G.n << endl;
   for (int i = 0; i < G.n; i++) {
@@ -507,10 +520,16 @@ vec<vec<vec<int>>> allShortestPathsWithPredicate(const Graph &G, function<bool(i
   return R;
 }
 
-bool isAPath(const Graph &G, const vec<int> &v, bool isCycleOk, bool areChordsOk) {
+bool isAPath(const Graph &G, const vec<int> &v, bool isCycleOk, bool areChordsOk, bool holeRequired) {
+  if (holeRequired && !isCycleOk) {
+    throw invalid_argument("Hole required but cycle not allowed!");
+  }
+
   if (v.size() <= 1) return false;
 
   if (!isDistinctValues(v)) return false;
+
+  if (holeRequired && (v.size() <= 3 || !G.areNeighbours(v[0], v.back()))) return false;
 
   for (int i = v.size() - 1; i > 0; i--) {
     for (int j = 0; j < i; j++) {
@@ -525,6 +544,8 @@ bool isAPath(const Graph &G, const vec<int> &v, bool isCycleOk, bool areChordsOk
 
   return true;
 }
+
+bool isHole(const Graph &G, const vec<int> &v) { return isAPath(G, v, true, false, true); }
 
 vec<int> getFirstPath(const Graph &G, int len, bool isCycleOk) {
   vec<int> ret;
@@ -545,7 +566,8 @@ vec<int> getFirstPath(const Graph &G, int len, bool isCycleOk) {
   return ret;
 }
 
-void nextPathInPlaceInternal(const Graph &G, vec<int> &v, int len, bool isCycleOk, bool areChordsOk) {
+void nextPathInPlaceInternal(const Graph &G, vec<int> &v, int len, bool isCycleOk, bool areChordsOk,
+                             bool holeRequired) {
   while (true) {
     if (v.back() == -1) {
       v.pop_back();
[…]

### 2020-09-02 code/src/oddHoles.cpp

@@ -7,16 +7,12 @@
 using std::get;
 using std::to_string;
 
-bool isHole(const Graph &G, const vec<int> &v) {
-  return v.size() >= 3 && isAPath(G, v, true, false) && G.areNeighbours(v[0], v.back());
-}
-
 vec<int> findHoleOfSize(const Graph &G, int size) {
   if (size <= 3) return vec<int>();
 
   vec<int> v;
   while (true) {
-    nextPathInPlace(G, v, size, true);
+    nextPathInPlace(G, v, size, true, false, true);
     if (v.size() == size && isHole(G, v)) return v;
 
     if (v.empty()) break;

### 2020-09-02 code/test/cuPerfTest/generate.cpp

@@ -1,26 +1,0 @@
-#include <ctime>
-#include <map>
-#include <random>
-#include "commons.h"
-#include "oddHoles.h"
-#include "perfect.h"
-#include "testCommons.h"
-
-int main() {
-  srand(time(0));
-
-  for (int k = 0; k < 5; k++) {
-    double p = getDistr();
-    Graph G(0);
-    int counter = 0;
-    do {
-      G = getRandomGraph(20, p);
-      counter++;
-      if (counter % 100000 == 0) {
-        p = getDistr();
-      }
-    } while (!isPerfectGraph(G, false));
-
-    cout << G << endl;
-  }
-}

### 2020-09-02 code/test/cuPerfTest/run.sh

@@ -11,12 +11,14 @@ cuPerfectExec="$scriptDir/../../obj/test/cuPerfTest/cuPerfect.e"
 naiveExec="$scriptDir/../../obj/test/cuPerfTest/naive.e"
 
 perfectTests=(
-  "perf.t.in"
+  "perf2.t.in"
+  # "perf.t.in"
   # "perfSmaller.t.in"
 )
 
 naiveTests=(
-  "naive.t.in"
+  # "naive.t.in"
+  "perfSmaller.t.in"
 )
 
 benchTests=(
@@ -28,28 +30,28 @@ benchTests=(
 #   $cuPerfectExec <$testsDir/$file >$resultsDir/$file.cuPerfect.out.csv
 # done
 
-for file in "${perfectTests[@]}"; do
-  echo "Running Perfect on $file"
-  $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running Perfect on $file"
+#   $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+# done
 
-for file in "${perfectTests[@]}"; do
-  echo "Running CuPerfect on $file"
-  $cuPerfectExec <$testsDir/$file >$resultsDir/$file.cuPerfect.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running CuPerfect on $file"
+#   $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+# done
 
-for file in "${perfectTests[@]}"; do
-  echo "Running CuPerfectNaive on $file"
-  $cuPerfectNaiveExec <$testsDir/$file >$resultsDir/$file.cuPerfectNaive.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running CuPerfectNaive on $file"
+#   $cuPerfectNaiveExec <$testsDir/$file >>$resultsDir/$file.out.csv
+# done
 
 
 # for file in "${naiveTests[@]}"; do
 #   echo "Running CuPerfect on $file"
-#   $cuPerfectNaiveExec <$testsDir/$file >$resultsDir/$file.cuPerfectNaive.out.csv
+#   $cuPerfectNaiveExec <$testsDir/$file >$resultsDir/$file.out.csv
 # done
 
-# for file in "${naiveTests[@]}"; do
-#   echo "Running Naive on $file"
[…]

### 2020-09-02 code/test/generate/generate.cpp

@@ -1,0 +1,28 @@
+#include <ctime>
+#include <map>
+#include <random>
+#include "commons.h"
+#include "oddHoles.h"
+#include "perfect.h"
+#include "testCommons.h"
+
+int main() {
+  srand(time(0));
+
+  int minN = 10;
+  int maxN = 19;
+
+  for (int i = 0; i < 10; i++) {
+    set<int> done;
+
+    while (done.size() < maxN - minN + 1) {
+      Graph G = getBipariteGraph(8 + getDistr() * 3, getDistr()).getLineGraph();
+      if (rand() % 2) G = G.getComplement();
+
+      if (G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+        G.printOut();
+        done.insert(G.n);
+      }
+    }
+  }
+}

### 2020-09-02 code/test/permaTest/perfect.cu

@@ -10,18 +10,18 @@
 
 void testPerfectVsCuNaiveVsCuda() {
   Graph G = getRandomGraph(14 + getDistr() * 10, getDistrWide());
-  testGraph(G, {algoPerfect, algoCudaNaive, algoCudaPerfect}, {nullptr, cuIsPerfectNaive, cuIsPerfect});
+  testGraph(G, {algoPerfect, algoCudaNaive, algoCudaPerfect, algoNaive}, {nullptr, cuIsPerfectNaive, cuIsPerfect});
 }
 
 void testPerfectVsCuda() {
   Graph G = getRandomGraph(14 + getDistrWide() * 15, getDistrWide());
-  testGraph(G, {algoPerfect, algoCudaPerfect}, {nullptr, cuIsPerfect});
+  testGraph(G, {algoPerfect, algoCudaPerfect, algoNaive}, {nullptr, cuIsPerfect});
 }
 
 void testPerfectVsCudaLine() {
   Graph G = getBipariteGraph(11 + getDistrWide() * 3, getDistrWide()).getLineGraph();
   cerr << G.n << endl;
-  testGraph(G, {algoPerfect, algoCudaPerfect}, {nullptr, cuIsPerfect});
+  testGraph(G, {algoPerfect, algoCudaPerfect, algoNaive}, {nullptr, cuIsPerfect});
 }
 
 // void testLineBiparite() {

### 2020-09-02 code/test/plot.py

@@ -35,6 +35,8 @@ csv_testNCShortestPaths = 'Test NC Shortest Paths'
 csv_gpuCopyR = 'GPU Test NC Copy R'
 csv_gpuWork = 'GPU Test NC work'
 csv_testNCRest = 'Test NC Rest'
+csv_cpuPreparation = 'CPU Preparation'
+csv_gpuCalculation = 'GPU Calculation'
 
 
 csv_ints = []
@@ -48,19 +50,19 @@ csv_detailed_fields = [csv_simpleStructures, csv_getNearCleaners, csv_testNCShor
 #                        csv_list_rank, csv_distance_parent, csv_find_bridges, csv_naive_bridges]
 
 hatches = ['++', '**', 'oo', '----', '||', '..']
-algo_colors = {"Cuda Perfect": "#377eb8", "Perfect": "#ff7f00"}
-algo_markers = {"Cuda Perfect": ".", "Perfect": "x"}
+algo_colors = {"Cuda Perfect": "#377eb8", "Perfect": "#ff7f00", "CUDA Naive": "#ff0000"}
+algo_markers = {"Cuda Perfect": ".", "Perfect": "x", "CUDA Naive": "o"}
 
-algo_labels = {"Cuda Perfect": "GPU Perfect", "Perfect": "Perfect",
-#  "naive": u"GPU Naïve", "CPU Inlabel": "CPU Inlabel",
-#                "tarjan": "GPU TV", "naive": "GPU CK", "cpu": "CPU DFS", "hybrid": "GPU Hybrid"
-               }
+algo_labels = {"Cuda Perfect": "GPU Perfect", "Perfect": "Perfect", "CUDA Naive": "GPU Naive"}
 
 algo_field_labels = {csv_simpleStructures : "Simple Structures", csv_testNCRest: "Test NC Rest",
                      csv_getNearCleaners: "Get Near Cleaners", csv_testNCShortestPaths: "Test NC Shortest Paths", csv_gpuCopyR: "GPU Test NC Copy R", csv_gpuWork: "GPU test NC work"}
-field_colors = {"Perfect": {csv_simpleStructures: "#0f2231", csv_getNearCleaners: "#2c6593", csv_testNCShortestPaths: "#6ca5d3", csv_testNCRest: "#aaaaaa"},
[…]

### 2020-09-02 code/test/unitTest/perfect.cpp

@@ -141,17 +141,18 @@ XX..X.....\
 
 void testPerfectVsNaive() {
   RaiiTimer timer("Perfect vs naive ");
-  for (int i = 0; i < (bigTests ? 30 : 100); i++) {
-    Graph G = getRandomGraph(bigTests ? 8 : 6, 0.5);
+  for (int i = 0; i < (bigTests ? 300 : 100); i++) {
+    Graph G = getRandomGraph(bigTests ? 10 : 6, 0.5);
     testGraphSimple(G);
   }
 }
 
 void testNonPerfect() {
   RaiiTimer timer("Non Perfect");
-  for (int i = 0; i < 100; i++) {
+  for (int i = 0; i < 1000; i++) {
     Graph G = getNonPerfectGraph(9, 10, 0.5);
     assert(isPerfectGraph(G) == false);
+    assert(isPerfectGraphNaive(G) == false);
   }
 }
 

### 2020-09-04 paper/coloringAppendix/mainToInclude.tex
Work on combinatorial graphs

\section{Notes}

In appendix we use a slightly different notation than before, with many concepts represented by inline symbols. This is intended to reduce the length of algorithm's text and simplify its analysis.

\begin{itemize}
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
	\item $a \gets b$ -- let a be equal b.
	\item $a :\in X$ -- let a be equal to any element of $X$
	\item $a \xor b$ -- $a$ xor $b$
\end{itemize}

\section{Algorithms}
\begin{algorithm}
	\SetKwFunction{colorGraph}{\textsc{Color-Graph}}
\end{algorithm}

\input{coloringAppendix/algII.tex}
\clearpage

\input{coloringAppendix/algIII.tex}
\clearpage

\input{coloringAppendix/algIV.tex}
\clearpage

\input{coloringAppendix/algV.tex}
\clearpage

\subsection{ALG VI}
\input{coloringAppendix/algVIa.tex}
\clearpage

\input{coloringAppendix/algVIb.tex}
\clearpage

\input{coloringAppendix/algVII.tex}
\clearpage

\input{coloringAppendix/algVIII.tex}
\clearpage

### 2020-09-04 paper/coloringBergeGraphs.tex
Add citation
Work on combinatorial graphs

@@
 \begin{wrapfigure}{r}{0.35\textwidth}
-  \label{fig:c5}
 	\input{tikzpictures/c5.tex}
 	\caption{Example noisy channel}%
+  \label{fig:c5}
 	% \vspace{-0.5cm}
@@
 
-For a channel defined by graph $C_5$ using five messages of length 2 gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\alpha(C_5^2)$).
+For a channel defined by a graph $C_5$, using five messages of length 2 to communicate gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\alpha(C_5^2)$).
 
 Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length \todo{picture}.
-Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90°.
+Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90$^\circ$.
 This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
@@
 
-It turns out, that we can obtain a similar representation of the nodes of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^3k$, so that any two non-adjacent nodes are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}).
+It turns out, that we can obtain a similar representation of the nodes of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^{3k}$, so that any two non-adjacent nodes are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}).
 Moreover, we still get $e_1^\intercal v_i = 5^{-k/4}$ for every $i \in V(C_5^k)$ (the proof is quite technical and we omit it here).
@@
 
-Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on Shannon capacity of the graph.
-However, these two equal in some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" \cref{thm:sandwich}.
+Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it.
+However, these two equal in some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\cref{thm:sandwich}).
 
@@
 \subsection{Coloring perfect graph using ellipsoid method}
+The following is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.
+
 \subsubsection{Maximum cardinality stable set}
-
-\TODO{cite the paper on using theta to color.}
 
@@
 \label{sec:classicalColoring}
+
+Ever since Grötschel et al.
+published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs, a combinatorial algorithm for doing the same has been sought.
+As of yet, it is not known, although there is much progress in the field.
+
+A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
+Notice, that for a graph to contain no odd hole, all three paths in a prism must have the same parity.
+A prism with all three paths odd is called an \emph{odd prism}.
+
+In 2005 Maffray and Trotignon a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
+They later improved the time complexity to $O(|V|^2|E|)$ \cite{Lvque2009}.
+
+In 2015 Maffray showed an algorithm for coloring Berge graphs with no squares (a square is a $C_4$) and no odd prism \cite{Maff2015}.
+
+In 2016 Chudnovsky et al. published an algorithm that given a perfect graph $G$ with $\omega(G) = k$ colors it optimally in a time polynomial for a fixed $k$ \cite{Chudnovsky2017}.
+
+A most recent advancement (2018) is an algorithm by Chudnovsky et al.
+that colors any square-free Berge graphs in time of $O(|V|^9)$ \cite{Chudnovsky2019}.
+Before proving strong perfect graph conjecture, a similar conjecture for square-free Berge graphs has been proven by Conforti et al.
+\cite{Conforti2004} During one of her lectures, Maria Chudnovsky expressed hope that discovery of full algorithm for coloring Berge graphs might follow a similar pattern.
+We analyze this algorithm and provide its pseudocode in \cref{ch:coloringSquareFree}.

### 2020-09-04 paper/perfectGraphs.tex
Implementation WIP
Work on combinatorial graphs

@@
 \begin{theorem}[Perfect graph theorem]
-	A graph is perfect if and only if its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}
+	\label{thm:pgt}
+	A graph is perfect if and only if its complement graph is also perfect.
 \end{theorem}
+
+This theorem is a consequence of a stronger result proven by \Lovasz:
+\begin{theorem}
+	\label{thm:omegaalpha}
+	A graph $G$ is perfect iff for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof?}
+\end{theorem}
+
+Then, since $\alpha(H) = \omega(\overline{H})$ and $\omega(H) = \alpha(\overline{H})$ \cref{thm:omegaalpha} implies \cref{thm:pgt}.
 
@@
 have proven it and published the proof in an over 150 pages long paper \citetitle{MC06} \cite{MC06}.
-The following overview of the proof will be based on this paper and on an article with the same name by Cornuéjols \cite{GC03}.
 
 \begin{theorem}[Strong perfect graph theorem]
+	\label{thm:spgt}
 	A graph is perfect if and only if it is Berge.
@@
 
-\TODO{How long and detailed overview of the proof should we provide?}
-\TODO{Znakomite pytanie.
-Generalnie ponieważ dowód jest drobiazgowy i trikowy, to wystarczy "z lotu ptaka" tj.
-to, co Chudnovsky i Seymour piszą w pracach popularnych i referują w wystąpieniach gościnnych typu te nagrania na YT.
-Głębiej nie ma sensu.
-Warto podkreślić, że technika dowodu i sam algorytm są zależne na dużo głębszym poziomie niż widać tj.
-ktoś mając dowód Stron Perfect Graph Theorem pewnie nie rozgryzłby algorytmu i vice versa.}
+The proof is long and complicated.
+Moreover, it has little noticeable connection to the algorithm of recognizing Berge graphs we discuss later.
+Therefore we will discuss it very briefly following the overview by Cornuéjols \cite{GC03}.
+
+\subsubsection{Basic classes of perfect graphs}
+Bipartite graphs are perfect, since we can color them with two colors.
+From the theorem of König we get that line graphs of bipartite graphs are also perfect \cite{Knig1916, GC03}.
+From the perfect graph theorem (\cref{thm:pgt}) it follows that complements of bipartite graphs and complement of line graphs of bipartite graphs are also perfect.
+We will call these four classes \emph{basic}.
+
+\subsubsection{2-join, Homogeneous Pair and Skew Partition}
+A graph $G$ has a \emph{2-join} if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$.
+When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect iff $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.
+
+A graph $G$ has a \emph{homogeneous pair} if $V(G)$ can be partitioned into subsets $A_1$, $A_2$, $B$, such that $|A_1|+|A_2| \geq 3$, $|B| \geq 2$ and if a vertex $v \in B$ is adjacent to a vertex from $A_i$, then it is adjacent to all vertices from $A_i$.
+Chvátal and Sbihi proved that no minimally imperfect graph has a homogeneous pair \cite{Chvtal1987}.
+
+A graph $G$ has a \emph{skew partition} if $V(G)$ can be partitioned into nonempty subsets $A, B, C, D$ such that there are all possible edges between $A$ and $B$ and no edges between $C$ and $D$.
+Chudnovsky et at.
+proved that no minimally imperfect graph has a skew partition.
+
+The proof of \cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
+\begin{theorem}[Decomposition theorem]
+	\label{thm:decomposition}
+	Every Berge graph $G$ is basic or has a skew partition or a homogeneous pair, or $G$ or $\overline{G}$ has a 2-join.
+\end{theorem}
+
+See \cite{MC06} for the proof of \cref{thm:decomposition} and \cref{thm:spgt}.
 
@@
 
-The following is based on the paper by Maria Chudnovsky et al. \citetitle*[]{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
+The following is based on the paper by Maria \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}.
+We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
 
-Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple structures as a induced subgraph (\ref{SimpleStructures}).
+Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}).
 If they do, we output that graph is not Berge and stop.
-Else, we check if there is a near-cleaner for a shortest odd hole (\ref{AmenableHoles}).
+Else, we check if there is a near-cleaner for a shortest odd hole (\cref{AmenableHoles}).
 
-\subsection{Simple structures}
+\subsection{Simple forbidden structures}
 \label{SimpleStructures}
@@
 \subsubsection{Pyramids}
-
-% \begin{floatingfigure}{0.35\textwidth}
 
@@
 	\vspace{-1.2cm}
-	% \end{floatingfigure}
 \end{wrapfigure}
@@
 
-First, let us enumerate all 6-tuples $b_1, b_2, b_3, s_1, s_2, s_3$ such that:
+\begin{alg}[Test if $G$ contains a Pyramid]
+	\label{alg:testPyramid}
+	Input: A graph $G$.
+
+	\noindent Output: Returns whether $G$ contains a pyramid as an induced subgraph.
+\end{alg}
+\begin{algtext}
+
+Enumerate all 6-tuples $(b_1, b_2, b_3, s_1, s_2, s_3)$ such that:
 \begin{itemize}
 	\item $\{b_1, b_2, b_3\}$ is a triangle
-	\item for $1 \leq i < j \leq 3$, ${b_i, s_i}$ is disjoint from ${b_j, s_j}$ and $b_ib_j$ is the only edge between them
-	\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i \ b_i$.
+	\item for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them
+	\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i = b_i$.
 \end{itemize}
 
-There are $O(|V(G)|^6)$ 6-tuples, and it takes $O(|V(G)|)$ time to check each one. For each such 6-tuple we follow with the rest of the algorithm.
+There are $O(|V(G)|^6)$ 6-tuples, and for each we check above conditions in $O(|V(G)|)$ time. For each such 6-tuple we follow with the rest of the algorithm.
 
-We define $M = V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$.
-Now, for each $m \in M$, we set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
-We set $S_2$ and $S_3$ similarly.
-Then similarly we set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
-We do similar for $T_2$ and $T_3$.
-It takes $O(|V(G)|^2)$ time to calculate paths $T_i(m)$ for all $i$ and $m$.
+Let $M \leftarrow V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$.
 
-Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ and paths $P_2(m)$, $P_3(m)$ will be defined in a similar manner.
+For each $m \in M$, set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
+Set $S_2$ and $S_3$ similarly.
+Set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists, and set $T_2$, $T_3$ similarly.
+It takes $O(|V(G)|^2)$ time to calculate paths $S_i(m)$ and $T_i(m)$ for all $i$ and $m$.
+
+Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ with paths $P_2(m)$, $P_3(m)$ defined in a similar manner.
 
@@
 \end{itemize}
-If so, then we assign a path $s_1-S_1(m)-m-T_1(m)-b_1$ to $P_1(m)$, otherwise we let $P_1(m)$ be undefined.
-It takes $O(|V(G)|^2)$ to check this, given $m$.
+If it is true for some $m \in M$, then we assign $P_1(m) \leftarrow s_1-S_1(m)-m-T_1(m)-b_1$, otherwise we let $P_1(m)$ be undefined.
+It takes $O(|V(G)|^2)$ to check this, for a given $m$.
 We assign $P_2$ and $P_3$ in a similar manner.
@@
 
-For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$, $P_j(m_j)$ both exist and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
+For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
 
@@
 Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
+\end{algtext}
 
-\TODO{some proofs}
+It is easy to see, that if algorithm outputs that $G$ contains a pyramid, it indeed does. The proof of the converse is rather technical and we refer to \cite{MC05} for it.
 
@@
 
-Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required.
+Most obvious way to find a jewel would be to enumerate all (possibly chordal) cycles of length 5 as $v_1, \ldots v_5$, check if it has all required nonedges and if it does, try to find a path $P$ as required.
 This gives us a time of $O(|V|^7)$.
-We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
+We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole Berge recognition algorithm takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
 
@@
 A configuration of type $\T_1$ is a hole of length 5.
-To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole.
-See \cref{Optimizations} for more implementation details.
+To find it, we simply iterate over all paths of length 4 and check if there exists a fifth vertex to complete the hole.
+See \cref{sec:usesGeneration} for more implementation details.
 
@@
 
-To prove that existence of $\T_2$ configuration implies that the graph is not berge, we will need the following Roussel-Rubio lemma:
+To prove that existence of $\T_2$ configuration implies that the graph is not Berge, we will need the following Roussel-Rubio lemma:
 
@@
 
+\begin{alg}
+	\label{alg:t3}
+	Input: A graph $G$.
+
+	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
+\end{alg}
+\begin{algtext}
+
 For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices.
@@
 If we exhaust our search and find none, report that graph does not contain it.
+\end{algtext}
 
-To see that the algorithm below has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
+To see that the \cref{alg:t3} has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
 This gives us the total running time of $O(|V(G)|^6)$.
 
-We will skip the proof that each graph containing $\T_3$ is not Berge. See section6 6.7 of \cite{MC05} for the proof.
+We will skip the proof that each graph containing $\T_3$ is not Berge. See section 6 6.7 of \cite{MC05} for the proof.
 
@@
 	\label{alg:testNearCleaner}
-	Input: A graph $G$ containing no simple bad structure \todo{define this somewhere}, and a subset $X \subseteq V(G)$.
+	Input: A graph $G$ containing no simple forbidden structure, and a subset $X \subseteq V(G)$.
 

### 2020-09-05 code/src/perfect.cpp
Plots wip

@@ -7,19 +7,19 @@
 #include "testCommons.h"
 
 bool containsSimpleProhibited(const Graph &G, bool gatherStats) {
-  // if (gatherStats) StatsFactory::startTestCasePart("Jewel");
+  if (gatherStats) StatsFactory::startTestCasePart("Jewel");
   if (containsJewelNaive(G)) return true;
 
-  // if (gatherStats) StatsFactory::startTestCasePart("Pyramid");
+  if (gatherStats) StatsFactory::startTestCasePart("Pyramid");
   if (containsPyramid(G)) return true;
 
-  // if (gatherStats) StatsFactory::startTestCasePart("T1");
+  if (gatherStats) StatsFactory::startTestCasePart("T1");
   if (containsT1(G)) return true;
 
-  // if (gatherStats) StatsFactory::startTestCasePart("T2");
+  if (gatherStats) StatsFactory::startTestCasePart("T2");
   if (containsT1(G)) return true;
 
-  // if (gatherStats) StatsFactory::startTestCasePart("T3");
+  if (gatherStats) StatsFactory::startTestCasePart("T3");
   if (containsT1(G)) return true;
 
   return false;

### 2020-09-05 code/src/testCommons.cpp

@@ -160,8 +160,7 @@ Graph getKnightGraph(int W, int H) {
   return getGridWithMoves(W, H, dx, dy);
 }
 
-Graph getHypercube(int k) {
-  int n = (1 << k);
+Graph getHypercube(int n) {
   vec<vec<int>> neighbors(n);
   for (int i = 0; i < n; i++) {
     for (int j = i + 1; j < n; j++) {

### 2020-09-05 code/test/cuPerfTest/run.sh

@@ -13,15 +13,15 @@ naiveExec="$scriptDir/../../obj/test/cuPerfTest/naive.e"
 perfectTests=(
   # "perf2.t.in"
   # "perf.t.in"
-  # "perfSmaller.t.in"
   # "bench.t.in"
-  # "fullBinary.t.in"
   # "fullBinaryBig.t.in"
-  "grid6by5to8.t.in"
+  # "fullBinary20to55.t.in"
+  # "grid6by5to9.t.in"
   # "knightGraph6by5to8.t.in"
-  # "hypercubes2to5.t.in"
+  # "knightGraph8by4to8.t.in"
+  "hypercubes16to50.t.in"
   # "kingGraph3by3to12.t.in"
-  # "rookGraph5by4to6.t.in"
+  # "rookGraph5by4to7.t.in"
 )
 
 naiveTests=(

### 2020-09-05 code/test/generate/generate.cpp

@@ -26,25 +26,25 @@ int main() {
   //   }
   // }
 
-  // int minN = 10;
-  // int maxN = 40;
+  // int minN = 20;
+  // int maxN = 55;
   // for (int k = minN; k <= maxN; k++) {
   //   Graph G = getFullBinaryTree(k);
   //   G.printOut();
   // }
 
-  vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}};
-  for (auto size : sizes) {
-    // Graph G = getCityGrid(size[0], size[1]);
-    // Graph G = getKnightGraph(size[0], size[1]);
-    Graph G = getRookGraph(size[0], size[1]);
-    G.printOut();
-  }
-
-  // for (int k = 2; k < 7; k++) {
-  //   Graph G = getHypercube(k);
+  // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}};
+  // for (auto size : sizes) {
+  //   // Graph G = getCityGrid(size[0], size[1]);
+  //   // Graph G = getKnightGraph(size[0], size[1]);
+  //   Graph G = getRookGraph(size[0], size[1]);
   //   G.printOut();
   // }
+
+  for (int k = 16; k <= 50; k++) {
+    Graph G = getHypercube(k);
+    G.printOut();
+  }
 
   // for (int k = 3; k <= 12; k++) {
   //   Graph G = getGridWithMoves(3, k, {1, -1, 0, 0, 1, 1, -1, -1}, {0, 0, 1, -1, 1, -1, 1, -1});

### 2020-09-05 code/test/plot.py

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-# usePgf = True
-usePgf = False
+usePgf = True
+# usePgf = False
 
 import matplotlib as mpl
 if usePgf:
@@ -25,6 +25,7 @@ import ntpath
 
 plt.rcParams.update({'pgf.texsystem': 'pdflatex', 'font.family': 'serif', 'pgf.rcfonts': False, })
 
+csv_filename = "Filename"
 csv_N = 'n'
 csv_result = 'result'
 csv_algo = 'algorithm'
@@ -65,14 +66,15 @@ field_colors = {"Perfect": {csv_simpleStructures: "#0f2231", csv_getNearCleaners
                 "CUDA Naive": { csv_cpuPreparation: "#ff0000", csv_gpuCalculation: "#aa0000"}
                 }
 
-sizes_in_inches = {"regular": (5, 3.5), "wide": (
-    6.8, 2.4), "huge": (6.8, 8), "allGraphs": (10, 25), "wideDetailed":(6.8, 3)}
+sizes_in_inches = {"regular": (4.77, 3.5), "wide": (
+    6.8, 2.4), "huge": (6.8, 8), "allGraphs": (10, 25), "wideDetailed":(4.77, 4)}
 # sizes_in_inches = {"regular": (5, 3), "wide": (8, 3)}
 
 func_formatter = ticker.FuncFormatter(lambda y, _: '{:g}'.format(y))
 
 #labels for plot axes
 label_lca_N = "Number of nodes"
+label_time_percentage = "Time ratio"
 label_lca_preprocessing_over_s = "Nodes preprocessed per second"
 label_lca_queries_over_s = "Queries answered per second"
 label_lca_queries_over_N = "Queries-to-nodes ratio"
@@ -91,10 +93,27 @@ experiments = [
      "x_param": csv_N, "x_show": csv_N, "type": "lines", "size": sizes_in_inches["regular"],
      "y_param": csv_overall, "ylog": False, "x_label": "N", "y_label": label_time_overall_s},
 
-    # {"restrictions": [(csv_result, 1)],
-    #  "x_param": csv_N, "x_show": csv_N, "type": "detailed", "size": sizes_in_inches["wideDetailed"],
-    #  "x_label": label_time_overall_s},
-     
[…]

### 2020-09-05 code/inc/commons.h
Naive oddHole len=0 opt

@@ -162,6 +162,7 @@ bool isHole(const Graph &G, const vec<int> &v);
 
 // Returns (in &v) next path of length len in G (in some order). If v is empty returns first path. If v is
 // the last path returns empty vec. Iterating from empty vector to empty vector gives all paths of length len.
+// len=0 triggers search for any odd hole (isCycleOk should =1, areChordsOk should =0, holeRequired should =1)
 void nextPathInPlace(const Graph &G, vec<int> &v, int len, bool isCycleOk = false, bool areChordsOk = false,
                      bool holeRequired = false);
 

### 2020-09-05 code/src/commons.cpp

@@ -615,16 +615,60 @@ void nextPathInPlaceInternal(const Graph &G, vec<int> &v, int len, bool isCycleO
   }
 }
 
+void nextHoleInPlaceInternal(const Graph &G, vec<int> &v) {
+  while (true) {
+    if (v.back() == -1) {
+      v.pop_back();
+      if (v.size() == 1) {
+        v[0]++;
+        if (v[0] >= G.n) {
+          v = {};
+          return;
+        }
+        continue;
+      } else {
+        v.back() = G.getNextNeighbour(v[v.size() - 2], v.back());
+        continue;
+      }
+    }
+
+    if (v.size() < G.n) {
+      while (v.size() > 1 && v.back() != -1 && (!isAPath(G, v, true, false, false) || v.back() <= v[0])) {
+        v.back() = G.getNextNeighbour(v[v.size() - 2], v.back());
+      }
+      if (v.back() == -1) continue;
+
+      if ((v.size() % 2) && isAPath(G, v, true, false, true)) return;
+
+      v.push_back(G.getFirstNeighbour(v.back()));
+      if ((v.size() % 2) && isAPath(G, v, true, false, true))
+        return;
+      else
+        continue;
+    }
+
+    do {
+      v.back() = G.getNextNeighbour(v[v.size() - 2], v.back());
+    } while (v.back() != -1 && !isAPath(G, v, true, false, true));
+
+    if ((v.size() % 2) == 0 || v.back() == -1) continue;
+
+    return;
+  }
+}
+
 void nextPathInPlace(const Graph &G, vec<int> &v, int len, bool isCycleOk, bool areChordsOk,
                      bool holeRequired) {
-  if (len <= 1) {
-    throw invalid_argument("Length of next path must be at least 2");
+  if (len == 0 && (!holeRequired || !isCycleOk || areChordsOk)) {
+    throw invalid_argument("len=0 only supported for holes");
   }
   if (v.empty()) {
     v = {0};
   }
 
   v.reserve(len);
+
+  if (len == 0) return nextHoleInPlaceInternal(G, v);
 
   return nextPathInPlaceInternal(G, v, len, isCycleOk, areChordsOk, holeRequired);
 }

### 2020-09-05 code/src/oddHoles.cpp

@@ -24,16 +24,22 @@ vec<int> findHoleOfSize(const Graph &G, int size) {
 bool constainsHoleOfSize(const Graph &G, int size) { return !findHoleOfSize(G, size).empty(); }
 
 vec<int> findOddHoleNaive(const Graph &G, bool gatherStats) {
-  for (int size = 5; size <= G.n; size += 2) {
-    if (gatherStats) StatsFactory::startTestCasePart(to_string(size));
-    auto v = findHoleOfSize(G, size);
-    if (!v.empty()) return v;
-  }
+  // for (int size = 5; size <= G.n; size += 2) {
+  //   if (gatherStats) StatsFactory::startTestCasePart(to_string(size));
+  //   auto v = findHoleOfSize(G, size);
+  //   if (!v.empty()) return v;
+  // }
 
-  return vec<int>();
+  // return vec<int>();
+  vec<int> v;
+  nextPathInPlace(G, v, 0, true, false, true);
+  return v;
 }
 
 bool containsOddHoleNaive(const Graph &G, bool gatherStats) {
+  // auto v = findOddHoleNaive(G, gatherStats);
+  // cout<<v<<endl;
+  // return !v.empty();
   return !findOddHoleNaive(G, gatherStats).empty();
 }
 

### 2020-09-05 code/src/perfect.cpp

@@ -7,19 +7,19 @@
 #include "testCommons.h"
 
 bool containsSimpleProhibited(const Graph &G, bool gatherStats) {
-  if (gatherStats) StatsFactory::startTestCasePart("Jewel");
+  // if (gatherStats) StatsFactory::startTestCasePart("Jewel");
   if (containsJewelNaive(G)) return true;
 
-  if (gatherStats) StatsFactory::startTestCasePart("Pyramid");
+  // if (gatherStats) StatsFactory::startTestCasePart("Pyramid");
   if (containsPyramid(G)) return true;
 
-  if (gatherStats) StatsFactory::startTestCasePart("T1");
+  // if (gatherStats) StatsFactory::startTestCasePart("T1");
   if (containsT1(G)) return true;
 
-  if (gatherStats) StatsFactory::startTestCasePart("T2");
+  // if (gatherStats) StatsFactory::startTestCasePart("T2");
   if (containsT1(G)) return true;
 
-  if (gatherStats) StatsFactory::startTestCasePart("T3");
+  // if (gatherStats) StatsFactory::startTestCasePart("T3");
   if (containsT1(G)) return true;
 
   return false;
@@ -33,10 +33,10 @@ bool isPerfectGraph(const Graph &G, bool gatherStats) {
   Graph GC = G.getComplement();
   if (containsSimpleProhibited(G, gatherStats) || containsSimpleProhibited(GC, gatherStats)) return false;
 
-  // if (gatherStats) StatsFactory::startTestCasePart("Get Near Cleaners");
+  if (gatherStats) StatsFactory::startTestCasePart("Get Near Cleaners");
   auto Xs = getPossibleNearCleaners(G, GC, gatherStats);
 
-  if (gatherStats) StatsFactory::startTestCasePart("Get TriplePaths");
+  if (gatherStats) StatsFactory::startTestCasePart("Test NC Rest");
   vec<vec<int>> triplePaths = getAllPaths(G, 3);
 
   for (auto X : Xs) {
@@ -46,10 +46,10 @@ bool isPerfectGraph(const Graph &G, bool gatherStats) {
     }
   }
 
-  // if (gatherStats) StatsFactory::startTestCasePart("Get Near Cleaners");
+  if (gatherStats) StatsFactory::startTestCasePart("Get Near Cleaners");
   auto XsC = getPossibleNearCleaners(GC, G, gatherStats);
 
[…]

### 2020-09-05 code/test/generate/generate.cpp

@@ -26,8 +26,8 @@ int main() {
   //   }
   // }
 
-  // int minN = 20;
-  // int maxN = 55;
+  // int minN = 30;
+  // int maxN = 40;
   // for (int k = minN; k <= maxN; k++) {
   //   Graph G = getFullBinaryTree(k);
   //   G.printOut();
@@ -41,7 +41,7 @@ int main() {
   //   G.printOut();
   // }
 
-  for (int k = 16; k <= 50; k++) {
+  for (int k = 30; k <= 40; k++) {
     Graph G = getHypercube(k);
     G.printOut();
   }

### 2020-09-07 code/src/color.cpp
Color tests

@@ -2,12 +2,12 @@
 #include <tuple>
 #include "commons.h"
 #include "perfect.h"
+#include "testCommons.h"
 using namespace std;
 
 extern "C" {
 #include "theta.h"
 }
-
 
 tuple<int, int, vec<int>, vec<int>> getGraphEdges(const Graph &G, const vec<int> &isNodeRemoved) {
   vec<int> nodeStays(isNodeRemoved.size());
@@ -46,7 +46,7 @@ tuple<int, int, vec<int>, vec<int>> getGraphEdges(const Graph &G, const vec<int>
   return {nodeNr.back(), m, from, to};
 }
 
-int getTheta(const Graph &G, const vec<int> &isNodeRemoved) {
+int getTheta(const Graph &G, const vec<int> &isNodeRemoved, bool gatherStats) {
   auto e = getGraphEdges(G, isNodeRemoved);
 
   if (get<0>(e) == 0) {
@@ -64,7 +64,14 @@ int getTheta(const Graph &G, const vec<int> &isNodeRemoved) {
       return 1;
   }
 
+  static map<tuple<int, int, vec<int>, vec<int>>, int> MEM;
+  if (MEM.count(e) > 0) {
+    return MEM[e];
+  }
+
+  if (gatherStats) StatsFactory::startTestCasePart("Color CSDP");
   double th = theta(get<0>(e), get<1>(e), get<2>(e).data(), get<3>(e).data());
+  if (gatherStats) StatsFactory::startTestCasePart("Color rest");
 
   if (th == -1) {
     throw logic_error("Theta returned -1");
@@ -80,10 +87,14 @@ int getTheta(const Graph &G, const vec<int> &isNodeRemoved) {
       throw logic_error("Theta returned non-integer for a Perfect Graph: " + to_string(th));
   }
 
+  MEM[e] = thInt;
+
   return thInt;
 }
 
-int getOmega(const Graph &G) { return getTheta(G.getComplement()); }
+int getOmega(const Graph &G, bool gatherStats) {
+  return getTheta(G.getComplement(), vec<int>(), gatherStats);
+}
 
 bool isStableSet(const Graph &G, vec<int> nodes) {
   if (!isDistinctValues(nodes)) return false;
@@ -97,15 +108,15 @@ bool isStableSet(const Graph &G, vec<int> nodes) {
   return true;
 }
 
[…]

### 2020-09-07 code/src/colorTestCommons.cpp

@@ -20,7 +20,7 @@ map<int, int> casesTestedColor;
 void testGraphColor(const Graph &G) {
   StatsFactory::startTestCase(G, algo_color);
 
-  auto coloring = color(G);
+  auto coloring = color(G, true);
   assert(isColoringValid(G, coloring));
 
   StatsFactory::endTestCase(true);

### 2020-09-07 code/test/colorPerfTest/run.sh

@@ -8,8 +8,13 @@ mkdir -p $resultsDir
 colorExec="$scriptDir/../../obj/test/colorPerfTest/color.e"
 
 colorTests=(
-  # "small.t.in"
   "perf.t.in"
+  "perfLin.t.in"
+  "fullBinary20to45.t.in"
+  "grid5by4to9.t.in"
+  "hypercube20to40.t.in"
+  "knightGraph6by4to8.t.in"
+  "rookGraph6by4to8.t.in"
 )
 
 # for file in "${colorTests[@]}"; do
@@ -21,5 +26,5 @@ colorTests=(
 
 for file in "${colorTests[@]}"; do
   echo "Running Color on $file"
-  $colorExec <$testsDir/$file
+  $colorExec <$testsDir/$file >>$resultsDir/$file.out.csv
 done

### 2020-09-07 code/test/generate/generate.cpp

@@ -9,10 +9,10 @@
 int main() {
   srand(time(0));
 
-  // int minN = 10;
+  // int minN = 15;
   // int maxN = 19;
 
-  // for (int i = 0; i < 10; i++) {
+  // for (int i = 0; i < 5; i++) {
   //   set<int> done;
 
   //   while (done.size() < maxN - minN + 1) {
@@ -27,23 +27,26 @@ int main() {
   // }
 
   // int minN = 20;
-  // int maxN = 100;
+  // int maxN = 45;
   // for (int k = minN; k <= maxN; k+=5) {
+  // // for (int k = minN; k <= maxN; k++) {
   //   Graph G = getFullBinaryTree(k);
   //   G.printOut();
   // }
 
-  // vec<vec<int>> sizes = {{6, 5}, {6, 6}, {6, 7}, {6, 8}, {6, 9}, {6, 10}, {6, 11}};
-  vec<vec<int>> sizes = {{6,14}, {6, 15}, {6, 16}, {6, 17}};
+  // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}, {5, 8}, {5, 9}};
+  vec<vec<int>> sizes = {{6,4},{6, 5}, {6, 6}, {6, 7}, {6, 8} };
+  // vec<vec<int>> sizes = {{6,14}, {6, 15}, {6, 16}, {6, 17}};
   // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}};
+  // vec<vec<int>> sizes = {{4, 4}, {4, 5}, {4, 6}, {4, 7}};
   for (auto size : sizes) {
-    Graph G = getCityGrid(size[0], size[1]);
+    // Graph G = getCityGrid(size[0], size[1]);
     // Graph G = getKnightGraph(size[0], size[1]);
-    // Graph G = getRookGraph(size[0], size[1]);
+    Graph G = getRookGraph(size[0], size[1]);
     G.printOut();
   }
 
-  // for (int k = 30; k <= 40; k++) {
+  // for (int k = 20; k <= 40; k++) {
   //   Graph G = getHypercube(k);
   //   G.printOut();
   // }

### 2020-09-07 code/test/perfTest/naive.cpp

@@ -26,16 +26,14 @@ int main() {
   random_shuffle(Gs.begin(), Gs.end());
 
   {
-    cout << "N=" << n << endl;
-
     RaiiProgressBar bar(Gs.size());
 
     for (int i = 0; i < Gs.size(); i++) {
-      testWithStats(Gs[i], true);
+      testGraph(Gs[i], {algoNaive});
       bar.update(i + 1);
     }
   }
   cout << endl;
 
-  printStats();
+  StatsFactory::printStats2();
 }

### 2020-09-07 code/test/perfTest/perfect.cpp

@@ -26,16 +26,15 @@ int main() {
   random_shuffle(Gs.begin(), Gs.end());
 
   {
-    cout << "N=" << n << endl;
-
     RaiiProgressBar bar(Gs.size());
 
     for (int i = 0; i < Gs.size(); i++) {
-      testWithStats(Gs[i], false);
+      testGraph(Gs[i], {algoPerfect});
+
       bar.update(i + 1);
     }
   }
   cout << endl;
 
-  printStats();
+  StatsFactory::printStats2();
 }

### 2020-09-07 code/test/perfTest/run.sh

@@ -10,10 +10,12 @@ naiveExec="$scriptDir/../../obj/test/perfTest/naive.e"
 
 perfectTests=(
   "perf.t.in"
+  "perfLin.t.in"
 )
 
 naiveTests=(
-  "naive.t.in"
+  "perf.t.in"
+  "perfLin.t.in"
 )
 
 perfectTestsValgrind=(
@@ -26,24 +28,24 @@ naiveTestsValgrind=(
 
 for file in "${perfectTests[@]}"; do
   echo "Running Perfect on $file"
-  $perfectExec <$testsDir/$file >$resultsDir/$file.perfect.out
+  $perfectExec <$testsDir/$file >>$resultsDir/$file.out
 done
 
 for file in "${naiveTests[@]}"; do
   echo "Running Naive on $file"
-  $naiveExec <$testsDir/$file >$resultsDir/$file.naive.out
+  $naiveExec <$testsDir/$file >>$resultsDir/$file.out
 done
 
-for file in "${perfectTestsValgrind[@]}"; do
-  echo "Profiling Perfect on $file"
-  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $perfectExec <$testsDir/$file >$resultsDir/$file.Valgrind.perfect.out
-  python3 $scriptDir/gprof2dot.py -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.perfect.dot
-  rm $resultsDir/callgrind.tmp.out
-done
+# for file in "${perfectTestsValgrind[@]}"; do
+#   echo "Profiling Perfect on $file"
+#   valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $perfectExec <$testsDir/$file >$resultsDir/$file.Valgrind.perfect.out
+#   python3 $scriptDir/gprof2dot.py -f callgrind $resultsDir/callgrind.tmp.out >$resultsDir/$file.perfect.dot
+#   rm $resultsDir/callgrind.tmp.out
+# done
 
-for file in "${naiveTestsValgrind[@]}"; do
-  echo "Profiling Naive on $file"
-  valgrind --callgrind-out-file=$resultsDir/callgrind.tmp.out --tool=callgrind $naiveExec <$testsDir/$file >$resultsDir/$file.Valgrind.naive.out
[…]

### 2020-09-07 code/test/plot.py

@@ -1,13 +1,14 @@
 # coding: utf-8
 
-usePgf = True
-# usePgf = False
+# usePgf = True
+usePgf = False
 
 import matplotlib as mpl
+
 if usePgf:
-    mpl.use('pgf')
+    mpl.use("pgf")
 else:
-    mpl.use('Agg')
+    mpl.use("Agg")
 
 
 from cycler import cycler
@@ -23,56 +24,127 @@ import matplotlib.patches as patches
 import numpy as np
 import ntpath
 
-plt.rcParams.update({'pgf.texsystem': 'pdflatex', 'font.family': 'serif', 'pgf.rcfonts': False, })
+plt.rcParams.update(
+    {
+        "pgf.texsystem": "pdflatex",
+        "font.family": "serif",
+        "pgf.rcfonts": False,
+    }
+)
 
 csv_filename = "Filename"
-csv_N = 'n'
-csv_result = 'result'
-csv_algo = 'algorithm'
-csv_overall = 'Overall'
-csv_numRuns = 'num_runs'
-csv_simpleStructures = 'Simple Structures'
-csv_getNearCleaners = 'Get Near Cleaners'
-csv_testNCShortestPaths = 'Test NC Shortest Paths'
-csv_gpuCopyR = 'GPU Test NC Copy R'
-csv_gpuWork = 'GPU Test NC work'
-csv_testNCRest = 'Test NC Rest'
-csv_cpuPreparation = 'CPU Preparation'
-csv_gpuCalculation = 'GPU Calculation'
+csv_N = "n"
+csv_result = "result"
+csv_algo = "algorithm"
+csv_overall = "Overall"
+csv_numRuns = "num_runs"
+csv_simpleStructures = "Simple Structures"
+csv_getNearCleaners = "Get Near Cleaners"
+csv_testNCShortestPaths = "Test NC Shortest Paths"
+csv_gpuCopyR = "GPU Test NC Copy R"
+csv_gpuWork = "GPU Test NC work"
+csv_testNCRest = "Test NC Rest"
+csv_cpuPreparation = "CPU Preparation"
+csv_gpuCalculation = "GPU Calculation"
+csv_color_res = "Color rest"
+csv_color_CSDP = "Color CSDP"
 
 
 csv_ints = []
 csv_ints.extend([csv_N, csv_result, csv_numRuns])
 csv_floats = []
[…]

### 2020-09-07 code/test/plot.py
Color pgf

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-# usePgf = True
-usePgf = False
+usePgf = True
+# usePgf = False
 
 import matplotlib as mpl
 

### 2020-09-07 paper/coloringAppendix/algI.tex
Algos and KT fixes

\begin{algorithm}
  \SetKwFunction{colorGraph}{\textsc{Color-Graph}}
  \Indm\nonl\colorGraph($G$)\\
  \KwData{$G$ -- square-free Berge graph}
  \KwResult{A $\chi(G)$-coloring of $G$}
  \Indp
  TODO \;
  TODO 2\;
  \Return Todo\;
\end{algorithm}

### 2020-09-07 paper/coloringBergeGraphs.tex
Algos and KT fixes

@@
 
-Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs (polynomial or not).
+Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs in finite time.
 If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$.
@@
 Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it.
-However, these two equal in some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\cref{thm:sandwich}).
+However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\Cref{thm:sandwich}).
 
@@
 \subsection{Coloring perfect graph using ellipsoid method}
+\label{sec:coloringEllipsoid}
 The following is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.
@@
 
-In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$.
+In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$, as the former values are always integral.
 
@@
 There are at most $|V|$ maximum cardinality cliques in $G$.
-Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(V^2)$ and running \cref{alg:maxStableSet} on it.
+Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \cref{alg:maxStableSet} on it.
 Therefore total running time is polynomial.

### 2020-09-07 paper/definitions.tex
Algos and KT fixes

@@
 
-Given a graph $G = (V, E)$ and a set set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.
+Given a graph $G = (V, E)$ and a set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.
 
@@
 The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P.
-$\{x_1, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.
+$\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.
 
@@
 \begin{defn}[anticomponent]
-  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $G$.
+  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $\overline{G}$.
 \end{defn}
@@
 \begin{defn}[clique]
-  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique of $n$ vertices as $K_n$.
+  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
 \end{defn}
@@
 
+\TODO{Defs below to ch. 1}
+
 \begin{defn}[Berge graph]
   \label{def:bergeGraph}
-  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole.
+  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
 \end{defn}

### 2020-09-07 paper/implementation.tex
Plots heavy wip
Algos and KT fixes

@@
 
-\section{Berge graphs recognition}
+\section{Berge graphs recognition: na\"ive approach}
+\TODO{rewrite to describe naive}
+
+\section{Berge graphs recognition: polynomial algorithm}
+\todo{rewrite/rearrange text below}
 
@@
 \TODO{moderngpu - allows us to run simple transforms}
+\TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}
 
@@
 
+\begin{figure}
+  \centering
+  \input{plots/hypercubes16to50.t.in.out.csv.lines.pgf}
+  \caption{testPlot 1}
+  % \label{fig:LCA_batch}
+\end{figure}
+
 Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\
@@
 
-Description.\\
+We used an open source CSDP \cite{csdpRepo, csdp1999} library, that implements predictor corrector variant of the semidefinite programming algorithm to calculate $\vartheta(G)$, given $G$ on the input.
+The CSDP library has been used in many recent publications across different fields, such as \cite{Ampountolas_2017, Adasme_2011}.
 
-Implementation.\\
+Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm.
+With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}.
+Our main goal of the implementation was to check if this method is still impractical, even on modern equipment.
+Let us proceed straight to experiments and results.
 
-Experiments and results.\\
+\subsubsection{Experiments and results}
 

### 2020-09-07 paper/main.tex
Work on combinatorial graphs
Algos and KT fixes

@@
 \chapter{Perfect Graph Coloring algorithm}
-TODO
+\label{ch:coloringSquareFree}
+\section{Notes}
+
+In appendix we use a slightly different notation than before, with many concepts represented by inline symbols. This is intended to reduce the length of algorithm's text and simplify its analysis.
+
+\begin{itemize}
+	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
+	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
+	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
+	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
+	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
+	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
+	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
+	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
+	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
+	\item $[n]$  -- $\{1, \ldots, n\}$.
+	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
+	\item $a \gets b$ -- let a be equal b.
+	\item $a :\in X$ -- let a be equal to any element of $X$
+	\item $a \xor b$ -- $a$ xor $b$
+
+	\item Strip $S_{uv}$ is \emph{rich} iff $S_{uv} \setminus T_{uv} \neq \emptyset$
+\end{itemize}
+\TODO{Introduction on unknown structures - J-strip etc etc}
+
+\section{Algorithms}
+
+\graphAppendix{Color Graph}
+\input{coloringAppendix/algI.tex}
+\clearpage
+
+\graphAppendix{Color Good Partition}
+\input{coloringAppendix/algII.tex}
+\clearpage
+
+\graphAppendix{Grow Hyperprism}
+\input{coloringAppendix/algIII.tex}
+\clearpage
+
+\graphAppendix{Good Partition from an even hyperprism}
+\input{coloringAppendix/algIV.tex}
+\clearpage
+
+\graphAppendix{Good Partition from odd hyperprism}
+\input{coloringAppendix/algV.tex}
+\clearpage
+
+\graphAppendix{Good Partition from $J$-strip system}
+\input{coloringAppendix/algVIa.tex}
+\clearpage
+
+\graphAppendix{Good Partition from a special $K_4$ strip system}
+\input{coloringAppendix/algVIb.tex}
+\clearpage
+
+\graphAppendix{Find a special $K_4$ system}
+\input{coloringAppendix/algVII.tex}
+\clearpage
+
+\graphAppendix{Growing a $J$-strip}
+\input{coloringAppendix/algVIII.tex}
+\clearpage
+
+% \graphAppendix{LAST}
+% \input{coloringAppendix/algIXa.tex}
+% \clearpage
 
@@
 
+\begin{figure}
+	\input{tikzpictures/3dtest.tex}
+	\caption{3d test}
+\end{figure}
+
 \end{document}

### 2020-09-07 paper/plots_backup/plot.py

@@ -1,0 +1,666 @@
+# coding: utf-8
+
+# usePgf = True
+usePgf = False
+
+import matplotlib as mpl
+
+if usePgf:
+    mpl.use("pgf")
+else:
+    mpl.use("Agg")
+
+
+from cycler import cycler
+import re
+import io
+import os
+import sys
+import csv
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter
+import matplotlib.ticker as ticker
+import matplotlib.patches as patches
+import numpy as np
+import ntpath
+
+plt.rcParams.update(
+    {
+        "pgf.texsystem": "pdflatex",
+        "font.family": "serif",
+        "pgf.rcfonts": False,
+    }
+)
+
+csv_filename = "Filename"
+csv_N = "n"
+csv_result = "result"
+csv_algo = "algorithm"
+csv_overall = "Overall"
+csv_numRuns = "num_runs"
+csv_simpleStructures = "Simple Structures"
+csv_getNearCleaners = "Get Near Cleaners"
+csv_testNCShortestPaths = "Test NC Shortest Paths"
+csv_gpuCopyR = "GPU Test NC Copy R"
+csv_gpuWork = "GPU Test NC work"
+csv_testNCRest = "Test NC Rest"
+csv_cpuPreparation = "CPU Preparation"
+csv_gpuCalculation = "GPU Calculation"
+
+
+csv_ints = []
+csv_ints.extend([csv_N, csv_result, csv_numRuns])
+csv_floats = []
+csv_floats.extend(
+    [
+        csv_overall,
+        csv_simpleStructures,
+        csv_getNearCleaners,
+        csv_testNCShortestPaths,
+        csv_gpuCopyR,
+        csv_gpuWork,
+        csv_testNCRest,
+    ]
+)
+
+csv_detailed_fields = [
+    csv_simpleStructures,
+    csv_getNearCleaners,
+    csv_testNCShortestPaths,
+    csv_gpuCopyR,
+    csv_gpuWork,
+    csv_testNCRest,
+]
+
+# csv_detailed_fields = [csv_BFS, csv_spanning_tree,
+#                        csv_list_rank, csv_distance_parent, csv_find_bridges, csv_naive_bridges]
+
+hatches = ["++", "**", "oo", "----", "||", ".."]
+algo_colors = {
+    "Cuda Perfect": "#1f77b4",
[…]

### 2020-09-08 code/inc/testCommons.h
Perf results

@@ -45,6 +45,7 @@ Graph getCityGrid(int W, int H);
 Graph getKnightGraph(int W, int H);
 Graph getHypercube(int k);
 Graph getRookGraph(int W, int H);
+Graph getSplitGraph(int n, double p);
 
 void handler(int sig);
 void init(bool srandTime = false);

### 2020-09-08 code/src/testCommons.cpp

@@ -196,6 +196,26 @@ Graph getRookGraph(int W, int H) {
   return getGridWithMoves(W, H, dx, dy);
 }
 
+Graph getSplitGraph(int n, double p) {
+  vec<vec<int>> neighbors(n * 2);
+  for (int i = 0; i < n; i++) {
+    for (int j = 0; j < n; j++) {
+      if (i != j) neighbors[i].push_back(j);
+    }
+  }
+
+  for (int i = 0; i < n; i++) {
+    for (int j = n; j < 2 * n; j++) {
+      if (probTrue(p)) {
+        neighbors[i].push_back(j);
+        neighbors[j].push_back(i);
+      }
+    }
+  }
+
+  return Graph(neighbors).getShuffled();
+}
+
 void handler(int sig) {
   void *array[100];
   size_t size;
@@ -301,8 +321,6 @@ bool testGraph(const Graph &G, vec<algos> algosToTest, vec<cuIsPerfectFunction> 
 
   return result;
 }
-
-
 
 // void printStats() {
 //   for (int algo = algoPerfect; algo < algo_last; algo++) {

### 2020-09-08 code/test/cuPerfTest/run.sh

@@ -11,18 +11,20 @@ cuPerfectExec="$scriptDir/../../obj/test/cuPerfTest/cuPerfect.e"
 naiveExec="$scriptDir/../../obj/test/cuPerfTest/naive.e"
 
 perfectTests=(
-  # # "perf2.t.in"
-  # # "perf.t.in"
   # # "bench.t.in"
   # # "fullBinaryBig.t.in"
   # # "knightGraph6by5to8.t.in"
-  # "knightGraph8by4to8.t.in"
   # "hypercubes16to50.t.in"
   # # "kingGraph3by3to12.t.in"
-  # "rookGraph5by4to7.t.in"
 
-  # "fullBinary20to100.t.in"
-  # "grid6by5to11.t.in"
+  "perf2.t.in"
+  "perf.t.in"
+  "fullBinary20to100.t.in"
+  "grid6by5to11.t.in"
+  "hypercubes20to55.t.in"
+  "knightGraph8by4to8.t.in"
+  "rookGraph5by4to7.t.in"
+  "split20to50.t.in"
 )
 
 pefectSupplement=(
@@ -31,41 +33,54 @@ pefectSupplement=(
 
 cudaPerfectSupplement=(
   "grid6by5to11.t.in"
+  "hypercubes20to55.t.in"
+  "rookGraph5by4to7.t.in"
+  "split20to50.t.in"
 )
 
-naiveTests=(
-  # "naive.t.in"
-  "perfSmaller.t.in"
+naivePerfectSupplement=(
+  "rookGraph5by4to7.t.in"
+  "split20to50.t.in"
 )
 
-benchTests=(
-  "hypercubes30to40.t.in"
-)
+# naiveTests=(
+#   # "naive.t.in"
+#   "perfSmaller.t.in"
+# )
+
+# benchTests=(
+#   "hypercubes30to40.t.in"
+# )
 
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running Perfect on $file"
-#   $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-# done
+for file in "${perfectTests[@]}"; do
+  echo "Running Perfect on $file"
+  $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+done
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running CuPerfect on $file"
-#   $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-# done
[…]

### 2020-09-08 code/test/generate/generate.cpp

@@ -35,18 +35,18 @@ int main() {
   // }
 
   // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}, {5, 8}, {5, 9}};
-  vec<vec<int>> sizes = {{6,4},{6, 5}, {6, 6}, {6, 7}, {6, 8} };
+  // vec<vec<int>> sizes = {{6, 4}, {6, 5}, {6, 6}, {6, 7}, {6, 8}};
   // vec<vec<int>> sizes = {{6,14}, {6, 15}, {6, 16}, {6, 17}};
   // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}};
-  // vec<vec<int>> sizes = {{4, 4}, {4, 5}, {4, 6}, {4, 7}};
-  for (auto size : sizes) {
-    // Graph G = getCityGrid(size[0], size[1]);
-    // Graph G = getKnightGraph(size[0], size[1]);
-    Graph G = getRookGraph(size[0], size[1]);
-    G.printOut();
-  }
+  // vec<vec<int>> sizes = {{5, 10}, {5, 11}, {5, 12} };
+  // for (auto size : sizes) {
+  //   // Graph G = getCityGrid(size[0], size[1]);
+  //   // Graph G = getKnightGraph(size[0], size[1]);
+  //   Graph G = getRookGraph(size[0], size[1]);
+  //   G.printOut();
+  // }
 
-  // for (int k = 20; k <= 40; k++) {
+  // for (int k = 60; k <= 75; k += 5) {
   //   Graph G = getHypercube(k);
   //   G.printOut();
   // }
@@ -55,4 +55,9 @@ int main() {
   //   Graph G = getGridWithMoves(3, k, {1, -1, 0, 0, 1, 1, -1, -1}, {0, 0, 1, -1, 1, -1, 1, -1});
   //   G.printOut();
   // }
+
+  for (int i = 10; i <= 25; i+=3) {
+    Graph G = getSplitGraph(i, getDistr());
+    G.printOut();
+  }
 }

### 2020-09-08 paper/coloringBergeGraphs.tex
Calculating \vartheta

@@
-\section{Coloring Perfect Graphs}
-
 A natural problem for perfect graphs is a problem of coloring them.
@@
 published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}.
-We consider it in section \cref{sec:ellipsoidMethod}.
+We consider it in \cref{sec:coloringEllipsoid}.
 However due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
@@
 
-\subsection{Information theory background}
-\label{sec:ellipsoidMethod}
+\section{Information theory background}
+\label{sec:InformationTheory}
 
-\subsubsection{Shannon Capacity of a graph}
+\Cref{sec:InformationTheory} and \cref{sec:computingTheta} are based on excellent lecture notes by Lovász \cite{Lovasz95}.
 
@@
 
+\subsection{Shannon Capacity of a graph}
+
 \begin{wrapfigure}{r}{0.35\textwidth}
   \input{tikzpictures/c5.tex}
-	\caption{Example noisy channel}%
+  \caption{An example of a noisy channel}%
   \label{fig:c5}
@@
 
-\subsubsection{\Lovasz number}
-
-The following introduction of what has become known as \emph{\Lovasz number} is based on excellent lecture notes by \Lovasz \cite{Lovasz95}. \todo{rewrite this so its not blatantly copied.}
+\subsection{Lovász number}
 
@@
 On the other hand each term on the left hand side is $5^{-1/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
-Thus we get $\alpha(C_5^k) \leq 5 ^{k/2}$ and $\Theta(C_5) = \sqrt{5}$.
+Since $|S|$ was an arbitrary stable set, we get $\alpha(C_5^k) \leq 5 ^{k/2}$ and $\Theta(C_5) = \sqrt{5}$.
 
-This method extends to any graph $G$ in place of $C_5$.
+It turns out that this method extends to any graph $G$ in place of $C_5$.
 All we have to do is find a orthogonal representation that will give us the best bound.
-So, we can define the \emph{\Lovasz number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
+So, we can define the \emph{Lovász number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
 $$\vartheta(G) = \min\limits_{c,U} \max\limits_{i\in V} \frac{1}{(c^\intercal u_i)^2},$$
@@
 
-Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it.
-However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\Cref{thm:sandwich}).
+Contrary to Lovász's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it.
+However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the Lovász "sandwich theorem".
 
-But how can we construct an optimum (or even good) orthogonal representation? It turns out that it can be computed in polynomial time using semidefinite optimization.
-
-\subsection{Computing \boldmath$\vartheta$}
-
-\TODO{TODO}
-
-\begin{theorem}[\Lovasz "sandwich theorem"]
+\begin{theorem}[Lovász "sandwich theorem" \cite{Knuth1994}]
   \label{thm:sandwich}
@@
 
-Because in perfect graphs $\omega(G) = \chi(G)$, we get $\omega(G) = \vartheta(G) = \chi(G)$.
+Because in perfect graphs $\omega(G) = \chi(G)$, we get $\omega(G) = \vartheta(\overline{G}) = \chi(G)$.
 
-\TODO{TODO}
+Therefore, if for any perfect graph $G$, we could calculate $\vartheta(G)$ and $\vartheta(\overline{G})$, we would get $\omega(G)$, $\chi(G)$ and $\alpha(G)$.
 
-\subsection{Coloring perfect graph using ellipsoid method}
+But how can we construct an optimum (or even good) orthogonal representation? It turns out that it can be computed in polynomial time using semidefinite optimization.
+
+\section{Computing \boldmath$\vartheta$}
+\label{sec:computingTheta}
+
+First, let us recall some definitions, with \cite{gilbertstrang2020} as a reference for linear algebra. \todo{do we want more lin. algebra definitions?}
+
+\begin{defn}[eigenvector, eigenvalue]
+  Let $A$ be an $n \times n$ real matrix.
+An \emph{eigenvector} of $A$ is a vector $x$ such that $Ax$ is parallel to $x$.
+In other words, there is a real or complex number $\lambda$, such that $Ax = \lambda x$.
+This $\lambda$ is called the \emph{eigenvalue} of $A$ belonging to eigenvector $x$.
+\end{defn}
+
+If a matrix $A$ is symmetric \footnote{Matrix $A$ is symmetric iff $A = A^\intercal$}, all the eigenvalues are real.
+
+\begin{defn}[positive semidefinite matrix]
+  Let $A$ be an $n \times x$ symmetric matrix. $A$ is \emph{positive semidefinite} if all of its eigenvalues are nonnegative. We denote it by $A \succeq 0$.
+\end{defn}
+
+We have equivalent definitions of semidefinite matrices.
+\begin{theorem}
+  For a real symmetric $n \times n$ matrix $A$, the following are equivalent:
+  \begin{enumerate}[(i)]
+    \item $A$ is positive semidefinite
+    \item \label{en:ei2} for every $x \in \mathbb{R}^n$, $x^\intercal Ax$ is nonnegative
+    \item for some matrix $U$, $A = U^\intercal U$
+    \item $A$ is a nonnegative linear combination of matrices of the type $xx^\intercal$
+  \end{enumerate}
+\end{theorem}
+
+From (\ref{en:ei2}) it follows that diagonal entries of any positive semidefinite matrix are nonnegative and the sum of two positive semidefinite matrices is positive semidefinite.
+
+We will think of $n \times n$ matrices as vectors with $n^2$ coordinates.
+\begin{defn}[convex cone]
+  A subset $C$ of $\mathbb{R}^n$ is a \emph{convex cone}, if for any positive scalars $\alpha, \beta$ and for any $x, y \in C$, $\alpha x + \beta y \in C$.
+\end{defn}
+
+The fact that the sum of two positive semidefinite matrices is again positive semidefinite, with the fact that every positive scalar multiple of a positive semidefinite matrix is positive semidefinite, translates into the geometric statement that the set of all positive semidefinite matrices forms a convex closed cone $\mathcal{P}_n$ in $\mathbb{R}^{n \times n}$ with vertex 0.
+This cone $\mathcal{P}_n$ is important but its structure is not trivial.
+
+\paragraph{Semidefinite programs}
+
+Now, we can define a \emph{semidefinite program} to be an optimization problem of the following form:
+
+\begin{equation*}
+  \begin{array}{ll@{}ll}
+    \text{minimize}   & c^\intercal x                          & \\
+    \text{subject to} & x_1A_1 + \ldots + x_nA_n - B \succeq 0   \\
+  \end{array}
+\end{equation*}
+Here $A_1, \ldots, A_n, B$ are given symmetric $m \times m$ matrices and $c \in \mathbb{R}^n$ is a given vector.
+Any choice of the values $x_i$ that satisfies the given constraint is called a \emph{feasible solution}.
+
+The special case when $A_1, \ldots A_n, B$ are diagonal matrices is a ''generic'' linear program, in fact we can think of semidefinite programs as generalizations of linear programs.
+Not all properties of linear programs are carried over to semidefinite programs, but the intuition is helpful.
+
+Solving semidefinite programs is a complex topic, we refer to \cite{grotschel1993} for reference.
+All we need to know is that we can solve semidefinite programs up to an error of $\epsilon$ in polynomial time.
+One of the methods to do this is called the \emph{ellipsoid method}, hence the name for the coloring algorithm.
+
+\paragraph{Calculating \boldmath$\vartheta$}
+
+Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all nonedges $ij$.
+An \emph{orthonormal} representation is an orthogonal representation with $|u_i| = 1$ for all $i$.
+The \emph{angle} of an orthogonal representation is the smallest half-angle of a rotational cone containing the representing vectors.
+
+\begin{theorem}[Proposition 5.1 of \cite{Lovasz95}]
+  The minimum angle $\phi$ of any orthogonal representation of $G$ is given by $\cos^2\phi = 1/\vartheta(G)$.
+\end{theorem}
+\TODO{mark all theorems everywhere accordingly}
+
+This leads us to definition of $\vartheta(G)$ in terms of semidefinite programming.
+
+\begin{theorem}[Proposition 5.3 of \cite{Lovasz95}]
+  $\vartheta(G)$ is the optimum of the following semidefinite program:
+
+  \begin{equation*}
+    \begin{array}{ll@{}ll}
+      \text{minimize}   & t      &                                              \\
+      \text{subject to} & Y      & \succeq 0                                    \\
+                        & Y_{ij} & = -1      & (\forall~ij \in E(\overline{G})) \\
+                        & Y_{ii} & = t - 1                                      \\
+    \end{array}
+  \end{equation*}
+
+  It is also the optimum of the dual program
+
+  \begin{equation*}
+    \begin{array}{l@{}rlll}
+      \text{maximize~~}   & \sum_{i \in V} \sum_{j \in V}  Z_{ij} &                                     \\
+      \text{subject to~~} & Z                                     & \succeq & 0                         \\
+                          & Z_{ij}                                & =       & 0 & (\forall~ij \in E(G)) \\
+                          & tr(Z)                                 & =       & 1                         \\
+    \end{array}
+  \end{equation*}
+\end{theorem}
+
+Any stable set $S$ of $G$ provides a feasible solution of the sual program, by choosing $Z_{ij} = \frac{1}{S}$, if $i, j \in S$ and 0 otherwise.
+Similarly, any $k$-coloring of $\overline{G}$ provides a feasible solution of the former semidefinite program, by choosing $Y_{ij} = -1$ if $i$ and $j$ have different colors, $Y_{ii} = k-1$, and $Y_{ij} = 0$ otherwise.
+
+Now, that we know how to calculate $\vartheta(G)$, let us describe the algorithm to calculate the coloring of $G$.
+
+\section{Coloring perfect graph using ellipsoid method}
 \label{sec:coloringEllipsoid}
@@
 
-\subsubsection{Maximum cardinality stable set}
+\subsection{Maximum cardinality stable set}
 
@@
 
-\subsubsection{Stable set intersecting all maximum cardinality cliques}
+\subsection{Stable set intersecting all maximum cardinality cliques}
 Next, let us show how to find a stable set intersecting all the maximum cardinality cliques of $G$.
@@
 
-\subsubsection{Minimum coloring}
+\subsection{Minimum coloring}
 
@@
 
-\subsection{Classical algorithms}
+\section{Classical algorithms}
 \label{sec:classicalColoring}

### 2020-09-08 paper/definitions.tex
Calculating \vartheta

@@
 \begin{defn}[connected graph, subset]
-  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$. \todo{formal enough?}
+  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$.
   A subset $X \subseteq V(G)$ is connected if the graph $G[X]$ is connected.
@@
 
-\begin{defn}[Berge graph]
-  \label{def:bergeGraph}
-  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
-\end{defn}
-
-\begin{defn}[perfect graph]
-  \label{def:perfectGraph}
-  A graph $G$ is \emph{perfect} if for its every induced subgraph $G'$ we have $\chi(G') = \omega(G')$
-\end{defn}
-
 \begin{defn}[C-major vertices]

### 2020-09-08 paper/perfectGraphs.tex
Algos and KT fixes
Calculating \vartheta

@@
 We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.
+This leads us to the definition of \emph{perfect graphs}
 
-A definition of perfect graphs (\cref{def:perfectGraph}) states that given a graph $G$, the chromatic number and cardinality of the largest clique of \emph{its every induced subgraph} should be equal.
+\begin{defn}[perfect graph]
+  \label{def:perfectGraph}
+  A graph $G$ is \emph{perfect} iff for its every induced subgraph $H$ we have $\chi(H) = \omega(H)$
+\end{defn}
+
 The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures some of the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum (weighted) clique problem, and maximum (weighted) independent set problem can be solved in polynomial time \cite{grotschel1993}.
@@
 The most fundamental problem -- the problem of recognizing perfect graphs -- was open since its posing in 1961 until recently.
-Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge (\cref{def:bergeGraph}) and an algorithm for recognizing Berge graphs in polynomial time (\cref{sec:recognizingBerge}).
+Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge and an algorithm for recognizing Berge graphs in polynomial time (\cref{sec:recognizingBerge}).
+
+\begin{defn}[Berge graph]
+  \label{def:bergeGraph}
+  A graph $G$ is \emph{Berge} iff both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
+\end{defn}
 
@@
 
-The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72}.
+The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by Lovász in 1972~\cite{LL72}.
 
@@
 
-This theorem is a consequence of a stronger result proven by \Lovasz:
+This theorem is a consequence of a stronger result proven by Lovász:
 \begin{theorem}
@@
 \end{theorem}
-\begin{proof}
-	\TODO{do we want it here? 1-2 pages long}
-\end{proof}
 

### 2020-09-08 paper/implementation.tex
Implementation rewrite heavy WIP

@@
-\TODO{link to repo}
+A repository containing the discussed source code and tests is available under the link: \href{https://github.com/AdrianSiwiec/Perfect-Graphs}{https://github.com/AdrianSiwiec/Perfect-Graphs}
+\todo{make repo public and add readme on howto run}
 
 \section{Berge graphs recognition: na\"ive approach}
-\TODO{rewrite to describe naive}
+When implementing an algorithm with the running time of $O(n^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is applicable at all.
+We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.\todo{well..
+there's this java impl} So, to test the usability of CCLSV implementation, we measured it against our own na\"ive Perfect recognition algorithm.
+Let us describe it briefly.
+
+We will try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is Perfect, else that it is not.
+
+To find an odd hole, we use a backtracking technique.
+We will enumerate all paths and holes and for each test if it is an odd hole.
+A partial solution to our problem is a path in $G$.
+To move forward from a partial solution, we append consecutively to its end all neighbors of current path's last vertex and continue recursively after each.
+When a current solution is an odd hole we return it.
+When we exhaust all possible paths from the current partial solution, we remove last vertex and continue.
+Also notice, that we can abandon ''paths'' that have chords.
+
+This backtracking algorithm is very simple, but has a great potential for optimizations in implementation.
+We also use path enumeration algorithm in CCLSV algorithm, so we give much attention to its optimization.
+
+\subsubsection{Path enumerating optimizations}
+Below, we will talk about enumerating all paths.
+This is a generalization of the problem of finding an odd hole, if we allow a path to have a single chord between the first and the last of its vertices iff the hole formed would be odd.
+
+First of all, there are many methods for generating all possible paths to choose from.
+We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no chords), but this would be too slow and render our algorithm unusable.
+
+We notice that returning a new path for each call of the method is wasteful.
+Therefore, we need a method that receives a reference to a path on the input (or a special flag indicating it should generate first path) and returns next path in some order (or a first path, or a code signaling all paths have been generated) using memory from the input.
+As this method will be used many, many times we require of it to work in place with constant additional space.
+
+With those requirements defined a simplest algorithm would be to implement a sort of a "counter" with base of $|V(G)|$.
+In short: we take a path on a input, increment its last vertex until it is a neighbor of the vertex one before last.
+Then we check if generated sequence is a path (all vertices unique and no chords).
+If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process.
+If still no path is found, we increment vertices closer to beginning of the path, until all a path is found or we check all candidates.
+
+But we can do much better with some care and a better data structure.
+For a given graph we create a data structure that suits best the goal of generating paths.
+In addition to having for each vertex a list of its neighbors we create data structure that will allow us to generate a candidate for next path in amortized $O(1)$ time.
+
+We have an array $first$ in which for each vertex is written its first neighbor on its neighbors list, and an array $next$ of size $|V(G)|^2$ where for each pair of vertices $a, b$ if $a$ and $b$ are connected, there is written a neighbor of $a$ that is next after $b$ in a neighbors list of $a$ (or a flag indicating $b$ is $a$'s last neighbor).
+Then, say our input is a path $v = v_1, \ldots v_k$.
+If $next[v_{k-1}][v_k]$ exists we change $v_k$ to $next[v_{k-1}][v_k]$ and return $v$.
+If it indicated that $v_k$ is $v_{k-1}$'s last neighbor, we set $v_{k-1}$ to $next[v_{k-2}][v_{k-1}]$ and then $v_k$ to $first[v_{k-1}]$ (or we go further back, if all neighbors of $v_{k-2}$ are done).
+
+This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of 20x\todo{check this}.
+
+Another crucial optimization is to eliminate partial solutions that have chords right away. This is especially useful in graphs that have many chords and reduces running time dramatically.
+
+\paragraph{Array unique}
+
+For each path candidate $v$ we call a subroutine $areUnique(v)$ to determine whether all vertices in it are unique.
+As this subroutine could be called many times for generating a single path, its optimization is very important.
+
+A theoretically optimal solution in general would be to have a hashing set of vertices.
+For each vertex in a path candidate, we check if it is already in a set.
+If it is, return that not all vertices are unique, else add it to the set.
+
+In our use case, a few optimizations can be made.
+First, we don't need a hashing set.
+We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there.
+Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this.
+Second, we notice that we don't need to create this array for each call of $areUnique$ procedure.
+Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called $areUnique$ method.
+For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique.
+Else we set $stamp[v_i] = counter$.
+When returning from the $areUnique$ method we increment $counter$.
+
+This optimization alone is crucial for performance.
+In our testing, all calls of $areUnique$ took abour 70\% of total running time of the CCLSV algorithm, and virtually all running time of the na\"ive algorithm \todo{check}.
+After using static $stamp$ array, it fell to 5.2\% in CCLSV and to X\% in na\"ive.
+The overall speedup of the CCLSV algorithm was about 6x.
+\todo{check if for sure it didn't use path speedup} The speedup of na\"ive algorithm was even greater -- about 20x.
+
+\paragraph{Other uses for path generation}
+\label{sec:usesGeneration}
+
+Because of a good performance of our optimized algorithm for generating paths, we use it whenever possible.
+It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the CCLSV algorithm.
+For example, when searching for Jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a Jewel.
+This proved to be much faster than generating vertices that don't have forbidden chords one by one.
+We use the same algorithm for generating starting vertices for a possible $T_2$ and $T_3$.
+
+With all those optimizations made, our na\"ive algorithm proved to be quite fast in some cases, although its running time is very dependent on the properties of the input, as we should expect from an optimized non-polynomial algorithm.
+See \cref{sec:experiments} for running times.
 
 \section{Berge graphs recognition: polynomial algorithm}
+
 \todo{rewrite/rearrange text below}
@@
 
-\subsubsection{Generating paths}
+Before any optimizatios, a major part of Berge recognition algorithm was being spent on enumerating all possible paths of given length -- this is done either to find a hole by itself, find a simple structure or check a possible near cleaner for amenable odd hole.
+Therefore optimizations of the path enumerating algorithm were also helpful in speeding up CCLSV implementation.
 
-\TODO{we also optimize na\"ive, in fact it makes a bigger difference there.}
-A major part of Berge recognition algorithm is spent on enumerating all possible paths of given length -- this is done either to find a hole by itself, find a simple structure or check a possible near cleaner for amenable odd hole.
-Therefore a quick method for generating paths, a problem that could seem trivial at first, is a crucial part to optimize and we give it much attention.
-
-First of all, there are many methods for generating all possible paths to choose from.
-We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no chords), but this would be too slow and render our algorithm unusable.
-
-We notice that nowhere in the algorithm we need all the paths at once.
-It would suffice for us to have a path, check if it has the properties we further require of it and then proceed to generate next path (in some ordering of paths).
-Therefore, we need a method that receives a path on the input (or a special flag indicating it should generate first path) and returns next path in some order (or a first path, or a code signaling all paths have been generated).
-As this method will be used many, many times we require of it to work in place with constant additional space.
-
-With those requirements defined a simplest algorithm would be to implement a sort of a "counter" with base of $|V(G)|$.
-In short: we take a path on a input, increment its last vertex until it is a neighbor of one before last vertex.
-Then we check if generated sequence is a path (all vertices unique and no chords).
-If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process.
-If still no path is found, we increment vertices closer to beginning of the path, until all a path is found or we check all candidates.
-
-This method is significantly faster than simply enumerating all combinations, but still leaves a problem of generating paths a main bottleneck of our algorithm (in our preliminary test it took about 70\% of running time for graphs with $|V(G)| = 10$ and growing with bigger graphs.
-
-But we can do much better with some care and better data structure.
-For a given graph we create a data structure that suits best the goal of generating paths.
-Instead of having for each vertex a list of its neighbors we create data structure that will allow us to generate a candidate for next path in amortized $O(1)$ time.
-
-We have an array $first$ in which for each vertex is written its first neighbor on its neighbors list, and an array $next$ of size $|V(G)|^2$ where for each pair of vertices $a, b$ if $a$ and $b$ are connected, there is written a neighbor of $a$ that is next after $b$ in a neighbors list of $a$ (or a flag indicating $b$ is $a$'s last neighbor).
-Then, say our input is a path $v = v_1, \ldots v_k$.
-If $next[v_{k-1}][v_k]$ exists we change $v_k$ to $next[v_{k-1}][v_k]$ and return $v$.
-If it indicated that $v_k$ is $v_{k-1}$'s last neighbor, we set $v_{k-1}$ to $next[v_{k-2}][v_{k-1}]$ and then $v_k$ to $first[v_{k-1}]$ (or we go further back, if all neighbors of $v_{k-2}$ are done).
-
-This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of 20x\todo{check this}, with much bigger speedup for na\"ive algorithm (around TODOx).
-
-\paragraph{Array unique}
-
-For each path candidate we call a subroutine to determine whether all vertices in it are unique.
-As this subroutine could be called many times for generating a single path, its optimization is very important.
-
-A theoretically optimal solution in general would be to have a hashing set of vertices.
-For each vertex in a path candidate, we check if it is already in a set.
-If it is, return that not all vertices are unique, else add it to the set.
-
-In our use case, a few optimizations can be made.
-First, we don't need a hashing set.
-We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there.
-Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this.
-Second, we notice that we don't need to create this array for each call of $unique$ procedure.
-Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called $unique$ method.
-For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique.
-Else we set $stamp[v_i] = counter$.
-When returning from the $unique$ method we increment $counter$.
-
-This optimization alone is crucial for performance.
-In our testing, all calls of $unique$ took abour 70\% of total running time of the algorithm.
-After using static $stamp$ array, it fell to 5.2\%.
-The overall speedup of the algorithm was about 6x.
-\todo{check if for sure it didn't use path speedup} The speedup of na\"ive algorithm was even greater -- about 20x.
-
-\paragraph{Other uses for path generation}
-\label{sec:usesGeneration}
-
-Because of a good performance of our optimized algorithm for generating paths use it whenever possible.
-It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the algorithm.
-For example, when searching for Jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a Jewel.
-This proved to be much faster than generating vertices that don't have forbidden chords one by one.
-We use the same algorithm for generating starting vertices for a possible $T_2$ and $T_3$.
+\TODO{bitsets}
 
@@
 \subsection{Experiments}
+\label{sec:experiments}
 

### 2020-09-09 paper/experiments.tex
experiments wip

\subsection{Experiments}
\label{sec:experiments}

Let us describe experiments and their results. All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one. Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.

\paragraph{Random perfect graphs}
Our first method of generating graphs is to set $|V|$ and for each pair of vertices $u, v$ let $uv$ be the edge with probability of $1/2$. Then we check if generated graph is perfect and continue as long as we don't get sufficient number of perfect graphs.

First, we note that this method of generating perfect graphs is very inefficient and we couldn't generate any graphs with $|V| \geq 20$. Second, those graphs favour the na\"ive algortihm, because there is very low probability of long chordless paths to appear (each chord has a $1/2$ chance to appear).

When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we ser the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV. Slight GPU improvement is explained by anylysis of the components of the overall time (\Cref{plot:perfDet}). Testing all near cleaners takes up around half of total time, so we cannot speed up the overall time by much. These are also relatively small tests, so the latency from copying data to the GPU is significant.

\begin{figure}
  \centering
  \input{plots/perf.t.in.out.csv.lines.pgf}
  \caption{Random perfect graphs}
  \label{plot:perfLines}
\end{figure}

\begin{figure}
  \centering
  \input{plots/perf.t.in.out.csv.detailed.pgf}
  \caption{Random perfect graphs}
  \label{plot:perfDet}
\end{figure}

\paragraph{Random bipartite graphs}
\TODO{TODO}

\paragraph{Line graphs of random bipartite graphs}
\TODO{data with bigger N}
Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs. We repeated the process until we had sufficieng number of graphs for each $|V|$. On \cref{plot:perf2Lines} we can see GPU gives us much better improvement than in random graphs. This is due to the fact, that testing near cleaners takes over 80\% of the time for bigger graphs (\Cref{plot:perf2Det}).

\begin{figure}
  \centering
  \input{plots/perf2.t.in.out.csv.lines.pgf}
  \caption{Line graphs of random bipartite graphs}
  \label{plot:perf2Lines}
\end{figure}

\begin{figure}
  \centering
  \input{plots/perf2.t.in.out.csv.detailed.pgf}
  \caption{Line graphs of random bipartite graphs}
  \label{plot:perf2Det}
\end{figure}

\paragraph{Lattice graphs}

\begin{figure}
\input{tikzpictures/graphs.tex}
\end{figure}

Next, we turn our attention to graphs generated on a grid, or a checker board (see later paragraphs). First, we take lattice graphs. In lattice graph, each vertex is connected to vertices that are above, below, to the left and to the right of it, if such vertices exist.

Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\

Description of tests used.\\

Results and Corollary - almost usable algorithm.

\section{Coloring Berge Graphs}

\subsection{Ellipsoid method}

We used an open source CSDP \cite{csdpRepo, csdp1999} library, that implements predictor corrector variant of the semidefinite programming algorithm to calculate $\vartheta(G)$, given $G$ on the input. The CSDP library has been used in many recent publications across different fields, such as \cite{Ampountolas_2017, Adasme_2011}.

Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm. With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}. Our main goal of the implementation was to check if this method is still impractical, even on modern equipment. Let us proceed straight to experiments and results.

\subsubsection{Experiments and results}

\subsection{Combinatorial Method}

Cite the paper.\\

On its complexity - point to appendix for pseudo-code.

### 2020-09-09 paper/implementation.tex
experiments wip

@@
 \TODO{implement other CUDA opts and describe them}
-
-\subsection{Experiments}
-\label{sec:experiments}
-
-\begin{figure}
-  \centering
-  \input{plots/hypercubes16to50.t.in.out.csv.lines.pgf}
-  \caption{testPlot 1}
-  % \label{fig:LCA_batch}
-\end{figure}
-
-Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\
-
-Description of tests used.\\
-
-Results and Corollary - almost usable algorithm.
-
-\section{Coloring Berge Graphs}
-
-\subsection{Ellipsoid method}
-
-We used an open source CSDP \cite{csdpRepo, csdp1999} library, that implements predictor corrector variant of the semidefinite programming algorithm to calculate $\vartheta(G)$, given $G$ on the input.
-The CSDP library has been used in many recent publications across different fields, such as \cite{Ampountolas_2017, Adasme_2011}.
-
-Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm.
-With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}.
-Our main goal of the implementation was to check if this method is still impractical, even on modern equipment.
-Let us proceed straight to experiments and results.
-
-\subsubsection{Experiments and results}
-
-\subsection{Combinatorial Method}
-
-Cite the paper.\\
-
-On its complexity - point to appendix for pseudo-code.

### 2020-09-09 code/test/plot.py

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-usePgf = True
-# usePgf = False
+# usePgf = True
+usePgf = False
 
 import matplotlib as mpl
 
@@ -41,7 +41,7 @@ csv_numRuns = "num_runs"
 csv_simpleStructures = "Simple Structures"
 csv_getNearCleaners = "Get Near Cleaners"
 csv_testNCShortestPaths = "Test NC Shortest Paths"
-csv_gpuCopyR = "GPU Test NC Copy R"
+csv_gpuCopyR = "GPU Test NC Copy"
 csv_gpuWork = "GPU Test NC work"
 csv_testNCRest = "Test NC Rest"
 csv_cpuPreparation = "CPU Preparation"
@@ -134,11 +134,11 @@ field_colors = {
 }
 
 sizes_in_inches = {
-    "regular": (4.77, 3.5),
+    "regular": (4.77, 3),
     "wide": (6.8, 2.4),
     "huge": (6.8, 8),
     "allGraphs": (10, 25),
-    "wideDetailed": (4.77, 4),
+    "wideDetailed": (4.77, 3.5),
 }
 # sizes_in_inches = {"regular": (5, 3), "wide": (8, 3)}
 
@@ -171,6 +171,36 @@ experiments = [
         "ylog": False,
         "x_label": "N",
         "y_label": label_time_overall_s,
+    },
+    {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_filename, "perf.t.in"),
+            # (csv_N, "20|25|30|35|40|45|50|55"),
+            (csv_algo, "GPU Perfect|Perfect"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "detailed",
+        "size": sizes_in_inches["wideDetailed"],
+        "x_label": "N",
+        "y_label": label_time_percentage,
+        "ylim": (0, 1),
+    },
+      {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_filename, "perf2.t.in"),
+            (csv_N, "15|16|17|18|19"),
+            (csv_algo, "GPU Perfect|Perfect"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "detailed",
+        "size": sizes_in_inches["wideDetailed"],
+        "x_label": "N",
+        "y_label": label_time_percentage,
+        "ylim": (0, 1),
     },
     {
         "restrictions": [

### 2020-09-09 paper/experiments.tex
Graphs tikz
Plots

@@
 \label{sec:experiments}
+
+\subsubsection{Data sets}
 
@@
 Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.
+
+We ran tests on X classes of perfect graphs, see \Cref{fig:graphClasses} for some examples:
+\begin{itemize}
+  \item Random perfect graphs,
+  \item Random bipartite graphs,
+  \item Line graphs of random bipartite graphs,
+  \item Lattice graphs (\cref{fig:lattice}),
+  \item Rook graphs (\cref{fig:rook}),
+  \item Knight graphs (\cref{fig:knight}),
+  \item Hypercube graphs (\cref{fig:hypercube}),
+  \item Split graphs (\cref{fig:split}).
+\end{itemize}
+
+In later paragraphs we describe each class one by one and benchmark our implementations on them.
+
+\begin{figure}
+  \input{tikzpictures/graphs.tex}
+  \caption{Graph classes}
+  \label{fig:graphClasses}
+\end{figure}
 
@@
 
+\TODO{Better plot by a lot WIP}
+
 \begin{figure}
+  \begin{subfigure}{\textwidth}
     \centering
@@
     \label{plot:perfLines}
-\end{figure}
+  \end{subfigure}
 
-\begin{figure}
+  \begin{subfigure}{\textwidth}
     \centering
@@
     \label{plot:perfDet}
+  \end{subfigure}
+  \caption{Random perfect graphs}
 \end{figure}
@@
 \begin{figure}
+  \begin{subfigure}{\textwidth}
     \centering
@@
     \label{plot:perf2Lines}
-\end{figure}
+  \end{subfigure}
 
-\begin{figure}
+  \begin{subfigure}{\textwidth}
     \centering
@@
     \label{plot:perf2Det}
+  \end{subfigure}
+  \caption{Line graphs of random bipartite graphs}
 \end{figure}
@@
 
-\begin{figure}
-\input{tikzpictures/graphs.tex}
-\end{figure}
-
 Next, we turn our attention to graphs generated on a grid, or a checker board (see later paragraphs).
@@
 In lattice graph, each vertex is connected to vertices that are above, below, to the left and to the right of it, if such vertices exist.
+See \cref{fig:lattice} for an example of $4 \times 4$ lattice.
 
-Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\
+Let us take a look at \cref{plot:gridLines}.
+It is a clear example of why polynomial algorithms can be useful, even the ones with time complexity as high as CCLSV.
+For $|V| = 48$ the running time for the CCLSV is 22.2s, for GPU CCLSV is 7.7s and for na\"ive is 1.5s.
+Na\"ive is almost 15x faster.
+But with growing $|V|$ its running time grows very fast, reaching 41s for $|V| = 60$ and 210s for $|V| = 66$.
+CCLSV growth is much gentler and for $|V| = 66$ it is 2.5x faster than na\"ive.
 
-Description of tests used.\\
+With growing $|V|$ also grows the speedup gained from utilizing GPU. For $|V| = 78$ the running time for the whole algorithm is almost 3x better.
 
-Results and Corollary - almost usable algorithm.
+\begin{figure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+    \label{plot:gridLines}
+  \end{subfigure}
 
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/grid6by5to11.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:gridDet}
+  \end{subfigure}
+  \caption{Lattice graphs}
+\end{figure}
+
+\paragraph{Rook graphs}
+
+If we imagine our grid to be a chessboard we can define a Rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
+See \cref{fig:rook} for an example of $4 \times 4$ Rook graph.
+
+Rook graphs have many more chords than Lattice graphs, so the na\"ive's performance is much better here.
+What is more interesting, the overall performance of CCLSV is much worse (\cref{plot:rookLines}).
+Looking at \cref{fig:rookDet} we can see that the majority of CCLSV time is spent checking all near cleaners.
+This can be explained by the fact that rook graphs are much denser than lattice graphs and have many more 3-vertex paths (see \cref{alg:testNearCleaner}).
+This is confirmed by greater CCLSV GPU speedup of around 6x on graph with $|V| = 35$.
+
+\begin{figure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+    \label{plot:rookLines}
+  \end{subfigure}
+
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/rookGraph5by4to7.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:rookDet}
+  \end{subfigure}
+  \caption{Rook graphs}
+\end{figure}
+
+\paragraph{Knight graph}
+
+A knight graph is constructed in a similar way to rook graph, but by taking potential moves of a knight.
+
+\TODO{add 800s result for naive}
+
+\begin{figure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+    \label{plot:knightLines}
+  \end{subfigure}
+
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:knightDet}
+  \end{subfigure}
+  \caption{Knight graphs}
+\end{figure}
+
+\paragraph{Hypercube graphs}
+
+A hypercube is a generalization of a cube to a higher dimensional space.
+We use hypercubes that are not complete, to achieve higher granularity of data.
+In a hypercube of $n$ vertices there is an edge between vertices $u$ and $v$ iff binary representations of $u$ and $v$ differ by exactly one bit.
+
+Hypercube graphs tell a similar story to lattice graphs and knight graphs.
+Na\"ive is very fast at first, but becomes unbearably slow for $|V|$ higher than 55.
+Unfortunately, CCLSV doesnt fare much better, although it grows slower.
+Again, the speedup of GPU CCLSV is noticeable, being around 4.8x for $|V| = 55$.
+
+\begin{figure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+    \label{plot:hypercubeLines}
+  \end{subfigure}
+
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:hypercubeDet}
+  \end{subfigure}
+  \caption{Hypercube graphs}
+\end{figure}
+
+\paragraph{Split graphs}
+
+Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
+In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.
+
+There are no long chordless paths here, so na\"ive fares great (\cref{plot:splitLines}).
+What is interesting, when looking at detailed times of GPU CCLSV, we can see that checking the existence of simple forbidden structures takes more than 30\% of the time.
+This opens a possibility of further GPU speedups, as previous tests indicated that checking simple forbidden structures is usually very quick on the CPU.
+
+\begin{figure}
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/split20to50.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+    \label{plot:splitLines}
+  \end{subfigure}
+
+  \begin{subfigure}{\textwidth}
+    \centering
+    \input{plots/split20to50.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:splitDet}
+  \end{subfigure}
+  \caption{Split graphs}
+\end{figure}
+
+\pagebreak
 \section{Coloring Berge Graphs}
@@
 The CSDP library has been used in many recent publications across different fields, such as \cite{Ampountolas_2017, Adasme_2011}.
+
+\TODO{setting $\epsilon = 1/2$ in csdp helped a lot -- how much?}
 
@@
 
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.perf.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.perf.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+  \end{subfigure}
+  \caption{Random perfect graphs}
+\end{figure}
+
+\begin{figure}
+  \TODO{TODO}
+  % \begin{subfigure}{.5\textwidth}
+  %   \centering
+  %   \input{plots/color.perf2.t.in.out.csv.lines.pgf}
+  %   \caption{Overall running times}
+  %   \label{plot:colorPerfLines}
+  % \end{subfigure}%
+  % \begin{subfigure}{.5\textwidth}
+  %   \centering
+  %   \input{plots/color.perf2.t.in.out.csv.detailed.pgf}
+  %   \caption{Percentage of time taken be each part}
+  %   \label{plot:colorPerfDet}
+  % \end{subfigure}
+  \caption{Line graphs of random bipartite graphs}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.grid5by4to9.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.grid5by4to9.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+  \end{subfigure}
+  \caption{Lattice graphs}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.rookGraph6by4to8.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.rookGraph6by4to8.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+    \label{plot:colorRookDet}
+  \end{subfigure}
+  \caption{Rook graphs}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.knightGraph6by4to8.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.knightGraph6by4to8.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+  \end{subfigure}
+  \caption{Knight graphs}
+\end{figure}
+
+\begin{figure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.hypercube20to40.t.in.out.csv.lines.pgf}
+    \caption{Overall running times}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.hypercube20to40.t.in.out.csv.detailed.pgf}
+    \caption{Percentage of time taken be each part}
+  \end{subfigure}
+  \caption{Hypercube graphs}
+\end{figure}
+
+\begin{figure}
+  \TODO{TODOa}
+  % \begin{subfigure}{.5\textwidth}
+  %   \centering
+  %   \input{plots/color.perf2.t.in.out.csv.lines.pgf}
+  %   \caption{Overall running times}
+  %   \label{plot:colorPerfLines}
+  % \end{subfigure}%
+  % \begin{subfigure}{.5\textwidth}
+  %   \centering
+  %   \input{plots/color.perf2.t.in.out.csv.detailed.pgf}
+  %   \caption{Percentage of time taken be each part}
+  %   \label{plot:colorPerfDet}
+  % \end{subfigure}
+  \caption{Split graphs}
+\end{figure}
+
+A few things of note.
+We notice that in rook graphs the graph manipulation other than calculating CSDP takes close to half of overall running time (\cref{plot:colorRookDet}).
+We didn't particularly optimize this, other than by use of methods developed for Berge graph recognition algorithm.
+There are surely some optimizations to be made here if need be.
+Altough, as we can see on other plots, it won't help im majority of the cases.
+
 \subsection{Combinatorial Method}

### 2020-09-09 code/test/plot.py

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-# usePgf = True
-usePgf = False
+usePgf = True
+# usePgf = False
 
 import matplotlib as mpl
 
@@ -139,6 +139,8 @@ sizes_in_inches = {
     "huge": (6.8, 8),
     "allGraphs": (10, 25),
     "wideDetailed": (4.77, 3.5),
+    "regular_small": (2.38, 1.5),
+    "wideDetailed_small": (2.38, 1.5),
 }
 # sizes_in_inches = {"regular": (5, 3), "wide": (8, 3)}
 
@@ -274,6 +276,20 @@ experiments = [
         "y_label": label_time_percentage,
         "ylim": (0, 1),
     },
+    {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_filename, "split"),
+            (csv_algo, "GPU Perfect|Perfect"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "detailed",
+        "size": sizes_in_inches["wideDetailed"],
+        "x_label": "N",
+        "y_label": label_time_percentage,
+        "ylim": (0, 1),
+    },
     #
     # COLOR
     #
@@ -282,7 +298,7 @@ experiments = [
         "x_param": csv_N,
         "x_show": csv_N,
         "type": "lines",
-        "size": sizes_in_inches["regular"],
+        "size": sizes_in_inches["regular_small"],
         "y_param": csv_overall,
         "ylog": False,
         "x_label": "N",
@@ -294,7 +310,7 @@ experiments = [
         "x_param": csv_N,
         "x_show": csv_N,
         "type": "detailed",
-        "size": sizes_in_inches["wideDetailed"],
+        "size": sizes_in_inches["wideDetailed_small"],
         "x_label": "N",
         "y_label": label_time_percentage,
         "ylim": (0, 1),

### 2020-09-11 paper/coloringBergeGraphs.tex
Save!

@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
   Let $v_1, \ldots v_n$ be an ordering of vertices of $G$.
@@
   Return $G_n$.
-\end{algtext}
+\end{algtext2}
 
@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
   We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$.
@@
 
-\end{algtext}
+\end{algtext2}
 
@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
   If $G$ is equal to its maximum cardinality stable set, color all vertices one color and return.
@@
 Color recursively all vertices of $G \setminus S$ with $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors and all vertices of $S$ with one additional color.
-\end{algtext}
+\end{algtext2}
 

### 2020-09-11 paper/perfectGraphs.tex
Save!

@@
 
+% \begin{algorithm}
+% 	\SetKwFunction{ContainsPyramid}{\textsc{Contains-Pyramid}}
+% 	% \Indm\nonl\ContainsPyramid{$G$}\\
+% 	\KwData{$G = (V, E)$ -- a graph}
+% 	\KwResult{Whether $G$ contains a pytamid as an induced subgraph.}
+% 	\Indp
+
+% 	\ForEach{ triangle $b_1, b_2, b_3$ }{
+% 		\ForEach{ $s_1, s_2, s_3$, such that for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them }{
+% 			\If{ there is a vertex $a$, adjacent to all of $s_1, s_2, s_3$, and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ } {
+% 				$M \gets V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$\;
+% 				\ForEach{$m \in M$} {
+% 					$S_1(m) \gets$ the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists. \;
+% 					Calculate $S_2(m), S_3(m)$ similarly\;
+% 					$T_1(m) \gets$ the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists\;
+% 					Calculate $T_2(m), T_3(m)$ similarly\;
+% 				}
+% 				\ForEach{$m \in M \cup \{b_1\}$}{
+% 					\If{$s_1 = b_1$}{
+% 						$P_1(b_1) \gets$ the one-vertex path with vertex $b_1$\;
+% 						$\forall_{m \in M}: P_1(m) \gets$ \textsc{undefined}\;
+% 					} \Else{
+% 						$P_1(b_1) \gets $ \textsc{undefined}\;
+% 						\ForEach{$m \in M$}{
+% 							\If{all the following are true:
+% 								\begin{itemize}
+% 									\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
+% 									\item $S_1(m)$ and $T_1(m)$ both exist
+% 									\item $V(S_1(m) \cap T_1(m)) = \{m\}$
+% 									\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
+% 								\end{itemize}
+% 							}
+% 							{
+% 								TODO\;
+% 							}
+% 						}
+% 					}
+% 				}
+% 			}
+% 		}
+% 	}
+
+% 	\label{aab}
+% 	\caption{Contains-Pyramid}
+% \end{algorithm}
+
 \begin{alg}[Test if $G$ contains a Pyramid]
@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
 
@@
 Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
-\end{algtext}
+\end{algtext2}
 
@@
 If we exhaust our search and find none, report that graph does not contain it.
-\end{algtext}
+\end{algtext2}
 
@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
 	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
@@
 	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
-\end{algtext}
+\end{algtext2}
 
@@
 \end{alg}
-\begin{algtext}
+\begin{algtext2}
 	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$.
@@
 	If there is such a choice of $x_1$, $x_2$, $x_3$, $y_1$ then we output that there is an odd hole. If not, we report that there is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
-\end{algtext}
+\end{algtext2}
 

### 2020-09-11 paper/perfectGraphs.tex
algoritmicx works with algorithm2e lolz
Contains Pyramid WIP

--- 2020-09-08 paper/perfectGraphs.tex
@@
 \paragraph{Finding Pyramids}
-
 \begin{alg}[Test if $G$ contains a Pyramid]
@@
 \end{alg}
-\begin{algtext}
+\begin{algorithmic}[1]
+	\mProcedure{Contains-Pyramid}{$G$}
+	\mForEach{triangle $b_1, b_2, b_3$}
+		\mForEach{$s_1, s_2, s_3$, such that for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint
+			\lsx  from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them}
+			\mIf{there is a vertex $a$, adjacent to all of $s_1, s_2, s_3$, and to at most
+				\lsx one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ \lsx}
+				\ls $M \gets V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$
+				\mForEach{$m \in M$}
+					\ls $S_1(m) \gets$ the shortest path between $s_1$ and $m$ such that
+					\lsx $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a 
+					\lsx path exists.
+					\ls calculate $S_2(m), S_3(m)$ similarly
+					\ls $T_1(m) \gets$ the shortest path between $m$ and $b_1$, such that
+					\lsx $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a
+					\lsx path exists
+					\ls calculate $T_2(m), T_3(m)$ similarly
+				\mEndFor
+				\mForEach{$m \in M \cup \{b_1\}$}
+					\mIf{$s_1 = b_1$}
+						\ls $P_1(b_1) \gets$ the one-vertex path with vertex $b_1$
+						\ls \algorithmicforeach ~$m \in M$ \algorithmicdo~ $P_1(m) \gets$ \textsc{undefined}
+					\mElse
+						\ls $P_1(b_1) \gets $ \textsc{undefined}
+						\mForEach{$m \in M$}
+							\mIf{ $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$ \AND
+								\lsx $S_1(m)$ and $T_1(m)$ both exist \AND
+								\lsx $V(S_1(m) \cap T_1(m)) = \{m\}$ \AND
+								\lsx there are no edges between $V(S_1(m) \setminus m)$ 
+								\lsx and $V(T_1(m) \setminus m)$ 
+								\lsx
+							}
+								\ls $P_1(m) \gets s_1-S_1(m)-m-T_1(m)-b_1$
+							\mElse
+								\ls $P_1(m) \gets$ \textsc{undefined}
+							\mEndIf
+						\mEndFor
+					\mEndIf
+				\mEndFor
+				\ls assign $P_2$ and $P_3$ in a similar manner
+				\ls $good\_pairs_{1,2} \gets \emptyset$
+				\mForEach{$m_1 \in M \cup \{b_1\}$} \Comment{calculate good $(1, 2)$-pairs}
+					\mIf{$P_1(m_1) \neq \UND$}
+						\ls color black the vertices of $M$ that either belong to
+						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
+						\lsx color all other vertices white.
+						\mForEach{$m_2 \in M \cup \{b_2\}$}
+							\mIf{$P_2(m_2)$ exists and contains no black vertices}
+								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
+							\mEndIf
+						\mEndFor
+					\mEndIf
+				\mEndFor
+				\ls calculate $good\_pairs_{1,3}$ and $good\_pairs_{2,3}$ in similar way
+				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$}
+					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
+						\ls \RETURN \TRUE
+					\mEndIf
+				\mEndFor
+			\mEndIf
+		\mEndFor
+	\mEndFor
+	\ls \RETURN \FALSE
+	\mEndProcedure
+\end{algorithmic}
+
+\begin{algtext2}
 

### 2020-09-11 paper/perfectGraphs.tex
Pyramids look nice

@@
 \paragraph{Finding Pyramids}
+
 \begin{alg}[Test if $G$ contains a Pyramid]
@@
 	\mProcedure{Contains-Pyramid}{$G$}
-	\mForEach{triangle $b_1, b_2, b_3$}
+	\mForEach{triangle $b_1, b_2, b_3$} \label{line:pyramidTriangle}
 		\mForEach{$s_1, s_2, s_3$, such that for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint
-			\lsx  from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them}
+			\lsx  from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them} \label{line:pyramidTriple}
 			\mIf{there is a vertex $a$, adjacent to all of $s_1, s_2, s_3$, and to at most
-				\lsx one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ \lsx}
+				\lsx one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $b_i = s_i$ \lsx}\label{line:a}
 				\ls $M \gets V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$
-				\mForEach{$m \in M$}
+				\mForEach{$m \in M$} \label{line:pyramidSStart}
 					\ls $S_1(m) \gets$ the shortest path between $s_1$ and $m$ such that
@@
 					\ls calculate $T_2(m), T_3(m)$ similarly
-				\mEndFor
-				\mForEach{$m \in M \cup \{b_1\}$}
-					\mIf{$s_1 = b_1$}
+				\mEndFor \label{line:pyramidSEnd}
+
+					\mIf{$s_1 = b_1$} \Comment{calculate all possible $P_1$ paths}
 						\ls $P_1(b_1) \gets$ the one-vertex path with vertex $b_1$
@@
 					\mEndIf
-				\mEndFor
+
 				\ls assign $P_2$ and $P_3$ in a similar manner
-				\ls $good\_pairs_{1,2} \gets \emptyset$
+				\ls $good\_pairs_{1,2} \gets \emptyset$ \Comment{see below for definition}
 				\mForEach{$m_1 \in M \cup \{b_1\}$} \Comment{calculate good $(1, 2)$-pairs}
 					\mIf{$P_1(m_1) \neq \UND$}
-						\ls color black the vertices of $M$ that either belong to
+						\ls color black the vertices of $M$ that either belong to \label{line:pyramidColor}
 						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
@@
 						\mForEach{$m_2 \in M \cup \{b_2\}$}
-							\mIf{$P_2(m_2)$ exists and contains no black vertices}
+							\mIf{$P_2(m_2)$ exists and contains no black vertices} \label{line:pyramidColor2}
 								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
@@
 				\ls calculate $good\_pairs_{1,3}$ and $good\_pairs_{2,3}$ in similar way
-				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$}
+				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$} \label{line:m1m2m3}
 					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
-						\ls \RETURN \TRUE
+						\ls \RETURN \TRUE \label{line:pyramidTrue}
 					\mEndIf
 				\mEndFor
-			\mEndIf
+			\mEndIf \label{line:pyramidEnd}
 		\mEndFor
@@
 
-\begin{algtext2}
+With definitions as above, for $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
 
-	Enumerate all 6-tuples $(b_1, b_2, b_3, s_1, s_2, s_3)$ such that:
-	\begin{itemize}
-		\item $\{b_1, b_2, b_3\}$ is a triangle
-		\item for $1 \leq i < j \leq 3$, $\{b_i, s_i\}$ is disjoint from $\{b_j, s_j\}$ and $b_ib_j$ is the only edge between them
-		\item there is a vertex $a$ adjacent to all of $s_1, s_2, s_3$ and to at most one of $b_1, b_2, b_3$, such that if $a$ is adjacent to $b_i$, then $s_i = b_i$.
-	\end{itemize}
+It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ it was found for via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}.
+The proof of the converse is rather technical and we refer to \cite{MC05} for it.
 
-	There are $O(|V(G)|^6)$ 6-tuples, and for each we check above conditions in $O(|V(G)|)$ time. For each such 6-tuple we follow with the rest of the algorithm.
+Now we will proove the time complexity.
 
-	Let $M \leftarrow V(G) \setminus \{b_1, b_2, b_3, s_1, s_2, s_3\}$.
+\begin{theorem}
+	Procedure \textsc{Contains-Pyramid($G$)} works in $O(|V|^9)$ time.
+\end{theorem}
+\begin{proof}
+	There are $O(|V|^3)$ triangles (line \ref{line:pyramidTriangle}) and $O(|V|^3)$ triples $s_1$, $s_2$, $s_3$ (line \ref{line:pyramidTriple}), so lines \ref{line:a}-\ref{line:pyramidEnd} are executed at most $O(|V|^6)$ times.
 
-	For each $m \in M$, set $S_1(m)$ equal to the shortest path between $s_1$ and $m$ such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists.
-Set $S_2$ and $S_3$ similarly.
-Set $T_1(m)$ to be the shortest path between $m$ and $b_1$, such that $s_2, s_3, b_2, b_3$ have no neighbors in its interior, if such a path exists, and set $T_2$, $T_3$ similarly.
-It takes $O(|V(G)|^2)$ time to calculate paths $S_i(m)$ and $T_i(m)$ for all $i$ and $m$.
+	Checking if there exists an appropriate $a$ takes linear time (line \ref{line:a}).
+Calculating paths $S_i$ and $T_i$ (lines \ref{line:pyramidSStart}-\ref{line:pyramidSEnd}) takes $O(|V|^2)$ time for each $m \in M$ and $O(|V|^3)$ in total.
+Similarly, it takes $O(|V|^3)$ time to calculate all $P_i$ paths.
 
-	Now, we will calculate all possible paths $P_i$. For each $m \in M \cup \{b_1\}$ we will define a path $P_1(m)$ with paths $P_2(m)$, $P_3(m)$ defined in a similar manner.
+	Then, for each $m_1$ we do at most $O(|V|)$ work in line \ref{line:pyramidColor} and for each $(m_1, m_2)$ we do at most $O(|V|)$ work in line \ref{line:pyramidColor2}.
 
-	If $s_1 = b_1$ let $P_1(b_1)$ be the one-vertex path with vertex $b_1$, and let $P_1(m)$ be undefined for each $m \in M$.
-
-	If $s_1 \neq b_1$, then $P_1(b_1)$ is undefined and for all $m \in M$ we will check if all the following are true:
-	\begin{itemize}
-		\item $m$ is nonadjacent to all of $b_2, b_3, s_2, s_3$
-		\item $S_1(m)$ and $T_1(m)$ both exist
-		\item $V(S_1(m) \cap T_1(m)) = \{m\}$
-		\item there are no edges between $V(S_1(m) \setminus m)$ and $V(T_1(m) \setminus m)$
-	\end{itemize}
-	If it is true for some $m \in M$, then we assign $P_1(m) \leftarrow s_1-S_1(m)-m-T_1(m)-b_1$, otherwise we let $P_1(m)$ be undefined.
-It takes $O(|V(G)|^2)$ to check this, for a given $m$.
-We assign $P_2$ and $P_3$ in a similar manner.
-Total time of finding all $P_i(m)$ paths for a given 6-tuple is $O(|V(G)|^3)$.
-
-	Now we want to check if there is a triple $m_1, m_2, m_3$, so that $P_1(m_1)$, $P_2(m_2)$, $P_3(m_3)$ form a pyramid.
-A most obvious approach of enumerating them all would be too slow, so we do it carefully.
-
-	For $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
-
-	We show how to find the list of all good $(1, 2)$-pairs, with similar algorithm for all other good $(i, j)$-pairs.
-For each $m_1 \in M \cup \{b_1\}$, we find the set of all $m_2$ such that $(m_1, m_2)$ is a good $(1,2)$-pair as follows.
-
-	If $P_1(m_1)$ does not exist, there are no such good pairs.
-If it exists, color black the vertices of $M$ that either belong to $P_1(m_1)$ or have a neighbor in $P_1(m_1)$.
-Color all other vertices white.
-(We can do this in $O(|V(G)|^2)$) Then for each $m_2 \in M \cup \{b_2\}$, test whether $P_2(m_2)$ exists and contains no black vertices.
-We do this for all $m_1$ and get a set of all $(1,2)$-good pairs.
-In similar way we calculate all good $(1,3)$-pair and $(2,3)$-pairs (in $O(|V(G)|^3)$ time).
-
-	Now, we examine all triples $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$ and test whether $(m_i, m_j)$ is a good $(i, j)$-pair.
-If we find a triple such that all three pairs are good, we output that G contains a pyramid and stop.
-
-	If after examining all choices of $b_1, b_2, b_3, s_1, s_2, s_3$ we find no pyramid, output that $G$ contains no pyramid.
-Since there are $O(|V(G)|^6)$ such choices and it takes a time of $O(|V(G)|^3)$ to analyze each one, the total time is $O(|V(G)|^9)$.
-\end{algtext2}
-
-It is easy to see, that if algorithm outputs that $G$ contains a pyramid, it indeed does. The proof of the converse is rather technical and we refer to \cite{MC05} for it.
+	Finally, there are $O(|V|^3)$ pairs $m_1, m_2, m_3$ and checking each takes $O(1)$ time.
+\end{proof}
 
@@
 
-\begin{lemma}
+\begin{theorem}
 	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
-\end{lemma}
+\end{theorem}
 \begin{proof}
@@
 \end{alg}
-\begin{algtext2}
+% \begin{algorithmic}
+% 	\mProcedure{Contains-T3}{$G$}
+% 	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges}
+% 	\mEndFor
+% 	\mEndProcedure
+% \end{algorithmic}
+% \begin{algorithmic}[1]
+% 	\mProcedure{Contains-Pyramid}{$G$}
+% 	\ls \RETURN \FALSE
+% 	\mEndProcedure
+% \end{algorithmic}
+
+% \begin{algtext2}
 
@@
 If we exhaust our search and find none, report that graph does not contain it.
-\end{algtext2}
+% \end{algtext2}
 

### 2020-09-12 paper/coloringAppendix/algVII.tex
Algos and KT fixes
Fixes KT

--- 2020-05-20 paper/algVII.tex
@@
   saturates $L(H)$ but does not saturate $L(H')$\;
-  \Assert{$R_{ij} \neq R'_{ij} \iff \{i, j\} = [2]$}
+  \Assert{$R_{ij} \neq R'_{ij} \if and only if \{i, j\} = [2]$}
   $r_{ij}, r_{ji} \gets$ ends of each $R_{ij}$\;
@@
   \Assert{$T_3 = T'_3, T_4 = T'_4$}
-  relabel $G$ and $J$, so that $|X \cap T_1| = 2$ and $|X \cap T'_1| = 1$\;
+  relabel 1 and 2 in $J$, so that $|X \cap T_1| = 2$ and $|X \cap T'_1| = 1$\;
   \Assert{$r_{12} \in X, r'_{12} \notin X$}
   \Assert{$r_{13} \in X \xor r_{14} \in X$}
-  relabel $G$ and $J$, so that $r_{13} \in X, r_{14} \notin X$\;
+  relabel 3 and 4 in $J$, so that $r_{13} \in X, r_{14} \notin X$\;
   \Assert[6.3.(3)]{$R_{34}$ is even and $[X \cap V(L(H'))] \setminus V(R_{34}) = \{r_{31}, r_{32}, r_{41}, r_{42} \}$}
@@
   }
+  \vspace{-10cm}
 \end{algorithm}

### 2020-09-12 paper/coloringBergeGraphs.tex
Fixes KT

@@
 A natural problem for perfect graphs is a problem of coloring them.
-In 1988 Martin Grötschel et al.
+In 1988 Gr\"otschel et al.
 published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}.
@@
 
-\Cref{sec:InformationTheory} and \cref{sec:computingTheta} are based on excellent lecture notes by Lovász \cite{Lovasz95}.
+\Cref{sec:InformationTheory} and \cref{sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.
 
@@
 The connection of coloring graphs and the cones of semi-definite matrices might be surprising, so let us take a brief digression into the field of information theory, where we will see the connection more clearly.
-Also, this is the background which motivated Berge to introduce perfect graphs \cite{Chudnovsky2003}.
+Also, this was exactly the background which motivated Berge to introduce perfect graphs \cite{Chudnovsky2003}.
 
 \subsection{Shannon Capacity of a graph}
+\label{sec:ShannonCapacity}
 
@@
 However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
-This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected iff values they represent can be confused.
+This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if values they represent can be confused.
 
@@
 Let us be more precise.
-Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in G(V)^k$ of length $k$ are non-confoundable iff there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
+Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in V(G)^k$ of length $k$ are non-confoundable if and only if there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
 We are interested in the maximum rate at which we can reliably transmit information (the \emph{Shannon capacity} of the channel defined by $G$).
@@
 For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$.
-To describe longer messages we use \emph{Strong Product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ iff $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
+To describe longer messages we use \emph{strong product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ if and only if $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
 Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ -- which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission.
@@
 
-where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is a orthogonal representation of $G$.
+\noindent where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is a orthogonal representation of $G$.
 
@@
 Because in perfect graphs $\omega(G) = \chi(G)$, we get $\omega(G) = \vartheta(\overline{G}) = \chi(G)$.
-
 Therefore, if for any perfect graph $G$, we could calculate $\vartheta(G)$ and $\vartheta(\overline{G})$, we would get $\omega(G)$, $\chi(G)$ and $\alpha(G)$.
@@
 
-First, let us recall some definitions, with \cite{gilbertstrang2020} as a reference for linear algebra. \todo{do we want more lin. algebra definitions?}
+First, let us recall some definitions, with \cite{gilbertstrang2020} as a reference for linear algebra.
 
@@
 
-If a matrix $A$ is symmetric \footnote{Matrix $A$ is symmetric iff $A = A^\intercal$}, all the eigenvalues are real.
+If a matrix $A$ is symmetric\footnote{Matrix $A$ is symmetric if and only if $A = A^\intercal$}, all the eigenvalues are real.
 
 \begin{defn}[positive semidefinite matrix]
-  Let $A$ be an $n \times x$ symmetric matrix. $A$ is \emph{positive semidefinite} if all of its eigenvalues are nonnegative. We denote it by $A \succeq 0$.
+  Let $A$ be an $n \times n$ symmetric matrix. $A$ is \emph{positive semidefinite} if all of its eigenvalues are nonnegative. We denote it by $A \succeq 0$.
 \end{defn}
@@
   \begin{enumerate}[(i)]
-    \item $A$ is positive semidefinite
-    \item \label{en:ei2} for every $x \in \mathbb{R}^n$, $x^\intercal Ax$ is nonnegative
-    \item for some matrix $U$, $A = U^\intercal U$
-    \item $A$ is a nonnegative linear combination of matrices of the type $xx^\intercal$
+    \item $A$ is positive semidefinite,
+    \item \label{en:ei2} for every $x \in \mathbb{R}^n$, $x^\intercal Ax$ is nonnegative,
+    \item for some matrix $U$, $A = U^\intercal U$,
+    \item $A$ is a nonnegative linear combination of matrices of the type $xx^\intercal$.
   \end{enumerate}
@@
 
-We will think of $n \times n$ matrices as vectors with $n^2$ coordinates.
+We may think equivalently of $n \times n$ matrices as vectors with $n^2$ coordinates.
 \begin{defn}[convex cone]
@@
 
-\paragraph{Semidefinite programs}
+\paragraph{Semidefinite programs.}
 
@@
 Solving semidefinite programs is a complex topic, we refer to \cite{grotschel1993} for reference.
-All we need to know is that we can solve semidefinite programs up to an error of $\epsilon$ in polynomial time.
+All we need to know is that we can solve semidefinite programs up to an arbitrarily small error in polynomial time.
 One of the methods to do this is called the \emph{ellipsoid method}, hence the name for the coloring algorithm.
 
-\paragraph{Calculating \boldmath$\vartheta$}
+\paragraph{Calculating \boldmath$\vartheta$.}
 
@@
 
-In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$, as the former values are always integral.
+In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision smaller than $1/2$, as the former values are always integral.
 
@@
 Given a weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ in the following manner.
-Create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ iff the nodes $v$, $u$ are adjacent in $G$.
+Create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the nodes $v$, $u$ are adjacent in $G$.
 Then calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.
@@
 We analyze this algorithm and provide its pseudocode in \cref{ch:coloringSquareFree}.
+
+\TODO{Dałbym ze 2-3 zdania braggowania, ze algorytm jest duzo bardziej zlozony niz rozpoznawanie + na czym sie opiera.}

### 2020-09-12 paper/definitions.tex
Fixes KT

@@
 \begin{wrapfigure}{r}{0.4\textwidth}
-  \label{fig:examplePath}
   \centering\begin{tikzpicture}[scale=.7, simplegraph]
@@
   \caption{An example graph $G_0$}
+  \label{fig:examplePath}
 \end{wrapfigure}
@@
 If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}.
-The size of the vertex set of a graph $G$ will be called the \emph{cardinality} of $G$.
+When the context of $G$ is clear we will use $V$ and $E$ to denote its vertex and edge set.
 
 An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$.
-Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{unordered}).
+Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{undirected}).
 If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring.
@@
 
-Figure \ref{fig:examplePath} shows an example of a graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$.
+\Cref{fig:examplePath} shows an example of a graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$.
 We will mark edges as solid lines on figures.
@@
 
-Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we would add any edge to $G_0$ it would stop being a path (sometimes we call such an edge a \emph{chord}).
+Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we would add any edge to $G_0$ it would stop being a path.
 
@@
 \begin{defn}[complement]
-  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is two vertices $x, y$ are adjacent in $\overline{G}$ iff they are not adjacent in $G$.
+  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
 \end{defn}
@@
 
+\begin{defn}[antihole]
+  An \emph{antihole} is a subgraph of $G$ whose complement is a hole in $G$.
+\end{defn}
+
 \begin{defn}[clique]
@@
 \end{defn}
-In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) iff $G[V']$ is an anticlique.
+In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.
 
@@
 \begin{defn}[coloring]
-  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that for every edge $xy \in E(G)$, $c(x)$ is different from $c(y)$.
-A $k-coloring$ of $G$ (if exists) is a coloring, such that for all vertices $x \in V(G)$, $c(x) \leq k$.
+  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that $c(x) \neq c(y)$ for every edge $xy \in E(G)$.
+A $k$-coloring of $G$ (if exists) is a coloring, such that $c(x) \leq k$ for all vertices $x \in V(G)$.
 \end{defn}
@@
 \TODO{Defs below to ch. 1}
-
-\begin{defn}[C-major vertices]
-  Given a shortest off hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C-major$ if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
-  \TODO{a picture of this, clean odd hole, amenable hole}
-\end{defn}
-
-\begin{defn}[clean odd hole]
-  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
-\end{defn}
-
-\begin{defn}[cleaner]
-  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
-\end{defn}
-
-Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.
-
-\begin{defn}[near-cleaner]
-  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
-\end{defn}
-
-\begin{defn}[amenable odd hole]
-  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
-\end{defn}

### 2020-09-12 paper/experiments.tex
Fixes KT

@@
 We use hypercubes that are not complete, to achieve higher granularity of data.
-In a hypercube of $n$ vertices there is an edge between vertices $u$ and $v$ iff binary representations of $u$ and $v$ differ by exactly one bit.
+In a hypercube of $n$ vertices there is an edge between vertices $u$ and $v$ if and only if binary representations of $u$ and $v$ differ by exactly one bit.
 

### 2020-09-12 paper/implementation.tex
Fixes KT

@@
 A repository containing the discussed source code and tests is available under the link: \href{https://github.com/AdrianSiwiec/Perfect-Graphs}{https://github.com/AdrianSiwiec/Perfect-Graphs}
-\todo{make repo public and add readme on howto run}
+\todo{make repo public and add readme on howto run, some script creating and running default tests}
 
@@
 \subsubsection{Path enumerating optimizations}
-Below, we will talk about enumerating all paths.
-This is a generalization of the problem of finding an odd hole, if we allow a path to have a single chord between the first and the last of its vertices iff the hole formed would be odd.
+Now let's turn our attention to enumerating all paths.
+This is a generalization of the problem of finding an odd hole, if we allow a path to have a single chord between the first and the last of its vertices if and only if the hole formed would be odd.
 
@@
 
-\paragraph{Array unique}
+\paragraph{Array unique.}
 
@@
 It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the CCLSV algorithm.
-For example, when searching for Jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a Jewel.
+For example, when searching for jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a jewel.
 This proved to be much faster than generating vertices that don't have forbidden chords one by one.
-We use the same algorithm for generating starting vertices for a possible $T_2$ and $T_3$.
+We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$.
 

### 2020-09-12 paper/perfectGraphs.tex
Fixes KT

@@
 Not necessarily so.
-Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ equal to the union of $G$ and a clique $K_n$.
-We can see that indeed $\chi(G') = n = \omega(G')$, but it gives us no indication of the structure of $G$ or $G'$.
-This leads us to the definition of \emph{perfect graphs}
+Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ as the union of $G$ and a clique $K_n$.
+We can see that indeed $\chi(G') = \omega(G') = n$, but it gives us no indication of the structure of $G$ or $G'$.
+This leads us to the hereditary definition of \emph{perfect graphs}.
 
@@
 	\label{def:perfectGraph}
-	A graph $G$ is \emph{perfect} iff for its every induced subgraph $H$ we have $\chi(H) = \omega(H)$
+	A graph $G$ is \emph{perfect} if and only if for its every induced subgraph $H$ we have $\chi(H) = \omega(H)$.
 \end{defn}
@@
 	\label{def:bergeGraph}
-	A graph $G$ is \emph{Berge} iff both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
+	A graph $G$ is \emph{Berge} if and only if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph.
 \end{defn}
@@
 Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
-We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ellipsoidMethod}.
+We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ShannonCapacity}.
 
@@
 	\label{thm:omegaalpha}
-	A graph $G$ is perfect iff for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof?}
+	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof!}
 \end{theorem}
@@
 
-In 1961 Berge conjured that a graph is perfect iff it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture.
+In 1961 Berge conjured that a graph is perfect if and only if it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture.
 In 2001 Chudnovsky et al.
@@
 A graph $G$ has a \emph{2-join} if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$.
-When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect iff $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.
+When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect if and only if $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.
 
@@
 	\label{thm:decomposition}
-	Every Berge graph $G$ is basic or has a skew partition or a homogeneous pair, or $G$ or $\overline{G}$ has a 2-join.
+	Every Berge graph $G$ is basic or has a skew partition or a homogeneous pair, or either $G$ or $\overline{G}$ has a 2-join.
 \end{theorem}
 
-See \cite{MC06} for the proof of \cref{thm:decomposition} and \cref{thm:spgt}.
+See \cite{MC06} for the proof of \cref{thm:spgt} and \cref{thm:decomposition}.
 
@@
 
-Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}).
+Berge graph recognition algorithm (later called CCLSV from the names of its authors) could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}).
 If they do, we output that graph is not Berge and stop.
@@
 \begin{itemize}
-	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$
-	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$.
+	\item $\forall_{1\leq i \leq 3}$ $P_i$ is a path between $a$ and $b_i$,
+	\item $\forall_{1\leq i < j \leq 3}$ $a$ is the only vertex in both $P_i$ and $P_j$ and $b_ib_j$ is the only edge between $V(P_i)\setminus\{a\}$ and $V(P_j)\setminus\{a\}$,
 	\item $a$ is adjacent to at most one of $\{b_1, b_2, b_3\}$.
@@
 
-We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$. Let us notice, that a pyramid is determined by its paths $P_1$, $P_2$, $P_3$.
+We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$.
+Let us notice, that a pyramid is uniquely determined by its paths $P_1$, $P_2$, $P_3$.
 
@@
 						\mForEach{$m_2 \in M \cup \{b_2\}$}
-							\mIf{$P_2(m_2)$ exists and contains no black vertices} \label{line:pyramidColor2}
+							\mIf{$P_2(m_2)$ exists and contains no black vertices \lsx} \label{line:pyramidColor2}
 								\ls add $(m_1, m_2)$ to $good\_pairs_{1,2}$
@@
 
-With definitions as above, for $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, iff $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
+With definitions as above, for $1 \leq i < j \leq 3$, we say that $(m_i, m_j)$ is a \emph{good $(i, j)$-pair}, if and only if $m_i \in M \cup \{b_i\}$, $m_j \in M \cup \{b_j\}$, $P_i(m_i)$ and $P_j(m_j)$ both exist, and the sets $V(P_i(m_i))$,$V(P_j(m_j))$ are both disjoint and $b_ib_j$ is the only edge between them.
+In line \ref{line:pyramidColor} we color vertices of $P_1(m_1)$ black, so that for each $m_2$ we can check if paths $P_1(m_1)$ and $P_2(m_2)$ are disjoint in $O(|V|)$ time.
 
-It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ it was found for via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}.
-The proof of the converse is rather technical and we refer to \cite{MC05} for it.
+It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} the vertex $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}.
+The proof of the converse is rather technical and we refer to \todo{dokładny nr twierdzenia} \cite{MC05} for it.
 
@@
 
-Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} iff:
+Five vertices $v_1, \ldots, v_5$ and a path $P$ form a \emph{jewel} if and only if:
 
 \begin{itemize}
-	\item $v_1, \ldots, v_5$ are distinct vertices.
-	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges.
-	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges.
+	\item $v_1, \ldots, v_5$ are distinct vertices,
+	\item $v_1v_2, v_2v_3, v_3v_4, v_4v_5, v_5v_1$ are edges,
+	\item $v_1v_3, v_2v_4, v_1,v_4$ are nonedges,
 	\item $P$ is a path between $v_1$ and $v_4$, such that $v_2, v_3, v_5$ have no neighbors in its inside.
@@
 
-The following algorithm with running time of $O(|V(G)|^6)$ checks whether $G$ contains a configuration of type $T_3$:
+The following algorithm with running time of $O(|V|^6)$ checks whether $G$ contains a configuration of type $\T_3$:
 
@@
 \end{alg}
-% \begin{algorithmic}
-% 	\mProcedure{Contains-T3}{$G$}
-% 	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges}
-% 	\mEndFor
-% 	\mEndProcedure
-% \end{algorithmic}
-% \begin{algorithmic}[1]
-% 	\mProcedure{Contains-Pyramid}{$G$}
-% 	\ls \RETURN \FALSE
-% 	\mEndProcedure
-% \end{algorithmic}
 
-% \begin{algtext2}
+\begin{algorithmic}[1]
+	\mProcedure{Contains-T3}{$G$}
+	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge \AND
+		\lsx $v_1v_5, v_2v_5$ are nonedges}
+		\ls $Y \gets$ the set of all $\{v_1, v_2, v_5\}$-complete vertices.
+		\mForEach{$X$ -- an anticomponent of $Y$}
+			\ls $F' \gets$ maximal connected subset containing $v_5$, such that $v_1, v_2$
+			\lsx have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
+			\ls $F'' \gets$ the set of all $X$-complete vertices that have a neighbor in 
+			\lsx $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$
+			\ls $F \gets F' \cup F''$
+			\mForEach{$v_4 \in V(G) \setminus\{v_1, v_2, v_5\}$, such that $v_4$ is adjacent to $v_1$
+			\lsx and not to $v_2$ and $v_5$}
+				\mIf{$v_4$ has a neighbor in $F$ and a nonneibhbor in $X$}
+					\ls $v_6 \gets$ a neighbor of $v_4$ in $F$
+					\mForEach{$v_3 \in V(G) \setminus\{v_1, v_2, v_4, v_5, v_6\}$}
+						\mIf{$v_3$ is adjacent to $v_2, v_4, v_5$ and not adjacent to $v_1$ \lsx}
+							\ls $P \gets$ a path from $v_6$ to $v_5$ with interior in $F'$
+							\ls \RETURN \TRUE \Comment{$v_1, \ldots v_6, P, X$ is a $\T_3$}
+						\mEndIf
+					\mEndFor
+				\mEndIf
+			\mEndFor
+		\mEndFor
+	\mEndFor
+	\ls \RETURN \FALSE
+	\mEndProcedure
+\end{algorithmic}
 
-	For each triple $v_1, v_2, v_5$ of vertices such that $v_1v_2$ is an edge and $v_1v_5, v_2v_5$ are nonedges find the set $Y$ of all $\{v_1, v_2, v_5\}$-complete vertices.
-For each anticomponent $X$ of $Y$ find the maximal connected subset $F'$ containing $v_5$ such that $v_1, v_2$ have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
-Let $F$ be the union of $F'$ and the set of all $X$-complete vertices that have a neighbor in $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$.
+We will skip the proof that each graph containing $\T_3$ is not Berge, as it is quite technical. See section 6.7 of \cite{MC05} for the proof.
 
-	Then, for each choice of $v_4$ that is adjacent to $v_1$ and not to $v_2$ and $v_5$ and has a neighbor in $F$ (call it $v_6$) and a nonneibhbor in $X$, we test whether there is a vertex $v_3$, adjacent to $v_2, v_4, v_5$ and not to $v_1$, with a nonneibhbor in $X$.
-If there is such a vertex $v_3$, find $P$ -- a path from $v_6$ to $v_5$ with interior in $F'$ and return that $v_1, \ldots v_6, P, X$ is a configuration of type $\T_3$.
-If we exhaust our search and find none, report that graph does not contain it.
-% \end{algtext2}
+\begin{theorem}
 
-To see that the \cref{alg:t3} has a running time of $O(|V(G)|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V(G)|^3)$, there are linear many choices of $X$, each taking $O(|V(G)|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
-This gives us the total running time of $O(|V(G)|^6)$.
+\end{theorem}
 
-We will skip the proof that each graph containing $\T_3$ is not Berge. See section 6 6.7 of \cite{MC05} for the proof.
+To see that the \cref{alg:t3} has a running time of $O(|V|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V|^3)$, there are linear many choices of $X$, each taking $O(|V|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
+This gives us the total running time of $O(|V|^6)$.
+
+.
 
@@
 \label{AmenableHoles}
+
+First, let us introduce a few new definitions.
+
+\begin{defn}[C-major vertices]
+  Given a shortest odd hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C$-major if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
+  \TODO{a picture of this, clean odd hole, amenable hole}
+\end{defn}
+
+\begin{defn}[clean odd hole]
+  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
+\end{defn}
+
+\begin{defn}[cleaner]
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
+\end{defn}
+
+Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.
+
+\begin{defn}[near-cleaner]
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
+\end{defn}
+
+\begin{defn}[amenable odd hole]
+  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
+\end{defn}
 
@@
 
-With \cref{thm:amenableHoles} we can describe the rest of the algorithm.
+With \Cref{thm:amenableHoles} we can describe the rest of the algorithm.
 
@@
 
-	\noindent Output: $O(|V(G)|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
+	\noindent Output: $O(|V|^5)$ subsets of $V(G)$, such that if $C$ is an amenable hole in $G$, then one of the subsets is a near-cleaner for $C$.
 \end{alg}
 \begin{algtext2}
-	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a, b$ are distinct (possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
+	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
 
@@
 
-\begin{alg}[Test possible near clener, 5.1 of \cite{MC05}]
+\begin{alg}[Test possible near cleaner, 5.1 of \cite{MC05}]
 	\label{alg:testNearCleaner}
@@
 	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$.
-If there is one, let $r(x, y)$ be its length, if not, let $r(x, y)$ be infinite.
+If there is one, let $r(x, y)$ be its length, if not, let $r(x, y) = \infty$.
 
@@
 	\end{itemize}
+	\TODO{moze raczej $min(r(x_3, y_1), r(x_3, y_2)) = r(x_2, y_1) = r(x_1, y_2) = r(x_1, y_1) + 1$?}
 

### 2020-09-12 paper/experiments.tex
Minor fixes

@@
-\subsection{Experiments}
+\section{Experiments}
 \label{sec:experiments}
@@
 
-When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we ser the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV.
+When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we see the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV.
 Slight GPU improvement is explained by anylysis of the components of the overall time (\Cref{plot:perfDet}).
@@
 In lattice graph, each vertex is connected to vertices that are above, below, to the left and to the right of it, if such vertices exist.
-See \cref{fig:lattice} for an example of $4 \times 4$ lattice.
+See \cref{fig:lattice} for an example of a $4 \times 4$ lattice graph.
 
@@
 
-With growing $|V|$ also grows the speedup gained from utilizing GPU. For $|V| = 78$ the running time for the whole algorithm is almost 3x better.
+With larger $|V|$ the speedup gained from utilizing GPU is also more significant. For $|V| = 78$ the running time for the whole algorithm is almost 3x better.
 
@@
 What is more interesting, the overall performance of CCLSV is much worse (\cref{plot:rookLines}).
-Looking at \cref{fig:rookDet} we can see that the majority of CCLSV time is spent checking all near cleaners.
-This can be explained by the fact that rook graphs are much denser than lattice graphs and have many more 3-vertex paths (see \cref{alg:testNearCleaner}).
-This is confirmed by greater CCLSV GPU speedup of around 6x on graph with $|V| = 35$.
+Looking at \cref{plot:rookDet} we can see that the majority of CCLSV time is spent checking all near cleaners.
+This can be explained by the fact that rook graphs are much denser than lattice graphs and have many more 3-vertex paths (see line TODO of \cref{alg:testNearCleaner}).
+This is confirmed by greater CCLSV GPU speedup of around 6x on graphs with $|V| = 35$.
 
@@
 Na\"ive is very fast at first, but becomes unbearably slow for $|V|$ higher than 55.
-Unfortunately, CCLSV doesnt fare much better, although it grows slower.
+Unfortunately, CCLSV doesn't fare much better, although it grows slower.
 Again, the speedup of GPU CCLSV is noticeable, being around 4.8x for $|V| = 55$.
@@
 What is interesting, when looking at detailed times of GPU CCLSV, we can see that checking the existence of simple forbidden structures takes more than 30\% of the time.
-This opens a possibility of further GPU speedups, as previous tests indicated that checking simple forbidden structures is usually very quick on the CPU.
+This opens a possibility of further GPU speedups, not explored by us.
 
@@
 With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}.
+In most of our tests, the majority of running time was consumed on calculating $\vartheta$ of various graphs.
+As it was done by an external library, there isn't much optimization potential for us.
+One thing of note is, that specifying the precision of $\vartheta$ we want to calculate to be $1/3$ sped up the algorithm by TODO.
 Our main goal of the implementation was to check if this method is still impractical, even on modern equipment.
@@
 There are surely some optimizations to be made here if need be.
-Altough, as we can see on other plots, it won't help im majority of the cases.
-
-\subsection{Combinatorial Method}
-
-Cite the paper.\\
-
-On its complexity - point to appendix for pseudo-code.
+Altough, as we can see on other plots, it won't help in majority of the cases.

### 2020-09-12 paper/implementation.tex
Minor fixes

@@
 The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case.
-Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\cref{sec:Optimizations}) make a very big difference and make it usable -- or at least much more usable than na\"ive algorithm could be.
-Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with good results (\cref{sec:CUDA}).
+Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\cref{sec:Optimizations}) make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
+Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\cref{sec:CUDA}).
 
@@
 When implementing a complicated algorithm that has a time complexity of $O(n^9)$ optimizations can be both crucial and difficult to implement.
-There is not a single code path that takes up all the running time -- or at lest there isn't one from theoretical point of view.
+There is not a single code path that takes up all the running time -- or at lest there isn't one from a theoretical point of view.
 Therefore a tool for inspecting running time bottlenecks is needed.
@@
 
-\TODO{bitsets}
+Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners (\Cref{alg:listNearCleaners}).
+At its very end, it returns a set that is an union \todo{after rewriting alg, point to a line}.
+We used a \texttt{dynamic\_bitset} from the boost library \cite{boost} for this purpose.
+It is a data structure to represent a set of bits, that also allows for fast bitwise operators that one can apply to builtin integers.
+By using it, the speedup of \Cref{alg:listNearCleaners} was about x.
+\todo{todo}
+
+After these optimizations, checking each potential near-cleaner (\Cref{alg:testNearCleaner}) is by far the biggest bottlenecks of the CCLSV algorithm.
+We didn't find any major optimizations there, but \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.
 
@@
 
-\subsection{Parallelism with CUDA (?)}
+\section{Parallelism with CUDA}
 \label{sec:CUDA}
 
-\TODO{a section?}
 \TODO{CUDA background}
@@
 On the other the algorithm is complex and not easy to parallelise.
-Therefore we decided to implement whole na\"ive algorithm and most time consuming parts of the CCLSV\todo{a good name for it?} algorithm.
+Therefore we decided to analyze the  CCLSV\todo{a good name for it?} algorithm and parrallelize parts that would benefit from it the most.
 
-\subsubsection{Na\"ive parallelisation}
+% \subsubsection{Na\"ive parallelisation}
 
-Na\"ive algorithm is very simple -- generate all possible odd hole candidates, check if any of them is an odd hole and repeat for the complement. But its parallelisation is not trivial.
+% Na\"ive algorithm is very simple -- generate all possible odd hole candidates, check if any of them is an odd hole and repeat for the complement. But its parallelisation is not trivial.
 
-The biggest problem of implementing na\"ive algorithm is in splitting the work between CUDA threads.
+% The biggest problem of implementing na\"ive algorithm is in splitting the work between CUDA threads.
 This is very important because while GPU is faster when all its cores are working efficiently, single core performance is much slower than CPU.
@@
 
-Our first attempt was to switch our slightly more sophisticated way of generating paths (\cref{sec:usesGeneration}) in favor of generating all combinations.
+% Our first attempt was to switch our slightly more sophisticated way of generating paths (\cref{sec:usesGeneration}) in favor of generating all combinations.
 We could code a prefix of a combination as a number (we use combinations with repetitions for simplicity).
@@
 
-A better approach is to generate all paths of some length $k$ on CPU (using algorithm described in \cref{sec:usesGeneration}), copy them on GPU and have each thread process them as described above.
+% A better approach is to generate all paths of some length $k$ on CPU (using algorithm described in \cref{sec:usesGeneration}), copy them on GPU and have each thread process them as described above.
 This is superior to the previous algorithm in utilizing GPU -- each prefix takes similar time to process.
@@
 
-\subsubsection{CCLSV parallelisation}
+% \subsubsection{CCLSV parallelisation}
 
@@
 Let us notice, that for all $X$s all 3-vertex paths are the same.
-We calculate them beforehand \todo{do it also in CPU} \todo{acutally do this}.
-Then each thread receives a 3-vertex path and an additional vertex and performs the required checks.
-This is almost perfect scenario for GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.
+We calculate them beforehand, then each thread receives a 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks.
+This is almost perfect scenario for the GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.
 
-It turns out that this optimization alone speeds up \cref{alg:testNearCleaner} almost 30x \todo{check} on bigger tests, which gives us a speedup of about 5x \todo{check} for overall algorithm.
+It turns out that this optimization alone speeds up \cref{alg:testNearCleaner} almost 7x \todo{check} on bigger tests, which gives us a speedup of about 6x \todo{check} for overall algorithm.
 

### 2020-09-12 code/test/cuPerfTest/run.sh
Cuda naive wip

@@ -17,14 +17,14 @@ perfectTests=(
   # "hypercubes16to50.t.in"
   # # "kingGraph3by3to12.t.in"
 
-  "perf2.t.in"
-  "perf.t.in"
+  # "perf2.t.in"
+  # "perf.t.in"
   "fullBinary20to100.t.in"
-  "grid6by5to11.t.in"
-  "hypercubes20to55.t.in"
-  "knightGraph8by4to8.t.in"
-  "rookGraph5by4to7.t.in"
-  "split20to50.t.in"
+  # "grid6by5to11.t.in"
+  # "hypercubes20to55.t.in"
+  # "knightGraph8by4to8.t.in"
+  # "rookGraph5by4to7.t.in"
+  # "split20to50.t.in"
 )
 
 pefectSupplement=(
@@ -32,10 +32,11 @@ pefectSupplement=(
 )
 
 cudaPerfectSupplement=(
-  "grid6by5to11.t.in"
-  "hypercubes20to55.t.in"
-  "rookGraph5by4to7.t.in"
-  "split20to50.t.in"
+  # "grid6by5to11.t.in"
+  # "hypercubes20to55.t.in"
+  # "rookGraph5by4to7.t.in"
+  # "split20to50.t.in"
+  "knightGraph8by4to8.t.in"
 )
 
 naivePerfectSupplement=(
@@ -53,34 +54,44 @@ naivePerfectSupplement=(
 # )
 
 
-for file in "${perfectTests[@]}"; do
-  echo "Running Perfect on $file"
-  $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running Perfect on $file"
+#   $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+# done
 
-for file in "${perfectTests[@]}"; do
-  echo "Running CuPerfect on $file"
-  $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running CuPerfect on $file"
+#   $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+# done
 
-for file in "${perfectTests[@]}"; do
-  echo "Running Naive on $file"
-  $naiveExec <$testsDir/$file >>$resultsDir/$file.out.csv
-done
+# for file in "${perfectTests[@]}"; do
+#   echo "Running Naive on $file"
[…]

### 2020-09-12 code/test/unitTest/color.cpp

@@ -203,8 +203,8 @@ void testColor() {
 
 int main() {
   init();
-  // cout<<"Skipping Color tests..." <<endl;
-  // return 0;
+  cout<<"Skipping Color tests..." <<endl;
+  return 0;
 
   testGetGraphEdges();
   testGetTheta();

### 2020-09-12 code/test/unitTest/devCode.cu

@@ -437,86 +437,86 @@ void testDevIsAHole(context_t &context) {
   context.synchronize();
 }
 
-void testCuContainsHoleOfSize(context_t &context) {
-  Graph G(6,
-          "\
-  .XX...\
-  X.XX..\
-  XX....\
-  .X..X.\
-  ...X.X\
-  ....X.\
-  ");
-  CuGraph CG(G, context);
+// void testCuContainsHoleOfSize(context_t &context) {
+//   Graph G(6,
+//           "\
+//   .XX...\
+//   X.XX..\
+//   XX....\
+//   .X..X.\
+//   ...X.X\
+//   ....X.\
+//   ");
+//   CuGraph CG(G, context);
 
-  assert(!cuContainsHoleOfSize(CG, 3, context));
-  assert(!cuContainsHoleOfSize(CG, 4, context));
-  assert(!cuContainsHoleOfSize(CG, 5, context));
-  assert(!cuContainsHoleOfSize(CG, 6, context));
+//   assert(!cuContainsHoleOfSize(CG, 3, context));
+//   assert(!cuContainsHoleOfSize(CG, 4, context));
+//   assert(!cuContainsHoleOfSize(CG, 5, context));
+//   assert(!cuContainsHoleOfSize(CG, 6, context));
 
-  G = Graph(6,
-            "\
-  .XX...\
-  X.XX..\
-  XX..X.\
-  .X..X.\
-  ..XX.X\
-  ....X.\
-  ");
-  CuGraph CG2(G, context);
-  assert(cuContainsHoleOfSize(CG2, 4, context));
-  assert(!cuContainsHoleOfSize(CG2, 3, context));
-  assert(!cuContainsHoleOfSize(CG2, 5, context));
-  assert(!cuContainsHoleOfSize(CG2, 6, context));
+//   G = Graph(6,
+//             "\
+//   .XX...\
+//   X.XX..\
+//   XX..X.\
+//   .X..X.\
+//   ..XX.X\
+//   ....X.\
+//   ");
+//   CuGraph CG2(G, context);
+//   assert(cuContainsHoleOfSize(CG2, 4, context));
+//   assert(!cuContainsHoleOfSize(CG2, 3, context));
+//   assert(!cuContainsHoleOfSize(CG2, 5, context));
+//   assert(!cuContainsHoleOfSize(CG2, 6, context));
 
-  // assert(!cuContainsHoleOfSize(CG, 3, context, 6));
[…]

### 2020-09-12 code/test/plot.py
plots

@@ -147,7 +147,7 @@ sizes_in_inches = {
 func_formatter = ticker.FuncFormatter(lambda y, _: "{:g}".format(y))
 
 # labels for plot axes
-label_lca_N = "Number of nodes"
+label_lca_N = "$|V|$"
 label_time_percentage = "Time ratio"
 label_lca_preprocessing_over_s = "Nodes preprocessed per second"
 label_lca_queries_over_s = "Queries answered per second"
@@ -162,7 +162,6 @@ label_time_overall_s = "Total time [s]"
 
 # Here we declare what tests consist an experiment.
 experiments = [
-    # Perfect
     {
         "restrictions": [(csv_result, 1), (csv_algo, "Perfect|Naive")],
         "x_param": csv_N,
@@ -171,8 +170,144 @@ experiments = [
         "size": sizes_in_inches["regular"],
         "y_param": csv_overall,
         "ylog": False,
-        "x_label": "N",
+        "x_label": label_lca_N,
         "y_label": label_time_overall_s,
+    },
+    {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_algo, "Perfect|Naive"),
+            (csv_filename, "grid"),
+            (csv_N, "42|48|54|60|66|72|78|84|90|96|102"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "lines",
+        "size": sizes_in_inches["regular"],
+        "y_param": csv_overall,
+        "ylog": True,
+        "yformatter": func_formatter,
+        "x_label": label_lca_N,
+        "y_label": label_time_overall_s,
+        "x_ticks": [42, 54, 66, 78, 90, 102],
+        "x_ticks_labels": [
+            # "$6 \\times 5$",
+            "$6 \\times 7$",
+            "$6 \\times 9$",
+            "$6 \\times 11$",
+            "$6 \\times 13$",
+            "$6 \\times 15$",
+            "$6 \\times 17$",
+        ],
+        "ylim": (0.5, 250),
+    },
+    {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_algo, "Perfect|Naive"),
+            (csv_filename, "rook"),
+            # (csv_N, "42|48|54|60|66|72|78|84|90|96|102"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "lines",
[…]

### 2020-09-13 code/test/plot.py
plot detailed wip

@@ -1,7 +1,7 @@
 # coding: utf-8
 
 usePgf = True
-# usePgf = False
+usePgf = False
 
 import matplotlib as mpl
 
@@ -312,9 +312,9 @@ experiments = [
     {
         "restrictions": [
             (csv_result, 1),
-            (csv_filename, "perf.t.in"),
+            (csv_filename, "detailed"),
             # (csv_N, "20|25|30|35|40|45|50|55"),
-            (csv_algo, "GPU Perfect|Perfect"),
+            # (csv_algo, "GPU Perfect|Perfect"),
         ],
         "x_param": csv_N,
         "x_show": csv_N,
@@ -322,122 +322,123 @@ experiments = [
         "size": sizes_in_inches["wideDetailed"],
         "x_label": "N",
         "y_label": label_time_percentage,
-        "ylim": (0, 1),
+        "x_ticks_labels": ["aa", "bb"]
+        # "ylim": (0, 1),
     },
-    {
-        "restrictions": [
-            (csv_result, 1),
-            (csv_filename, "perf2.t.in"),
-            (csv_N, "15|16|17|18|19"),
-            (csv_algo, "GPU Perfect|Perfect"),
-        ],
-        "x_param": csv_N,
-        "x_show": csv_N,
-        "type": "detailed",
-        "size": sizes_in_inches["wideDetailed"],
-        "x_label": "N",
-        "y_label": label_time_percentage,
-        "ylim": (0, 1),
-    },
-    {
-        "restrictions": [
-            (csv_result, 1),
-            (csv_filename, "fullBinary"),
-            (csv_N, "20|25|30|35|40|45|50|55"),
-            (csv_algo, "GPU Perfect|Perfect"),
-        ],
-        "x_param": csv_N,
-        "x_show": csv_N,
-        "type": "detailed",
-        "size": sizes_in_inches["wideDetailed"],
-        "x_label": "N",
-        "y_label": label_time_percentage,
-        "ylim": (0, 1),
-    },
-    {
-        "restrictions": [
-            (csv_result, 1),
-            (csv_filename, "grid"),
-            (csv_algo, "GPU Perfect|Perfect"),
-            (csv_N, "42|48|54|60|66|72|78"),
-        ],
-        "x_param": csv_N,
-        "x_show": csv_N,
-        "type": "detailed",
-        "size": sizes_in_inches["wideDetailed"],
-        "x_label": "N",
-        "y_label": label_time_percentage,
[…]

### 2020-09-13 paper/experiments.tex
plots
Plot detailed almost done

@@
 Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.
+For every test, the vertex number were shuffled.
 
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/perf.t.in.out.csv.lines.pgf}
-    \caption{Random perfect graphs}
   \label{plot:perfLines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/perf.t.in.out.csv.detailed.pgf}
-    \caption{Random perfect graphs}
-    \label{plot:perfDet}
-  \end{subfigure}
   \caption{Random perfect graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/perf2.t.in.out.csv.lines.pgf}
-    \caption{Line graphs of random bipartite graphs}
   \label{plot:perf2Lines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/perf2.t.in.out.csv.detailed.pgf}
-    \caption{Line graphs of random bipartite graphs}
-    \label{plot:perf2Det}
-  \end{subfigure}
   \caption{Line graphs of random bipartite graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
   \label{plot:gridLines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/grid6by5to11.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:gridDet}
-  \end{subfigure}
   \caption{Lattice graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
   \label{plot:rookLines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/rookGraph5by4to7.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:rookDet}
-  \end{subfigure}
   \caption{Rook graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
   \label{plot:knightLines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:knightDet}
-  \end{subfigure}
   \caption{Knight graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
   \label{plot:hypercubeLines}
-  \end{subfigure}
-
-  \begin{subfigure}{\textwidth}
-    \centering
-    \input{plots/knightGraph8by4to8.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:hypercubeDet}
-  \end{subfigure}
   \caption{Hypercube graphs}
@@
 \begin{figure}
-  \begin{subfigure}{\textwidth}
   \centering
   \input{plots/split20to50.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
   \label{plot:splitLines}
-  \end{subfigure}
+  \caption{Split graphs}
+\end{figure}
 
-  \begin{subfigure}{\textwidth}
+\begin{figure}
   \centering
-    \input{plots/split20to50.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:splitDet}
-  \end{subfigure}
-  \caption{Split graphs}
+  \input{plots/detailed.csv.detailed.pgf}
+  \label{plot:splitLines}
+  \caption{\the\textwidth \the\textheight}
 \end{figure}

### 2020-09-13 code/test/plot.py

@@ -1,7 +1,7 @@
 # coding: utf-8
 
 usePgf = True
-usePgf = False
+# usePgf = False
 
 import matplotlib as mpl
 
@@ -106,12 +106,12 @@ algo_labels = {
 }
 
 algo_field_labels = {
-    csv_simpleStructures: "Simple Structures",
-    csv_testNCRest: "Test NC Rest",
-    csv_getNearCleaners: "Get Near Cleaners",
-    csv_testNCShortestPaths: "Test NC Shortest Paths",
-    csv_gpuCopyR: "GPU Test NC Copy R",
-    csv_gpuWork: "GPU test NC work",
+    csv_simpleStructures: "Simple structures",
+    csv_testNCRest: "CPU test",
+    csv_getNearCleaners: "Get near cleaners",
+    csv_testNCShortestPaths: "Calculare $R$",
+    csv_gpuCopyR: "Copy $R$",
+    csv_gpuWork: "GPU test",
     csv_color_res: "Rest",
     csv_color_CSDP: "CSDP",
 }
@@ -138,7 +138,7 @@ sizes_in_inches = {
     "wide": (6.8, 2.4),
     "huge": (6.8, 8),
     "allGraphs": (10, 25),
-    "wideDetailed": (4.77, 3.5),
+    "wideDetailed": (4.77, 7.1),
     "regular_small": (2.38, 1.5),
     "wideDetailed_small": (2.38, 1.5),
 }
@@ -317,12 +317,11 @@ experiments = [
             # (csv_algo, "GPU Perfect|Perfect"),
         ],
         "x_param": csv_N,
-        "x_show": csv_N,
+        "x_show": csv_filename,
         "type": "detailed",
         "size": sizes_in_inches["wideDetailed"],
-        "x_label": "N",
-        "y_label": label_time_percentage,
-        "x_ticks_labels": ["aa", "bb"]
+        "x_label": label_time_overall_s,
+        "x_ticks_labels": ["aaaaaaaaaaa", "bb"]
         # "ylim": (0, 1),
     },
     # {
@@ -612,12 +611,14 @@ for i_exp, experiment in enumerate(experiments):
                     y_sum[i_xval] -= y[i_xval][i_field]
 
             ax.set_yticks(apparent_x)
-            ax.yaxis.set_tick_params(rotation=45)
+            ax.yaxis.set_tick_params(rotation=0)
             # ax.set_xticklabels(x)
             # if "x_ticks" in experiment:
[…]

### 2020-09-13 code/test/plot.py
Detailed color

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-usePgf = True
-# usePgf = False
+# usePgf = True
+usePgf = False
 
 import matplotlib as mpl
 
@@ -313,6 +313,7 @@ experiments = [
         "restrictions": [
             (csv_result, 1),
             (csv_filename, "detailed"),
+            (csv_algo, "Perfect|Naive"),
             # (csv_N, "20|25|30|35|40|45|50|55"),
             # (csv_algo, "GPU Perfect|Perfect"),
         ],
@@ -441,28 +442,45 @@ experiments = [
     #
     # COLOR
     #
+    # {
+    #     "restrictions": [(csv_algo, "CSDP")],
+    #     "x_param": csv_N,
+    #     "x_show": csv_N,
+    #     "type": "lines",
+    #     "size": sizes_in_inches["regular_small"],
+    #     "y_param": csv_overall,
+    #     "ylog": False,
+    #     "x_label": "N",
+    #     "y_label": label_time_overall_s,
+    #     "out_prefix": "color",
+    # },
+    # {
+    #     "restrictions": [(csv_algo, "CSDP")],
+    #     "x_param": csv_N,
+    #     "x_show": csv_N,
+    #     "type": "detailed",
+    #     "size": sizes_in_inches["wideDetailed_small"],
+    #     "x_label": "N",
+    #     "y_label": label_time_percentage,
+    #     "ylim": (0, 1),
+    #     "out_prefix": "color",
+    # },
     {
-        "restrictions": [(csv_algo, "CSDP")],
+        "restrictions": [
+            (csv_result, 1),
+            (csv_filename, "detailed"),
+            (csv_algo, "CSDP")
+            # (csv_N, "20|25|30|35|40|45|50|55"),
+            # (csv_algo, "GPU Perfect|Perfect"),
+        ],
         "x_param": csv_N,
-        "x_show": csv_N,
-        "type": "lines",
-        "size": sizes_in_inches["regular_small"],
-        "y_param": csv_overall,
-        "ylog": False,
-        "x_label": "N",
-        "y_label": label_time_overall_s,
-        "out_prefix": "color",
-    },
-    {
-        "restrictions": [(csv_algo, "CSDP")],
-        "x_param": csv_N,
-        "x_show": csv_N,
+        "x_show": csv_filename,
         "type": "detailed",
-        "size": sizes_in_inches["wideDetailed_small"],
-        "x_label": "N",
[…]

### 2020-09-13 code/test/cuPerfTest/run.sh
Perf2 data

@@ -17,9 +17,9 @@ perfectTests=(
   # "hypercubes16to50.t.in"
   # # "kingGraph3by3to12.t.in"
 
-  # "perf2.t.in"
+  "perf2.t.in"
   # "perf.t.in"
-  "fullBinary20to100.t.in"
+  # "fullBinary20to100.t.in"
   # "grid6by5to11.t.in"
   # "hypercubes20to55.t.in"
   # "knightGraph8by4to8.t.in"
@@ -36,12 +36,14 @@ cudaPerfectSupplement=(
   # "hypercubes20to55.t.in"
   # "rookGraph5by4to7.t.in"
   # "split20to50.t.in"
-  "knightGraph8by4to8.t.in"
+  # "knightGraph8by4to8.t.in"
+  "perf2.t.in"
 )
 
 naivePerfectSupplement=(
-  "rookGraph5by4to7.t.in"
-  "split20to50.t.in"
+  # "rookGraph5by4to7.t.in"
+  # "split20to50.t.in"
+  "perf2.t.in"
 )
 
 # naiveTests=(
@@ -54,20 +56,20 @@ naivePerfectSupplement=(
 # )
 
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running Perfect on $file"
-#   $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-# done
+for file in "${perfectTests[@]}"; do
+  echo "Running Perfect on $file"
+  $perfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+done
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running CuPerfect on $file"
-#   $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
-# done
+for file in "${perfectTests[@]}"; do
+  echo "Running CuPerfect on $file"
+  $cuPerfectExec <$testsDir/$file >>$resultsDir/$file.out.csv
+done
 
-# for file in "${perfectTests[@]}"; do
-#   echo "Running Naive on $file"
-#   $naiveExec <$testsDir/$file >>$resultsDir/$file.out.csv
-# done
+for file in "${perfectTests[@]}"; do
+  echo "Running Naive on $file"
+  $naiveExec <$testsDir/$file >>$resultsDir/$file.out.csv
+done
 
 # for file in "${perfectTests[@]}"; do
 #   echo "Running CuNaive on $file"
[…]

### 2020-09-13 code/test/generate/generate.cpp

@@ -9,22 +9,23 @@
 int main() {
   srand(time(0));
 
-  // int minN = 15;
-  // int maxN = 19;
+  int minN = ;
+  int maxN = 56;
+  int step = 2;
 
-  // for (int i = 0; i < 5; i++) {
-  //   set<int> done;
+  for (int i = 0; i < 10; i++) {
+    set<int> done;
 
-  //   while (done.size() < maxN - minN + 1) {
-  //     Graph G = getBipariteGraph(8 + getDistr() * 3, getDistr()).getLineGraph();
-  //     if (rand() % 2) G = G.getComplement();
+    while (done.size() < (maxN - minN + 1) / step) {
+      Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
+      if (rand() % 2) G = G.getComplement();
 
-  //     if (G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
-  //       G.printOut();
-  //       done.insert(G.n);
-  //     }
-  //   }
-  // }
+      if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+        G.printOut();
+        done.insert(G.n);
+      }
+    }
+  }
 
   // int minN = 20;
   // int maxN = 45;
@@ -56,8 +57,8 @@ int main() {
   //   G.printOut();
   // }
 
-  for (int i = 10; i <= 25; i+=3) {
-    Graph G = getSplitGraph(i, getDistr());
-    G.printOut();
-  }
+  // for (int i = 10; i <= 25; i+=3) {
+  //   Graph G = getSplitGraph(i, getDistr());
+  //   G.printOut();
+  // }
 }

### 2020-09-13 code/test/generate/generate.cpp
bipartite tests

@@ -9,22 +9,30 @@
 int main() {
   srand(time(0));
 
-  int minN = ;
-  int maxN = 56;
-  int step = 2;
+  // int minN = ;
+  // int maxN = 56;
+  // int step = 2;
 
-  for (int i = 0; i < 10; i++) {
-    set<int> done;
+  // for (int i = 0; i < 10; i++) {
+  //   set<int> done;
 
-    while (done.size() < (maxN - minN + 1) / step) {
+  //   while (done.size() < (maxN - minN + 1) / step) {
       Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
-      if (rand() % 2) G = G.getComplement();
+  //     if (rand() % 2) G = G.getComplement();
 
-      if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
-        G.printOut();
-        done.insert(G.n);
-      }
-    }
+  //     if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+  //       G.printOut();
+  //       done.insert(G.n);
+  //     }
+  //   }
+  // }
+
+  int minN = 42;
+  int maxn = 60;
+  int step = 2;
+  for(int i=minN; i<=maxn; i+=step) {
+    auto G = getBipariteGraph(i, 0.5);
+    G.printOut();
   }
 
   // int minN = 20;

### 2020-09-13 code/test/plot.py
Tests rewrite WIP

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-# usePgf = True
-usePgf = False
+usePgf = True
+# usePgf = False
 
 import matplotlib as mpl
 
@@ -162,16 +162,104 @@ label_time_overall_s = "Total time [s]"
 
 # Here we declare what tests consist an experiment.
 experiments = [
+    # {
+    #     "restrictions": [(csv_result, 1), (csv_algo, "Perfect|Naive")],
+    #     "x_param": csv_N,
+    #     "x_show": csv_N,
+    #     "type": "lines",
+    #     "size": sizes_in_inches["regular"],
+    #     "y_param": csv_overall,
+    #     "ylog": False,
+    #     "x_label": label_lca_N,
+    #     "y_label": label_time_overall_s,
+    # },
     {
-        "restrictions": [(csv_result, 1), (csv_algo, "Perfect|Naive")],
+        "restrictions": [
+            (csv_result, 1),
+            (csv_algo, "Perfect|Naive"),
+            (csv_filename, "perf2"),
+            # (csv_N, "42|48|54|60|66|72|78|84|90|96|102"),
+        ],
         "x_param": csv_N,
         "x_show": csv_N,
         "type": "lines",
         "size": sizes_in_inches["regular"],
         "y_param": csv_overall,
-        "ylog": False,
+        "ylog": True,
+        "yformatter": func_formatter,
         "x_label": label_lca_N,
         "y_label": label_time_overall_s,
+        # "x_ticks": [42, 54, 66, 78, 90, 102],
+        "x_ticks": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
+        "x_ticks_labels": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
+        #     # "$6 \\times 5$",
+        #     "$6 \\times 7$",
+        #     "$6 \\times 9$",
+        #     "$6 \\times 11$",
+        #     "$6 \\times 13$",
+        #     "$6 \\times 15$",
+        #     "$6 \\times 17$",
+        # ],
+        "ylim": (0.5, 250),
+    },
+       {
+        "restrictions": [
+            (csv_result, 1),
+            (csv_algo, "Perfect|Naive"),
+            (csv_filename, "biparite"),
+            # (csv_N, "42|48|54|60|66|72|78|84|90|96|102"),
+        ],
+        "x_param": csv_N,
+        "x_show": csv_N,
[…]

### 2020-09-13 code/test/plot.py
Plots

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-usePgf = True
-# usePgf = False
+# usePgf = True
+usePgf = False
 
 import matplotlib as mpl
 
@@ -202,7 +202,7 @@ experiments = [
         # ],
         "ylim": (0.5, 250),
     },
-       {
+    {
         "restrictions": [
             (csv_result, 1),
             (csv_algo, "Perfect|Naive"),
@@ -218,20 +218,11 @@ experiments = [
         "yformatter": func_formatter,
         "x_label": label_lca_N,
         "y_label": label_time_overall_s,
-        # "x_ticks": [42, 54, 66, 78, 90, 102],
-        # "x_ticks": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
-        # "x_ticks_labels": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
-        #     # "$6 \\times 5$",
-        #     "$6 \\times 7$",
-        #     "$6 \\times 9$",
-        #     "$6 \\times 11$",
-        #     "$6 \\times 13$",
-        #     "$6 \\times 15$",
-        #     "$6 \\times 17$",
-        # ],
-        "ylim": (0.5, 250),
+        "x_ticks": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
+        "x_ticks_labels": [20, 24, 28, 32, 36, 40, 44, 48, 52, 56],
+        "ylim": (0.1, 250),
     },
-       {
+    {
         "restrictions": [
             (csv_result, 1),
             (csv_algo, "Perfect|Naive"),
@@ -405,7 +396,7 @@ experiments = [
             # (csv_N, "20|25|30|35|40|45|50|55"),
             # (csv_algo, "GPU Perfect|Perfect"),
         ],
-        "x_param": csv_N,
+        "x_param": csv_filename,
         "x_show": csv_filename,
         "type": "detailed",
         "size": sizes_in_inches["wideDetailed"],
@@ -641,10 +632,10 @@ for i_exp, experiment in enumerate(experiments):
         continue
 
     # Scan for algos to plot
-    algos = set()
+    algos = list()
     for row in current_rows:
         if row[csv_algo] not in algos:
-            algos.add(row[csv_algo])
+            algos.append(row[csv_algo])
 
     for i_algo, algo in reversed(list(enumerate(algos))):
         # Filter data of a given algorithm
[…]

### 2020-09-13 paper/appendA.tex
Plots and appendix

\chapter{Coloring Square-free Berge graphs}
\label{ch:coloringSquareFree}

The following appendix is based on the paper \citetitle{coloringSquareFree} by \citeauthor{coloringSquareFree} \cite{coloringSquareFree}.

\section{Introduction}
\TODO{some intro}

Recall, that a prism (\cref{def:prism}) is a graph consisting of two disjoint triangles and two disjoint paths between them.

\begin{defn}[Artemis graph]
  A graph $G$ is an \emph{Artemis graph} if it contains no odd hole, no antihole of length at least five, and no prism.
\end{defn}

In 2003 Maffray et al. published a paper on Artemis graphs where they show polynomial algorithms to recognize and color them \cite{Maffray2006}. In 2005 Maffray et al. published a paper on Artemis graphs\cite{Maffray2005} they showed an polynomial algorithm that checks if a perfect graph contains a prism, and returns it if so.

\begin{theorem}{\cite{Maffray2005}}
  \label{thm:getPrism}
  There is a polynomial algorithm, that given a perfect graph $G$, returns an induced prism $K$ of $G$, or an answer that $G$ contains no prisms.
\end{theorem}

In 2009 Maffray et al. published a paper on coloring Artemis graphs in time of $O(|V|^2|E|)$ \cite{coloringArtemis}. The paper contains simple pseudocode of the algorithm.

\begin{theorem}{\cite{coloringArtemis}}
  \label{thm:colorArtemis}
  There is a polynomial algorithm, that given an Artemis graph $G$, returns a $\omega(G)$-coloring of $G$.
\end{theorem}

So, we will focus on square-free perfect graphs that are not Artemis graphs. Let us notice, that every antihole of length at least 6 contains a square, therefore a square-free perfect graph that is not an Artemis graph must contain a prism. We will use this fact extensively.

Let us state a few definitions.

\begin{defn}[subdivision]
  In a graph $G$, subdividing an edge $uv \in E(G)$ means removing the edge $uv$ and adding a new vertex $w$ and two new edges $uw, wv$. Starting with a graph $G$, the effect of repeatedly subdividing edges prioduces a graph $H$ called a \emph{subdivision of $G$}. Note that $V(G) \subseteq V(H)$.
\end{defn}

\begin{defn}[triad]
  In a graph $G$, a \emph{triad} is a set of three pairwise non-adjacent vertices.
\end{defn}

\begin{defn}[good partition]
  A \emph{good partition} of a graph $G$ is a partition $(K_1, K_2, K_3, L, R)$ of $V(G)$ such that:
  \begin{itemize}
    \item $L$ and $R$ are not empty, and $L$ is anticomplete to $R$,
    \item $K_1 \cup K_2$ and $K_2 \cup K_3$ are cliques,
    \item in the graph obtained from $G$ by removing all edges between $K_1$ and $K_3$, every chordless path with one end in $K_1$, the other in $K_3$, and interior in $L$ contains a vertex from $L$ that is complete to $K_1$,
    \item either $K_1$ is anticomplete to $K_3$, or no vertex in $L$ has neighbors in both $K_1$ and $K_3$,
    \item for some $x \in L$ and $y \in R$, there is a triad of $G$ that contains $\{x, y\}$.
  \end{itemize}
\end{defn}

\TODO{we need many more definitions, scan pseudocode}

The algorithm we present is derived from contructive proof of the following two theorems.

\begin{theorem}{}[Theorem 2.1 of \cite{coloringSquareFree}]
  Let $G$ be a square-free Berge graph. If $G$ contains a prism, then $G$ has a good partition.
\end{theorem}

\begin{theorem}{}[Lemma 2.2 of \cite{coloringSquareFree}]
  Let $G$ be a square-free Berge graph. Suppose that $V(G)$ has a good partition $(K_1, K_2, K_3, L, R)$. Let $G_1 = G \setminus R$, $G_2 = G \setminus L$ and for $i = 1,2$ let $c_i$ be an $\omega(G_i)$-coloring of $G_i$. Then an $\omega(G)$-coloring of $G$ can be obtained in polynomial time.
\end{theorem}

\section{Notation}

In the following algorithms we use a slightly different notation than before, with many concepts represented by inline symbols. This is intended to reduce the length of algorithm's text and simplify its analysis.

\begin{itemize}
	\item $a \gets b$ -- let a be equal b.
	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$
	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.

	\item Strip $S_{uv}$ is \emph{rich} if and only if $S_{uv} \setminus T_{uv} \neq \emptyset$
\end{itemize}
\TODO{Introduction on unknown structures - J-strip etc etc}

\section{Algorithms}

\graphAppendix{Color Graph}
\input{coloringAppendix/algI.tex}
\clearpage

\graphAppendix{Color Good Partition}
\input{coloringAppendix/algII.tex}
\clearpage

\graphAppendix{Grow Hyperprism}
\input{coloringAppendix/algIII.tex}
\clearpage

\graphAppendix{Good Partition from an even hyperprism}
\input{coloringAppendix/algIV.tex}
\clearpage

\graphAppendix{Good Partition from odd hyperprism}
\input{coloringAppendix/algV.tex}
\clearpage

\graphAppendix{Good Partition from $J$-strip system}
\input{coloringAppendix/algVIa.tex}
\clearpage

\graphAppendix{Good Partition from a special $K_4$ strip system}
\input{coloringAppendix/algVIb.tex}
\clearpage

\graphAppendix{Find a special $K_4$ system}
\input{coloringAppendix/algVII.tex}
\clearpage

\graphAppendix{Growing a $J$-strip}
\input{coloringAppendix/algVIII.tex}
\clearpage

% \graphAppendix{LAST}
% \input{coloringAppendix/algIXa.tex}
% \clearpage

### 2020-09-13 paper/coloringAppendix/algVII.tex
Plots and appendix

@@
-\begin{algorithm}
+\begin{mynameforalgorithm}
   \SetKwFunction{FindSpecialK}{\textsc{Find-Special-K4-Strip-System}}
@@
   saturates $L(H)$ but does not saturate $L(H')$\;
-  \Assert{$R_{ij} \neq R'_{ij} \if and only if \{i, j\} = [2]$}
+  \Assert{$R_{ij} \neq R'_{ij}$ if and only if $\{i, j\} = [2]$}
   $r_{ij}, r_{ji} \gets$ ends of each $R_{ij}$\;
@@
   \vspace{-10cm}
-\end{algorithm}
+\end{mynameforalgorithm}

### 2020-09-13 paper/experiments.tex
Plots and appendix

@@
 
-We ran tests on X classes of perfect graphs, see \Cref{fig:graphClasses} for some examples:
+Below, we first present our data sets then overall time results on them and lastly a plot breaking down what parts of CCLSV and GPU CCLSV constitute their overall running time.
+
+We ran tests on nine classes of perfect graphs.
 \begin{itemize}
-  \item Random perfect graphs,
+  \item perfect Erd\H{o}s--Rényi graphs,
   \item Random bipartite graphs,
@@
   \item Hypercube graphs (\cref{fig:hypercube}),
-  \item Split graphs (\cref{fig:split}).
+  \item Split graphs (\cref{fig:split}),
+  \item Full binary trees.
 \end{itemize}
-
-In later paragraphs we describe each class one by one and benchmark our implementations on them.
 
@@
 
-\paragraph{Random perfect graphs}
-Our first method of generating graphs is to set $|V|$ and for each pair of vertices $u, v$ let $uv$ be the edge with probability of $1/2$.
-Then we check if generated graph is perfect and continue as long as we don't get sufficient number of perfect graphs.
+In \Cref{fig:graphClasses} we present small examples of some of the above classes. Let us describe them briefly.
 
-First, we note that this method of generating perfect graphs is very inefficient and we couldn't generate any graphs with $|V| \geq 20$.
-Second, those graphs favour the na\"ive algortihm, because there is very low probability of long chordless paths to appear (each chord has a $1/2$ chance to appear).
+An \emph{Erd\H{o}s--Rényi} model is a method of generating random graphs.
+Every possible edge is included in a graph with probability $1/2$.
+We generated them as long as we found enough perfect graphs for each $|V|$ we wanted to test.
+\todo{implement generating perfect graphs by removing long cycles} This method of generating perfect graphs is very inefficient and we couldn't generate any graphs with $|V| \geq 20$.
+Second, those graphs favour the na\"ive algortihm, because there is very low probability of long paths to appear.
+
+Next, we generate bipartite graphs in similar manner -- each edge between two equal sized node sets has a probability of $1/2$ to appear.
+We also generate line graphs of bipartite graphs.
+This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
+
+There are also a few interesting classes of perfect graphs that appear on a grid, or a checker board.
+In lattice graph, each vertex is connected to vertices that are above, below, to the left and to the right of it, if such vertices exist.
+See \Cref{fig:lattice} for an example of a $4 \times 4$ lattice graph.
+If we imagine our grid to be a chessboard we can define a rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
+See \Cref{fig:rook} for an example of $4 \times 4$ rook graph.
+In similar manner we can define a knight graph (\Cref{fig:knight}).
+
+A hypercube is a generalization of a cube to a higher dimensional space.
+We use hypercubes that are not complete, to achieve higher granularity of data.
+In a hypercube of $n$ vertices there is an edge between vertices $u$ and $v$ if and only if binary representations of $u$ and $v$ differ by exactly one bit.
+
+\TODO{split better granulity and detailed}
+Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
+In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.
+
+Finally, we benchmark on full binary trees to see how CCLSV works with a tree as an input.
+
+\subsubsection{Time results}
+
+% \begin{figure}
+%   \centering
+%   \input{plots/perf.t.in.out.csv.lines.pgf}
+%   \caption{Random perfect graphs}
+%   \label{plot:perfLines}
+% \end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/biparite.t.in.out.csv.lines.pgf}
+  \caption{TODO: redo with more data Random bipartite graphs}
+  \label{plot:perf2Lines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/perf2.t.in.out.csv.lines.pgf}
+  \caption{Line graphs of random bipartite graphs}
+  \label{plot:perf2Lines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
+  \caption{Lattice graphs}
+  \label{plot:gridLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
+  \caption{Rook graphs}
+  \label{plot:rookLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
+  \caption{Knight graphs}
+  \label{plot:knightLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
+  \caption{Hypercube graphs}
+  \label{plot:hypercubeLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/split20to50.t.in.out.csv.lines.pgf}
+  \caption{Split graphs}
+  \label{plot:splitLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/fullBinary20to100.t.in.out.csv.lines.pgf}
+  \caption{Full binary trees}
+  \label{plot:splitLines}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \input{plots/detailed.csv.detailed.pgf}
+  \caption{Detailed running times}
+  \label{plot:splitLines}
+\end{figure}
 
@@
 
-\TODO{Better plot by a lot WIP}
+Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs.
+This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
+On \cref{plot:perf2Lines} we can see na\"ive algorithm being much faster on the majority of the tests, although its faster growth allows GPU CCLSV to be faster on the biggest tests.
 
-\begin{figure}
-  \centering
-  \input{plots/perf.t.in.out.csv.lines.pgf}
-  \label{plot:perfLines}
-  \caption{Random perfect graphs}
-\end{figure}
-
-\paragraph{Random bipartite graphs}
-\TODO{TODO}
-
-\paragraph{Line graphs of random bipartite graphs}
-\TODO{data with bigger N}
-Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs.
-We repeated the process until we had sufficieng number of graphs for each $|V|$.
-On \cref{plot:perf2Lines} we can see GPU gives us much better improvement than in random graphs.
-This is due to the fact, that testing near cleaners takes over 80\% of the time for bigger graphs (\Cref{plot:perf2Det}).
-
-\begin{figure}
-  \centering
-  \input{plots/perf2.t.in.out.csv.lines.pgf}
-  \label{plot:perf2Lines}
-  \caption{Line graphs of random bipartite graphs}
-\end{figure}
-
-\paragraph{Lattice graphs}
-
-Next, we turn our attention to graphs generated on a grid, or a checker board (see later paragraphs).
+We turn our attention to graphs generated on a grid, or a checker board (see later paragraphs).
 First, we take lattice graphs.
@@
 
-With larger $|V|$ the speedup gained from utilizing GPU is also more significant. For $|V| = 78$ the running time for the whole algorithm is almost 3x better.
-
-\begin{figure}
-  \centering
-  \input{plots/grid6by5to11.t.in.out.csv.lines.pgf}
-  \label{plot:gridLines}
-  \caption{Lattice graphs}
-\end{figure}
-
-\paragraph{Rook graphs}
-
-If we imagine our grid to be a chessboard we can define a Rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
+If we imagine our grid to be a chessboard we can define a rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
 See \cref{fig:rook} for an example of $4 \times 4$ Rook graph.
@@
 
-\begin{figure}
-  \centering
-  \input{plots/rookGraph5by4to7.t.in.out.csv.lines.pgf}
-  \label{plot:rookLines}
-  \caption{Rook graphs}
-\end{figure}
-
-\paragraph{Knight graph}
-
-A knight graph is constructed in a similar way to rook graph, but by taking potential moves of a knight.
-
-\TODO{add 800s result for naive}
-
-\begin{figure}
-  \centering
-  \input{plots/knightGraph8by4to8.t.in.out.csv.lines.pgf}
-  \label{plot:knightLines}
-  \caption{Knight graphs}
-\end{figure}
-
-\paragraph{Hypercube graphs}
-
 A hypercube is a generalization of a cube to a higher dimensional space.
@@
 Hypercube graphs tell a similar story to lattice graphs and knight graphs.
-Na\"ive is very fast at first, but becomes unbearably slow for $|V|$ higher than 55.
+Na\"ive algorithm is very fast at first, but becomes unbearably slow for $|V|$ higher than 55.
 Unfortunately, CCLSV doesn't fare much better, although it grows slower.
 Again, the speedup of GPU CCLSV is noticeable, being around 4.8x for $|V| = 55$.
-
-\begin{figure}
-  \centering
-  \input{plots/hypercubes20to55.t.in.out.csv.lines.pgf}
-  \label{plot:hypercubeLines}
-  \caption{Hypercube graphs}
-\end{figure}
-
-\paragraph{Split graphs}
 
@@
 
-There are no long chordless paths here, so na\"ive fares great (\cref{plot:splitLines}).
+There are no long paths here, so na\"ive algorithm works great (\cref{plot:splitLines}).
 What is interesting, when looking at detailed times of GPU CCLSV, we can see that checking the existence of simple forbidden structures takes more than 30\% of the time.
 This opens a possibility of further GPU speedups, not explored by us.
-
-\begin{figure}
-  \centering
-  \input{plots/split20to50.t.in.out.csv.lines.pgf}
-  \label{plot:splitLines}
-  \caption{Split graphs}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \input{plots/detailed.csv.detailed.pgf}
-  \label{plot:splitLines}
-  \caption{\the\textwidth \the\textheight}
-\end{figure}
 
@@
 \begin{figure}
+  % \begin{subfigure}{.5\textwidth}
+  %   \centering
+  %   \input{plots/color.perf.t.in.out.csv.lines.pgf}
+  %   \caption{Random perfect graphs}
+  % \end{subfigure}%
   \begin{subfigure}{.5\textwidth}
     \centering
-    \input{plots/color.perf.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
+    TODO
+    \caption{Random perfect graphs}
   \end{subfigure}%
@@
     \centering
-    \input{plots/color.perf.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
+    TODO
+    \caption{Line graphs of random perfect graphs}
   \end{subfigure}
-  \caption{Random perfect graphs}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.grid5by4to9.t.in.out.csv.lines.pgf}
+    \caption{Lattice graphs}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.rookGraph6by4to8.t.in.out.csv.lines.pgf}
+    \caption{Rook graphs}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    \input{plots/color.knightGraph6by4to8.t.in.out.csv.lines.pgf}
+    \caption{Knight graphs}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering%
+    \input{plots/color.hypercube20to40.t.in.out.csv.lines.pgf}
+    \caption{Hypercube graphs}
+  \end{subfigure}
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    TODO
+    \caption{Split graphs}
+  \end{subfigure}%
+  \begin{subfigure}{.5\textwidth}
+    \centering
+    TODO
+    \caption{Full binary trees}
+  \end{subfigure}
 \end{figure}
@@
 \begin{figure}
-  \TODO{TODO}
-  % \begin{subfigure}{.5\textwidth}
-  %   \centering
-  %   \input{plots/color.perf2.t.in.out.csv.lines.pgf}
-  %   \caption{Overall running times}
-  %   \label{plot:colorPerfLines}
-  % \end{subfigure}%
-  % \begin{subfigure}{.5\textwidth}
-  %   \centering
-  %   \input{plots/color.perf2.t.in.out.csv.detailed.pgf}
-  %   \caption{Percentage of time taken be each part}
-  %   \label{plot:colorPerfDet}
-  % \end{subfigure}
-  \caption{Line graphs of random bipartite graphs}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{.5\textwidth}
   \centering
-    \input{plots/color.grid5by4to9.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
-  \end{subfigure}%
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.grid5by4to9.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-  \end{subfigure}
-  \caption{Lattice graphs}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.rookGraph6by4to8.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
-  \end{subfigure}%
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.rookGraph6by4to8.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-    \label{plot:colorRookDet}
-  \end{subfigure}
-  \caption{Rook graphs}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.knightGraph6by4to8.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
-  \end{subfigure}%
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.knightGraph6by4to8.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-  \end{subfigure}
-  \caption{Knight graphs}
-\end{figure}
-
-\begin{figure}
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.hypercube20to40.t.in.out.csv.lines.pgf}
-    \caption{Overall running times}
-  \end{subfigure}%
-  \begin{subfigure}{.5\textwidth}
-    \centering
-    \input{plots/color.hypercube20to40.t.in.out.csv.detailed.pgf}
-    \caption{Percentage of time taken be each part}
-  \end{subfigure}
-  \caption{Hypercube graphs}
-\end{figure}
-
-\begin{figure}
-  \TODO{TODOa}
-  % \begin{subfigure}{.5\textwidth}
-  %   \centering
-  %   \input{plots/color.perf2.t.in.out.csv.lines.pgf}
-  %   \caption{Overall running times}
-  %   \label{plot:colorPerfLines}
-  % \end{subfigure}%
-  % \begin{subfigure}{.5\textwidth}
-  %   \centering
-  %   \input{plots/color.perf2.t.in.out.csv.detailed.pgf}
-  %   \caption{Percentage of time taken be each part}
-  %   \label{plot:colorPerfDet}
-  % \end{subfigure}
-  \caption{Split graphs}
+  \input{plots/color.detailed.csv.detailed.pgf}
+  \caption{Detailed times of coloring}
 \end{figure}

### 2020-09-13 code/test/plot.py

@@ -1,7 +1,7 @@
 # coding: utf-8
 
-# usePgf = True
-usePgf = False
+usePgf = True
+# usePgf = False
 
 import matplotlib as mpl
 
@@ -102,7 +102,7 @@ algo_labels = {
     "Perfect": "Perfect",
     "CUDA Naive": "GPU Naive",
     "Naive": "Naive",
-    "CSDP Color": "CSDP Color",
+    "CSDP Color": "Color",
 }
 
 algo_field_labels = {
@@ -162,17 +162,6 @@ label_time_overall_s = "Total time [s]"
 
 # Here we declare what tests consist an experiment.
 experiments = [
-    # {
-    #     "restrictions": [(csv_result, 1), (csv_algo, "Perfect|Naive")],
-    #     "x_param": csv_N,
-    #     "x_show": csv_N,
-    #     "type": "lines",
-    #     "size": sizes_in_inches["regular"],
-    #     "y_param": csv_overall,
-    #     "ylog": False,
-    #     "x_label": label_lca_N,
-    #     "y_label": label_time_overall_s,
-    # },
     {
         "restrictions": [
             (csv_result, 1),
@@ -404,135 +393,22 @@ experiments = [
         "x_ticks_labels": ["aaaaaaaaaaa", "bb"]
         # "ylim": (0, 1),
     },
-    # {
-    #     "restrictions": [
-    #         (csv_result, 1),
-    #         (csv_filename, "perf2.t.in"),
-    #         (csv_N, "15|16|17|18|19"),
-    #         (csv_algo, "GPU Perfect|Perfect"),
-    #     ],
-    #     "x_param": csv_N,
-    #     "x_show": csv_N,
-    #     "type": "detailed",
-    #     "size": sizes_in_inches["wideDetailed"],
-    #     "x_label": "N",
-    #     "y_label": label_time_percentage,
-    #     "ylim": (0, 1),
-    # },
-    # {
-    #     "restrictions": [
-    #         (csv_result, 1),
-    #         (csv_filename, "fullBinary"),
-    #         (csv_N, "20|25|30|35|40|45|50|55"),
-    #         (csv_algo, "GPU Perfect|Perfect"),
-    #     ],
-    #     "x_param": csv_N,
-    #     "x_show": csv_N,
-    #     "type": "detailed",
-    #     "size": sizes_in_inches["wideDetailed"],
-    #     "x_label": "N",
-    #     "y_label": label_time_percentage,
[…]

### 2020-09-13 code/test/cuPerfTest/run.sh
Biparite many tests

@@ -25,7 +25,7 @@ perfectTests=(
   # "knightGraph8by4to8.t.in"
   # "rookGraph5by4to7.t.in"
   # "split20to50.t.in"
-  # "biparite.t.in"
+  "biparite.t.in"
 )
 
 pefectSupplement=(

### 2020-09-13 code/test/generate/generate.cpp

@@ -17,7 +17,7 @@ int main() {
   //   set<int> done;
 
   //   while (done.size() < (maxN - minN + 1) / step) {
-      Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
+  // Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
   //     if (rand() % 2) G = G.getComplement();
 
   //     if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
@@ -28,11 +28,13 @@ int main() {
   // }
 
   int minN = 42;
-  int maxn = 60;
+  int maxn = 58;
   int step = 2;
-  for(int i=minN; i<=maxn; i+=step) {
-    auto G = getBipariteGraph(i, 0.5);
-    G.printOut();
+  for (int i = 0; i < 10; i++) {
+    for (int i = minN; i <= maxn; i += step) {
+      auto G = getBipariteGraph(i, 0.5);
+      G.printOut();
+    }
   }
 
   // int minN = 20;

### 2020-09-13 paper/coloringAppendix/algI.tex
Save!
Appendix ALG I

@@
-\begin{algorithm}
+\begin{mynameforalgorithm}
+  % \myalgorithmcommand
   \SetKwFunction{colorGraph}{\textsc{Color-Graph}}
@@
   \KwData{$G$ -- square-free Berge graph}
-  \KwResult{A $\chi(G)$-coloring of $G$}
+  \KwResult{A $\omega(G)$-coloring of $G$}
   \Indp
-  TODO \;
-  TODO 2\;
-  \Return Todo\;
-\end{algorithm}
+  \If(\tcp*[f]{\Cref{thm:getPrism}}){$G$ is an Artemis graph}{
+    \Return coloring of an Artemis graph $G$ \tcp*{\Cref{thm:colorArtemis}}
+  }
+  $H \gets$ an induced prism of $G$ \tcp*{\Cref{thm:getPrism}}
+  \TODO{do we get $H$ ready from A.1.1?}
+
+  \While{$P = $ \textsc{undefined}}{
+
+    \If{$\exists$ a component of $G \setminus(H \cup M)$ with a set of attachments in $H$ not local}{
+      $F \gets$ a minimal component of $G \setminus(H \cup M)$ with a set of attachments in $H$ not local
+
+      $M \gets \{v: v$ is a major neighbor of H$\}$\;
+      \TODO{how do we get M?}
+
+      $H' \gets$ \textsc{Grow-Hyperprism}$(G, H, M, F)$\;
+      \If{$H'$ is  a \LGBSK}{
+        $J \gets H'$\;
+        $(S, N) \gets$ a $J$-strip system\;
+        \TODO{how?}
+      }\Else{
+        $H \gets H'$\;
+      }
+    }
+    \Else(\tcp*[f]{$H$ is a maximal hyperprism}){
+      $M \gets \{v: v$ is a major neighbor of H$\}$\;
+      \If{$H$ is an even hyperprism}{
+        $P \gets$ \textsc{Good-Partition-From-Even-Hyperprism}$(G, H, M)$
+        \textbf{break}
+      }
+      \Else{
+        $P \gets$ \textsc{Goog-Partition-From-Odd-Hyperprism}$(G, H, M)$\;
+        \textbf{break}
+      }
+    }
+    \If(\tcp*[f]{a $J$-strip system was encountered}){$J \neq$ \textsc{undefined}}{
+      $J', (S', N') \gets$ \textsc{Growing-J-Strip}$(G, J, (S, N))$\;
+      $M \gets$ a set of major vertives w.r.t. $(S, N)$\;
+      \If{$J', (S', N')$ is a special $K_4$ system}{
+        $P \gets$ \textsc{Good-Partition-From-Special-Strip-System}$(G, (S, N), M)$
+      }\Else{
+        $P \gets$ \textsc{Good-Partition-From-J-Strip-System}$(G, J, (S, N), M)$
+      }
+    }
+  }
+  \Return \textsc{Color-Good-Partition}$(G, P)$\;
+\end{mynameforalgorithm}

### 2020-09-14 code/test/colorPerfTest/run.sh
save

@@ -8,13 +8,16 @@ mkdir -p $resultsDir
 colorExec="$scriptDir/../../obj/test/colorPerfTest/color.e"
 
 colorTests=(
-  "perf.t.in"
-  "perfLin.t.in"
-  "fullBinary20to45.t.in"
-  "grid5by4to9.t.in"
-  "hypercube20to40.t.in"
-  "knightGraph6by4to8.t.in"
-  "rookGraph6by4to8.t.in"
+  # "perf.t.in"
+
+  # "fullBinary20to45.t.in"
+  # "grid5by4to9.t.in"
+  # "hypercube20to40.t.in"
+  # "knightGraph6by4to8.t.in"
+  # "rookGraph6by4to8.t.in"
+  "biparite18to48.t.in"
+  # "perfLin.t.in"
+  # "split.t.in"
 )
 
 # for file in "${colorTests[@]}"; do

### 2020-09-14 code/test/generate/generate.cpp

@@ -9,33 +9,33 @@
 int main() {
   srand(time(0));
 
-  // int minN = ;
-  // int maxN = 56;
-  // int step = 2;
+  int minN = 20;
+  int maxN = 45;
+  int step = 5;
 
-  // for (int i = 0; i < 10; i++) {
-  //   set<int> done;
-
-  //   while (done.size() < (maxN - minN + 1) / step) {
-  // Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
-  //     if (rand() % 2) G = G.getComplement();
-
-  //     if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
-  //       G.printOut();
-  //       done.insert(G.n);
-  //     }
-  //   }
-  // }
-
-  int minN = 42;
-  int maxn = 58;
-  int step = 2;
   for (int i = 0; i < 10; i++) {
-    for (int i = minN; i <= maxn; i += step) {
-      auto G = getBipariteGraph(i, 0.5);
-      G.printOut();
+    set<int> done;
+
+    while (done.size() < (maxN - minN + 1) / step) {
+      Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
+      // if (rand() % 2) G = G.getComplement();
+
+      if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+        G.printOut();
+        done.insert(G.n);
+      }
     }
   }
+
+  // int minN = 18;
+  // int maxn = 48;
+  // int step = 6;
+  // for (int i = 0; i < 10; i++) {
+  //   for (int i = minN; i <= maxn; i += step) {
+  //     auto G = getBipariteGraph(i, 0.5);
+  //     G.printOut();
+  //   }
+  // }
 
   // int minN = 20;
   // int maxN = 45;
@@ -67,8 +67,10 @@ int main() {
   //   G.printOut();
   // }
 
-  // for (int i = 10; i <= 25; i+=3) {
-  //   Graph G = getSplitGraph(i, getDistr());
-  //   G.printOut();
+  // for (int k = 0; k < 10; k++) {
+  //   for (int i = 12; i <= 24; i += 3) {
+  //     Graph G = getSplitGraph(i, getDistr());
+  //     G.printOut();
+  //   }
   // }
 }

### 2020-09-14 paper/definitions.tex
Plots and appendix
List near cleaners algo

@@
 By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge.
+Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, that is all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$.
 If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.
@@
 
-\TODO{Defs below to ch. 1}
+\begin{defn}[line graph]
+  The \emph{line graph} of a graph $G = (V, E)$ is the graph $L(G)$ with vertex set equal $E$, where $e, h \in E$ are adjacent in $L(G)$ if and only if they share an end in $G$.
+\end{defn}

### 2020-09-14 paper/perfectGraphs.tex
List near cleaners algo

@@
 Hamiltonian path \cite{Mller1996}, maximum cut problem \cite{Bodlaender1994} or dominating set problem \cite{Dewdney81}.
-\todo{all theese citations are about subclasses e.g.
-biparite graphs.
-Should we mention some subclasses?}
+There are many subclasses of perfect graphs, we take a look and benchmark our implementations on some of them in \Cref{sec:experiments}
 
@@
 This theorem is a consequence of a stronger result proven by Lovász:
-\begin{theorem}
+\begin{theorem}[\cite{LL72}, Claim 1 of \cite{GC03}]
 	\label{thm:omegaalpha}
-	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$. \todo{proof!}
+	A graph $G$ is perfect if and only if for every induced subgraph $H$, the number of vertices of $H$ is at most $\alpha(H)\omega(H)$.
 \end{theorem}
+\todo{proof? min. 1 page}
+% \begin{proof}
+% 	First assume that $G$ is perfect -- for every induced subgraph $H$, $\omega(G) = \chi(H)$. Since the number of vertices of $H$ is at most $\alpha(H)\chi(H)$, the claim follows.
+
+% 	The proof of the converse we show is due to Gasparyan \cite{Gasparian1996}.
+Assume that $G$ is not perfect.
+Let $H$ be a minimally imperfect subgraph of $G$ and let $n$ be the number of vertices of $H$.
+Let $\alpha = \alpha(H), \omega = \omega(H)$.
+
+% 	Then, because $H$ is \emph{minimally} imperfect, it satisfies:
+% 	\begin{itemize}
+% 		\item $\omega = \chi(H \setminus v)$, for every $v \in H(V)$,
+% 		\item $\omega = \omega(H \setminus S)$, for every stable set $S \subseteq V(H)$. 
+% 	\end{itemize}
+
+% 	Let $A_0$ be a maximal stable set of $H$. Then $|A_0| = \alpha$ and for each $s \in A_0$ fix an $\omega$-coloring of the graph $H \setminus s$.
+% \end{proof}
 
@@
 
+\begin{defn}[relevant triple]
+	Given a graph $G$, a triple $(a, b, c)$ of vertices is called \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
+\end{defn}
+
 \begin{defn}[C-major vertices]
@@
 \end{alg}
-\begin{algtext2}
-	We will call a triple $(a, b, c)$ of vertices \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
 
-	Given a relevant triple $(a, b, c)$ we can compute the following:
-	\begin{itemize}
-		\item $r(a,b,c) \leftarrow$~the cardinality of the largest anticomponent of $N(a, b)$, that contains a nonneibhbor of $c$, or 0, if $c$ is $N(a, b)$-complete.
-		\item $Y(a,b,c) \leftarrow$~the union of all anticomponents of $N(a, b)$ that have cardinality strictly greater than $r(a, b, c)$.
-		\item $W(a, b, c) \leftarrow$~the anticomponent of $N(a,b) \cup \{c\}$ that contains $c$.
-		\item $Z(a, b, c) \leftarrow$~the set of all $Y(a, b, c) \cup W(a,b,c)$-complete vertices.
-		\item $X(a, b, c) \leftarrow$~$Y(a,b,c) \cup Z(a,b,c)$.
-	\end{itemize}
-
-	For every two adjacent vertices $u, v$ compute the set $N(u, v)$ and list all such sets.
-	For each relevant triple $(a,b,c)$ compute the set $X(a,b,c)$ and list all such sets.
-
-	Output all subsets of $V(G)$ that are the union of a set from the first list and a set from the second list.
-\end{algtext2}
+\begin{algorithmic}[1]
+	\mProcedure{List-Possible-Near-Cleaners}{$G$}
+	\ls $X \gets \emptyset$
+	\mForEach{relevant triple $(a, b, c)$}
+		\ls $A \gets$ anticomponents of $N(\{a, b\})$
+		\mIf{$c$ is $N(\{a, b\})$-complete}
+			\ls $r \gets 0$
+		\mElse
+			\ls $r \gets$ the cardinality of the largest set of $A$ that contains 
+			\lsx a nonneibhbor of $c$ 
+		\mEndIf
+		\ls $Y \gets \emptyset$ 
+		\mForEach{$A_i \in A$}
+			\mIf{$|V(A_i)| > r$}
+				\ls $Y \gets Y \cup A_i$
+			\mEndIf
+			\mIf{$c \in A_i$}
+				\ls $W \gets A_i$
+			\mEndIf
+		\mEndFor
+		\ls $Z \gets$ the set of all $Y \cup W$-complete vertices
+		\ls $X \gets X \cup (Y \cup Z)$ 
+	\mEndFor
+	\ls $N \gets \emptyset$
+	\mForEach{edge $uv \in E(G)$}
+		\ls $N \gets N \cup N(\{u, v\})$
+	\mEndFor
+	\ls $R \gets \emptyset$
+	\mForEach{$X_i \in X$}
+		\mForEach{$N_j \in N$}
+			\ls $R \gets R \cup (X_i \cup N_j)$
+		\mEndFor
+	\mEndFor
+	\ls \RETURN $R$
+	\mEndProcedure
+\end{algorithmic}
 
@@
 		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
-		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ ($=n$ say) 
-		\item $r(x_3, y_1), r(x_3, y_2) \geq n$
+		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2) = min(r(x_3, y_1), r(x_3, y_2))$ 
 	\end{itemize}
-	\TODO{moze raczej $min(r(x_3, y_1), r(x_3, y_2)) = r(x_2, y_1) = r(x_1, y_2) = r(x_1, y_1) + 1$?}
 

### 2020-09-14 paper/perfectGraphs.tex
Odd holes algo

@@
 	\mForEach{$v_1, v_2, v_5 \in V(G)$, so that $v_1v_2$ is an edge \AND
-		\lsx $v_1v_5, v_2v_5$ are nonedges}
+		\lsx $v_1v_5, v_2v_5$ are nonedges \label{line:t3start}}
 		\ls $Y \gets$ the set of all $\{v_1, v_2, v_5\}$-complete vertices.
 		\mForEach{$X$ -- an anticomponent of $Y$}
-			\ls $F' \gets$ maximal connected subset containing $v_5$, such that $v_1, v_2$
+			\ls $F' \gets$ maximal connected subset containing $v_5$, such that $v_1, v_2$ \label{line:t3n4start}
 			\lsx have no neighbors in $F'$ and no vertex of $F'\setminus\{v_5\}$ is $X$-complete.
@@
 			\lsx $F'$ and are nonadjacent to all of $v_1, v_2$ and $v_5$
-			\ls $F \gets F' \cup F''$
+			\ls $F \gets F' \cup F''$ \label{line:t3mid}
 			\mForEach{$v_4 \in V(G) \setminus\{v_1, v_2, v_5\}$, such that $v_4$ is adjacent to $v_1$
 			\lsx and not to $v_2$ and $v_5$}
-				\mIf{$v_4$ has a neighbor in $F$ and a nonneibhbor in $X$}
+				\mIf{$v_4$ has a neighbor in $F$ and a nonneibhbor in $X$ \label{line:t3v4if}}
 					\ls $v_6 \gets$ a neighbor of $v_4$ in $F$
@@
 				\mEndIf
-			\mEndFor
+			\mEndFor \label{line:t3n4end}
 		\mEndFor
@@
 \begin{theorem}
+	\Cref{alg:t3} runs in $O(|V|^6)$ time.
+\end{theorem}
+\begin{proof}
+	There are $O(|V|^3)$ triples $(v_1, v_2, v_5)$ we enumerate in line \ref{line:t3start}.
+For each, there are $O(|V|)$ $X$s, so lines \ref{line:t3n4start}-\ref{line:t3n4end} are executed $O(|V|^4)$ times.
 
-\end{theorem}
-
-To see that the \cref{alg:t3} has a running time of $O(|V|^6)$, let us note that for each triple $v_1, v_2, v_5$ we examine, of which there are $O(|V|^3)$, there are linear many choices of $X$, each taking $O(|V|^2)$ time to process and generating a linear many choices of $v_4$ which take a linear time to process in turn.
-This gives us the total running time of $O(|V|^6)$.
-
-.
+	Each execution of lines \ref{line:t3n4start}-\ref{line:t3mid} takes $O(|V|^2)$ time, and there are $O(|V|)$ $v_4$s to enumerate.
+Line \ref{line:t3v4if} takes $O(|V|)$ time and then there are $O(|V|)$ $v_3$s to enumerate.
+Each is checked in $O(1)$ time.
+If we find the correct one, we calculate a path $P$, but return right away, so we calculate $P$ at most once in whole algorithm.
+\end{proof}
 
@@
 	\mProcedure{List-Possible-Near-Cleaners}{$G$}
-	\ls $X \gets \emptyset$
+	\ls $\mathcal{X} \gets \emptyset$
 	\mForEach{relevant triple $(a, b, c)$}
@@
 		\ls $Z \gets$ the set of all $Y \cup W$-complete vertices
-		\ls $X \gets X \cup (Y \cup Z)$ 
+		\ls $X(a, b, c) \gets Y \cup Z)$ \Comment{we use $X(a, b, c)$ in the proof of correctness}
+		\ls $\mathcal{X} \gets \mathcal{X} \cup X(a, b, c)$
 	\mEndFor
-	\ls $N \gets \emptyset$
+	\ls $\mathcal{N} \gets \emptyset$
 	\mForEach{edge $uv \in E(G)$}
-		\ls $N \gets N \cup N(\{u, v\})$
+		\ls $\mathcal{N} \gets \mathcal{N} \cup N(\{u, v\})$
 	\mEndFor
-	\ls $R \gets \emptyset$
+	\ls $\mathcal{R} \gets \emptyset$
 	\mForEach{$X_i \in X$}
 		\mForEach{$N_j \in N$}
-			\ls $R \gets R \cup (X_i \cup N_j)$
+			\ls $\mathcal{R} \gets \mathcal{R} \cup (X_i \cup N_j)$
 		\mEndFor
 	\mEndFor
-	\ls \RETURN $R$
+	\ls \RETURN $\mathcal{R}$
 	\mEndProcedure
@@
 	\label{thm:91}
-	Let $C$ be a shortest odd hole in $G$, with length at least 7. Then there is a relevant triple $(a, b, c)$ of vertices such that
+	Let $C$ be a shortest odd hole in $G$, with length at least seven. Then there is a relevant triple $(a, b, c)$ of vertices such that
 	\begin{itemize}
@@
 
+\begin{theorem}
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
+Then the result of the \Cref{alg:listNearCleaners} on the graph $G$ is a set $\mathcal{R}$, such that for every shortest amenable hole $C$, there is a near-cleaner for $C$ in $\mathcal{R}$.
+\end{theorem}
+\begin{proof}
 	Let us suppose that $C$ is an amenable hole in $G$.
@@
 Since $C$ is amenable, there is an edge $uv$ of $C$ that is $T$-complete, and therefore $T \subseteq N(u, v)$.
-But then $N(u, v) \cup X(a, b, c)$ is a near-cleaner for $C$.
+But then $N(u, v) \cup X(a, b, c) \in \mathcal{R}$ is a near-cleaner for $C$.
 Therefore the output of the \cref{alg:listNearCleaners} is correct.
+\end{proof}
 
@@
 \end{alg}
-\begin{algtext2}
-	For every pair $x, y \in V(G)$ of distinct vertices find shortest path $R(x, y)$ between $x, y$ with no internal vertex in $X$.
-If there is one, let $r(x, y)$ be its length, if not, let $r(x, y) = \infty$.
 
-	For all $y_1 \in V(G)\setminus X$ and all 3-vertex paths $x_1-x_2-x_3$ of $G\setminus y_1$ we check the following:
-	\begin{itemize}
-		\item $R(x_1, y_1), R(x_2, y_2)$ both exist -- define $y_2$ as the neighbor of $y_1$ in $R(x_2, y_1)$.
-		\item $r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2) = min(r(x_3, y_1), r(x_3, y_2))$ 
-	\end{itemize}
-
-	If there is such a choice of $x_1$, $x_2$, $x_3$, $y_1$ then we output that there is an odd hole. If not, we report that there is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.
-\end{algtext2}
-
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/nearCleanerFound.tex}
-	\caption{An odd hole is found}%
-	\vspace{-0.5cm}
-\end{wrapfigure}
+\begin{algorithmic}[1]
+	\mProcedure{Test-Near-Cleaner}{$G, X$}
+		\mForEach{pair $x, y \in V(G)$, such that $x \neq y$}
+			\mIf{there is a path between $x$ and $y$ with no internal vertices in $X$ \lsx}
+				\ls $R(x, y) \gets$ the shortest path $R(x, y)$ between $x, y$ with no
+				\lsx internal vertex in $X$.
+				\ls $r(x, y) \gets$ the length of $R(x, y)$
+			\mElse
+				\ls $R(x, y) \gets \textsc{undefined}$
+				\ls $r(x, y) \gets \infty$
+			\mEndIf
+			\mForEach{$y_1 \in V(G) \setminus X$}
+				\mForEach{3-vertex path $x_1-x_2-x_3$ of $G\setminus y_1$}
+					\mIf{$R(x_1, y_1), R(x_2, y_2)$ both exist}
+						\ls $y_2 \gets$ the neighbor of $y_1$ in $R(x_2, y_1)$
+						\mIf{$r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2) =$\lsx$min(r(x_3, y_1), r(x_3, y_2))$}
+						\ls \RETURN an odd hole found
+						\mEndIf
+					\mEndIf
+				\mEndFor
+			\mEndFor
+		\mEndFor
+		\RETURN no odd hole found
+	\mEndProcedure
+\end{algorithmic}
 
@@
 
+\begin{theorem}[Theorem 5.1 of \cite{MC05}]
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
+Let $X$ be a subset of $V(G)$.
+If \Cref{alg:testNearCleaner} reports an odd hole, then $G$ contains an odd hole.
+\end{theorem}
 \begin{proof}
@@
 We claim that $G$ contains an odd hole.
+
+	{\makeatletter
+	\let\par\@@par
+	\par\parshape0
+	\everypar{}\begin{wrapfigure}{r}{0.3\textwidth}
+		\input{tikzpictures/nearCleanerFound.tex}
+		\caption{An odd hole is found}%
+		% \vspace{-0.2cm}
+		\end{wrapfigure}
+		Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$.
+From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$.
+Also, from the definition of $y_1$, $y_1 \notin X$.
 
@@
 Since $r(x_3, y_1), r(x_3, y_2) \geq n (= r(x_1, y_2))$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
-Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.
+Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.\par}%
 
@@
 
+\begin{wrapfigure}{r}{0.35\textwidth}
+
+\end{wrapfigure}
+
 \subsection{Summary}

### 2020-09-14 code/test/colorPerfTest/run.sh

@@ -15,9 +15,9 @@ colorTests=(
   # "hypercube20to40.t.in"
   # "knightGraph6by4to8.t.in"
   # "rookGraph6by4to8.t.in"
-  "biparite18to48.t.in"
-  # "perfLin.t.in"
-  # "split.t.in"
+  # "biparite18to48.t.in"
+  "perfLin.t.in"
+  "split.t.in"
 )
 
 # for file in "${colorTests[@]}"; do

### 2020-09-14 code/test/generate/generate.cpp

@@ -9,14 +9,14 @@
 int main() {
   srand(time(0));
 
-  int minN = 20;
-  int maxN = 45;
+  int minN = 50;
+  int maxN = 50;
   int step = 5;
 
   for (int i = 0; i < 10; i++) {
     set<int> done;
 
-    while (done.size() < (maxN - minN + 1) / step) {
+    while (done.size() < (maxN - minN + step) / step) {
       Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
       // if (rand() % 2) G = G.getComplement();
 
@@ -68,7 +68,7 @@ int main() {
   // }
 
   // for (int k = 0; k < 10; k++) {
-  //   for (int i = 12; i <= 24; i += 3) {
+  //   for (int i = 24; i <= 30; i += 3) {
   //     Graph G = getSplitGraph(i, getDistr());
   //     G.printOut();
   //   }

### 2020-09-14 paper/coloringBergeGraphs.tex
Plots and appendix
Progress

@@
 We will now show how to find a stable set in $G$ of size $\alpha(G)$.
+We will construct a sequence of induced subgraphs $G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_{|V|}$, so that $G_{|V|}$ is a required stable set.
 
@@
 \end{alg}
-\begin{algtext2}
-  Let $v_1, \ldots v_n$ be an ordering of vertices of $G$.
-We will construct a sequence of induced subgraphs $G = G_0 \supseteq G_1 \supseteq \ldots \supseteq G_n$, so that $G_n$ is a required stable set.
 
-  Let $G_0 \leftarrow G$.
-Then, for each $i \geq 1$, compute $\alpha(G_{i-1} \setminus v_i)$.
-If $\alpha(G_{i-1} \setminus v_i) = \alpha(G)$, then set $G_i \leftarrow G_{i-1} \setminus \{v_i\}$, else set $G_i \leftarrow G_{i-1}$.
+\begin{algorithmic}[1]
+  \mProcedure{Get-Max-Stable-Set}{$G$}
+  \ls $v_1, \ldots, v_n \gets$ an ordering of $V(G)$
+  \ls $G_0 \leftarrow G$
+  \ls $\alpha_G = \alpha(G)$
+  \mForEach{$1 \leq i \leq |V|$}
+    \mIf{$\alpha(G_{i-1} \setminus v_i) = \alpha_G$}
+      \ls $G_i \leftarrow G_{i-1} \setminus \{v_i\}$
+    \mElse
+      \ls $G_i \leftarrow G_{i-1}$
+    \mEndIf
+  \mEndFor
+  \ls \RETURN $G_{|V|}$
+  \mEndProcedure
+\end{algorithmic}
 
-  Return $G_n$.
-\end{algtext2}
+\begin{theorem}
+  \Cref{alg:maxStableSet} works in polynomial time and for an input of $G$ returns a maximal cardinality stable set of $G$.
+\end{theorem}
+\begin{proof}
+  Let us prove that $G_{|V|}$ is indeed a stable set.
+Suppose otherwise and let $v_iv_j$ be an edge in $G_{|V|}$ with $i < j$ and $i$ minimal.
+But then $\alpha(G_{i-1} \setminus v_i) = \alpha(G_{i-1}) = \alpha(G)$ so by our construction $v_i$ is not in $G_i$ and $v_iv_j$ is not an edge of $G_n$.
+Therefore there are no edges in $G_{|V|}$.
 
-Let us prove that $G_n$ is indeed a stable set.
-Suppose otherwise and let $v_iv_j$ be an edge in $G_n$ with $i < j$ and $i$ minimal.
-But then $\alpha(G_{i-1} \setminus v_i) = \alpha(G_{i-1}) = \alpha(G)$ so by our construction $v_i$ is not in $G_i$ and $v_iv_j$ is not an edge of $G_n$.
-Therefore there are no edges in $G_n$.
+  Because at every step we have $\alpha(G_i) = \alpha(G_{i-1})$, therefore $\alpha(G_{|V|}) = \alpha(G)$, so $G_{|V|}$ is required maximum cardinality stable set.
 
-Because at every step we have $\alpha(G_i) = \alpha(G_{i-1})$, therefore $\alpha(G_n) = \alpha(G)$, so $G_n$ is required maximum cardinality stable set.
+  The running time of \cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
+\end{proof}
 
-The running time of \cref{alg:maxStableSet} is polynomial, because we construct $n$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
+Given a natural weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ using the following modification:
 
-Given a weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ in the following manner.
-Create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the nodes $v$, $u$ are adjacent in $G$.
-Then calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.
-We will use this technique later on.
+\begin{alg}[maximum weighted stable set in a perfect graph]
+  \label{alg:maxWeightedStableSet}
+  Input: A perfect graph $G = (V, E)$ and a weight function $w : V \rightarrow \mathbb{N}$.
+
+  \noindent Output: A maximum weighted stable set in $G$.
+\end{alg}
+
+\begin{algorithmic}[1]
+  \mProcedure{Get-Max-Weighted-Stable-Set}{$G, w$}
+  \mForEach{$v \in V(G)$}
+    \ls $W_v \gets$ a set of nonadjacent vertices of size $w(v)$
+  \mEndFor
+  \ls $V' \gets \bigcup W_v$, for $v \in V(G)$ \Comment{$|V'| = \sum_{v\in V(G)} w(v)$ \vspace{-.1cm}}
+  \ls $E' \gets \{xy$ for $x, y \in V'$, such that for some $u, v \in V, u \neq v$:
+  \lsx~~~~~~~~ $x \in W_u$, $y \in W_v$, and $uv \in E(G)\}$
+  \ls $G' \gets (V', E')$
+  \ls $S' \gets$ \textsc{Get-Max-Stable-Set$(G')$}
+  \ls $S \gets \{v \in V(G)$, such that for some $x\in W_v$, $x \in S'\}$
+  \ls \RETURN $S$
+  \mEndProcedure
+\end{algorithmic}
+
+We create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the nodes $v$, $u$ are adjacent in $G$.
+Then we can calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.
 
@@
 Next, let us show how to find a stable set intersecting all the maximum cardinality cliques of $G$.
+We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$ and return a stable set intersecting them all.
+
+Recall that to calculate a maximum cardinality clique of $G$, we can calculate a maximum cardinality stable set of $\overline{G}$.
 \begin{alg}
@@
 \end{alg}
-\begin{algtext2}
-  We will create a list $Q_1, \ldots Q_t$ of all maximum cardinality cliques of $G$.
 
-  Let $Q_1 \leftarrow$ a maximum cardinality clique of $G$. We calculate this by running \cref{alg:maxStableSet} on $\overline{G}$.
+\begin{algorithmic}[1]
+  \mProcedure{Get-Stable-Set-Intersecting-Max-Cliques}{$G$}
+    \ls $\omega_G \gets \omega(G)$
+    \ls $Q_1 \gets$ \textsc{Max-Stable-Set}$(\overline{G})$
+    \ls $t \gets 1$
+    \mWhile{true}
+      \ls $w \gets$ a weight function $V \rightarrow \mathbb{N}$, so that for $v \in V$, $w(v)$ is equal to
+      \lsx the number of cliques $Q_1, \ldots Q_t$ that contain $v$.
+      \ls $S \gets$ \textsc{Max-Weighted-Stable-Set}$(G, w)$ \label{line:ssGetS}
+      \mIf{$\omega(G \setminus S) < \omega_G$}
+        \ls \RETURN $S$
+      \mElse
+        \ls $t \gets t+1$ \vspace{-.1cm}
+        \ls $Q_t \gets$ \textsc{Max-Stable-Set}$(\overline{G \setminus S})$
+      \mEndIf
+    \mEndWhile
+  \mEndProcedure
+\end{algorithmic}
 
-  Now suppose $Q_1, \ldots, Q_t$ have been found. We show how to calculate $Q_{t+1}$ or see that we are done.
-
-  Let us define a weight function $w : V \rightarrow \mathbb{N}$, so that for $v \in V$, $w(v)$ is equal to the number of cliques $Q_1, \ldots Q_t$ that contain $v$.
-
-  Assign $S \leftarrow$ the maximum $w$-weighted stable set, as described in a remark to \cref{alg:maxStableSet}.
-It is easy to see that $S$ has weight $t$, which means that $S$ meets each of $Q_1, \ldots Q_t$.
-
-  If $\omega(G \setminus S) < \omega(G)$, then $S$ meets all the maximum cardinality cliques in G so we return $S$.
-Otherwise we find a maximum cardinality clique in $G \setminus S$ (it will be of size $\omega(G)$, because $\omega(G \setminus S) = \omega(G)$), add it to our list as $Q_{t+1}$ and continue with longer list.
-
-\end{algtext2}
+To understand \Cref{alg:ssIntersectingCliques}, let us note that $S$ calculated in line \ref{line:ssGetS} has a weight equal $t$, which means that $S$ meets each of $Q_1, \ldots Q_t$.
+Then, if $\omega(G \setminus S) < \omega(G)$, then $S$ meets all the maximum cardinality cliques in G so we return $S$.
 
@@
 
-  \noindent Output: A coloring of $G$ using $\chi(G)$ colors.
+  \noindent Output: $C$ -- a coloring of $G$ using $\chi(G)$ colors.
 \end{alg}
-\begin{algtext2}
-  If $G$ is equal to its maximum cardinality stable set, color all vertices one color and return.
 
-  Else find $S$ intersecting all maximum cardinality cliques of $G$ (\cref{alg:ssIntersectingCliques}).
-Color recursively all vertices of $G \setminus S$ with $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors and all vertices of $S$ with one additional color.
-\end{algtext2}
+\begin{algorithmic}[1]
+  \mProcedure{Color-Perfect-Graph}{$G$}
+  \mIf{$G =$~\textsc{Get-Max-Stable-Set$(G)$}}
+    \ls $C \gets$ coloring all vertices of $G$ with one color
+    \ls \RETURN $C$
+  \mElse
+    \ls $S \gets$ \textsc{Get-Stable-Set-Intersecting-Max-Cliques}$(G)$
+    \ls $C' \gets$ \textsc{Color-Perfect-Graph}$(G \setminus S)$
+    \ls $C \gets C'$ with vertices of $S$ colored with an additional color
+    \ls \RETURN $C$
+  \mEndIf
+  \mEndProcedure
+\end{algorithmic}
 
-We will call recursion at most $O(|V|)$ times, each step of recursion is polynomial in time. Therefore the running time of \cref{alg:minColoring} is polynomial.
+Note that coloring $C'$ uses $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$.
+We will call recursion at most $O(|V|)$ times, each step of recursion is polynomial in time.
+Therefore the running time of \cref{alg:minColoring} is polynomial.
 
@@
 
+\begin{defn}[prism]
   A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
@@
 A prism with all three paths odd is called an \emph{odd prism}.
+  \label{def:prism}
+\end{defn}
 

### 2020-09-14 paper/experiments.tex
Plot
save
Progress

@@
   \input{plots/biparite.t.in.out.csv.lines.pgf}
-  \caption{TODO: redo with more data Random bipartite graphs}
+  \caption{Random bipartite graphs}
   \label{plot:perf2Lines}
@@
     \centering
-    TODO
-    \caption{Random perfect graphs}
+    \input{plots/color.biparite18to48.t.in.out.csv.lines.pgf}
+    \caption{Random bipartite graphs}
   \end{subfigure}%
@@
     \centering
-    TODO
-    \caption{Line graphs of random perfect graphs}
+    \input{plots/color.perfLin.t.in.out.csv.lines.pgf}
+    \caption{Line graphs of random bipartite graphs}
   \end{subfigure}
@@
     \centering
-    TODO
+    \input{plots/color.split.t.in.out.csv.lines.pgf}
     \caption{Split graphs}
@@
     \centering
-    TODO
+    \input{plots/color.fullBinary20to45.t.in.out.csv.lines.pgf}
     \caption{Full binary trees}
   \end{subfigure}
+  \caption{Overall times of CSDP Color}
 \end{figure}

### 2020-09-14 code/test/colorPerfTest/run.sh

@@ -16,8 +16,15 @@ colorTests=(
   # "knightGraph6by4to8.t.in"
   # "rookGraph6by4to8.t.in"
   # "biparite18to48.t.in"
+  # "split.t.in"
+
   "perfLin.t.in"
+  "lattice.t.in"
+  "rook.t.in"
+  "knight.t.in"
+  "hypercube.t.in"
   "split.t.in"
+  "fullBinary.t.in"
 )
 
 # for file in "${colorTests[@]}"; do

### 2020-09-14 code/test/generate/generate.cpp

@@ -9,23 +9,23 @@
 int main() {
   srand(time(0));
 
-  int minN = 50;
-  int maxN = 50;
-  int step = 5;
+  // int minN = 18;
+  // int maxN = 48;
+  // int step = 6;
 
-  for (int i = 0; i < 10; i++) {
-    set<int> done;
+  // for (int i = 0; i < 10; i++) {
+  //   set<int> done;
 
-    while (done.size() < (maxN - minN + step) / step) {
-      Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
-      // if (rand() % 2) G = G.getComplement();
+  //   while (done.size() < (maxN - minN + step) / step) {
+  //     Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
+  //     // if (rand() % 2) G = G.getComplement();
 
-      if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
-        G.printOut();
-        done.insert(G.n);
-      }
-    }
-  }
+  //     if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+  //       G.printOut();
+  //       done.insert(G.n);
+  //     }
+  //   }
+  // }
 
   // int minN = 18;
   // int maxn = 48;
@@ -37,27 +37,27 @@ int main() {
   //   }
   // }
 
-  // int minN = 20;
-  // int maxN = 45;
-  // for (int k = minN; k <= maxN; k+=5) {
-  // // for (int k = minN; k <= maxN; k++) {
-  //   Graph G = getFullBinaryTree(k);
-  //   G.printOut();
-  // }
+  int minN = 18;
+  int maxN = 48;
+  for (int k = minN; k <= maxN; k+=6) {
+  // for (int k = minN; k <= maxN; k++) {
+    Graph G = getFullBinaryTree(k);
+    G.printOut();
+  }
 
-  // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}, {5, 8}, {5, 9}};
-  // vec<vec<int>> sizes = {{6, 4}, {6, 5}, {6, 6}, {6, 7}, {6, 8}};
[…]

### 2020-09-14 code/test/plot.py

@@ -407,7 +407,7 @@ experiments = [
         "x_label": label_lca_N,
         "y_label": label_time_overall_s,
         "out_prefix": "color",
-        "ylim": (0.5, 250),
+        "ylim": (0.2, 350),
     },
     # {
     #     "restrictions": [(csv_algo, "CSDP")],

### 2020-09-14 paper/experiments.tex
Plots

@@
     \centering
-    \input{plots/color.grid5by4to9.t.in.out.csv.lines.pgf}
+    \input{plots/color.lattice.t.in.out.csv.lines.pgf}
     \caption{Lattice graphs}
@@
     \centering
-    \input{plots/color.rookGraph6by4to8.t.in.out.csv.lines.pgf}
+    \input{plots/color.rook.t.in.out.csv.lines.pgf}
     \caption{Rook graphs}
@@
     \centering
-    \input{plots/color.knightGraph6by4to8.t.in.out.csv.lines.pgf}
+    \input{plots/color.knight.t.in.out.csv.lines.pgf}
     \caption{Knight graphs}
@@
     \centering%
-    \input{plots/color.hypercube20to40.t.in.out.csv.lines.pgf}
+    \input{plots/color.hypercube.t.in.out.csv.lines.pgf}
     \caption{Hypercube graphs}
@@
     \centering
-    \input{plots/color.fullBinary20to45.t.in.out.csv.lines.pgf}
+    \input{plots/color.fullBinary.t.in.out.csv.lines.pgf}
     \caption{Full binary trees}

### 2020-09-14 code/test/colorPerfTest/run.sh

@@ -18,13 +18,13 @@ colorTests=(
   # "biparite18to48.t.in"
   # "split.t.in"
 
-  "perfLin.t.in"
-  "lattice.t.in"
-  "rook.t.in"
-  "knight.t.in"
-  "hypercube.t.in"
+  # "perfLin.t.in"
+  # "lattice.t.in"
+  # "rook.t.in"
+  # "knight.t.in"
+  # "hypercube.t.in"
   "split.t.in"
-  "fullBinary.t.in"
+  # "fullBinary.t.in"
 )
 
 # for file in "${colorTests[@]}"; do

### 2020-09-14 code/test/generate/generate.cpp

@@ -37,13 +37,13 @@ int main() {
   //   }
   // }
 
-  int minN = 18;
-  int maxN = 48;
-  for (int k = minN; k <= maxN; k+=6) {
-  // for (int k = minN; k <= maxN; k++) {
-    Graph G = getFullBinaryTree(k);
-    G.printOut();
-  }
+  // int minN = 18;
+  // int maxN = 48;
+  // for (int k = minN; k <= maxN; k+=6) {
+  // // for (int k = minN; k <= maxN; k++) {
+  //   Graph G = getFullBinaryTree(k);
+  //   G.printOut();
+  // }
 
   // // vec<vec<int>> sizes = {{5, 4}, {5, 5}, {5, 6}, {5, 7}, {5, 8}, {5, 9}};
   // vec<vec<int>> sizes = {{6, 3}, {6, 4}, {6, 5}, {6, 6}, {6, 7}, {6, 8}};
@@ -67,10 +67,10 @@ int main() {
   //   G.printOut();
   // }
 
-  // for (int k = 0; k < 10; k++) {
-  //   for (int i = 9; i <= 19; i += 3) {
-  //     Graph G = getSplitGraph(i, getDistr());
-  //     G.printOut();
-  //   }
-  // }
+  for (int k = 0; k < 10; k++) {
+    for (int i = 9; i <= 24; i += 3) {
+      Graph G = getSplitGraph(i, getDistr());
+      G.printOut();
+    }
+  }
 }

### 2020-09-14 code/test/plot.py

@@ -102,7 +102,7 @@ algo_labels = {
     "Perfect": "Perfect",
     "CUDA Naive": "GPU Naive",
     "Naive": "Naive",
-    "CSDP Color": "Color",
+    "CSDP Color": "",
 }
 
 algo_field_labels = {
@@ -112,7 +112,7 @@ algo_field_labels = {
     csv_testNCShortestPaths: "Calculare $R$",
     csv_gpuCopyR: "Copy $R$",
     csv_gpuWork: "GPU test",
-    csv_color_res: "Rest",
+    csv_color_res: "Graph manipulation",
     csv_color_CSDP: "CSDP",
 }
 field_colors = {
@@ -428,7 +428,7 @@ experiments = [
             # (csv_N, "20|25|30|35|40|45|50|55"),
             # (csv_algo, "GPU Perfect|Perfect"),
         ],
-        "x_param": csv_N,
+        "x_param": csv_filename,
         "x_show": csv_filename,
         "type": "detailed",
         "size": sizes_in_inches["wideDetailed"],
@@ -633,7 +633,6 @@ for i_exp, experiment in enumerate(experiments):
         handles, labels = ax.get_legend_handles_labels()
         ax.legend(handles[::-1], labels[::-1], ncol=3)
     elif experiment["type"] == "detailed":
-        fig.tight_layout(rect=[0, 0.1, 1, 1])
 
         handles, labels = ax.get_legend_handles_labels()
         legend = ax.legend(handles, labels)
@@ -641,6 +640,7 @@ for i_exp, experiment in enumerate(experiments):
             zip(ax.get_legend_handles_labels()[0], ax.get_legend_handles_labels()[1])
         )
         if len(handles_and_labels) > 3:
+            fig.tight_layout(rect=[0, 0.1, 1, 1])
             rect = patches.Rectangle(
                 (-29, -2.37),
                 165,
@@ -735,23 +735,33 @@ for i_exp, experiment in enumerate(experiments):
             plt.gca().add_artist(legend1)
             plt.gca().add_artist(legend2)
         else:
+            fig.tight_layout(rect=[0, 0.04, 1, 1])
             rect = patches.Rectangle(
-                (-28, -1.98),
-                166,
-                1,
+                (-5, -1.42),
+                140,
+                .35,
                 linewidth=1,
                 edgecolor="black",
                 facecolor="white",
                 clip_on=False,
             )
             shadow = patches.Rectangle(
-                (-27, -1.99),
-                166,
[…]

### 2020-09-14 paper/appendA.tex
Much pogrress

@@
 
-\begin{defn}[Artemis graph]
+\begin{defnTwo}[Artemis graph]
   A graph $G$ is an \emph{Artemis graph} if it contains no odd hole, no antihole of length at least five, and no prism.
-\end{defn}
+\end{defnTwo}
 
@@
 
-\begin{defn}[subdivision]
+\begin{defnTwo}[subdivision]
   In a graph $G$, subdividing an edge $uv \in E(G)$ means removing the edge $uv$ and adding a new vertex $w$ and two new edges $uw, wv$.
@@
 Note that $V(G) \subseteq V(H)$.
-\end{defn}
+\end{defnTwo}
 
-\begin{defn}[triad]
+\begin{defnTwo}[triad]
   In a graph $G$, a \emph{triad} is a set of three pairwise non-adjacent vertices.
-\end{defn}
+\end{defnTwo}
 
-\begin{defn}[good partition]
+\begin{defnTwo}[good partition]
   A \emph{good partition} of a graph $G$ is a partition $(K_1, K_2, K_3, L, R)$ of $V(G)$ such that:
@@
   \end{itemize}
-\end{defn}
+\end{defnTwo}
 
@@
 
-\graphAppendix{Color Graph}
+\graphAppendix{Color square-free perfect graph}
 \input{coloringAppendix/algI.tex}
@@
 
-\graphAppendix{Color Good Partition}
+\graphAppendix{Color good partition}
 \input{coloringAppendix/algII.tex}
@@
 
-\graphAppendix{Grow Hyperprism}
+\graphAppendix{Grow hyperprism}
 \input{coloringAppendix/algIII.tex}
@@
 
-\graphAppendix{Good Partition from an even hyperprism}
+\graphAppendix{Good partition from an even hyperprism}
 \input{coloringAppendix/algIV.tex}
@@
 
-\graphAppendix{Good Partition from odd hyperprism}
+\graphAppendix{Good partition from an odd hyperprism}
 \input{coloringAppendix/algV.tex}
@@
 
-\graphAppendix{Good Partition from $J$-strip system}
+\graphAppendix{Good partition from a $J$-strip system}
 \input{coloringAppendix/algVIa.tex}
@@
 
-\graphAppendix{Good Partition from a special $K_4$ strip system}
+\graphAppendix{Good partition from a special $K_4$ strip system}
 \input{coloringAppendix/algVIb.tex}

### 2020-09-14 paper/coloringBergeGraphs.tex
Much pogrress

@@
 
-Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length \todo{picture}.
+\begin{wrapfigure}{l}{0.4\textwidth}
+  \input{tikzpictures/umbrella.tex}
+  \caption{Lovász's umbrella}
+  \label{fig:umbrella}
+\end{wrapfigure}
+
+Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.
 Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90$^\circ$.
 This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
+See \Cref{fig:umbrella}.
 We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.
@@
 
-\begin{alg}[maximum cardinality stable set in a perfect graph]
+\begin{alg}[Maximum cardinality stable set in a perfect graph]
   \label{alg:maxStableSet}
@@
 
-\begin{alg}[maximum weighted stable set in a perfect graph]
+\begin{alg}[Maximum weighted stable set in a perfect graph]
   \label{alg:maxWeightedStableSet}
@@
 Recall that to calculate a maximum cardinality clique of $G$, we can calculate a maximum cardinality stable set of $\overline{G}$.
-\begin{alg}
+\begin{alg}[Stable set intersecting all maximum cardinality cliques]
   \label{alg:ssIntersectingCliques}
@@
 
-\begin{alg}
+\begin{alg}[Color perfect graph]
   \label{alg:minColoring}
@@
 Before proving strong perfect graph conjecture, a similar conjecture for square-free Berge graphs has been proven by Conforti et al.
-\cite{Conforti2004} During one of her lectures, Maria Chudnovsky expressed hope that discovery of full algorithm for coloring Berge graphs might follow a similar pattern.
-We analyze this algorithm and provide its pseudocode in \cref{ch:coloringSquareFree}.
+\cite{Conforti2004}.
+During one of her lectures, Maria Chudnovsky expressed hope that discovery of full algorithm for coloring Berge graphs might follow a similar pattern.
 
-\TODO{Dałbym ze 2-3 zdania braggowania, ze algorytm jest duzo bardziej zlozony niz rozpoznawanie + na czym sie opiera.}
+The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement.
+The main idea is that, if square-free Berge graph $G$ is a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism.
+We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.
+The paper in which the algorithm is presented \cite{Chudnovsky2019} is of much more mathematical ''flavor'' then \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward.
+We do it in the Appendix A.

### 2020-09-14 paper/experiments.tex
Much pogrress

@@
   \caption{Detailed running times}
-  \label{plot:splitLines}
+  \label{plot:perfDetailed}
 \end{figure}
 
-When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we see the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV.
+First, let us take a look at the performance of CCLSV algorithm.
+If we limit runtime to about two minutes, we can run it on graphs of sizes up to 40-70, depending on the type of the graph we test.
+What is interesting, that there isn't that much of a variance of the running time depending on the type of graph we test on.
+This is a big advantage of CCLSV over the na\"ive algorithm, which is highly dependent on the type of input.
+On some graphs, it works almost instantenously, what is to be expected, given its nature of enumerating paths.
+But on some graphs, e.g.
+lattice graphs (\Cref{plot:gridLines}) its overall running time grows much faster than CCLSV's.
+
+Let us turn our attention to the GPU CCLSV's results.
+\Cref{plot:perfDetailed} shows breakdown of each implementation running times on a single graph of each class.
+We can clearly see that in most cases, testing possible near-cleaners takes most of the running time, so the speedup by the GPU is significant.
+
+Examples of full binary graph, and lattice graph show that getting near cleaners still can be a big bottleneck.
+Parallelization of this method could be considered in the future.
+A possible idea would be to use recently developed dynamic dictionary for the GPU \cite{Ashkiani2018}.
+When running GPU CCLSV on split graphs, quite a lot of time is spent checking simple structures.
+This should be easily parallelizable if need be, or if graphs that require it are encountered.
+
+% When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we see the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV.
 Slight GPU improvement is explained by anylysis of the components of the overall time (\Cref{plot:perfDet}).
@@
 
-Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs.
+% Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs.
 This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
@@
 
-We turn our attention to graphs generated on a grid, or a checker board (see later paragraphs).
+% We turn our attention to graphs generated on a grid, or a checker board (see later paragraphs).
 First, we take lattice graphs.
@@
 
-Let us take a look at \cref{plot:gridLines}.
+% Let us take a look at \cref{plot:gridLines}.
 It is a clear example of why polynomial algorithms can be useful, even the ones with time complexity as high as CCLSV.
@@
 
-If we imagine our grid to be a chessboard we can define a rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
+% If we imagine our grid to be a chessboard we can define a rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
 See \cref{fig:rook} for an example of $4 \times 4$ Rook graph.
 
-Rook graphs have many more chords than Lattice graphs, so the na\"ive's performance is much better here.
+% Rook graphs have many more chords than Lattice graphs, so the na\"ive's performance is much better here.
 What is more interesting, the overall performance of CCLSV is much worse (\cref{plot:rookLines}).
@@
 
-A hypercube is a generalization of a cube to a higher dimensional space.
+% A hypercube is a generalization of a cube to a higher dimensional space.
 We use hypercubes that are not complete, to achieve higher granularity of data.
@@
 
-Hypercube graphs tell a similar story to lattice graphs and knight graphs.
+% Hypercube graphs tell a similar story to lattice graphs and knight graphs.
 Na\"ive algorithm is very fast at first, but becomes unbearably slow for $|V|$ higher than 55.
@@
 
-Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
+% Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
 In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.
 
-There are no long paths here, so na\"ive algorithm works great (\cref{plot:splitLines}).
+% There are no long paths here, so na\"ive algorithm works great (\cref{plot:splitLines}).
 What is interesting, when looking at detailed times of GPU CCLSV, we can see that checking the existence of simple forbidden structures takes more than 30\% of the time.

### 2020-09-14 paper/implementation.tex
Much pogrress

@@
 
-Another crucial optimization is to eliminate partial solutions that have chords right away. This is especially useful in graphs that have many chords and reduces running time dramatically.
+Another crucial optimization is to eliminate partial solutions that have edges between not consecutive vertices right away.
+Also, when we look for an odd hole specifically, we can assume that its first vertex we enumerate is the lowest.
+Those two optimizations alone make a huge difference.
+With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a couple of minutes, to being faster than CCLSV on most of our tests.
 
@@
 
-This optimization alone is crucial for performance.
-In our testing, all calls of $areUnique$ took abour 70\% of total running time of the CCLSV algorithm, and virtually all running time of the na\"ive algorithm \todo{check}.
-After using static $stamp$ array, it fell to 5.2\% in CCLSV and to X\% in na\"ive.
-The overall speedup of the CCLSV algorithm was about 6x.
-\todo{check if for sure it didn't use path speedup} The speedup of na\"ive algorithm was even greater -- about 20x.
+This optimization almost cuts down na\"ive algorithm's running time in half.
 
@@
 We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$.
+Before optimizing path enumeration algorithm, all calls of $areUnique$ alone took abour 70\% of total running time of the CCLSV algorithm.
+After optimizing $areUnique$, path enumeration still took more than 50\% of total running time.
+After all optimizations it is almost unnoticable.
 
@@
 We used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
-
-\TODO{example of a call graph?}
-
-\TODO{callgrind}
-\TODO{first result to best result gains (like: we are 20x faster than what first comes to mind)}
-\TODO{regenerate speedup results to make sure what the gains were}
 
@@
 
-\TODO{CUDA background}
-\TODO{moderngpu - allows us to run simple transforms}
+CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs.
+It allows to run a program in parallel by many CUDA threads at once.
+Although usually described by PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing RAM algorith on a cpu.
+Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from large latency.
+What is more, there are no standard dynamic structures in PRAM model, let alone CUDA, that are taken for granted in PRAM model, such as hashing maps or sets.
+We used a library called \emph{moderngpu} for our implementation, because it allows a slightly cleaner code.
+
 \TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}
 
-We posed a question if it would be profitable to use GPU for this problem.
+We posed a question if it would be profitable to use GPU for the problem of recognizing Berge graphs.
 On one hand the graphs we are working on are small and our time complexity so large that a speedup from massively parallel architecture could be profitable.
 On the other the algorithm is complex and not easy to parallelise.
-Therefore we decided to analyze the  CCLSV\todo{a good name for it?} algorithm and parrallelize parts that would benefit from it the most.
+Therefore we decided to analyze the  CCLSV algorithm and parrallelize parts that would benefit from it the most.
 
@@
 
-It turns out that this optimization alone speeds up \cref{alg:testNearCleaner} almost 7x \todo{check} on bigger tests, which gives us a speedup of about 6x \todo{check} for overall algorithm.
-
-\TODO{implement other CUDA opts and describe them}
+The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall algorithm.

### 2020-09-14 paper/perfectGraphs.tex
Much pogrress

@@
 	\end{itemize}
-	\TODO{We may use this lemma quite often, might want to provide proof if so.}
 \end{lemma}
@@
 
-\begin{alg}
+\begin{alg}[Test if $G$ contains a $\T_3$]
 	\label{alg:t3}
@@
 	Each execution of lines \ref{line:t3n4start}-\ref{line:t3mid} takes $O(|V|^2)$ time, and there are $O(|V|)$ $v_4$s to enumerate.
-Line \ref{line:t3v4if} takes $O(|V|)$ time and then there are $O(|V|)$ $v_3$s to enumerate.
+Line \ref{line:t3v4if} takes $O(|V|)$ time and then there are $O(|V|)$ $v_3$ to enumerate.
 Each is checked in $O(1)$ time.
@@
   Given a shortest odd hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C$-major if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
-  \TODO{a picture of this, clean odd hole, amenable hole}
 \end{defn}
@@
 \begin{defn}[amenable odd hole]
-  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest off hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
+  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest odd hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
 \end{defn}
+
+\begin{figure}
+  \begin{minipage}{.5\textwidth}
+      \input{tikzpictures/amenable.tex}
+			\captionof{figure}{Amenable odd hole}
+			\label{fig:amenableOddHole}
+  \end{minipage}%
+  \begin{minipage}{.5\textwidth}
+      \input{tikzpictures/notAmenable.tex}
+			\caption{Not amenable odd hole}
+			\label{fig:notAmenableHole}
+  \end{minipage}
+  \end{figure}
+
+Some pictures might be helpful.
+\Cref{fig:amenableOddHole} shows an example of an amenable odd hole $C = v_1, \ldots, v_7$.
+It is not a clean hole -- vertices $v_8$ and $v_9$ are $C$-major, and $v_8, v_9, v_1, v_2, v_3$ is an axample of a near-cleaner for $C$.
+\Cref{fig:notAmenableHole} shows an odd hole $C = v_1, \ldots, v_7$ that is not amenable, because there is no $\{v_8, v_9\}$-complete edge in $C$.
 
@@
 
-The proof of this theorem is quite technical and we will not discuss it here. See section 8 of \cite{MC05} for the proof.
+The proof of this theorem is quite technical and we will not discuss it here.
+See section 8 of \cite{MC05} for the proof.
+We can see an example of the contraposition of the \Cref{thm:amenableHoles} working in \Cref{fig:notAmenableHole} -- vertices $v_1$, $v_2$, $v_8$, $v_6$, $v_7$ and a path $v_1-v_9-v_5-v_6$ form a jewel.
 

### 2020-09-14 paper/tikzpictures/umbrella.tex
Much pogrress

\centering\begin{tikzpicture}[scale=0.7,simplegraph]
  \node(z) at (6.07,- 6.07) {};
  % \node(zi)[draw=none] at (10.94, -6.07){};
  % \node(zii)[draw=none] at (10.94, -5.07){};
  \node(p1) at (9.23, -3.22) {$c_1$};
  \node(p2) at (11.37, -3.44) {$c_2$};
  \node(p3) at (11.72, -7.29) {$c_3$};
  \node(p4) at (9.91, -9.99) {$c_4$};
  \node(p5) at (8.57, -7.19) {$c_5$};

  \draw[dashed] (p1) to (p2);
  \draw[dashed] (p2) to (p3);
  \draw[dashed] (p3) to (p4);
  \draw[dashed] (p4) to (p5);
  \draw[dashed] (p5) to (p1);

  \draw[-{Triangle[width=7pt,length=6pt]}, line width=2pt] (z) to[edge node={node [draw=none,above] {$u_1$}}] (p1);
  \draw[-{Triangle[width=7pt,length=6pt]}, line width=2pt] (z) to[edge node={node [pos=0.7, draw=none,below] {$u_2$}}] (p2);
  \draw[-{Triangle[width=7pt,length=6pt]}, line width=2pt] (z) to[edge node={node [pos=0.7, draw=none, below right] {$u_3$}}] (p3);
  \draw[-{Triangle[width=7pt,length=6pt]}, line width=2pt] (z) to[edge node={node [draw=none,below] {$u_4$}}] (p4);
  \draw[-{Triangle[width=7pt,length=6pt]}, line width=2pt] (z) to[edge node={node [pos=0.7,draw=none,below] {$u_5$}}] (p5);
  \draw[dotted, line width = 1.5pt] (z) to (10.64, -6.07);
  \draw[dotted, line width = 1.5pt] (10.64, -5.27) to[out=0, in=0, looseness=1.9] (10.64, -6.07);
\end{tikzpicture}%

### 2020-09-14 code/test/generate/generate.cpp

@@ -2,6 +2,7 @@
 #include <map>
 #include <random>
 #include "commons.h"
+#include "jewels.h"
 #include "oddHoles.h"
 #include "perfect.h"
 #include "testCommons.h"
@@ -67,10 +68,24 @@ int main() {
   //   G.printOut();
   // }
 
-  for (int k = 0; k < 10; k++) {
-    for (int i = 9; i <= 24; i += 3) {
-      Graph G = getSplitGraph(i, getDistr());
-      G.printOut();
-    }
-  }
+  // for (int k = 0; k < 10; k++) {
+  //   for (int i = 9; i <= 24; i += 3) {
+  //     Graph G = getSplitGraph(i, getDistr());
+  //     G.printOut();
+  //   }
+  // }
+  Graph G(9,
+          "\
+  .X....X.X\
+  X.X....X.\
+  .X.X.....\
+  ..X.X...X\
+  ...X.X..X\
+  ....X.XX.\
+  X....X.X.\
+  .X...XX..\
+  X..XX....\
+  ");
+
+  cout << findJewelNaive(G);
 }

### 2020-09-14 code/test/plot.py

@@ -98,11 +98,11 @@ algo_markers = {
 }
 
 algo_labels = {
-    "Cuda Perfect": "GPU Perfect",
-    "Perfect": "Perfect",
-    "CUDA Naive": "GPU Naive",
-    "Naive": "Naive",
-    "CSDP Color": "",
+    "Cuda Perfect": "GPU CCLSV",
+    "Perfect": "CCLSV",
+    "CUDA Naive": 'GPU Na"ive',
+    "Naive": "Naïve",
+    "CSDP Color": "Color",
 }
 
 algo_field_labels = {
@@ -117,17 +117,17 @@ algo_field_labels = {
 }
 field_colors = {
     "Perfect": {
-        csv_simpleStructures: "#0f2231",
-        csv_getNearCleaners: "#2c6593",
-        csv_testNCShortestPaths: "#6ca5d3",
-        csv_testNCRest: "#aaaaaa",
+        csv_simpleStructures: "#2a1500",
+        csv_getNearCleaners: "#804000",
+        csv_testNCShortestPaths: "#d46a00",
+        csv_testNCRest: "#ff942a",
     },
     "Cuda Perfect": {
-        csv_simpleStructures: "#1a1a1a",
-        csv_getNearCleaners: "#4d4d4d",
-        csv_testNCShortestPaths: "#808080",
-        csv_gpuCopyR: "#b3b3b3",
-        csv_gpuWork: "#d2d2d2",
+        csv_simpleStructures: "#08131c",
+        csv_getNearCleaners: "#193a54",
+        csv_testNCShortestPaths: "#2a608c",
+        csv_gpuCopyR: "#3b86c4",
+        csv_gpuWork: "#73a9d5",
     },
     "CUDA Naive": {csv_cpuPreparation: "#ff0000", csv_gpuCalculation: "#aa0000"},
     "CSDP Color": {csv_color_res: "#0f2231", csv_color_CSDP: "#6ca5d3"},
@@ -395,8 +395,22 @@ experiments = [
     },
     # COLOR
     #
+    # {
+    #     "restrictions": [(csv_algo, "CSDP")],
+    #     "x_param": csv_N,
+    #     "x_show": csv_N,
+    #     "type": "lines",
+    #     "size": sizes_in_inches["regular_small"],
+    #     "y_param": csv_overall,
+    #     "ylog": True,
+    #     "yformatter": func_formatter,
+    #     "x_label": label_lca_N,
[…]

### 2020-09-15 paper/appendA.tex
Style fixes

@@
 \TODO{some intro}
+We give a brief overview of the square-free perfect graph coloring algorithm and a pseudocode thereof.
+The work is not intended to be self-contained and will be impossible to fully understand without \cite{coloringSquareFree} at hand.
+But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a major step required before an attempt to implement it would be made.
+For some, looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.
+
+What we present would not be trivial to implement.
+For example in many places we say ''choose $x$, so that \dots'', without specifying how to do it.
+A most glaring example is calculating an inverse of a line graph (in \Cref{alg:growingJStrip}) which is a complicated algorithm in and of itself, see \cite{Liu2014} for reference.
 
@@
     \item $K_1 \cup K_2$ and $K_2 \cup K_3$ are cliques,
-    \item in the graph obtained from $G$ by removing all edges between $K_1$ and $K_3$, every chordless path with one end in $K_1$, the other in $K_3$, and interior in $L$ contains a vertex from $L$ that is complete to $K_1$,
+    \item in the graph obtained from $G$ by removing all edges between $K_1$ and $K_3$, every path with one end in $K_1$, the other in $K_3$, and interior in $L$ contains a vertex from $L$ that is complete to $K_1$,
     \item either $K_1$ is anticomplete to $K_3$, or no vertex in $L$ has neighbors in both $K_1$ and $K_3$,
@@
 \end{defnTwo}
-
-\TODO{we need many more definitions, scan pseudocode}
 
@@
 
+A few more structures are used throughout the algorithm. Let us define them.
+
+For definitions \ref{def:majorNeiOfPrism} and \ref{def:localSubOfPrism}, let $K$ be a prism with triangles $\{a_1, a_2, a_3\}$ and $\{b_1, b_2, b_3\}$ and with paths $R_1, R_2, R_3$, where each $R_i$ has ends $a_i$ and $b_1$.
+
+\begin{defnTwo}[major neighbor of a prism]
+  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of pritm $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
+  \label{def:majorNeiOfPrism}
+\end{defnTwo}
+
+\begin{defnTwo}[local subset of a prism]
+  A subset $X \subseteq V(K)$ is \emph{local} if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
+  \label{def:localSubOfPrism}
+\end{defnTwo}
+
+\begin{defnTwo}[attachment]
+  Let $F, K$ be an induced subgraphs of a graph $G$, with $V(F) \cap V(K) = \emptyset$.
+Any vertex $k \in V(K)$ that has a neighbor in $V(F)$ in a graph $G$ is called an \emph{attachment} of $F$ in $K$.
+Whenever any vertex $k \in V(K)$ has an attachment of $F$ we say that $F$ \emph{attaches} to $K$.
+\end{defnTwo}
+
+\begin{defnTwo}[hyperprism]
+  A \emph{hyperprism} is a graph $H$, whose vertices can be partitioned into nine sets:
+  $$
+  \begin{tabular}{c c c}
+    $A_1$ & $C_1$ & $B_1$ \\
+    $A_2$ & $C_2$ & $B_2$ \\
+    $A_3$ & $C_3$ & $B_3$
+  \end{tabular}
+  $$
+  \noindent with the following properties:
+  \begin{itemize}
+    \item each of $A_1, A_2, A_3, B_1, B_2, B_3$ is nonempty,
+    \item for distinct $i, j \in \{1, 2, 3\}$, $A_i$ is complete to $A_j$, and $B_i$ is complete to $B_j$, and there are no other edges between $A_i \cup B_i \cup C_i$ and $A_j \cup B_j \cup C_j$,
+    \item for each $i \in \{1, 2, 3\}$, every vertex of $A_i \cup B_i \cup C_i$ belongs to a path between $A_i$ and $B_i$ with interior in $C_i$.
+  \end{itemize}
+\end{defnTwo}
+
+Whenever we will speak about hyperprisms, we will denote its subsets as in the above definition, unless stated otherwise.
+
+For a hyperprism $H$ we have a few more definitions:
+
+\begin{defnTwo}[$i$-rung of a hyperprism]
+  For each $i \in \{1, 2, 3\}$, any path from $A_i$ to $B_i$ with interior in $C_i$ is called an \emph{$i$-rung}.
+\end{defnTwo}
+
+\begin{defnTwo}[strip of a hyperprism]
+  For each $i \in \{1, 2, 3\}$, the triple $(A_i, C_i, B_i)$ is called a \emph{strip} of the hyperprism.
+\end{defnTwo}
+
+\begin{defnTwo}[instance of a hyperprism]
+  For each $i \in \{1, 2, 3\}$, let us pick any $i$-rung $R_i$. Then $R_1$, $R_2$, $R_3$ form a prism. Any such prism is called an \emph{instance} of a hyperprism.
+\end{defnTwo}
+
+From the definition of an instance of a hyperprism, we can see that any prism is also a hyperprism.
+
+Let us note, that if a hyperprism $H$ contains no odd hole, all rungs have the same parity. We then call the hyperprism odd or even accordingly.
+
+Given a graph $G$ that contains a hyperprism $H$, we can define a few more structures.
+
+\begin{defnTwo}[major neighbor of a hyperprism]
+  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if it is a major neighbor of some instance of $H$.
+\end{defnTwo}
+
+\begin{defnTwo}[local subset of a hyperprism]
+  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
+\end{defnTwo}
+
+\begin{defnTwo}[maximal hyperprism]
+  A hyperprism $H$ is \emph{maximal} if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
+\end{defnTwo}
+
+\Cref{alg:growHyperprism} for growing hyperprism is based upon the following theorem. Recall that by $K_4$ we denote a clique on 4 vertices.
+\begin{theorem}[Lemma 3.3 of \cite{coloringSquareFree}]
+  Let $G$ be a berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$.
+Let $F$ be a component of $V(G) \setminus(V(H) \cup M)$, such that the set of attachments of $F$ in $H$ is not local.
+Then one can find in polynomial time one of the following
+  \begin{itemize}
+    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, such that $V(H) \cup V(P)$ induces a hyperprism,
+    \item a path $P$, with $\emptyset \neq V(P) \subseteq V(F)$, and for each $i \in \{1, 2, 3\}$ an $i$-rung $R_i$ of $H$, such that $V(P) \cup V(R_1) \cup V(R_2) \cup V(R_3)$ induces the line graph of a bipartite subdivision of $K_4$.
+  \end{itemize}
+  \label{thm:growingHyperprism}
+\end{theorem}
+
+If at any time during growing a hyperprism we encounter the latter outcome of the \Cref{thm:growingHyperprism} we stop it and instead focus on the newly found line graph of a bipartite subdivision of $K_4$.
+Algorithms \ref{alg:goodPartitionJStrip}, \ref{alg:goodPartitionSpecialK4}, \ref{alg:findSpecialK4} and \ref{alg:growingJStrip} take their roots in the following theorem.
+
+\begin{theorem}[Theorem 6.1 of \cite{coloringSquareFree}]
+  Let $G$ be a square-free Berge graph, and assume that $G$ contains the line graph of a bipartite subdivision of $K_4$. Then $G$ admits a good partition.
+\end{theorem}
+
+Before providing the pseudocode, we need a few more definitions.
+
+\begin{defnTwo}[branch]
+  Given a graph $G$, a \emph{branch} is a path whose interior vertices have degree 2 and whose ends have degree at leas 3. A \emph{branch-vertex} is any vertex of degree at least 3.
+\end{defnTwo}
+
+\begin{defnTwo}[appearance of a graph]
+  Given a graph $G$, and \emph{appearance} of a graph $J$ is any induced subgraph of $G$ that is isomorphic to the line graph $L(H)$ of a bipartite subdivision $H$ of $J$.
+An appearance of $J$ is \emph{degenerate} if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
+\end{defnTwo}
+
+Note that a degenerate appearance of a graph contains a square.
+
+\begin{defnTwo}[overshadowed appearance]
+  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
+\end{defnTwo}
+
+\begin{defnTwo}[$J$-enlargement]
+  An \emph{enlargement} of a 3-connected graph $J$, or a $J$-enlargement is any 3-connected graph $J'$ such that there is a proper induced subgraph of $J'$ that is isomorphic to a subdivision of $J$.
+\end{defnTwo}
+
+\begin{defnTwo}[$J$-strip system, $uv$-rung]
+  Let $J$ be a 3-connected graph and let $G$ be a perfect graph. A \emph{$J$-strip system} $(S, N)$ in $G$ means
+  \begin{itemize}
+    \item for each edge $uv$ of $J$, a subset $S_{uv} = S_{vu}$ of $V(G)$,
+    \item for each vertex $v$ of $J$, s subset $N_v$ of $V(G)$,
+    \item $N_{uv} = S_{uv} \cap N_u$,
+  \end{itemize}
+  such that if we define a $uv$-rung to be a path $R$ of $G$ with ends $s, t$, where $V(R) \subseteq S_{uv}$, and $s$ is the unique vertex of $R$ in $N_u$, and $t$ is the unique vertex of $R$ in $N_v$, the following conditions are met:
+  \begin{itemize}
+    \item the sets $S_{uv}$, for $uv \in E(J)$ are pairwise disjoint,
+    \item for each $u \in V(J)$, $N_u \subseteq \bigcup_{uv \in E(J)} S_{uv}$,
+    \item for each $uv \in E(J)$, every vertex of $S_{uv}$ is in a $uv$-rung,
+    \item for any two edges $uv, wx$ of $J$, with $u, v, w, x$ all distinct, there are no edges between $S_{uv}$ and $S_{wx}$,
+    \item if $uv, uw \in E(J)$, with $v \neq w$, then $N_{uv}$ is complete to $N_{uw}$ and there are no other edges between $S_{uv}$ and $S_{uw}$,
+    \item for each $uv \in E(J)$, there is a \emph{special} $uv$-rung, such that for every cycle $C$ of $J$, the sum of the lengths of the special $uv$-rungs for $uv \in E(C)$ has the same parity as $|V(C)|$.
+  \end{itemize}
+\end{defnTwo}
+
+\noindent The vertex set of $(S, N)$, denoted by $V(S, N)$ is the set $\bigcup_{uv \in E(J)} S_{uv}$. Note that in general $N_{uv}$ is different from $N_{vu}$. On the other hand $S_{uv} = S_{vu}$.
+
+A $J$-strip system has the following properties:
+\begin{itemize}
+  \item for distinct $u, v \in V(J)$, if $uv \in E(J)$, then $N_u \cap N_v \subseteq S_{uv}$ and if $uv \notin E(J)$ then $N_u \cap N_v = \emptyset$,
+  \item for $uv \in E(J)$ and $w \in V(J)$, if $w \neq u$ then $S_{uv} \cap N_w = \emptyset$,
+  \item for every $uv \in E(J)$, all $uv$-rungs have lengths of the same parity,
+  \item for every cycle $C$ of $J$ and every choice of $uv$-rung for every $uv \in E(C)$, the sums of the lengths of the $uv$-rungs have the same parity as $|V(C)|$.
+In particular, for each edge $uv \in E(J)$, all $uv$-rungs have the same parity.
+\end{itemize}
+
+\begin{defnTwo}[choice of rungs]
+  Given a $J$-strip system, by a \emph{choice of rungs} we mean the choice of one $uv$-rung for each edge $uv$ of $J$.
+\end{defnTwo}
+
+Given a square-free perfect graph $G$ and a $J$-strip system, for every choice of rungs, the subgraph of $G$ induced by their union is the line-graph of a bipartite subdivision of $J$.
+
+\begin{defnTwo}[saturating $J$-strip system]
+  $X \subseteq V(G)$ \emph{saturates} the strip system if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
+\end{defnTwo}
+
+\begin{defnTwo}[major vertex w.r.t. a strip system]
+  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if the set of its neighbors saturates the strip system.
+\end{defnTwo}
+
+\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
+  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
+\end{defnTwo}
+
+\begin{defnTwo}[subset local w.r.t. a strip system]
+  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
+\end{defnTwo}
+
+The outline of the algorithm is as follows.
+Given a square-free perfect graph, first we test if it is an Artemis graph.
+If so, we color it according to \Cref{thm:colorArtemis}.
+If not, \Cref{thm:getPrism} gives us a prism $K$.
+We want to extend $K$ either to a maximal hyperprism or to the line graph of a bipartite subdivision of $K_4$.
+For each of them, we can construct a good partition, which we color recursively.
+
 \section{Notation}
@@
 \begin{itemize}
-	\item $a \gets b$ -- let a be equal b.
-	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$
-	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$
-	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
-	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
-	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
-	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
-	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
-	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
-	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
-	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
-	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
-	\item $[n]$  -- $\{1, \ldots, n\}$.
+	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$,
+	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,
+	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
+	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors,
+	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors,
+	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$,
+	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$,
+	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$,
+	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$,
+	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$,
+	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$,
+	\item $[n]$  -- $\{1, \ldots, n\}$,
 	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.
+\end{itemize}
 
-	\item Strip $S_{uv}$ is \emph{rich} if and only if $S_{uv} \setminus T_{uv} \neq \emptyset$
-\end{itemize}
-\TODO{Introduction on unknown structures - J-strip etc etc}
+Also, throughout the algorithms, we have many lines with asserts. These check some of the properties required before proceeding, and should all be true.
 
+\clearpage
 \section{Algorithms}
 
-\graphAppendix{Color square-free perfect graph}
+\graphAppendix{Color square-free perfect graph}{alg:colorSquareFree}
 \input{coloringAppendix/algI.tex}
@@
 
-\graphAppendix{Color good partition}
-\input{coloringAppendix/algII.tex}
+\graphAppendix{Color good partition}{alg:colorGoodPartition}
+\noindent\input{coloringAppendix/algII.tex}
 \clearpage
 
-\graphAppendix{Grow hyperprism}
-\input{coloringAppendix/algIII.tex}
+\graphAppendix{Grow hyperprism}{alg:growHyperprism}
+\noindent\input{coloringAppendix/algIII.tex}
 \clearpage
 
-\graphAppendix{Good partition from an even hyperprism}
+\graphAppendix{Good partition from an even hyperprism}{alg:goodPartitionEvenH}
 \input{coloringAppendix/algIV.tex}
@@
 
-\graphAppendix{Good partition from an odd hyperprism}
+\graphAppendix{Good partition from an odd hyperprism}{alg:goodPartitionOddH}
 \input{coloringAppendix/algV.tex}
@@
 
-\graphAppendix{Good partition from a $J$-strip system}
+\graphAppendix{Good partition from a $J$-strip system}{alg:goodPartitionJStrip}
 \input{coloringAppendix/algVIa.tex}
@@
 
-\graphAppendix{Good partition from a special $K_4$ strip system}
+\graphAppendix{Good partition from a special $K_4$ strip system}{alg:goodPartitionSpecialK4}
 \input{coloringAppendix/algVIb.tex}
@@
 
-\graphAppendix{Find a special $K_4$ system}
+\graphAppendix{Find a special $K_4$ system}{alg:findSpecialK4}
 \input{coloringAppendix/algVII.tex}
@@
 
-\graphAppendix{Growing a $J$-strip}
-\input{coloringAppendix/algVIII.tex}
+\graphAppendix{Growing a $J$-strip}{alg:growingJStrip}
+\noindent\input{coloringAppendix/algVIII.tex}
 \clearpage
-
-% \graphAppendix{LAST}
-% \input{coloringAppendix/algIXa.tex}
-% \clearpage

### 2020-09-15 paper/implementation.tex
Style fixes

@@
 When we exhaust all possible paths from the current partial solution, we remove last vertex and continue.
-Also notice, that we can abandon ''paths'' that have chords.
 
@@
 Now let's turn our attention to enumerating all paths.
-This is a generalization of the problem of finding an odd hole, if we allow a path to have a single chord between the first and the last of its vertices if and only if the hole formed would be odd.
+This is a generalization of the problem of finding an odd hole, if we allow a path to have a single additional edge between the first and the last of its vertices if and only if the hole formed would be odd.
 
 First of all, there are many methods for generating all possible paths to choose from.
-We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no chords), but this would be too slow and render our algorithm unusable.
+We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no other edges), but this would be too slow and render our algorithm unusable.
 
@@
 In short: we take a path on a input, increment its last vertex until it is a neighbor of the vertex one before last.
-Then we check if generated sequence is a path (all vertices unique and no chords).
+Then we check if generated sequence is a path.
 If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process.
@@
 Because of a good performance of our optimized algorithm for generating paths, we use it whenever possible.
-It can be easily modified to generate all possibly chordal paths or holes and therefore has much use in the CCLSV algorithm.
-For example, when searching for jewels we generate with it all possibly chordal paths of length 5 and for each check if it has required properties of a jewel.
-This proved to be much faster than generating vertices that don't have forbidden chords one by one.
+It can be easily modified to enumerate all ''paths'' that can have additional edges or to enumerate holes and therefore has much use in the CCLSV algorithm.
+For example, when searching for jewels we generate with it all ''paths'' with possible additional edges, of length 5 and for each check if it has required properties of a jewel.
+This proved to be much faster than generating vertices and checking their properties one by one.
 We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$.

### 2020-09-15 paper/main.tex
Calculating \vartheta
experiments wip
Save!
Fixes KT
Plots and appendix
Much pogrress
Style fixes

--- 2020-09-01 paper/main.tex
@@
 \begin{abstract}
-	TODOa
+	Perfect graphs are a subject of intense study since their introduction in 1961.
+Only in 2001 a famous conjecture known as a strong perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found.
+Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated an impractical.
+As recently as in 2018 a polynomial algorithm for coloring perfect graphs without squares was published, that uses a combinatorial approach.
+
+	In Chapter 1 we introduce perfect graphs and Berge graphs, give an overview of the strong perfect graph theorem and talk about an algorithm for polynomial perfect graph recognition.
+Chapter 2 is a study of the ellipsoid method of coloring perfect graphs.
+In Chapter 3 we present our implementation of algorithms from Chapters 1 and 2, along with notes on optimization and parallelisation.
+Appendix A is a overview of the recent algorithm for coloring square-free perfect graphs.
 \end{abstract}
@@
 \listoftheorems[ignoreall,show={defn}]
+\renewcommand{\listtheoremname}{List of algorithms}
+\listoftheorems[ignoreall,show={alg}]
 \tableofcontents
@@
 \input{perfectGraphs.tex}
+
+\chapter{Coloring Perfect Graphs}
 \input{coloringBergeGraphs.tex}
@@
 \input{implementation.tex}
+\input{experiments.tex}
 
@@
 
-\chapter{Perfect Graph Coloring algorithm}
-TODO
+\input{appendA.tex}
 
@@
 
+% \begin{figure}
+% 	\input{tikzpictures/3dtest.tex}
+% 	\caption{3d test}
+% \end{figure}
+
 \end{document}

### 2020-09-15 paper/perfectGraphs.tex
Style fixes

@@
 
-\begin{theorem}[Perfect graph theorem]
+\begin{theorem}[Perfect graph theorem from \cite{LL72}]
 	\label{thm:pgt}
@@
 
-\begin{theorem}[Strong perfect graph theorem]
+\begin{theorem}[Strong perfect graph theorem, Theorem 1.1 of \cite{MC06}]
 	\label{thm:spgt}
@@
 The proof of \cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
-\begin{theorem}[Decomposition theorem]
+\begin{theorem}[Decomposition theorem, stated as Theorem 4.2 of \cite{GC03}]
 	\label{thm:decomposition}
@@
 
-See \cite{MC06} for the proof of \cref{thm:spgt} and \cref{thm:decomposition}.
+See \cite{MC06} for the full proof of \cref{thm:spgt} and \cite{GC03} for its shorter overview.
 
@@
 It is easy to see, that if \textsc{Contains-Pyramid($G$)} outputs that $G$ contains a pyramid, it indeed does -- when we return in line \ref{line:pyramidTrue} the vertex $a$ found in line \ref{line:a} can be linked into a triangle $b_1, b_2, b_3$ via paths $P_1(m_1), P_2(m_2), P_3(m_3)$ for $m_1$, $m_2$, $m_3$ from line \ref{line:m1m2m3}.
-The proof of the converse is rather technical and we refer to \todo{dokładny nr twierdzenia} \cite{MC05} for it.
+The proof of the converse is rather technical and we refer to Theorem 2.2 of \cite{MC05} for it.
 
@@
 
-\begin{theorem}
+\begin{theorem}[part of Theorem 2.2 of \cite{MC05}]
 	Procedure \textsc{Contains-Pyramid($G$)} works in $O(|V|^9)$ time.
@@
 \begin{itemize}
-	\item $v_1v_2v_3v_4$ is a path in $G$.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete vertices.
+	\item $v_1v_2v_3v_4$ is a path in $G$,
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_4\}$-complete vertices,
 	\item $P$ is a path in $G\setminus(X \cup \{v_2, v_3\})$ between $v_1$ and $v_4$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_2$ or adjacent to $v_3$.
@@
 
-\begin{theorem}
+\begin{theorem}[Theorem 6.3 of \cite{MC05}]
 	If $G$ contains configuration of type $\T_2$ then $G$ is not Berge.
@@
 	\begin{itemize}
-		\item If $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
-		\item If $P$ is of length 3.
+		\item if $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
+		\item if $P$ is of length 3.
 \todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$.
 It follows from \cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
-We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole.
-		\item If $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
+We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole,
+		\item if $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
 This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
@@
 \begin{itemize}
-	\item $v_1, \ldots v_6$ are distinct vertices.
-	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges.
-	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete.
-	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$.
+	\item $v_1, \ldots v_6$ are distinct vertices,
+	\item $v_1v_2$, $v_3v_4$, $v_1v_4$, $v_2v_3$, $v_3v_5$, $v_4v_6$ are edges, and $v_1v_3$, $v_2v_4$, $v_1v_5$, $v_2v_5$, $v_1v_6$, $v_2v_6$, $v_4v_5$ are nonedges,
+	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete,
+	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$,
 	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
@@
 
-\begin{theorem}
+\begin{theorem}[part of Theorem 6.4 of \cite{MC05}]
 	\Cref{alg:t3} runs in $O(|V|^6)$ time.
@@
 
-\begin{theorem}
+\begin{theorem}[Theorem 8.1 of \cite{MC05}]
 	\label{thm:amenableHoles}
@@
 
-\begin{theorem}[9.1 of \cite{MC05}]
+\begin{theorem}[Theorem 9.1 of \cite{MC05}]
 	\label{thm:91}
@@
 	\begin{itemize}
-		\item the set of all $C$-major vertices not in $X(a, b, c)$ is anticonnected
+		\item the set of all $C$-major vertices not in $X(a, b, c)$ is anticonnected,
 		\item $X(a, b, c) \cap V(C)$ is a subset of the vertex set of some 3-vertex path of $C$.
@@
 
-\begin{theorem}
+\begin{theorem}[Theorem 9.2 of \cite{MC05}]
 	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
@@
 	\begin{itemize}
-		\item $G$ has an odd hole
+		\item $G$ has an odd hole,
 		\item There is no shortest odd hole $C$ such that $X$ is a near-cleaner for $C$.

### 2020-09-15 paper/coloringBergeGraphs.tex
Style fixes
Small fixes

@@
 published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs \cite{Grtschel1993}.
-We consider it in \cref{sec:coloringEllipsoid}.
+We consider it in \Cref{sec:coloringEllipsoid}.
 However due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
 
-There has been much progress on the quest of finding a more classical algorithm coloring perfect graphs, without the use of ellipsoid method (see \cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
+There has been much progress on the quest of finding a more classical algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
 \todo{better wording of this paragraph}
@@
 
-\Cref{sec:InformationTheory} and \cref{sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.
+\Cref{sec:InformationTheory} and \Cref{sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.
 
@@
 
+Suppose we have a noisy communication channel in which certain signal values can be confused with others.
+For instance, suppose our channel has five discrete signal values, represented as 0, 1, 2, 3, 4.
+However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
+This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if values they represent can be confused.
+
 \begin{wrapfigure}{r}{0.35\textwidth}
@@
 \end{wrapfigure}
-
-Suppose we have a noisy communication channel in which certain signal values can be confused with others.
-For instance, suppose our channel has five discrete signal values, represented as 0, 1, 2, 3, 4.
-However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
-This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if values they represent can be confused.
 
@@
 Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs in finite time.
-If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$.
+If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \Cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$.
 Let us now turn into search for some usable upper bound.
@@
 
+Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.
+Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90$^\circ$.
+This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
+See \Cref{fig:umbrella}.
+We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.
+
 \begin{wrapfigure}{l}{0.4\textwidth}
@@
 \end{wrapfigure}
-
-Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.
-Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90$^\circ$.
-This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
-See \Cref{fig:umbrella}.
-We can calculate $e_1^\intercal u_i = 5 ^ {-1/4}$.
 
@@
   For any graph $G$:
-  $$ \omega(G) \leq \vartheta(\overline{G}) \leq \chi(G) $$
+  $$ \omega(G) \leq \vartheta(\overline{G}) \leq \chi(G).$$
 \end{theorem}
@@
 
-First, let us recall some definitions, with \cite{gilbertstrang2020} as a reference for linear algebra.
+First, let us recall some definitions, with \cite{gilbertstrang2020} as a reference for the linear algebra.
 
@@
 We have equivalent definitions of semidefinite matrices.
-\begin{theorem}
+\begin{theorem}[Proposition 2.2 of \cite{Lovasz95}]
   For a real symmetric $n \times n$ matrix $A$, the following are equivalent:
@@
 \end{theorem}
-\TODO{mark all theorems everywhere accordingly}
 
@@
 
-  The running time of \cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
+  The running time of \Cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
 \end{proof}
@@
 There are at most $|V|$ maximum cardinality cliques in $G$.
-Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \cref{alg:maxStableSet} on it.
+Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \Cref{alg:maxStableSet} on it.
 Therefore total running time is polynomial.
@@
 We will call recursion at most $O(|V|)$ times, each step of recursion is polynomial in time.
-Therefore the running time of \cref{alg:minColoring} is polynomial.
+Therefore the running time of \Cref{alg:minColoring} is polynomial.
 

### 2020-09-15 paper/experiments.tex
Small fixes

@@
 
-An \emph{Erd\H{o}s--Rényi} model is a method of generating random graphs.
+% An \emph{Erd\H{o}s--Rényi} model is a method of generating random graphs.
 Every possible edge is included in a graph with probability $1/2$.
@@
 
-Next, we generate bipartite graphs in similar manner -- each edge between two equal sized node sets has a probability of $1/2$ to appear.
+We generate random bipartite graphs by creating two equal-sized sets of vertices and every possible edge between them has a probability of $1/2$ to appear.
 We also generate line graphs of bipartite graphs.
@@
 
-\pagebreak
 \section{Coloring Berge Graphs}
@@
 Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm.
-With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}.
+With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \Cref{sec:coloringEllipsoid}.
 In most of our tests, the majority of running time was consumed on calculating $\vartheta$ of various graphs.

### 2020-09-15 paper/implementation.tex
Small fixes

@@
 We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.\todo{well..
-there's this java impl} So, to test the usability of CCLSV implementation, we measured it against our own na\"ive Perfect recognition algorithm.
+there's this java impl} So, to test the usability of CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm.
 Let us describe it briefly.
 
-We will try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is Perfect, else that it is not.
+We try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is Perfect, else that it is not.
 
@@
 We will enumerate all paths and holes and for each test if it is an odd hole.
-A partial solution to our problem is a path in $G$.
+A partial solution to our backtracking problem is a path in $G$.
 To move forward from a partial solution, we append consecutively to its end all neighbors of current path's last vertex and continue recursively after each.
@@
 This backtracking algorithm is very simple, but has a great potential for optimizations in implementation.
-We also use path enumeration algorithm in CCLSV algorithm, so we give much attention to its optimization.
+We also use path enumeration algorithm in the CCLSV algorithm, so we give much attention to its optimization.
 
@@
 
-We notice that returning a new path for each call of the method is wasteful.
+We will create a method that enumerates all paths in some order.
+We notice that returning a new path for each call of the enumeration method is wasteful.
 Therefore, we need a method that receives a reference to a path on the input (or a special flag indicating it should generate first path) and returns next path in some order (or a first path, or a code signaling all paths have been generated) using memory from the input.
@@
 
-\paragraph{Other uses for path generation}
+\paragraph{Other uses for path generation.}
 \label{sec:usesGeneration}
@@
 With all those optimizations made, our na\"ive algorithm proved to be quite fast in some cases, although its running time is very dependent on the properties of the input, as we should expect from an optimized non-polynomial algorithm.
-See \cref{sec:experiments} for running times.
+See \Cref{sec:experiments} for running times.
 
@@
 The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case.
-Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\cref{sec:Optimizations}) make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
-Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\cref{sec:CUDA}).
+Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\Cref{sec:Optimizations}) make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
+Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).
 
@@
 Whole algorithm was divided into subroutines used in many places.
-One of such subroutines is a path generation algorithm described above (\cref{sec:usesGeneration}).
+One of such subroutines is a path generation algorithm described above (\Cref{sec:usesGeneration}).
 There are many other generalized methods we implemented: checking if a set of vertices is $X$-complete, getting a set of components of a graph, creating a induced graph or finding a shortest path, such that each internal vertex satisfies a predicate.
@@
 In addition to unit tests, we employ a range of end to end tests, that check the final answer of the algorithm.
-We compare answer to the na\"ive algorithm's answer and also to the result of the algorithm on CUDA (\cref{sec:CUDA}).
+We compare answer to the na\"ive algorithm's answer and also to the result of the algorithm on CUDA (\Cref{sec:CUDA}).
 
@@
 Because of callgrind's slow execution times compared to just running the program, we used manual timers for bigger tests.
-Using this method we identified testing all possible near-cleaners (\cref{alg:testNearCleaner}) as the biggest bottleneck for larger graphs.
-We considered two approaches: run whole \cref{alg:testNearCleaner} on a single CUDA core, testing multiple $X$s in parallel, or parallelize \cref{alg:testNearCleaner} itself and run it on one $X$ at a time.
+Using this method we identified testing all possible near-cleaners (\Cref{alg:testNearCleaner}) as the biggest bottleneck for larger graphs.
+We considered two approaches: run whole \Cref{alg:testNearCleaner} on a single CUDA core, testing multiple $X$s in parallel, or parallelize \Cref{alg:testNearCleaner} itself and run it on one $X$ at a time.
 It turned out that second approach is better and much simpler.
 
-Let us recall the \cref{alg:testNearCleaner}.
+Let us recall the \Cref{alg:testNearCleaner}.
 It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole.

### 2020-09-15 paper/perfectGraphs.tex
Small fixes

@@
 The most fundamental problem -- the problem of recognizing perfect graphs -- was open since its posing in 1961 until recently.
-Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge and an algorithm for recognizing Berge graphs in polynomial time (\cref{sec:recognizingBerge}).
+Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\Cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge and an algorithm for recognizing Berge graphs in polynomial time (\Cref{sec:recognizingBerge}).
 
@@
 Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
-We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \cref{sec:ShannonCapacity}.
+We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \Cref{sec:ShannonCapacity}.
 
@@
 
-Then, since $\alpha(H) = \omega(\overline{H})$ and $\omega(H) = \alpha(\overline{H})$ \cref{thm:omegaalpha} implies \cref{thm:pgt}.
+Then, since $\alpha(H) = \omega(\overline{H})$ and $\omega(H) = \alpha(\overline{H})$ \Cref{thm:omegaalpha} implies \Cref{thm:pgt}.
 
@@
 It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
-A graph with no odd hole and no odd antihole is called \emph{Berge} (\cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
+A graph with no odd hole and no odd antihole is called \emph{Berge} (\Cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
 
@@
 From the theorem of König we get that line graphs of bipartite graphs are also perfect \cite{Knig1916, GC03}.
-From the perfect graph theorem (\cref{thm:pgt}) it follows that complements of bipartite graphs and complement of line graphs of bipartite graphs are also perfect.
+From the perfect graph theorem (\Cref{thm:pgt}) it follows that complements of bipartite graphs and complement of line graphs of bipartite graphs are also perfect.
 We will call these four classes \emph{basic}.
@@
 
-The proof of \cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
+The proof of \Cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
 \begin{theorem}[Decomposition theorem, stated as Theorem 4.2 of \cite{GC03}]
@@
 
-See \cite{MC06} for the full proof of \cref{thm:spgt} and \cite{GC03} for its shorter overview.
+See \cite{MC06} for the full proof of \Cref{thm:spgt} and \cite{GC03} for its shorter overview.
 
@@
 
-The following is based on the paper by Maria \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}.
-We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
+The following is based on the paper by \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
 
-Berge graph recognition algorithm (later called CCLSV from the names of its authors) could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\cref{SimpleStructures}).
+Berge graph recognition algorithm (later called CCLSV from the names of its authors) could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple forbidden structures (\Cref{SimpleStructures}).
 If they do, we output that graph is not Berge and stop.
-Else, we check if there is a near-cleaner for a shortest odd hole (\cref{AmenableHoles}).
+Else, we check if there is a near-cleaner for a shortest odd hole (\Cref{AmenableHoles}).
 
@@
 
-\begin{wrapfigure}{r}{0.35\textwidth}
-	\input{tikzpictures/pyramid.tex}
-	\caption{An example  of a pyramid.}%
-	\vspace{-1.2cm}
-\end{wrapfigure}
+A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
 
-A \emph{pyramid} in G is an induced subgraph formed by the union of a triangle \footnote{A triangle is a clique $K_3$.} $\{b_1,b_2,b_3\}$, three paths $\{P_1, P_2, P_3\}$ and another vertex $a$, so that:
+\begin{minipage}{0.60\textwidth}
 \begin{itemize}
@@
 \end{itemize}
+\end{minipage}%
+% \begin{minipage}
+\begin{wrapfigure}{r}{0.32\textwidth}
+	\vspace{-2.5cm}
+	\input{tikzpictures/pyramid.tex}
+	\caption{An example  of a pyramid.}%
+	\vspace{-1.2cm}
+\end{wrapfigure}
+% \end{minipage}
 
@@
 
-\paragraph{Finding Pyramids}
+\paragraph{Finding Pyramids.}
 
@@
 	\caption{An example of a jewel.}
-	\vspace{-1.5cm}
+	\vspace{-1.8cm}
 \end{wrapfigure}
@@
 To find it, we simply iterate over all paths of length 4 and check if there exists a fifth vertex to complete the hole.
-See \cref{sec:usesGeneration} for more implementation details.
+See \Cref{sec:usesGeneration} for more implementation details.
 
@@
 \todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$.
-It follows from \cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
+It follows from \Cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
 We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole,
-		\item if $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
+		\item if $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \Cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
 This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
@@
 
-	\noindent Output: Returns whether $G$ contains a configuration of type $T_3$ as an induced subgraph.
+	\noindent Output: Returns whether $G$ contains a configuration of type $\T_3$ as an induced subgraph.
 \end{alg}
@@
 
-To prove the correctness of \cref{alg:listNearCleaners} we will need the following theorem.
+To prove the correctness of \Cref{alg:listNearCleaners} we will need the following theorem.
 
@@
 	Let us suppose that $C$ is an amenable hole in $G$.
-By \cref{thm:91}, there is a relevant triple $(a, b, c)$ satisfying that theorem.
+By \Cref{thm:91}, there is a relevant triple $(a, b, c)$ satisfying that theorem.
 Let $T$ be the set of all $C$-major vertices not in $X(a,b,c)$.
-From \cref{thm:91} we get that $T$ is anticonnected.
+From \Cref{thm:91} we get that $T$ is anticonnected.
 Since $C$ is amenable, there is an edge $uv$ of $C$ that is $T$-complete, and therefore $T \subseteq N(u, v)$.
 But then $N(u, v) \cup X(a, b, c) \in \mathcal{R}$ is a near-cleaner for $C$.
-Therefore the output of the \cref{alg:listNearCleaners} is correct.
+Therefore the output of the \Cref{alg:listNearCleaners} is correct.
 \end{proof}
@@
 
-Below we will prove that if the \cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
+Below we will prove that if the \Cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
 The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.
@@
 \begin{proof}
-	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying the three conditions in the \cref{alg:testNearCleaner} and let $y_2$ and $n$ be defined as in there.
+	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying the three conditions in the \Cref{alg:testNearCleaner} and let $y_2$ and $n$ be defined as in there.
 We claim that $G$ contains an odd hole.
@@
 	\par\parshape0
-	\everypar{}\begin{wrapfigure}{r}{0.3\textwidth}
+	\everypar{}\begin{wrapfigure}{r}{0.35\textwidth}
 		\input{tikzpictures/nearCleanerFound.tex}
 		\caption{An odd hole is found}%
-		% \vspace{-0.2cm}
+		\vspace{-0.3cm}
 		\end{wrapfigure}
@@
 
-\begin{wrapfigure}{r}{0.35\textwidth}
+% \subsection{Summary}
 
-\end{wrapfigure}
-
-\subsection{Summary}
-
-\TODO{todo?}
+% \TODO{todo?}

### 2020-09-15 paper/definitions.tex
Progress
Style fixes
Small fixes
Poprawki up to old Ch 1

--- 2020-09-12 paper/definitions.tex
@@
-\TODO{Run proofreader on all text (temporarily disabled because it slowed down IDE)}
-
-We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.
+We begin by recalling the basic notions of graph theory. We use standard definitions, sourced from the book by \citeauthor{BB98} \citetitle*{BB98}, modified and extended as needed.
 
 \begin{defn}[graph]
-  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V \choose 2$ that is of unordered pairs of $V$.
+  A \emph{graph} $G$ is an ordered pair of disjoint sets $(V, E)$ such that $E$ is the subset of the set $V \choose 2$, that is, of unordered pairs of $V$.
 \end{defn}
@@
 
-We will only consider finite graphs, that is $V$ and $E$ are always finite.
+We will only consider finite graphs, that is, $V$ and $E$ are always finite.
 If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}.
@@
 An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$.
-Thus $xy$ and $yx$ mean the same edge (all our graphs are \emph{undirected}).
+Thus $xy$ and $yx$ denote the same edge (all our graphs are \emph{undirected}).
 If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring.
-By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is all vertices $y$ such that $xy$ is an edge.
+By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is, all vertices $y$ such that $xy$ is an edge.
+Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$.
 If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.
 
-\Cref{fig:examplePath} shows an example of a graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$.
+\Cref{fig:examplePath} shows an example graph $G_0 = (V, E)$ with $V = \{v_1, v_2, v_3, v_4\}$ and $E = \{v_1v_2, v_2v_3, v_3v_4\}$.
 We will mark edges as solid lines on figures.
@@
 
+For example, for $X = \{v_2\}$, the set $\{v_1, v_3\}$ is $X$-complete in $G$, while the set $\{v_3, v_4\}$ is not.
+
 \begin{defn}[path]
@@
 $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.
+Notice that we don't allow any edges other than the ones between consecutive vertices for a graph to be called a path.
 
-Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we would add any edge to $G_0$ it would stop being a path.
+Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we  added any edge to $G_0$ it would stop being a path.
 
@@
 
-Notice, that a cycle is not a path (nor is a path a cycle). If we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
+Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
 
@@
 \begin{defn}[complement]
-  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
+  A \emph{complement} of a graph $G = (V, E)$ is a graph $\overline{G} = (V, {V \choose 2} \setminus E)$, that is, two vertices $x, y$ are adjacent in $\overline{G}$ if and only if they are not adjacent in $G$.
 \end{defn}
@@
 \begin{defn}[anticonnected graph, subset]
-  A graph $G$ is anticonnected if $\overline{G}$ is connected.
-  A subset $X$ is anticonnected if $\overline{G}[X]$ is connected.
+  A graph $G$ is \emph{anticonnected} if $\overline{G}$ is connected.
+  A subset $X$ is \emph{anticonnected} if $\overline{G}[X]$ is connected.
 \end{defn}
@@
 \begin{defn}[clique]
-  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
+  A \emph{complete graph} or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is, every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
 \end{defn}
@@
 \begin{defn}[anticlique]
-  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets}. 
+  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets} or \emph{stable sets}. 
 \end{defn}
@@
 
-\TODO{Defs below to ch. 1}
+\begin{defn}[line graph]
+  The \emph{line graph} of a graph $G = (V, E)$ is the graph $L(G)$ with $V(L(G)) = E$ and $E(L(G)) = \{e_1 e_2: e_1, e_2 \in E, e_1 \cap e_2 \neq \emptyset\}$, that is, $e_1, e_2 \in E$ are adjacent if and only if they share an endpoint in $G$.
+\end{defn}

### 2020-09-15 paper/experiments.tex
Poprawki up to old Ch 1

@@
 For every test, the vertex number were shuffled.
+For every randomly generated graph class and for each size, we ran the tests on 10 graphs generated with different seeds and took their average running time.
 
@@
 
-\TODO{split better granulity and detailed}
 Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
@@
 
-\TODO{setting $\epsilon = 1/2$ in csdp helped a lot -- how much?}
-
 Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm.
@@
 One thing of note is, that specifying the precision of $\vartheta$ we want to calculate to be $1/3$ sped up the algorithm by TODO.
+Also, we cache results of calculatin $\vartheta$, meaning that throught whole execution of our coloring algorithm, we only calculate $\vartheta$ for each graph once.
 Our main goal of the implementation was to check if this method is still impractical, even on modern equipment.
@@
 \subsubsection{Experiments and results}
+
+We ran our tests on the data sets generated in the same way as for perfect graph recognition. We only adjusted grah sizes to get the running times of up to a couple of minutes.
+
+First, we present overall running times of the coloring algorithm (\Cref{fig:CSDPLines}) and then breakdown the running time in two parts: calculating $\vartheta$ by the CSDP library and graphs manipulations which constitute the rest of the coloring algorithm (\Cref{fig:CSDPDet}).
+We note that $\vartheta$ calculation is highly dependent on the type of the graph.
+For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in biparite graphs, but only 12 seconds in line graphs of bipartite graphs.
+Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs.
+Hovewer, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs of lattice graphs.
+A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.
+
+We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ by the CSDP library is quite significant.
+Hovewer, the overall running times on these graphs are low, so we didn't particularly optimize this, so probably some improvements could be made if need be.
 
@@
   \caption{Overall times of CSDP Color}
+  \label{fig:CSDPLines}
 \end{figure}
@@
   \caption{Detailed times of coloring}
+  \label{fig:CSDPDet}
 \end{figure}
-
-A few things of note.
-We notice that in rook graphs the graph manipulation other than calculating CSDP takes close to half of overall running time (\cref{plot:colorRookDet}).
-We didn't particularly optimize this, other than by use of methods developed for Berge graph recognition algorithm.
-There are surely some optimizations to be made here if need be.
-Altough, as we can see on other plots, it won't help in majority of the cases.

### 2020-09-15 paper/implementation.tex
Poprawki up to old Ch 1

@@
 First of all, there are many methods for generating all possible paths to choose from.
-We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path (that is if all pairs of vertices next to each other are connected and that there are no other edges), but this would be too slow and render our algorithm unusable.
+We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path, i.e., if all pairs of vertices next to each other are connected and that there are no other edges, but this would be too slow and render our algorithm unusable.
 
@@
 
-This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of 20x\todo{check this}.
+This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of about 5x.
 
@@
 Also, when we look for an odd hole specifically, we can assume that its first vertex we enumerate is the lowest.
-Those two optimizations alone make a huge difference.
+Those two optimizations make a huge difference.
 With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a couple of minutes, to being faster than CCLSV on most of our tests.
@@
 
-For each path candidate $v$ we call a subroutine $areUnique(v)$ to determine whether all vertices in it are unique.
+For each path candidate $v$ we call a subroutine \texttt{areUnique}$(v)$ to determine whether all vertices in it are unique.
 As this subroutine could be called many times for generating a single path, its optimization is very important.
@@
 Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this.
-Second, we notice that we don't need to create this array for each call of $areUnique$ procedure.
-Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called $areUnique$ method.
+Second, we notice that we don't need to create this array for each call of \texttt{areUnique} procedure.
+Let's instead have a static array $stamp$ of ints and a static $counter$ of how many times we called \texttt{areUnique} method.
 For each element of a path $v_i$, if the value of $stamp$ array is equal to $counter$ we report that vertices are not unique.
 Else we set $stamp[v_i] = counter$.
-When returning from the $areUnique$ method we increment $counter$.
+When returning from the \texttt{areUnique} method we increment $counter$.
 
-This optimization almost cuts down na\"ive algorithm's running time in half.
+This optimization alone almost cuts down na\"ive algorithm's running time in half.
 
@@
 
-\todo{rewrite/rearrange text below}
-
 The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case.
-Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level (\Cref{sec:Optimizations}) make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
+Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
 Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).
-
-\TODO{Anything interesting about algo/data structure?}
 
@@
 
-Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners (\Cref{alg:listNearCleaners}).
-At its very end, it returns a set that is an union \todo{after rewriting alg, point to a line}.
-We used a \texttt{dynamic\_bitset} from the boost library \cite{boost} for this purpose.
+% \emergencystretch=10em
+
+Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners \Cref{alg:listNearCleaners}).
+We optimized it by using a a \texttt{dynamic\_bitset} from the boost library \cite{boost}.
 It is a data structure to represent a set of bits, that also allows for fast bitwise operators that one can apply to builtin integers.
-By using it, the speedup of \Cref{alg:listNearCleaners} was about x.
-\todo{todo}
+At the very end of \Cref{alg:listNearCleaners} a set $\mathcal{R}$ is constructed, which is an union of all possible unions of pairs $X_i$ and $N_j$.
+We used \texttt{dynamic\_bitset} to represent each of the sets $X_i$ and $N_j$, and the set $\mathcal{R}$.
+This significantly speeds up the operation of union of two sets (line \ref{line:listNCcalcR}).
+With this modification, the speedup of \Cref{alg:listNearCleaners} was about 20\%.
 
-After these optimizations, checking each potential near-cleaner (\Cref{alg:testNearCleaner}) is by far the biggest bottlenecks of the CCLSV algorithm.
-We didn't find any major optimizations there, but \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.
+After these optimizations, checking each potential near-cleaner by \Cref{alg:testNearCleaner} is by far the biggest bottleneck of the CCLSV algorithm.
+We didn't find any major optimizations there, but the \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.
 
@@
 
-In addition to correctness checking, extensive unit test suite allowed us to optimize our algorithm and test different subroutines with ease, without fear of introducing bugs.
+In addition to correctness checking, extensive unit test suite allowed us to optimize our algorithm and test different subroutines with ease, without the fear of introducing bugs.
 
@@
 Also, we test the algorithm on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof.
-In addition to that, a test on all perfect graphs up to a size of 10\todo{update to 11?} was performed -- we used \cite{graphRepo} as a source of perfect graphs.
+In addition to that, a test on all perfect graphs up to a size of 10 was performed -- we used \cite{graphRepo} as a source of perfect graphs.
 
@@
 
-In total over 100 \todo{update the munber}cpu-hours of end to end tests were performed without any errors.
+In total over 200 cpu-hours of end to end tests were performed without any errors.
 
@@
 CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs.
-It allows to run a program in parallel by many CUDA threads at once.
-Although usually described by PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing RAM algorith on a cpu.
-Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from large latency.
-What is more, there are no standard dynamic structures in PRAM model, let alone CUDA, that are taken for granted in PRAM model, such as hashing maps or sets.
-We used a library called \emph{moderngpu} for our implementation, because it allows a slightly cleaner code.
+It allows to run a program in by many CUDA threads at once.
+Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a cpu.
+Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from a large latency.
+What is more, there are no standard dynamic structures in the PRAM model, let alone CUDA, that are taken for granted in the RAM model, such as hashing maps or sets.
+% We used a library called \emph{moderngpu} for our implementation, because it allows a slightly cleaner code.
 
-\TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}
+% \TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}
 
@@
 It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole.
-We will parallelise the work after calculating $R$.
-Let us notice, that for all $X$s all 3-vertex paths are the same.
-We calculate them beforehand, then each thread receives a 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks.
+We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd} of the \Cref{alg:testNearCleaner}.
+Let us notice, that for all $X$s all 3-vertex paths enumerated in line \ref{line:3vertex} are the same.
+We calculate them beforehand, then each CUDA thread receives one 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks in lines \ref{line:cudaWorkStard}-\ref{line:cudaWorkEnd}.
 This is almost perfect scenario for the GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.
 
-The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall algorithm.
+The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall CCLSV algorithm.

### 2020-09-15 paper/perfectGraphs.tex
Poprawki up to old Ch 1

@@
 The notion of perfect graphs was first introduced by Berge in 1961 \cite{CB61} and it indeed captures some of the idea of graph being ''simple'' -- in all perfect graphs the coloring problem, maximum (weighted) clique problem, and maximum (weighted) independent set problem can be solved in polynomial time \cite{grotschel1993}.
-Other classical NP-complete problems are still NP-complete in perfect graphs e.g.
+Other classical NP-complete problems remain hard in perfect graphs e.g.
 Hamiltonian path \cite{Mller1996}, maximum cut problem \cite{Bodlaender1994} or dominating set problem \cite{Dewdney81}.
-There are many subclasses of perfect graphs, we take a look and benchmark our implementations on some of them in \Cref{sec:experiments}
+There are many well-known subclasses of perfect graphs, we take a look and benchmark our implementations on some of them in \Cref{sec:experiments}
 
 The most fundamental problem -- the problem of recognizing perfect graphs -- was open since its posing in 1961 until recently.
-Its solution, a polynomial algorithm recognizing perfect graphs is a union of the strong perfect graph theorem (\Cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge and an algorithm for recognizing Berge graphs in polynomial time (\Cref{sec:recognizingBerge}).
+Its solution, a polynomial algorithm recognizing perfect graphs, is a union of the strong perfect graph theorem (\Cref{sec:SPGT}) stating that a graph is perfect if and only if it is Berge and an algorithm for recognizing Berge graphs in polynomial time (\Cref{sec:recognizingBerge}).
 
@@
 integrality of polyhedra \cite{Chvtal1975, Chudnovsky2003}, radio channel assignment problem \cite{McDiarmid99, McDiarmid2000} and appear in the theory of Shannon capacity of a graph \cite{Lovasz1979}.
-Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003} algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
+Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003}, algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
 We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \Cref{sec:ShannonCapacity}.
@@
 
-The following is based on the paper by \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.
+The following is based on the paper by \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}. We will not provide full proof of its correctness, but we will aim to show the intuition behind the algorithm.
 
@@
 
-We will say that $a$ can be \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$.
+We will say that $a$ is \emph{linked onto} the triangle $\{b_1, b_2, b_3\}$ \emph{via} the paths $P_1$, $P_2$, $P_3$.
 Let us notice, that a pyramid is uniquely determined by its paths $P_1$, $P_2$, $P_3$.
@@
 
-To prove that existence of $\T_2$ configuration implies that the graph is not Berge, we will need the following Roussel-Rubio lemma:
+To prove that the existence of $\T_2$ configuration implies that the graph is not Berge, we will need the following lemma:
 
@@
 			\lsx and not to $v_2$ and $v_5$}
-				\mIf{$v_4$ has a neighbor in $F$ and a nonneibhbor in $X$ \label{line:t3v4if}}
+				\mIf{$v_4$ has a neighbor in $F$ and a nonneighbor in $X$ \label{line:t3v4if}}
 					\ls $v_6 \gets$ a neighbor of $v_4$ in $F$
@@
 		\mEndFor
-		\ls $Z \gets$ the set of all $Y \cup W$-complete vertices
-		\ls $X(a, b, c) \gets Y \cup Z)$ \Comment{we use $X(a, b, c)$ in the proof of correctness}
+		\ls $Z \gets$ the set of all $(Y \cup W)$-complete vertices
+		\ls $X(a, b, c) \gets Y \cup Z$ \Comment{we use $X(a, b, c)$ in the proof of correctness}
 		\ls $\mathcal{X} \gets \mathcal{X} \cup X(a, b, c)$
@@
 	\ls $\mathcal{R} \gets \emptyset$
-	\mForEach{$X_i \in X$}
-		\mForEach{$N_j \in N$}
-			\ls $\mathcal{R} \gets \mathcal{R} \cup (X_i \cup N_j)$
+	\mForEach{$X_i \in \mathcal{X}$}
+		\mForEach{$N_j \in \mathcal{N}$}
+			\ls $\mathcal{R} \gets \mathcal{R} \cup (X_i \cup N_j)$ \label{line:listNCcalcR}
 		\mEndFor
@@
 			\mEndIf
-			\mForEach{$y_1 \in V(G) \setminus X$}
-				\mForEach{3-vertex path $x_1-x_2-x_3$ of $G\setminus y_1$}
-					\mIf{$R(x_1, y_1), R(x_2, y_2)$ both exist}
+			\mForEach{$y_1 \in V(G) \setminus X$} \label{line:cudaStart}
+				\mForEach{3-vertex path $x_1-x_2-x_3$ of $G\setminus y_1$} \label{line:3vertex}
+					\mIf{$R(x_1, y_1), R(x_2, y_2)$ both exist} \label{line:cudaWorkStard}
 						\ls $y_2 \gets$ the neighbor of $y_1$ in $R(x_2, y_1)$
@@
 						\mEndIf
-					\mEndIf
+					\mEndIf \label{line:cudaWorkEnd}
 				\mEndFor
+			\mEndFor \label{line:cudaEnd}
 		\mEndFor
-		\mEndFor
-		\RETURN no odd hole found
+		\ls \RETURN no odd hole found
 	\mEndProcedure
@@
 		Since $r(x_1, y_1) = r(x_2, y_1) - 1$ and since $x_1$, $x_2$ are nonadjacent it follows that $x_2$ does not belong to $R(x_1, y_1)$ and $x_1$ does not belong to $R(x_2, y_1)$.
-Since $r(x_3, y_1), r(x_3, y_2) \geq n (= r(x_1, y_2))$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
+Since $r(x_3, y_1), r(x_3, y_2) \geq n = r(x_1, y_2)$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
 Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.\par}%
@@
 For suppose that there are $2 \leq i \leq n-1$ and $2 \leq j \leq n$ that $p_i = q_j$.
-Then the subpaths of these two paths between $p_i$, $y_1$ are both subpaths of the shortest paths, and therefore have the same length, that is $j=i+1$.
+Then the subpaths of these two paths between $p_i$, $y_1$ are both subpaths of the shortest paths, and therefore have the same length equal to $j=i+1$.
 So $p_1-\ldots-p_1-q_{j+1}-\ldots-q_n$ contains a path between $x_1$, $y_2$ of length $\leq n-2$, contradicting that $r(x_1, y_2) = n$.
@@
 	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$.
-But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, that is $j \geq i$.
+But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, which gives us $j \geq i$.
 So we get $i=j$.

### 2020-09-16 paper/appendA.tex
many many fixes

@@
 \section{Introduction}
-\TODO{some intro}
 We give a brief overview of the square-free perfect graph coloring algorithm and a pseudocode thereof.
@@
 In 2005 Maffray et al.
-published a paper on Artemis graphs\cite{Maffray2005} they showed an polynomial algorithm that checks if a perfect graph contains a prism, and returns it if so.
+published a paper on Artemis graphs \cite{Maffray2005} they showed an polynomial algorithm that checks if a perfect graph contains a prism, and returns it if so.
 
@@
     \item for any two edges $uv, wx$ of $J$, with $u, v, w, x$ all distinct, there are no edges between $S_{uv}$ and $S_{wx}$,
-    \item if $uv, uw \in E(J)$, with $v \neq w$, then $N_{uv}$ is complete to $N_{uw}$ and there are no other edges between $S_{uv}$ and $S_{uw}$,
+    \item if $uv, uw \in E(J)$ with $v \neq w$, then $N_{uv}$ is complete to $N_{uw}$ and there are no other edges between $S_{uv}$ and $S_{uw}$,
     \item for each $uv \in E(J)$, there is a \emph{special} $uv$-rung, such that for every cycle $C$ of $J$, the sum of the lengths of the special $uv$-rungs for $uv \in E(C)$ has the same parity as $|V(C)|$.
@@
 \begin{itemize}
-  \item for distinct $u, v \in V(J)$, if $uv \in E(J)$, then $N_u \cap N_v \subseteq S_{uv}$ and if $uv \notin E(J)$ then $N_u \cap N_v = \emptyset$,
-  \item for $uv \in E(J)$ and $w \in V(J)$, if $w \neq u$ then $S_{uv} \cap N_w = \emptyset$,
+  \item for distinct $u, v \in V(J)$, if $uv \in E(J)$, then $N_u \cap N_v \subseteq S_{uv}$ and if $uv \notin E(J)$, then $N_u \cap N_v = \emptyset$,
+  \item for $uv \in E(J)$ and $w \in V(J)$, if $w \neq u$, then $S_{uv} \cap N_w = \emptyset$,
   \item for every $uv \in E(J)$, all $uv$-rungs have lengths of the same parity,
@@
 \begin{itemize}
-	\item $a :\in X$, when $X$ is a set -- let a be equal to any element of $X$,
+	\item $a :\in X$, when $X$ is a set -- let $a$ be equal to any element of $X$,
 	\item $a \xor b$, when $a$ and $b$ are logical values -- $a$ xor $b$,

### 2020-09-16 paper/coloringBergeGraphs.tex
Poprawki up to old Ch 1
many many fixes

@@
 The polynomial technique of coloring perfect graphs known so far arose in the field of semidefinite programming.
-Semidefinite programs are linear programs over the cones of semi-definite matrices.
-The connection of coloring graphs and the cones of semi-definite matrices might be surprising, so let us take a brief digression into the field of information theory, where we will see the connection more clearly.
+Semidefinite programs are linear programs over the cones of semidefinite matrices.
+The connection of coloring graphs and the cones of semidefinite matrices might be surprising, so let us take a brief digression into the field of information theory, where we will see the connection more clearly.
 Also, this was exactly the background which motivated Berge to introduce perfect graphs \cite{Chudnovsky2003}.
 
-\subsection{Shannon Capacity of a graph}
+\subsection{Shannon capacity of a graph}
 \label{sec:ShannonCapacity}
@@
 Consider an "umbrella" in $\mathbb{R}^3$ with the unit vector $e_1 = (1, 0, 0)$ as its "handle" and 5 "ribs" of unit length.
-Open it up to the point where non-consecutive ribs are orthogonal, that is form an angle of 90$^\circ$.
+Open it up to the point where non-consecutive ribs are orthogonal, i.e., form an angle of 90$^\circ$.
 This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
@@
 
-\begin{wrapfigure}{l}{0.4\textwidth}
+\begin{wrapfigure}{r}{0.4\textwidth}
   \input{tikzpictures/umbrella.tex}
@@
 
-If $S$ is any stable set in $C_5^k$, then $\{v_i, i \in S\}$ is a set of mutually orthogonal unit vectors so we get \todo{why?}
-$$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq |e_1|^2 = 1$$
-(if $v_i$ formed a basis then this inequality would be an equality).
-
-On the other hand each term on the left hand side is $5^{-1/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
+If $S$ is any stable set in $C_5^k$, then $\{v_i: i \in S\}$ is a set of mutually orthogonal unit vectors, so we could extend $S$ to $S'$, so that $\{v_i: i \in S'\}$ is a basis of $\mathbb{R}^{3k}$.
+This gives us
+$$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq \sum\limits_{i \in S'}(e_1^\intercal v_i)^2 \leq ? = 1$$
+\todo{todo}
+Each term on the left hand side is $5^{-k/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
 Since $|S|$ was an arbitrary stable set, we get $\alpha(C_5^k) \leq 5 ^{k/2}$ and $\Theta(C_5) = \sqrt{5}$.
@@
 It turns out that this method extends to any graph $G$ in place of $C_5$.
-All we have to do is find a orthogonal representation that will give us the best bound.
+All we have to do is to find a orthogonal representation that will give us the best bound.
 So, we can define the \emph{Lovász number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
@@
 
-\noindent where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is a orthogonal representation of $G$.
+\noindent where $c$ is a unit vector in $\mathbb{R}^{|V(G)|}$ and $U$ is an orthogonal representation of $G$.
 
-Contrary to Lovász's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it.
-However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the Lovász "sandwich theorem".
+Contrary to Lovász's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, but it is only an upper bound on it.
+However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the Lovász "Sandwich theorem".
 
-\begin{theorem}[Lovász "sandwich theorem" \cite{Knuth1994}]
+\begin{theorem}[Lovász "Sandwich theorem" \cite{Knuth1994}]
   \label{thm:sandwich}
@@
 
-But how can we construct an optimum (or even good) orthogonal representation? It turns out that it can be computed in polynomial time using semidefinite optimization.
+But how can we construct an optimum (or even sufficiently good) orthogonal representation? It turns out that it can be computed in polynomial time using semidefinite optimization.
 
@@
 An \emph{eigenvector} of $A$ is a vector $x$ such that $Ax$ is parallel to $x$.
-In other words, there is a real or complex number $\lambda$, such that $Ax = \lambda x$.
+In other words, there is a real or a complex number $\lambda$, such that $Ax = \lambda x$.
 This $\lambda$ is called the \emph{eigenvalue} of $A$ belonging to eigenvector $x$.
@@
 
-Solving semidefinite programs is a complex topic, we refer to \cite{grotschel1993} for reference.
+Solving semidefinite programs is a complex topic, we refer to \cite{grotschel1993} for details.
 All we need to know is that we can solve semidefinite programs up to an arbitrarily small error in polynomial time.
@@
 \label{sec:coloringEllipsoid}
-The following is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.
+The following part is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.
 
@@
 
-Given a natural weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ using the following modification:
+Given a weight function $w : V \rightarrow \mathbb{N}$ we could calculate the maximum weighted stable set in $G$ using the following modification:
 
@@
 Note that coloring $C'$ uses $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$.
-We will call recursion at most $O(|V|)$ times, each step of recursion is polynomial in time.
-Therefore the running time of \Cref{alg:minColoring} is polynomial.
+We will call recursion at most $O(|V|)$ times, each step of recursion requires polynomial time.
+Therefore the total running time of \Cref{alg:minColoring} is polynomial.
 
@@
   A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
-Notice, that for a graph to contain no odd hole, all three paths in a prism must have the same parity.
+Notice that for a graph to contain no odd hole, all three paths in a prism must have the same parity.
 A prism with all three paths odd is called an \emph{odd prism}.
@@
 In 2005 Maffray and Trotignon a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
-They later improved the time complexity to $O(|V|^2|E|)$ \cite{Lvque2009}.
+They later improved the time complexity to $O(|V|^2|E|)$ \cite{coloringArtemis}.
 
@@
 
-In 2016 Chudnovsky et al. published an algorithm that given a perfect graph $G$ with $\omega(G) = k$ colors it optimally in a time polynomial for a fixed $k$ \cite{Chudnovsky2017}.
+In 2016 Chudnovsky et al.
+published an algorithm that given a perfect graph $G$ with $\omega(G) = k$ colors it optimally in a time polynomial for a fixed $k$ \cite{Chudnovsky2017}.
+In general case this algorithm has a time complexity of $O(|V|^{(k+1)^2})$.
 
 A most recent advancement (2018) is an algorithm by Chudnovsky et al.
-that colors any square-free Berge graphs in time of $O(|V|^9)$ \cite{Chudnovsky2019}.
+that colors any square-free Berge graphs in time of $O(|V|^9)$ \cite{coloringSquareFree}.
 Before proving strong perfect graph conjecture, a similar conjecture for square-free Berge graphs has been proven by Conforti et al.
@@
 We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.
-The paper in which the algorithm is presented \cite{Chudnovsky2019} is of much more mathematical ''flavor'' then \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward.
-We do it in the Appendix A.
+The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward.
+We provide its pseudocode in the Appendix A.

### 2020-09-16 paper/experiments.tex
many many fixes

@@
 
-We ran tests on nine classes of perfect graphs.
+We ran tests on eight classes of perfect graphs:
 \begin{itemize}
-  \item perfect Erd\H{o}s--Rényi graphs,
-  \item Random bipartite graphs,
-  \item Line graphs of random bipartite graphs,
-  \item Lattice graphs (\cref{fig:lattice}),
-  \item Rook graphs (\cref{fig:rook}),
-  \item Knight graphs (\cref{fig:knight}),
-  \item Hypercube graphs (\cref{fig:hypercube}),
-  \item Split graphs (\cref{fig:split}),
-  \item Full binary trees.
+  % \item perfect Erd\H{o}s--Rényi graphs,
+  \item random bipartite graphs,
+  \item line graphs of random bipartite graphs,
+  \item lattice graphs (\cref{fig:lattice}),
+  \item rook graphs (\cref{fig:rook}),
+  \item knight graphs (\cref{fig:knight}),
+  \item hypercube graphs (\cref{fig:hypercube}),
+  \item split graphs (\cref{fig:split}),
+  \item full binary trees.
 \end{itemize}
+
+\todo{generate perfect Erdos--Renyi graphs}
 
@@
 
-We generate random bipartite graphs by creating two equal-sized sets of vertices and every possible edge between them has a probability of $1/2$ to appear.
-We also generate line graphs of bipartite graphs.
+We generate random bipartite graphs by creating two equal-sized sets of vertices and every possible edge between them has a probability of $p = 0.5$ to appear.
+In this way we can also generate line graphs of bipartite graphs.
 This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
@@
 \Cref{plot:perfDetailed} shows breakdown of each implementation running times on a single graph of each class.
-We can clearly see that in most cases, testing possible near-cleaners takes most of the running time, so the speedup by the GPU is significant.
+We can clearly see that in most cases testing possible near-cleaners takes most of the running time, so the speedup by the GPU is significant.
 
-Examples of full binary graph, and lattice graph show that getting near cleaners still can be a big bottleneck.
+Examples of full binary graphs, and lattice graphs show that getting near cleaners still can be a big bottleneck.
 Parallelization of this method could be considered in the future.
@@
 When running GPU CCLSV on split graphs, quite a lot of time is spent checking simple structures.
-This should be easily parallelizable if need be, or if graphs that require it are encountered.
+This should be parallelizable, the biggest challange we can see is spreading work evenly across CUDA threads.
 
@@
 
-\section{Coloring Berge Graphs}
+\section{Coloring Berge graphs}
 
@@
 We ran our tests on the data sets generated in the same way as for perfect graph recognition. We only adjusted grah sizes to get the running times of up to a couple of minutes.
-
-First, we present overall running times of the coloring algorithm (\Cref{fig:CSDPLines}) and then breakdown the running time in two parts: calculating $\vartheta$ by the CSDP library and graphs manipulations which constitute the rest of the coloring algorithm (\Cref{fig:CSDPDet}).
-We note that $\vartheta$ calculation is highly dependent on the type of the graph.
-For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in biparite graphs, but only 12 seconds in line graphs of bipartite graphs.
-Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs.
-Hovewer, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs of lattice graphs.
-A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.
-
-We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ by the CSDP library is quite significant.
-Hovewer, the overall running times on these graphs are low, so we didn't particularly optimize this, so probably some improvements could be made if need be.
 
@@
 \end{figure}
+
+First, we present overall running times of the coloring algorithm (\Cref{fig:CSDPLines}) and then breakdown the running time in two parts: calculating $\vartheta$ by the CSDP library and graphs manipulations which constitute the rest of the coloring algorithm (\Cref{fig:CSDPDet}).
+We note that $\vartheta$ calculation is highly dependent on the type of the graph.
+For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in biparite graphs, but only 12 seconds in line graphs of bipartite graphs.
+Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs.
+However, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs of lattice graphs.
+A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.
+
+We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ by the CSDP library is quite significant.
+However, the overall running times on these graphs are low, so we didn't particularly optimize this, so probably some improvements could be made here.
+
+\section{Conclusions}
+We implemented and benchmarked two different approaches for recognizing perfect graphs.
+Both have their positives and drawbacks -- CCLSV's running times are more predictable, but on many graphs it is noticeably slower than the na\"ive algorithm.
+On the other hand, running na\"ive algorithm on a graph we don't know any properties of can lead to unbearably slow running time.
+
+The GPU CCLSV implementation shows that using parallel computation can be very profitable for this task.
+A further research can be done to see if further progress could be made, however there is no obvious improvement we can see.
+Generating all possible near-cleaners makes a heavy use of sets (our tests indicated that if we simply list all combinations of sets $X_i$ and $N_j$, the resulting list $\mathcal{R}$ would be much bigger than necessary).
+Possibly a newly developed dynamic dictionary for the GPU \cite{Ashkiani2018} would be of use here.
+Testing for simple forbidden structures should also be parallelizable, although our preliminary tests indicated that spreading all the work evenly between CUDA threads is not trivial.
+
+A GPU implementation of na\"ive algorithm could also be considered for future work.
+We have created one, but after all path-enumaration optimizations of the CPU implementation we didn't manage to achieve any noticeable speedup.
+The reason again was, that we could't spread the work evenly between CUDA threads.
+Because some prefixes of paths require much more processing than others, this is not a trivial task and a careful study would be needed.
+
+We also implemented algorithm for coloring perfect graphs.
+It is not entirely unusable, although far from fast.
+Maybe a better way of calculating $\vartheta$ could be found, or the GPU could be again usable for this task.
+We point to Nvidia's \cite{cusolver} as a possible starting point.

### 2020-09-16 paper/implementation.tex
many many fixes

@@
-A repository containing the discussed source code and tests is available under the link: \href{https://github.com/AdrianSiwiec/Perfect-Graphs}{https://github.com/AdrianSiwiec/Perfect-Graphs}
+A repository containing the discussed source code and tests is available under the link: \href{https://github.com/AdrianSiwiec/Perfect-Graphs}{\texttt{https://github.com/AdrianSiwiec/Perfect-Graphs}}
 \todo{make repo public and add readme on howto run, some script creating and running default tests}
@@
 
-First of all, there are many methods for generating all possible paths to choose from.
+First of all, there are many methods for generating all possible paths.
 We could simply enumerate all sequences of vertices without repetition and for each one of them check if it is a path, i.e., if all pairs of vertices next to each other are connected and that there are no other edges, but this would be too slow and render our algorithm unusable.
@@
 
-But we can do much better with some care and a better data structure.
-For a given graph we create a data structure that suits best the goal of generating paths.
+But we can do much better with some care and a suitable data structure.
 In addition to having for each vertex a list of its neighbors we create data structure that will allow us to generate a candidate for next path in amortized $O(1)$ time.
@@
 Else we set $stamp[v_i] = counter$.
-When returning from the \texttt{areUnique} method we increment $counter$.
+When returning from \texttt{areUnique} method we increment $counter$.
 
@@
 Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
-Also, we explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).
+We also explore a new frontier of implementing its most time consuming part on massively parallel GPU architecture, with some good results (\Cref{sec:CUDA}).
 
@@
 
-Callgrind is a profiling tool that records the call history of a program and presents it as a call-graph.
-When profiling a program, event counts (data reads, cache misses etc.) are attributed directly to the function that they occurred in.
-In addition to that, the costs are propagated to functions upwards the call stack.
-For example, say internal function $worker$ consumes most of programs running time.
-It is called from $run1$ and $run2$, with $run2$ calls taking twice as much time.
-$run1$ and $run2$ are in turn called from main.
-Total attribution of $worker$ would be nearly 100\%, of $run1$ about 33\% and of $run2$ about 66\%.
-The contribution of main would also be near 100\%.
-We used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
+% \TODO{Caly ponizszy akapit wymaga przeformulowania/skrocenia, nie trzeba wyjasniac detali dzialania callgrinda - tylko napisac ze zlicza event county wg funkcji + ze mozna to wizualizowac}
+
+Callgrind is a profiling tool that records the call history and event counts ((data reads, cache misses etc.) of a program and presents it as a call-graph.
+It is then possible to visualise this, we used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
 
@@
 
-\subsection{Correctness Testing}
+\subsection{Correctness testing}
 
@@
 
-In total over 200 cpu-hours of end to end tests were performed without any errors.
+In total over 200 CPU-hours of end to end tests were performed without any errors.
 
@@
 It allows to run a program in by many CUDA threads at once.
-Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a cpu.
+Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a CPU.
 Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from a large latency.
@@
 On one hand the graphs we are working on are small and our time complexity so large that a speedup from massively parallel architecture could be profitable.
-On the other the algorithm is complex and not easy to parallelise.
+On the other hand, the algorithm is complex and not easy to parallelise.
 Therefore we decided to analyze the  CCLSV algorithm and parrallelize parts that would benefit from it the most.
@@
 
-To identify parts of CCLSV to implement, we used callgrind and found potential bottlenecks.
-The initial tests showed that with growing size of a graph some parts take more and more relative time.
-Because of callgrind's slow execution times compared to just running the program, we used manual timers for bigger tests.
-Using this method we identified testing all possible near-cleaners (\Cref{alg:testNearCleaner}) as the biggest bottleneck for larger graphs.
+% \TODO{nizgrabnie, przepisać ponizszy}
+
+We identified testing all possible near-cleaners (\Cref{alg:testNearCleaner}) as the biggest bottleneck for larger graphs.
 We considered two approaches: run whole \Cref{alg:testNearCleaner} on a single CUDA core, testing multiple $X$s in parallel, or parallelize \Cref{alg:testNearCleaner} itself and run it on one $X$ at a time.
@@
 It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole.
-We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd} of the \Cref{alg:testNearCleaner}.
+We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd}.
 Let us notice, that for all $X$s all 3-vertex paths enumerated in line \ref{line:3vertex} are the same.
@@
 
-The part of the CCLSV implemented on the gpu achieved speedup of up to 15x. Which gives us a speedup of up to 9x for overall CCLSV algorithm.
+The part of the CCLSV implemented on the GPU achieved speedup of up to 15x. Which gave us a speedup of up to 9x for overall CCLSV algorithm.

### 2020-09-16 paper/perfectGraphs.tex
many many fixes

@@
 integrality of polyhedra \cite{Chvtal1975, Chudnovsky2003}, radio channel assignment problem \cite{McDiarmid99, McDiarmid2000} and appear in the theory of Shannon capacity of a graph \cite{Lovasz1979}.
-Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003}, algorithms to solve semi-definite programs grew out of the theory of perfect graphs.
-We will take a look at semi-definite programs and at perfect graph's relation to Shannon capacity in \Cref{sec:ShannonCapacity}.
+Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003}, algorithms to solve semidefinite programs grew out of the theory of perfect graphs.
+We will take a look at semidefinite programs and at perfect graph's relation to Shannon capacity in \Cref{sec:ShannonCapacity}.
 
-\section{Strong Perfect Graph Theorem}
+\section{Strong perfect graph theorem}
 \label{sec:SPGT}
@@
 \end{theorem}
-\todo{proof? min. 1 page}
 % \begin{proof}
@@
 
-\section{Recognizing Berge Graphs}
+\section{Recognizing berge graphs}
 \label{sec:recognizingBerge}
@@
 \begin{theorem}[part of Theorem 2.2 of \cite{MC05}]
+	\label{thm:containsPyramid9}
 	Procedure \textsc{Contains-Pyramid($G$)} works in $O(|V|^9)$ time.
@@
 		\item if $P$ is even, then $v_1, v_2, v_3, v_4, P, v_1$ is an odd hole,
-		\item if $P$ is of length 3.
-\todo{I merged a couple of proofs from \cite{MC06}, check in the morning if this is correct.} Let us name its vertices $v_1, p_2, p_3, v_4$.
+		\item if $P$ is of length 3, let us name its vertices $v_1, p_2, p_3, v_4$.
 It follows from \Cref{lem:Roussel-Rubio}, that there exists an odd antipath between $p_2$ and $p_3$ with interior in $X$.
 We can complete it with $v_2p_2$ and $v_2p_3$ into an odd antihole,
-		\item if $P$ is odd with the length of at least 5 \todo{check in the morning}, it follows from \Cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
-This gives us an odd hole: $v_2, x, p_2, \ldots, p_{n-1}, y, v_2$.
+		\item if $P$ is odd with the length of at least 5, it follows from \Cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
+This gives us an odd hole: $v_2-x-p_2-\ldots-p_{n-1}-y-v_2$.
 	\end{itemize}
@@
 \begin{theorem}[part of Theorem 6.4 of \cite{MC05}]
+	\label{thm:t3Time}
 	\Cref{alg:t3} runs in $O(|V|^6)$ time.
@@
 
-Let us notice, that if $X$ is a cleaner for $C$ then $C$ is a clean hole in $G \setminus X$.
+Let us notice, that if $X$ is a cleaner for $C$, then $C$ is a clean hole in $G \setminus X$.
 
@@
 	\label{thm:amenableHoles}
-	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest odd hole in $G$ is amenable.
 	% \TODO{Any ideas on what else to say here? List all 9 steps?}
@@
 \begin{theorem}[Theorem 9.2 of \cite{MC05}]
+	\label{thm:92}
 	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
@@
 Below we will prove that if the \Cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
-The proof of the correctness of the other possible result is more complicated, see section 4 and theorem 5.1 of \cite{MC05}.
+The proof of the correctness of the other possible result is more complicated, see section 4 and Theorem 5.1 of \cite{MC05}.
 
 \begin{theorem}[Theorem 5.1 of \cite{MC05}]
+	\label{thm:testNCWorks}
 	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
 Let $X$ be a subset of $V(G)$.
-If \Cref{alg:testNearCleaner} reports an odd hole, then $G$ contains an odd hole.
+If \Cref{alg:testNearCleaner} reports an odd hole, then $G$ contains an odd hole, else there is no shortest odd hole $C$ in $G$, such that $X$ is a near-cleaner for $C$.
 \end{theorem}
 \begin{proof}
+	Below we will prove that if the \Cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one. The rest of the proof is more complicated, see section 4 and Theorem 5.1 of \cite{MC05}.
+
 	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying the three conditions in the \Cref{alg:testNearCleaner} and let $y_2$ and $n$ be defined as in there.
@@
 
-% \subsection{Summary}
+\subsection{Algorithm for Berge graphs recognition}
 
-% \TODO{todo?}
+To summarize, we present a complete algorithm for recognizing Berge graphs.
+\begin{alg}[Determine if a graph is Berge]
+	\label{alg:testNearCleaner}
+	Input: A graph $G$.
+
+	\noindent Output: Determines if $G$ is Berge.
+	\label{alg:bergeness}
+\end{alg}
+
+\begin{algorithmic}[1]
+	\mProcedure{Check-Berge}{$G$}
+		\mIf{\texttt{Contains-Pyramid}$(G)$ \OR \texttt{Contains-Jewel}$(G)$ \OR \lsx 
+		\texttt{Contains-T1}$(G)$ \OR \texttt{Contains-T2}$(G)$ \OR \texttt{Contains-T3}$(G)$ \label{line:simpleStart}}
+			\ls \RETURN $G$ is not Berge
+		\mEndIf
+		\mIf{\texttt{Contains-Pyramid}$(\overline{G})$ \OR \texttt{Contains-Jewel}$(\overline{G})$ \OR \lsx 
+		\texttt{Contains-T1}$(\overline{G})$ \OR \texttt{Contains-T2}$(\overline{G})$ \OR \texttt{Contains-T3}$(\overline{G})$}
+			\ls \RETURN $G$ is not Berge
+		\mEndIf \label{line:simpleEnd}
+		\ls $\mathcal{R} \gets $\texttt{List-Possible-Near-Cleaners}$(G)$ \label{line:getR}
+		\mForEach{$X \in \mathcal{R}$} \label{line:testXStart}
+			\mIf{\texttt{Test-Near-Cleaner}$(G, X)$ reports an odd hole}
+				\ls \RETURN $G$ is not Berge
+			\mEndIf
+		\mEndFor \label{line:testXEnd}
+		\ls $\mathcal{R'} \gets $\texttt{List-Possible-Near-Cleaners}$(\overline{G})$
+		\mForEach{$X \in \mathcal{R'}$}
+			\mIf{\texttt{Test-Near-Cleaner}$(\overline{G}, X)$ reports an odd hole}
+				\ls \RETURN $G$ is not Berge
+			\mEndIf
+		\mEndFor
+		\ls \RETURN $G$ is Berge
+	\mEndProcedure
+\end{algorithmic}
+
+\begin{theorem}[Theorem 10.1 of \cite{MC05}]
+	Given a graph $G = (V, E)$, \Cref{alg:bergeness} works in $O(|V|^9)$ time and determines is $G$ is Berge.
+\end{theorem}
+\begin{proof}
+	First, in lines \ref{line:simpleStart}-\ref{line:simpleEnd} we test whether $G$ or $\overline{G}$ contain a pyramid, a jewel or a configuration of type $\T_1, \T_2$ or $\T_3$.
+If it is not the case, then by \Cref{thm:amenableHoles} every shortest odd hole in $G$ and in $\overline{G}$ is amenable.
+
+	By \Cref{thm:92} in line \ref{line:getR} we get a set $\mathcal{R}$, such that if $G$ contains an amenable hole $C$, one of the sets $X \in \mathcal{R}$ is a near-cleaner for $C$.
+In lines \ref{line:testXStart}-\ref{line:testXEnd} we test each $X \in \mathcal{R}$ and if an odd hole is reported, then by \Cref{thm:testNCWorks} $G$ is not Berge.
+If for all $X \in \mathcal{R}$ an odd hole is not reported, then by \Cref{thm:amenableHoles}, \Cref{thm:92} and \Cref{thm:testNCWorks} there is no odd hole in $G$.
+We  run the same procedure on $\overline{G}$ and if again we do not detect an odd hole, then $G$ is Berge and by \Cref{thm:spgt} $G$ is perfect.
+
+	Finally, let us add up the total running time.
+By \Cref{thm:containsPyramid9} checking if there is a pyramid in $G$ or $\overline{G}$ takes $O(|V|^9)$ time.
+Testing for jewels takes $O(|V|^7)$ time, testing for a configuration of type $\T_1$ takes $O(|V|^5)$ time and testing for configuration of type $\T_2$ takes $O(|V|^6)$ time.
+By \Cref{thm:t3Time} testing for a configuration of type $\T_3$ takes $O(|V|^6)$ time.
+Running \Cref{alg:listNearCleaners} takes $O(|V|^5)$ time and returns $O(|V|^5)$ subsets.
+For each subset running \Cref{alg:testNearCleaner} takes $O(|V|^4)$ time, so testing all possible near-cleaners takes $O(|V|^9)$ time.
+Then we repeat on the $\overline{G}$.
+
+	The overall running time is $O(|V|^9)$ with testing for pyramids and testing all possible near-cleaners being algorithms with biggest time complexity.
+\end{proof}

### 2020-09-16 code/test/plot.py

@@ -109,7 +109,7 @@ algo_field_labels = {
     csv_simpleStructures: "Simple structures",
     csv_testNCRest: "CPU test",
     csv_getNearCleaners: "Get near cleaners",
-    csv_testNCShortestPaths: "Calculare $R$",
+    csv_testNCShortestPaths: "Calculate $R$",
     csv_gpuCopyR: "Copy $R$",
     csv_gpuWork: "GPU test",
     csv_color_res: "Graph manipulation",

### 2020-09-16 paper/appendA.tex
Fixes

@@
 \begin{defnTwo}[Artemis graph]
-  A graph $G$ is an \emph{Artemis graph} if it contains no odd hole, no antihole of length at least five, and no prism.
+  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd hole, no antihole of length at least five, and no prism.
 \end{defnTwo}
@@
 \begin{defnTwo}[local subset of a prism]
-  A subset $X \subseteq V(K)$ is \emph{local} if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
+  A subset $X \subseteq V(K)$ is \emph{local} if and only if either $X \subseteq \{a_1, a_2, a_3\}$, or $X \subseteq \{b_1, b_2, b_3\}$, or $X \subseteq R_i$ for some $i \in \{1, 2, 3\}$.
   \label{def:localSubOfPrism}
@@
 \begin{defnTwo}[major neighbor of a hyperprism]
-  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if it is a major neighbor of some instance of $H$.
+  A vertex $v \in V(G) \setminus V(H)$ is a \emph{major neighbor} of $H$, if and only if it is a major neighbor of some instance of $H$.
 \end{defnTwo}
@@
 \begin{defnTwo}[local subset of a hyperprism]
-  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
+  A subset $X \subseteq V(H)$ is a local subset of a hyperprism $H$ if and only if either $X \subseteq A_i \cup A_2 \cup A_3$ or $X \subseteq B_1 \cup B_2 \cup B_3$ or $X \subseteq A_i \cup B_i \cup C_i$ for some $i \in \{1, 2, 3\}$.
 \end{defnTwo}
@@
 \begin{defnTwo}[maximal hyperprism]
-  A hyperprism $H$ is \emph{maximal} if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
+  A hyperprism $H$ is \emph{maximal} if and only if there is no hyperprism $H'$ in $G$, such that $V(H) \varsubsetneq V(H')$.
 \end{defnTwo}
@@
   Given a graph $G$, and \emph{appearance} of a graph $J$ is any induced subgraph of $G$ that is isomorphic to the line graph $L(H)$ of a bipartite subdivision $H$ of $J$.
-An appearance of $J$ is \emph{degenerate} if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
+An appearance of $J$ is \emph{degenerate} if and only if either $J = H = K_{3, 3}$\footnote{$K_{n, m}$ is a complete bipartite graph with $n$ vertices on the one side and $m$ vertices on the other}, or $J = K_4$ and the four vertices of $J$ form a square in $H$.
 \end{defnTwo}
@@
 \begin{defnTwo}[overshadowed appearance]
-  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
+  An appearance of $L(H)$ of $J$ in $G$ is \emph{overshadowed} if and only if there is a branch $B$ of $H$, of length at least 3, with ends $b_1, b_2$, such that some vertex of $G$ is non-adjacent in $G$ to at most one vertex in $\{b_1x \in V(L(H))$, for $x \in V(H), b_1x \in E(H)\}$ and at most one vertex in $\{b_2x \in V(L(H))$, for $x \in V(H), b_2x \in E(H)\}$.
 \end{defnTwo}
@@
 \begin{defnTwo}[saturating $J$-strip system]
-  $X \subseteq V(G)$ \emph{saturates} the strip system if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
+  $X \subseteq V(G)$ \emph{saturates} the strip system if and only if for every $u \in V(J)$ there is at most one neighbor $v$ of $u$ such that $N_{uv} \nsubseteq X$.
 \end{defnTwo}
@@
 \begin{defnTwo}[major vertex w.r.t. a strip system]
-  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if the set of its neighbors saturates the strip system.
+  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if and only if the set of its neighbors saturates the strip system.
 \end{defnTwo}
@@
 \begin{defnTwo}[major vertex w.r.t. some choice of rungs]
-  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
+  A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if and only if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
 \end{defnTwo}
@@
 \begin{defnTwo}[subset local w.r.t. a strip system]
-  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
+  A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if and only if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
 \end{defnTwo}
@@
 	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious,
-	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors,
-	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors,
-	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$,
-	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$,
-	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$,
-	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$,
-	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$,
-	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$,
+	\item $a - b$, when $a$ and $b$ are vertices -- $a$ and $b$ are neighbors,
+	\item $a \cdots b$, when $a$ and $b$ are vertices -- $a$ and $b$ are not neighbors,
+	\item $a - X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a neighbor in $X$,
+	\item $a \cdots X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ has a nonneighbor in $X$,
+	\item $a \blacktriangleleft  X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is complete to $X$,
+	\item $a \ntriangleleft X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is anticomplete to $X$,
+	\item $X \setComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is complete to $Y$,
+	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is anticomplete to $Y$,
 	\item $[n]$  -- $\{1, \ldots, n\}$,
-	\item \LGBSK -- the line-graph of a biparite subdivision of $K_4$.
+	\item \LGBSK -- the line-graph of a bipartite subdivision of $K_4$.
 \end{itemize}

### 2020-09-16 paper/coloringBergeGraphs.tex
Fixes

@@
 We consider it in \Cref{sec:coloringEllipsoid}.
-However due to its use of the ellipsoid method this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
+However due to its use of the ellipsoid method, this algorithm has been usually considered unpractical \cite{coloringSquareFree,Chudnovsky2003, coloringArtemis}.
 
-There has been much progress on the quest of finding a more classical algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
-\todo{better wording of this paragraph}
+There has been much progress on the quest of finding an algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
 
@@
 
-For a channel defined by a graph $C_5$, using five messages of length 2 to communicate gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\alpha(C_5^2)$).
+For a channel defined by a graph $C_5$, using five messages of length 2 to communicate gives us a lower bound on $\Theta(G)$ equal $\sqrt{5}$ (as does calculating $\sqrt{\alpha(C_5^2)}$).
 
@@
 Open it up to the point where non-consecutive ribs are orthogonal, i.e., form an angle of 90$^\circ$.
-This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent nodes are represented with orthogonal vectors.
+This way we get a representation of $C_5$ by 5 unit vectors $u_1, \ldots, u_5$ so that each $u_i$ forms the same angle with $e_1$ and any two non-adjacent vertices are represented with orthogonal vectors.
 See \Cref{fig:umbrella}.
@@
 
-It turns out, that we can obtain a similar representation of the nodes of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^{3k}$, so that any two non-adjacent nodes are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}).
+It turns out, that we can obtain a similar representation of the vertices of $C_5^k$ by unit vectors $v_i \in \mathbb{R}^{3k}$, so that any two non-adjacent vertices are labeled with orthogonal vectors (this representation is sometimes called the \emph{orthogonal representation} \cite{Lovsz1989Orthogonal}).
 Moreover, we still get $e_1^\intercal v_i = 5^{-k/4}$ for every $i \in V(C_5^k)$ (the proof is quite technical and we omit it here).
@@
 All we have to do is to find a orthogonal representation that will give us the best bound.
-So, we can define the \emph{Lovász number} of a graph $G$ as \todo{this equation does not really follow from the thought process above, it is a slightly different definition}:
+So, we can define the \emph{Lovász number} of a graph $G$ as:
 $$\vartheta(G) = \min\limits_{c,U} \max\limits_{i\in V} \frac{1}{(c^\intercal u_i)^2},$$
@@
 \begin{defn}[convex cone]
-  A subset $C$ of $\mathbb{R}^n$ is a \emph{convex cone}, if for any positive scalars $\alpha, \beta$ and for any $x, y \in C$, $\alpha x + \beta y \in C$.
+  A subset $C$ of $\mathbb{R}^n$ is a \emph{convex cone}, if and only if for any positive scalars $\alpha, \beta$ and for any $x, y \in C$, $\alpha x + \beta y \in C$.
 \end{defn}
@@
 
-Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all nonedges $ij$.
+Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all anticonnected vertices $i, j$.
 An \emph{orthonormal} representation is an orthogonal representation with $|u_i| = 1$ for all $i$.
@@
   \mProcedure{Get-Max-Stable-Set}{$G$}
-  \ls $v_1, \ldots, v_n \gets$ an ordering of $V(G)$
+  \ls $v_1, \ldots, v_n \gets$ vertices of $G$
   \ls $G_0 \leftarrow G$
@@
 
-  The running time of \Cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once plus additional $O(|V|^2)$ time for constructing the graph.
+  The running time of \Cref{alg:maxStableSet} is polynomial, because we construct $|V|$ auxiliary graphs, each requiring calculating $\alpha$ once with additional $O(|V|^2)$ time for constructing the graph.
 \end{proof}
@@
 
-We create graph $G'$ by replacing every node $v$ by a set $W_v$ of $w(v)$ nonadjacent nodes, making two nodes $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the nodes $v$, $u$ are adjacent in $G$.
+We create graph $G'$ by replacing every vertex $v$ by a set $W_v$ of $w(v)$ nonadjacent vertices, making two vertices $x \in W_v$, $y \in W_u$ adjacent in $G'$ if and only if the vertices $v$, $u$ are adjacent in $G$.
 Then we can calculate a maximum cardinality stable set in $G'$ (we remark that $G'$ is still perfect because every new introduced hole is even) and return a result of those vertices in $G$ whose any (and therefore all) copies were chosen.
@@
 
-In 2005 Maffray and Trotignon a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
+In 2005 Maffray and Trotignon showed a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
 They later improved the time complexity to $O(|V|^2|E|)$ \cite{coloringArtemis}.
@@
 The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement.
-The main idea is that, if square-free Berge graph $G$ is a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism.
+The main idea is that, if square-free Berge graph $G$ is not a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism.
 We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.

### 2020-09-16 paper/definitions.tex
Fixes

@@
 
-An edge $\{x, y\}$ is said to \emph{join}, or be between vertices $x$ and $y$ and is denoted by $xy$.
+An edge $\{x, y\}$ is said to \emph{join}, or \emph{be between} vertices $x$ and $y$ and is denoted by $xy$.
 Thus $xy$ and $yx$ denote the same edge (all our graphs are \emph{undirected}).
-If $xy \in E(G)$ then $x$ and $y$ are adjacent, connected or neighboring.
+If $xy \in E(G)$ then $x$ and $y$ are \emph{adjacent}, \emph{connected} or \emph{neighboring}.
 By $N(x)$ we will denote the \emph{neighborhood} of $x$, that is, all vertices $y$ such that $xy$ is an edge.
-Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the neighborhood of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$.
+Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the \emph{neighborhood} of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$.
 If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.
@@
 \begin{defn}[subgraph]
-  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if $V' \subseteq V$ and $E' \subseteq E$.
+  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if and only if $V' \subseteq V$ and $E' \subseteq E$.
 \end{defn}
@@
 \begin{defn}[$X$-completeness]
-  Given set $X \subseteq V$, vertex $v \notin X$ is \emph{$X$-complete} if it is adjacent to every node $x \in X$.
-A set $Y \subseteq V$ is $X$-complete if $X \cap Y = \emptyset$ and every node $y \in Y$ is $X$-complete.
+  Given a graph $G = (V, E)$ and a set $X \subseteq V$, vertex $v \in V(G) \setminus X$ is \emph{$X$-complete} if and only if it is adjacent to every vertex $x \in X$.
+A set $Y \subseteq V$ is $X$-complete if and only if $X \cap Y = \emptyset$ and every vertex $y \in Y$ is $X$-complete.
 \end{defn}
@@
 \end{defn}
-This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$.
+This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1$-$x_2$-$\ldots$-$x_l$.
 The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P.
@@
 \begin{defn}[connected graph, subset]
-  A graph $G$ is \emph{connected} if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$.
-  A subset $X \subseteq V(G)$ is connected if the graph $G[X]$ is connected.
+  A graph $G$ is \emph{connected} if and only if for every pair $\{x, y\} \subseteq V(G)$ of distinct vertices, there is a path from $x$ to $y$.
+  A subset $X \subseteq V(G)$ is connected if and only if the graph $G[X]$ is connected.
 \end{defn}
@@
 
-Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
-
 \begin{defn}[hole]
@@
 
-If a path, a cycle or a hole has an odd length, it will be called \emph{odd}. Otherwise, it will be called \emph{even}.
-
+If a path, a cycle or a hole has an odd length, it will be called \emph{odd}.
+Otherwise, it will be called \emph{even}.
+Notice that if we add an edge $v_1v_4$ to the path $G_0$ it becomes an even cycle $C_4$.
 \begin{defn}[complement]
@@
 \begin{defn}[anticonnected graph, subset]
-  A graph $G$ is \emph{anticonnected} if $\overline{G}$ is connected.
-  A subset $X$ is \emph{anticonnected} if $\overline{G}[X]$ is connected.
+  A graph $G$ is \emph{anticonnected} if and only if $\overline{G}$ is connected.
+  A subset $X$ is \emph{anticonnected} if and only if $\overline{G}[X]$ is connected.
 \end{defn}
@@
 \begin{defn}[anticlique]
-  An \emph{anticlique} is a graph in which there are no edges. We will also call anticliques \emph{independent sets} or \emph{stable sets}. 
+  An \emph{independent set} or an \emph{anticlique} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
 \end{defn}
@@
 \begin{defn}[coloring]
-  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that $c(x) \neq c(y)$ for every edge $xy \in E(G)$.
+  Given a graph $G$, its \emph{coloring} is a function $c: V(G) \rightarrow \mathbb{N}^+$, such that for every edge $xy \in E(G)$, $c(x) \neq c(y)$ .
 A $k$-coloring of $G$ (if exists) is a coloring, such that $c(x) \leq k$ for all vertices $x \in V(G)$.

### 2020-09-16 paper/experiments.tex
Fixes

@@
 All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one.
-Therefore, their running times are greatest with perfect graphs on the input and we decided to use mainly\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.
+Therefore, their running times are greatest with perfect graphs on the input and we decided to use\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.
 For every test, the vertex number were shuffled.
@@
 
-We generate random bipartite graphs by creating two equal-sized sets of vertices and every possible edge between them has a probability of $p = 0.5$ to appear.
-In this way we can also generate line graphs of bipartite graphs.
+We generate random bipartite graphs by creating two equal-sized sets of vertices, and then added every possible edge between them with a probability of $p = 0.5$.
+In this way we can also generate line graphs of random bipartite graphs.
 This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
@@
 See \Cref{fig:lattice} for an example of a $4 \times 4$ lattice graph.
-If we imagine our grid to be a chessboard we can define a rook graph to have an edge, when the rook from chess can move from one vertex to another in one move.
+If we imagine our grid to be a chessboard we can define two vertices a rook graph to share an edge, when the rook from chess can move from one vertex to the other in one move.
 See \Cref{fig:rook} for an example of $4 \times 4$ rook graph.
@@
 Split graphs we use are unions of cliques and independent sets of same size, with some edges between them.
-In generating them, each edge between a vertex from a clique and a vertex from an independent set has had $1/2$ chance to appear.
+In generating them, each edge between a vertex from a clique and a vertex from an independent set has had a chance $p = 0.5$ to appear.
 
@@
 \subsubsection{Time results}
+
+We ran our tests on Intel Xeon E5-2690 CPU and Nvidia Tesla K80 GPU with 4992 CUDA cores.
 
@@
 If we limit runtime to about two minutes, we can run it on graphs of sizes up to 40-70, depending on the type of the graph we test.
-What is interesting, that there isn't that much of a variance of the running time depending on the type of graph we test on.
+Worth noting is the fact that there isn't that much of a variance of the running time depending on the type of graph we test on.
 This is a big advantage of CCLSV over the na\"ive algorithm, which is highly dependent on the type of input.
-On some graphs, it works almost instantenously, what is to be expected, given its nature of enumerating paths.
+On some graphs, it works almost instantenously, what is to be expected, given its method of enumerating paths.
 But on some graphs, e.g.
@@
 
-Examples of full binary graphs, and lattice graphs show that getting near cleaners still can be a big bottleneck.
+Examples of full binary graphs, and lattice graphs show that getting possible near cleaners still can be a big bottleneck.
 Parallelization of this method could be considered in the future.
@@
 When running GPU CCLSV on split graphs, quite a lot of time is spent checking simple structures.
-This should be parallelizable, the biggest challange we can see is spreading work evenly across CUDA threads.
+The biggest challange we can see is in an attempt to parallelise this is spreading work evenly across CUDA threads.
 
@@
 
-\subsection{Ellipsoid method}
+\subsubsection{Ellipsoid method}
 
@@
 As it was done by an external library, there isn't much optimization potential for us.
-One thing of note is, that specifying the precision of $\vartheta$ we want to calculate to be $1/3$ sped up the algorithm by TODO.
+One thing of note is, that by specifying the precision of $\vartheta$ we want to calculate to be $1/3$ the algorithm sped up  by 20-40\%.
 Also, we cache results of calculatin $\vartheta$, meaning that throught whole execution of our coloring algorithm, we only calculate $\vartheta$ for each graph once.
@@
 We note that $\vartheta$ calculation is highly dependent on the type of the graph.
-For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in biparite graphs, but only 12 seconds in line graphs of bipartite graphs.
+For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in bipartite graphs, but only 12 seconds in line graphs of bipartite graphs.
 Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs.
-However, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs of lattice graphs.
+However, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs or lattice graphs.
 A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.
 
-We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ by the CSDP library is quite significant.
+We notice that on some graphs, namely line graphs of bipartite graphs, rook graphs and split graphs the time taken by operations other than calculating $\vartheta$ is quite significant.
 However, the overall running times on these graphs are low, so we didn't particularly optimize this, so probably some improvements could be made here.
@@
 Both have their positives and drawbacks -- CCLSV's running times are more predictable, but on many graphs it is noticeably slower than the na\"ive algorithm.
-On the other hand, running na\"ive algorithm on a graph we don't know any properties of can lead to unbearably slow running time.
+On the other hand, running na\"ive algorithm on a graph we don't know any properties of can lead to unbearably slow performance.
 
@@
 It is not entirely unusable, although far from fast.
-Maybe a better way of calculating $\vartheta$ could be found, or the GPU could be again usable for this task.
-We point to Nvidia's \cite{cusolver} as a possible starting point.
+Maybe a better way of calculating $\vartheta$ could be found, or the GPU could again be usable for this task.
+We point to Nvidia's cuSOLVER  cite{cusolver} as a possible starting point.

### 2020-09-16 paper/implementation.tex
Fixes

@@
 \section{Berge graphs recognition: na\"ive approach}
-When implementing an algorithm with the running time of $O(n^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is applicable at all.
+When implementing an algorithm with the running time of $O(|V|^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is at all usable.
 We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.\todo{well..
@@
 
-We try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is Perfect, else that it is not.
+We try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is perfect, else that it is not.
 
 To find an odd hole, we use a backtracking technique.
-We will enumerate all paths and holes and for each test if it is an odd hole.
+We will enumerate all paths and holes, and for each test if it is an odd hole.
 A partial solution to our backtracking problem is a path in $G$.
@@
 When a current solution is an odd hole we return it.
-When we exhaust all possible paths from the current partial solution, we remove last vertex and continue.
+When we exhaust all possible paths from the current partial solution, we remove its last vertex and continue.
 
-This backtracking algorithm is very simple, but has a great potential for optimizations in implementation.
+This backtracking algorithm is very simple, but has a great potential for optimizations in its implementation.
 We also use path enumeration algorithm in the CCLSV algorithm, so we give much attention to its optimization.
@@
 
-This simple change in data structure design gave us a speedup of overall running time of our algorithm in the range of about 5x.
+This simple change in data structure design gave us a speedup of overall running time of our na\"ive algorithm in the range of about 5x.
 
@@
 Those two optimizations make a huge difference.
-With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a couple of minutes, to being faster than CCLSV on most of our tests.
+With them, our na\"ive algorithm implementation went from being able to check graphs with $|V|$ up to 12-14, within a reasonable time, to being faster than CCLSV on most of our tests.
 
@@
 With all those optimizations made, our na\"ive algorithm proved to be quite fast in some cases, although its running time is very dependent on the properties of the input, as we should expect from an optimized non-polynomial algorithm.
-See \Cref{sec:experiments} for running times.
+See \Cref{sec:experiments} for the running times.
 
@@
 
-The Berge recognition algorithm's running time is $O(n^9)$, which brings into question its applicability to any real use case.
+The Berge recognition algorithm's running time is $O(|V|^9)$, which brings into question its applicability to any real use case.
 Although time complexity is indeed a limiting factor, a number of lower level optimizations done on implementation's level make a very big difference and make it more viable than na\"ive algorithm, at least on some test cases.
@@
 
-When implementing a complicated algorithm that has a time complexity of $O(n^9)$ optimizations can be both crucial and difficult to implement.
-There is not a single code path that takes up all the running time -- or at lest there isn't one from a theoretical point of view.
+When implementing a complicated algorithm that has a time complexity of $O(|V|^9)$ optimizations can be both crucial and difficult to implement.
+There is not a single code path that takes up all the running time -- or at least there isn't one from a theoretical point of view.
 Therefore a tool for inspecting running time bottlenecks is needed.
@@
 
-Callgrind is a profiling tool that records the call history and event counts ((data reads, cache misses etc.) of a program and presents it as a call-graph.
+Callgrind is a profiling tool that records the call history and event counts (data reads, cache misses etc.) of a program and presents it as a call-graph.
 It is then possible to visualise this, we used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
 
-Before any optimizatios, a major part of Berge recognition algorithm was being spent on enumerating all possible paths of given length -- this is done either to find a hole by itself, find a simple structure or check a possible near cleaner for amenable odd hole.
+Before any optimizatios, a major part of Berge recognition algorithm was being spent on enumerating all possible paths of given length -- this is done either to find a simple structure or check a possible near cleaner for an amenable odd hole.
 Therefore optimizations of the path enumerating algorithm were also helpful in speeding up CCLSV implementation.
@@
 
-Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners \Cref{alg:listNearCleaners}).
+Another algorithm for which we found major speedups is the algorithm to generate all possible near-cleaners (\Cref{alg:listNearCleaners}).
 We optimized it by using a a \texttt{dynamic\_bitset} from the boost library \cite{boost}.
@@
 At the very end of \Cref{alg:listNearCleaners} a set $\mathcal{R}$ is constructed, which is an union of all possible unions of pairs $X_i$ and $N_j$.
-We used \texttt{dynamic\_bitset} to represent each of the sets $X_i$ and $N_j$, and the set $\mathcal{R}$.
+We used \texttt{dynamic\_bitset} to represent each of the sets $X_i$ and $N_j$, and the elements of the set $\mathcal{R}$.
 This significantly speeds up the operation of union of two sets (line \ref{line:listNCcalcR}).
@@
 
-Also, we test the algorithm on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof.
+Also, we test our implementations on graphs that we know are perfect -- such as bipartite graphs, line graphs of bipartite graphs and complements thereof.
 In addition to that, a test on all perfect graphs up to a size of 10 was performed -- we used \cite{graphRepo} as a source of perfect graphs.
 
-We also test on graphs that we know are not perfect: we generate them by generating an odd hole and adding it with some edges to a random graph.
+We also test on graphs that we know are not perfect: we generate them by generating an odd hole and joining it with some edges to a random graph.
 
@@
 CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs.
-It allows to run a program in by many CUDA threads at once.
+It allows to run a program  by many CUDA threads at once.
 Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a CPU.
@@
 We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd}.
-Let us notice, that for all $X$s all 3-vertex paths enumerated in line \ref{line:3vertex} are the same.
+Let us notice, that for all $X$s, all 3-vertex paths enumerated in line \ref{line:3vertex} are the same.
 We calculate them beforehand, then each CUDA thread receives one 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks in lines \ref{line:cudaWorkStard}-\ref{line:cudaWorkEnd}.
@@
 
-The part of the CCLSV implemented on the GPU achieved speedup of up to 15x. Which gave us a speedup of up to 9x for overall CCLSV algorithm.
+The part of the CCLSV implemented on the GPU achieved speedup of up to 15x. Which gave us a speedup of up to 9x for overall CCLSV algorithm, depending on a class of graph we benchmark on.

### 2020-09-16 paper/main.tex
Poprawki up to old Ch 1
many many fixes
Fixes

--- 2020-09-01 paper/main.tex
@@
 \begin{abstract}
-	TODOa
+	Perfect graphs are a subject of intense study since their introduction in 1961.
+Only in 2001 the famous Perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found.
+Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated and impractical.
+As recently as in 2018 a polynomial algorithm for coloring perfect graphs without squares was published, that uses a combinatorial approach.
+
+	We begin with basic definitions in Chapter 1.
+In Chapter 2 we introduce perfect graphs and Berge graphs, give an overview of the strong perfect graph theorem and talk about an algorithm for polynomial perfect graph recognition.
+Chapter 3 is a study of the ellipsoid method of coloring perfect graphs.
+In Chapter 4 we present our implementation of algorithms from Chapters 2 and 3, along with notes on optimization and parallelisation.
+Appendix A is a overview of the recent algorithm for coloring square-free perfect graphs.
 \end{abstract}
@@
 
-\chapter*{Definitions}
+\chapter{Basic Graph Definitions}
 \input{definitions.tex}

### 2020-09-16 paper/perfectGraphs.tex
Fixes

@@
 This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$.
-The reverse is not always true, in fact we can construct a graph with no triangle and requiring arbitrarily large numbers of colors (e.g.
+The reverse is not always true, in fact we can construct a graph with no triangles and requiring arbitrarily large numbers of colors (e.g.
 construction by Mycielski \cite{Mycielski1955}).
@@
 Not necessarily so.
-Given a graph $G = (V, E)$, $|V| = n$, let us construct a graph $G'$ as the union of $G$ and a clique $K_n$.
-We can see that indeed $\chi(G') = \omega(G') = n$, but it gives us no indication of the structure of $G$ or $G'$.
+Given a graph $G = (V, E)$, let us construct a graph $G'$ as the union of $G$ and a clique $K_{|V|}$.
+We can see that indeed $\chi(G') = \omega(G') = |V|$, but it gives us no indication of the structure of $G$ or $G'$.
 This leads us to the hereditary definition of \emph{perfect graphs}.
@@
 Also, as pointed out in \cite{alfonsinPerfect2001, Chudnovsky2003}, algorithms to solve semidefinite programs grew out of the theory of perfect graphs.
-We will take a look at semidefinite programs and at perfect graph's relation to Shannon capacity in \Cref{sec:ShannonCapacity}.
+We will take a look at semidefinite programs and at perfect graph's relation to the Shannon capacity in \Cref{sec:ShannonCapacity}.
 
@@
 
-\begin{theorem}[Perfect graph theorem from \cite{LL72}]
+\begin{theorem}[Perfect graph theorem \cite{LL72}]
 	\label{thm:pgt}
@@
 Then, since $\alpha(H) = \omega(\overline{H})$ and $\omega(H) = \alpha(\overline{H})$ \Cref{thm:omegaalpha} implies \Cref{thm:pgt}.
+We skip the proof of \Cref{thm:omegaalpha}, as it is quite technical.
 
@@
 If they do, we output that graph is not Berge and stop.
-Else, we check if there is a near-cleaner for a shortest odd hole (\Cref{AmenableHoles}).
+Else, we check if there is a near-cleaner for a shortest odd hole or for shortest odd antihole (\Cref{AmenableHoles}).
 
@@
 
-					\mIf{$s_1 = b_1$} \Comment{calculate all possible $P_1$ paths}
+					\mIf{$s_1 = b_1$ \label{line:ShortestPathsStart}} \Comment{calculate all possible $P_1$ paths}
 						\ls $P_1(b_1) \gets$ the one-vertex path with vertex $b_1$
@@
 
-				\ls assign $P_2$ and $P_3$ in a similar manner
+				\ls assign $P_2$ and $P_3$ in a similar manner \label{line:ShortestPathsEnd}
 				\ls $good\_pairs_{1,2} \gets \emptyset$ \Comment{see below for definition}
@@
 Calculating paths $S_i$ and $T_i$ (lines \ref{line:pyramidSStart}-\ref{line:pyramidSEnd}) takes $O(|V|^2)$ time for each $m \in M$ and $O(|V|^3)$ in total.
-Similarly, it takes $O(|V|^3)$ time to calculate all $P_i$ paths.
+Similarly, it takes $O(|V|^3)$ time to calculate all $P_i$ paths (lines \ref{line:ShortestPathsStart}-\ref{line:ShortestPathsEnd}).
 
@@
 
-	Finally, there are $O(|V|^3)$ pairs $m_1, m_2, m_3$ and checking each takes $O(1)$ time.
+	Finally, there are $O(|V|^3)$ pairs $m_1, m_2, m_3$ and checking each takes $O(1)$ time which gives us the overall running time of $O(|V|^9)$.
 \end{proof}
@@
 
-Most obvious way to find a jewel would be to enumerate all (possibly chordal) cycles of length 5 as $v_1, \ldots v_5$, check if it has all required nonedges and if it does, try to find a path $P$ as required.
+Notice that given a jewel $v_1, \ldots, v_5, P$, if the path $P$ is odd, then $v_1$-$P$-$v_4$-$v_5$-$v_1$ is an odd hole.
+If the path $P$ is even, then $v_1$-$P$-$v_4$-$v_3$-$v_2$-$v_1$ is an odd hole.
+
+Most obvious way to find a jewel is to enumerate all (possibly chordal) cycles of length 5 as $v_1, \ldots v_5$, check if it has all required nonedges and if it does, try to find a path $P$ as required.
 This gives us a time of $O(|V|^7)$.
@@
 	\caption{An example of a $\T_2$.}%
-	\vspace{-1.5cm}
+	\vspace{-.5cm}
 \end{wrapfigure}
@@
 
-To prove that the existence of $\T_2$ configuration implies that the graph is not Berge, we will need the following lemma:
+To prove that the existence of a configuration of type $\T_2$ implies that the graph is not Berge, we will need the following lemma:
 
@@
 		\item if $P$ is odd with the length of at least 5, it follows from \Cref{lem:Roussel-Rubio} that we have $x, y \in X$ with only two edges to $P$ being $xp_2$ and $yp_{n-1}$.
-This gives us an odd hole: $v_2-x-p_2-\ldots-p_{n-1}-y-v_2$.
+This gives us an odd hole: $v_2$-$x$-$p_2$-$\ldots$-$p_{n-1}$-$y$-$v_2$.
 	\end{itemize}
@@
 \begin{wrapfigure}{r}{0.35\textwidth}
+	\vspace{-1cm}
 	\input{tikzpictures/t3.tex}
 	\caption{An example of a $\T_3$.}%
-	\vspace{-1.5cm}
+	\vspace{-2cm}
 \end{wrapfigure}
@@
 
-The following algorithm with running time of $O(|V|^6)$ checks whether $G$ contains a configuration of type $\T_3$:
+% The following algorithm with running time of $O(|V|^6)$ checks whether $G$ contains a configuration of type $\T_3$:
 
@@
 							\ls $P \gets$ a path from $v_6$ to $v_5$ with interior in $F'$
-							\ls \RETURN \TRUE \Comment{$v_1, \ldots v_6, P, X$ is a $\T_3$}
+							\ls \RETURN \TRUE \Comment{$v_1, \ldots v_6, P, X$ is a $\T_3$} \label{line:t3found}
 						\mEndIf
@@
 
-We will skip the proof that each graph containing $\T_3$ is not Berge, as it is quite technical. See section 6.7 of \cite{MC05} for the proof.
+It is easy to see that when \Cref{alg:t3} reports a configuration of type $\T_3$ in line \ref{line:t3found}, there indeed is one.
+We will skip the proof that each graph containing a $\T_3$ is not Berge, as it is quite technical.
+See section 6.7 of \cite{MC05} for the proof.
 
@@
 \label{AmenableHoles}
-
-First, let us introduce a few new definitions.
+As we will see (\Cref{thm:amenableHoles}), if graphs $G$ and $\overline{G}$ contain no jewels, pyramids or configurations of type $\T_1, \T_2$ or $\T_3$, then every shortest odd hole in $G$ or $\overline{G}$ will have a special structure and we will call it amenable.
+This fact will help us determine if $G$ or $\overline{G}$ contain an odd hole.
+But first, let us introduce a few new definitions.
 
 \begin{defn}[relevant triple]
-	Given a graph $G$, a triple $(a, b, c)$ of vertices is called \emph{relevant} if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
+	Given a graph $G$, a triple $(a, b, c)$ of vertices is called \emph{relevant} if and only if $a \neq b$ (but possibly $c \in \{a, b\}$) and $G[\{a,b,c\}]$ is an independent set.
 \end{defn}
@@
 \begin{defn}[C-major vertices]
-  Given a shortest odd hole $C$ in $G$, a node $v \in V(G) \setminus V(C)$ is $C$-major if the set of its neighbors in $C$ is not contained in any 3-node path of $C$.
+  Given a shortest odd hole $C$ in $G$, a vertex $v \in V(G) \setminus V(C)$ is $C$-major if and only if the set of its neighbors in $C$ is not contained in any 3-vertex path of $C$.
 \end{defn}
@@
 \begin{defn}[clean odd hole]
-  An odd hole $C$ of $G$ is \emph{clean} if no vertex in $G$ is $C$-major.
+  An odd hole $C$ of $G$ is \emph{clean} if and only if no vertex in $G$ is $C$-major.
 \end{defn}
@@
 \begin{defn}[cleaner]
-  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{cleaner for $C$} if and only if $X \cap V(C) = \emptyset$ and every $C$-major vertex belongs to $X$.
 \end{defn}
@@
 \begin{defn}[near-cleaner]
-  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-node path of $C$.
+  Given a shortest odd hole $C$ in $G$, a subset $X \subseteq V(G)$ is a \emph{near-cleaner for $C$} if and only if $X$ contains all $C$-major vertices and $X \cap V(C)$ is a subset of vertex set of some 3-vertex path of $C$.
 \end{defn}
@@
 \begin{defn}[amenable odd hole]
-  An odd hole $C$ of $G$ is \emph{amenable} if it is a shortest odd hole in $G$, it is of length at least 7 and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
+  An odd hole $C$ of $G$ is \emph{amenable} if and only if it is a shortest odd hole in $G$, $|E(C)| \geq 7$, and for every anticonnected set $X$ of $C$-major vertices there is a $X$-complete edge in $C$.
 \end{defn}
@@
 Some pictures might be helpful.
-\Cref{fig:amenableOddHole} shows an example of an amenable odd hole $C = v_1, \ldots, v_7$.
-It is not a clean hole -- vertices $v_8$ and $v_9$ are $C$-major, and $v_8, v_9, v_1, v_2, v_3$ is an axample of a near-cleaner for $C$.
-\Cref{fig:notAmenableHole} shows an odd hole $C = v_1, \ldots, v_7$ that is not amenable, because there is no $\{v_8, v_9\}$-complete edge in $C$.
+\Cref{fig:amenableOddHole} shows an example of an amenable odd hole $C = v_1$-$\ldots$-$v_7$-$v_1$.
+It is not a clean hole -- vertices $v_8$ and $v_9$ are $C$-major, and $\{v_8, v_9, v_1, v_2, v_3\}$ is an axample of a near-cleaner for $C$.
+\Cref{fig:notAmenableHole} shows an odd hole $C = v_1$-$\ldots$-$v_7$-$v_1$ that is not amenable, because there is no $\{v_8, v_9\}$-complete edge in $C$.
 
@@
 See section 8 of \cite{MC05} for the proof.
-We can see an example of the contraposition of the \Cref{thm:amenableHoles} working in \Cref{fig:notAmenableHole} -- vertices $v_1$, $v_2$, $v_8$, $v_6$, $v_7$ and a path $v_1-v_9-v_5-v_6$ form a jewel.
+We can see an example of the contraposition of the \Cref{thm:amenableHoles} working in \Cref{fig:notAmenableHole} -- vertices $v_1$, $v_2$, $v_8$, $v_6$, $v_7$ and a path $v_1$-$v_9$-$v_5$-$v_6$ form a jewel.
 
@@
 
-\begin{alg}[List possible near cleaners, 9.2 of \cite{MC05}]
+\begin{alg}[List possible near cleaners]
 	\label{alg:listNearCleaners}
@@
 
-\begin{alg}[Test possible near cleaner, 5.1 of \cite{MC05}]
+\begin{alg}[Test possible near cleaner]
 	\label{alg:testNearCleaner}
@@
 					\mIf{$R(x_1, y_1), R(x_2, y_2)$ both exist} \label{line:cudaWorkStard}
-						\ls $y_2 \gets$ the neighbor of $y_1$ in $R(x_2, y_1)$
-						\mIf{$r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2) =$\lsx$min(r(x_3, y_1), r(x_3, y_2))$}
+						\ls $y_2 \gets$ the neighbor of $y_1$ in $R(x_2, y_1)$ \label{line:definey2}
+						\mIf{$r(x_2, y_1) = r(x_1, y_1) + 1 = r(x_1, y_2)$ \AND
+						\lsx $r(x_2, y_1) \leq min(r(x_3, y_1), r(x_3, y_2))$ \label{line:manyconditions}}
 						\ls \RETURN an odd hole found
@@
 
-Below we will prove that if the \Cref{alg:testNearCleaner} reports an odd hole in $G$, there indeed is one.
-The proof of the correctness of the other possible result is more complicated, see section 4 and Theorem 5.1 of \cite{MC05}.
-
 \begin{theorem}[Theorem 5.1 of \cite{MC05}]
@@
 
-	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying the three conditions in the \Cref{alg:testNearCleaner} and let $y_2$ and $n$ be defined as in there.
+	Let us suppose that there is a choice of $x_1$, $x_2$, $x_3$, $y_1$ satisfying conditions in lines \ref{line:cudaWorkStard} and \ref{line:manyconditions}, let $y_2$ be defined as in line \ref{line:definey2} and let $k = r(x_2, y_1)$.
 We claim that $G$ contains an odd hole.
@@
 		\end{wrapfigure}
-		Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$.
-From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$.
-Also, from the definition of $y_1$, $y_1 \notin X$.
-
-		Let $R(x_1, y_1) = p_1-\ldots -p_n$, and let $R(x_2, y_1) = q_1-\ldots -q_{n+1}$, where $p_1 = x_1$, $p_n = q_{n+1} = y_1$, $q_1 = x_2$ and $q_n = y_2$.
-From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{n-1}, q_2, \ldots, q_n$ belong to $X$.
+		Let $R(x_1, y_1) = p_1$-$\ldots$-$p_k$, and let $R(x_2, y_1) = q_1$-$\ldots$-$q_{k+1}$, where $p_1 = x_1$, $p_k = q_{k+1} = y_1$, $q_1 = x_2$ and $q_k = y_2$.
+From the definition of $R(x_1, y_1)$ and $R(x_2, y_1)$, none of $p_2, \ldots, p_{k-1}, q_2, \ldots, q_k$ belong to $X$.
 Also, from the definition of $y_1$, $y_1 \notin X$.
@@
 		Since $r(x_1, y_1) = r(x_2, y_1) - 1$ and since $x_1$, $x_2$ are nonadjacent it follows that $x_2$ does not belong to $R(x_1, y_1)$ and $x_1$ does not belong to $R(x_2, y_1)$.
-Since $r(x_3, y_1), r(x_3, y_2) \geq n = r(x_1, y_2)$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
-Since $r(x_1, y_2) = n$ we get that $y_2$ does not belong to $R(x_1, y_1)$.\par}%
+Since $r(x_3, y_1), r(x_3, y_2) \geq k = r(x_1, y_2)$ it follows that $x_3$ does not belong to $R(x_1, y_1)$ or to $R(x_2, y_1)$, and has no neighbors in $R(x_1, y_1) \cup R(x_2, y_1)$ other than $x_1$, $x_2$.
+Since $r(x_1, y_2) = k$ we get that $y_2$ does not belong to $R(x_1, y_1)$.
 
 		We claim first that the insides of paths $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertices.
-For suppose that there are $2 \leq i \leq n-1$ and $2 \leq j \leq n$ that $p_i = q_j$.
+For suppose that there are $2 \leq i \leq k-1$ and $2 \leq j \leq k$ that $p_i = q_j$.
 Then the subpaths of these two paths between $p_i$, $y_1$ are both subpaths of the shortest paths, and therefore have the same length equal to $j=i+1$.
-So $p_1-\ldots-p_1-q_{j+1}-\ldots-q_n$ contains a path between $x_1$, $y_2$ of length $\leq n-2$, contradicting that $r(x_1, y_2) = n$.
-So $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertex except $y_1$.
+So $p_1$-$\ldots$-$p_1$-$q_{j+1}$-$\ldots$-$q_k$ contains a path between $x_1$, $y_2$ of length $\leq k-2$, contradicting that $r(x_1, y_2) = k$.
+So $R(x_1, y_1)$ and $R(x_2, y_1)$ have no common vertices except $y_1$.\par}%
 
-	If there are no edges between $R(x_1, y_1) \setminus y_1$ and $R(x_2, y_1) \setminus y_1$ then the union of these two paths and a path $x_1-x_3-x_2$ form an odd hole, so the answer is correct.
+	If there are no edges between $R(x_1, y_1) \setminus \{y_1\}$ and $R(x_2, y_1) \setminus \{y_1\}$ then the union of these two paths and a path $x_1$-$x_3$-$x_2$ forms an odd hole, so the answer is correct.
 
-	Suppose that $p_iq_j$ is an edge for some $1\leq i \leq n-1$ and $1 \leq j \leq n$.
+	Suppose that $p_iq_j$ is an edge for some $1\leq i \leq k-1$ and $1 \leq j \leq k$.
 We claim $i \geq j$.
 If $j = 1$ this is clear so let us assume $j > 1$.
-Then there is a path between $x_1$, $y_2$ within $\{p_1, \ldots , p_i, q_j, \ldots q_n\}$ which has length $\leq n-j+1$ and has no internal vertex in $X$ (since $j > 1$); and since $r(x_1, y_2) = n$, it follows that $n-j+i \geq n$, that is, $i \geq j$ as claimed.
+Then there is a path between $x_1$, $y_2$ within $\{p_1, \ldots , p_i, q_j, \ldots q_k\}$ which has length $\leq k-j+1$ and has no internal vertex in $X$ (since $j > 1$); and since $r(x_1, y_2) = k$, it follows that $k-j+i \geq k$, that is, $i \geq j$ as claimed.
 
-	Now, since $x_1$, $x_2$ are nonadjacent $i \geq 2$.
-But also $r(x_2, y_1) \geq n$ and so $j+n-i \geq n$, which gives us $j \geq i$.
+	Now, since $x_1$, $x_2$ are nonadjacent, we have $i \geq 2$.
+But also $r(x_2, y_1) \geq k$ and so $j+k-i \geq k$, which gives us $j \geq i$.
 So we get $i=j$.
-Let us choose $i$ minimum, then $x_3-x_1-\ldots-p_i-q_i-\ldots-x_2-x_3$ is an odd hole, which was what we wanted.
+Let us choose $i$ minimum, then $x_3$-$x_1$-$\ldots$-$p_i$-$q_i$-$\ldots$-$x_2$-$x_3$ is an odd hole, which was what we wanted.
 \end{proof}
 
-\subsection{Algorithm for Berge graphs recognition}
+\subsection{Algorithm for perfect graph recognition}
 
-To summarize, we present a complete algorithm for recognizing Berge graphs.
-\begin{alg}[Determine if a graph is Berge]
+To summarize, we present a complete algorithm for recognizing perfect graphs.
+\begin{alg}[Determine if a graph is perfect]
 	\label{alg:testNearCleaner}
@@
 
-	\noindent Output: Determines if $G$ is Berge.
+	\noindent Output: Determines if $G$ is perfect.
 	\label{alg:bergeness}
@@
 \begin{algorithmic}[1]
-	\mProcedure{Check-Berge}{$G$}
+	\mProcedure{Check-Is-Perfect}{$G$}
 		\mIf{\texttt{Contains-Pyramid}$(G)$ \OR \texttt{Contains-Jewel}$(G)$ \OR \lsx 
 		\texttt{Contains-T1}$(G)$ \OR \texttt{Contains-T2}$(G)$ \OR \texttt{Contains-T3}$(G)$ \label{line:simpleStart}}
-			\ls \RETURN $G$ is not Berge
+			\ls \RETURN $G$ is not perfect
 		\mEndIf
@@
 		\texttt{Contains-T1}$(\overline{G})$ \OR \texttt{Contains-T2}$(\overline{G})$ \OR \texttt{Contains-T3}$(\overline{G})$}
-			\ls \RETURN $G$ is not Berge
+			\ls \RETURN $G$ is not perfect
 		\mEndIf \label{line:simpleEnd}
@@
 			\mIf{\texttt{Test-Near-Cleaner}$(G, X)$ reports an odd hole}
-				\ls \RETURN $G$ is not Berge
+				\ls \RETURN $G$ is not perfect
 			\mEndIf
@@
 			\mIf{\texttt{Test-Near-Cleaner}$(\overline{G}, X)$ reports an odd hole}
-				\ls \RETURN $G$ is not Berge
+				\ls \RETURN $G$ is not perfect
 			\mEndIf
 		\mEndFor
-		\ls \RETURN $G$ is Berge
+		\ls \RETURN $G$ is perfect
 	\mEndProcedure
@@
 \begin{theorem}[Theorem 10.1 of \cite{MC05}]
-	Given a graph $G = (V, E)$, \Cref{alg:bergeness} works in $O(|V|^9)$ time and determines is $G$ is Berge.
+	Given a graph $G = (V, E)$, \Cref{alg:bergeness} works in $O(|V|^9)$ time and determines if $G$ is perfect.
 \end{theorem}
@@
 If for all $X \in \mathcal{R}$ an odd hole is not reported, then by \Cref{thm:amenableHoles}, \Cref{thm:92} and \Cref{thm:testNCWorks} there is no odd hole in $G$.
-We  run the same procedure on $\overline{G}$ and if again we do not detect an odd hole, then $G$ is Berge and by \Cref{thm:spgt} $G$ is perfect.
+We run the same checks on $\overline{G}$ and if again we do not detect an odd hole, then $G$ is Berge and by \Cref{thm:spgt} $G$ is perfect.
 
@@
 For each subset running \Cref{alg:testNearCleaner} takes $O(|V|^4)$ time, so testing all possible near-cleaners takes $O(|V|^9)$ time.
-Then we repeat on the $\overline{G}$.
 
-	The overall running time is $O(|V|^9)$ with testing for pyramids and testing all possible near-cleaners being algorithms with biggest time complexity.
+	The overall running time is $O(|V|^9)$ with testing for pyramids and testing all possible near-cleaners being parts with biggest time complexity.
 \end{proof}

### 2020-09-16 code/src/theta.c

@@ -5,26 +5,6 @@
 
 /* This theta.c file is based on  Csdp/theta/theta.c of Csdp project: https://github.com/coin-or/Csdp */
 
-int user_exit(n, k, C, a, dobj, pobj, constant_offset, constraints, X, y, Z, params) int n;
-int k;
-struct blockmatrix C;
-double *a;
-double dobj;
-double pobj;
-double constant_offset;
-struct constraintmatrix *constraints;
-struct blockmatrix X;
-double *y;
-struct blockmatrix Z;
-struct paramstruc params;
-{
-  double gap = trace_prod(X, Z);
-
-  if(gap < 0.1) return 2;
-
-  return 0;
-}
-
 double theta(int n, int m, int *from, int *to) {
   int i;
   int j;

### 2020-09-16 code/test/colorPerfTest/run.sh

@@ -23,8 +23,9 @@ colorTests=(
   # "rook.t.in"
   # "knight.t.in"
   # "hypercube.t.in"
-  "split.t.in"
+  # "split.t.in"
   # "fullBinary.t.in"
+  "tmp.t.in"
 )
 
 # for file in "${colorTests[@]}"; do

### 2020-09-16 code/test/generate/generate.cpp

@@ -10,23 +10,23 @@
 int main() {
   srand(time(0));
 
-  // int minN = 18;
-  // int maxN = 48;
-  // int step = 6;
+  int minN = 18;
+  int maxN = 36;
+  int step = 6;
 
-  // for (int i = 0; i < 10; i++) {
-  //   set<int> done;
+  for (int i = 0; i < 1; i++) {
+    set<int> done;
 
-  //   while (done.size() < (maxN - minN + step) / step) {
-  //     Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
-  //     // if (rand() % 2) G = G.getComplement();
+    while (done.size() < (maxN - minN + step) / step) {
+      Graph G = getBipariteGraph(8 + (rand() % 20), getDistr()).getLineGraph();
+      // if (rand() % 2) G = G.getComplement();
 
-  //     if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
-  //       G.printOut();
-  //       done.insert(G.n);
-  //     }
-  //   }
-  // }
+      if ((G.n % step == 0) && G.n >= minN && G.n <= maxN && done.count(G.n) == 0) {
+        G.printOut();
+        done.insert(G.n);
+      }
+    }
+  }
 
   // int minN = 18;
   // int maxn = 48;
@@ -74,18 +74,18 @@ int main() {
   //     G.printOut();
   //   }
   // }
-  Graph G(9,
-          "\
-  .X....X.X\
-  X.X....X.\
-  .X.X.....\
-  ..X.X...X\
-  ...X.X..X\
-  ....X.XX.\
-  X....X.X.\
-  .X...XX..\
-  X..XX....\
-  ");
+  // Graph G(9,
+  //         "\
+  // .X....X.X\
+  // X.X....X.\
+  // .X.X.....\
+  // ..X.X...X\
+  // ...X.X..X\
+  // ....X.XX.\
+  // X....X.X.\
+  // .X...XX..\
+  // X..XX....\
+  // ");
 
-  cout << findJewelNaive(G);
+  // cout << findJewelNaive(G);
 }

### 2020-09-17 paper/coloringBergeGraphs.tex
Fixes

@@
 
-The polynomial technique of coloring perfect graphs known so far arose in the field of semidefinite programming.
+The only polynomial technique of coloring perfect graphs known so far arose in the field of semidefinite programming.
 Semidefinite programs are linear programs over the cones of semidefinite matrices.
@@
 However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
-This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if values they represent can be confused.
+This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if the values they represent can be confused.
 
@@
 Given a graph $G$ modeling a communication channel and a number $k \geq 1$ we say that two messages $v_1v_2\ldots v_k$, $w_1w_2\ldots w_k \in V(G)^k$ of length $k$ are non-confoundable if and only if there is $1 \leq i \leq k$ such that $v_i$, $w_i$ are non-confoundable.
-We are interested in the maximum rate at which we can reliably transmit information (the \emph{Shannon capacity} of the channel defined by $G$).
+We are interested in the maximum rate at which we can reliably transmit information, that is, the \emph{Shannon capacity} of the channel defined by $G$.
 
@@
 To describe longer messages we use \emph{strong product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ if and only if $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
-Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ -- which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission.
+Given channel modeled by $G$ it is easy to see that the maximum number of distinguishable words of length 2 is equal to $\alpha(G \cdot G)$, and in general the number of distinguishable words of length $k$ is equal to $\alpha(G^k)$ which gives us $\sqrt[k]{\alpha(G^k)}$ as the number of distinguishable signals per single transmission.
 So, we can define the Shannon capacity of the channel defined by $G$ as $\Theta(G) = \sup\limits_k \sqrt[k]{\alpha(G^k)}$.
@@
 This gives us
-$$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq \sum\limits_{i \in S'}(e_1^\intercal v_i)^2 \leq ? = 1$$
+$$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq \sum\limits_{i \in S'}(e_1^\intercal v_i)^2 \leq |e_1|^2 = 1$$
 \todo{todo}
-Each term on the left hand side is $5^{-k/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
+Each term on the left hand side is equal to $5^{-k/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.
 Since $|S|$ was an arbitrary stable set, we get $\alpha(C_5^k) \leq 5 ^{k/2}$ and $\Theta(C_5) = \sqrt{5}$.
@@
 \begin{defn}[positive semidefinite matrix]
-  Let $A$ be an $n \times n$ symmetric matrix. $A$ is \emph{positive semidefinite} if all of its eigenvalues are nonnegative. We denote it by $A \succeq 0$.
+  Let $A$ be an $n \times n$ symmetric matrix. $A$ is \emph{positive semidefinite} if and only if all of its eigenvalues are nonnegative. We denote it by $A \succeq 0$.
 \end{defn}
@@
 
-The fact that the sum of two positive semidefinite matrices is again positive semidefinite, with the fact that every positive scalar multiple of a positive semidefinite matrix is positive semidefinite, translates into the geometric statement that the set of all positive semidefinite matrices forms a convex closed cone $\mathcal{P}_n$ in $\mathbb{R}^{n \times n}$ with vertex 0.
+The fact that the sum of two positive semidefinite matrices is again positive semidefinite, with the fact that every positive scalar multiple of a positive semidefinite matrix is positive semidefinite, translates into the geometric statement that the set of all positive semidefinite matrices forms a convex closed cone $\mathcal{P}_n$ in $\mathbb{R}^{n \times n}$ with its apex at 0.
 This cone $\mathcal{P}_n$ is important but its structure is not trivial.
@@
 
-Any stable set $S$ of $G$ provides a feasible solution of the sual program, by choosing $Z_{ij} = \frac{1}{S}$, if $i, j \in S$ and 0 otherwise.
+Any stable set $S$ of $G$ provides a feasible solution of the dual program, by choosing $Z_{ij} = \frac{1}{S}$ if $i, j \in S$ and 0 otherwise.
 Similarly, any $k$-coloring of $\overline{G}$ provides a feasible solution of the former semidefinite program, by choosing $Y_{ij} = -1$ if $i$ and $j$ have different colors, $Y_{ii} = k-1$, and $Y_{ij} = 0$ otherwise.
@@
 
-\section{Coloring perfect graph using ellipsoid method}
+\section{Coloring perfect graphs using ellipsoid method}
 \label{sec:coloringEllipsoid}
@@
 
-Given graph $G$, recall that stability number of $G$ is equal clique number of the complement of $G$. This gives us a way to compute $\alpha(G)$ for any perfect graph $G$.
+Given graph $G$, recall that the stability number of $G$ is equal the clique number of the complement of $G$. This gives us a way to compute $\alpha(G)$ for any perfect graph $G$.
 
@@
 There are at most $|V|$ maximum cardinality cliques in $G$.
-Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \Cref{alg:maxStableSet} on it.
+Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \Cref{alg:maxWeightedStableSet} on it.
 Therefore total running time is polynomial.
@@
 
-Note that coloring $C'$ uses $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$.
-We will call recursion at most $O(|V|)$ times, each step of recursion requires polynomial time.
+Note that coloring $C'$ uses $\chi(G \setminus S) = \omega(G \setminus S) = \omega(G) -1$ colors, so we will call the recursion $O(|V|)$ times, each step of recursion requires polynomial time.
 Therefore the total running time of \Cref{alg:minColoring} is polynomial.
@@
   A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
-Notice that for a graph to contain no odd hole, all three paths in a prism must have the same parity.
-A prism with all three paths odd is called an \emph{odd prism}.
+Notice that for a graph to contain no odd holes, all three paths in a prism must have the same parity.
   \label{def:prism}
@@
 
-In 2005 Maffray and Trotignon showed a coloring algorithm that colors graphs containing no odd hole, no antihole and no prism (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
+A prism with all three paths odd is called an \emph{odd prism} and a prism with all three paths even is called an \emph{even prism}.
+
+In 2005 Maffray and Trotignon showed a coloring algorithm that colors graphs containing no odd holes, no antiholes and no prisms (sometimes called Artemis graphs) in $O(|V|^4|E|)$ time \cite{Maffray2006}.
 They later improved the time complexity to $O(|V|^2|E|)$ \cite{coloringArtemis}.
-
-In 2015 Maffray showed an algorithm for coloring Berge graphs with no squares (a square is a $C_4$) and no odd prism \cite{Maff2015}.
+In 2015 Maffray showed an algorithm for coloring Berge graphs with no squares\footnote{sometimes called square-free Berge graphs} (a square is a $C_4$) and no odd prisms \cite{Maff2015}.
 
@@
 that colors any square-free Berge graphs in time of $O(|V|^9)$ \cite{coloringSquareFree}.
-Before proving strong perfect graph conjecture, a similar conjecture for square-free Berge graphs has been proven by Conforti et al.
+Before proving strong perfect graph conjecture a similar conjecture for square-free Berge graphs has been proven by Conforti et al.
 \cite{Conforti2004}.
@@
 The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement.
-The main idea is that, if square-free Berge graph $G$ is not a member of class that is simpler to analyze and color (Artemis graphs), then it must have an induced prism.
+The main idea is that, if square-free Berge graph $G$ is not a member of class that is simple to recognize and color (Artemis graphs), then it must have an induced prism.
 We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.

### 2020-09-17 paper/definitions.tex
Fixes

@@
 Similarly, for $X \subseteq V(G)$, by $N(X)$ we will denote the \emph{neighborhood} of $X$, meaning all vertices of $v \in V(G) \setminus X$, so that there is a $x \in X$, that $xv$ is an edge in $G$.
-If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{anticonnected}.
+If $xy \notin E(G)$ then $xy$ is a \emph{nonedge} and $x$ and $y$ are \emph{nonneighbors} or \emph{anticonnected}.
 
@@
 \begin{defn}[subgraph]
-  $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if and only if $V' \subseteq V$ and $E' \subseteq E$.
+  A graph $G' = (V', E')$ is a \emph{subgraph} of $G = (V, E)$ if and only if $V' \subseteq V$ and $E' \subseteq E$.
 \end{defn}
@@
 \begin{defn}[induced subgraph]
-  If $G' = (V', E')$ is a subgraph of $G$ and it contains \emph{all edges} of $G$ that join two vertices in $V'$, then $G'$ is said to be \emph{induced subgraph} of $G$ and is denoted $G[V']$.
+  If $G' = (V', E')$ is a subgraph of $G$ and it contains \emph{all edges} of $G$ that join two vertices in $V'$, then $G'$ is said to be an \emph{induced subgraph} of $G$ and is denoted $G[V']$.
 \end{defn}
@@
 
-Graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we  added any edge to $G_0$ it would stop being a path.
+Our graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we  added any edge to $G_0$ it would stop being a path.
 
@@
 
-This cycle $C$ is usually denoted by $x_1x_2\ldots x_lx_1$ or $x_1 - x_2 - \ldots - x_l - x_1$.
+This cycle $C$ is usually denoted by $x_1x_2\ldots x_lx_1$ or $x_1$-$x_2$-$\ldots$-$x_l$-$x_1$.
 $l = |E(C)|$ is the \emph{length} of the cycle $C$.
@@
 
+\begin{defn}[antipath]
+  An \emph{antipath} is a graph $G$ such that $\overline{G}$ is a path.
+\end{defn}
+
 \begin{defn}[antihole]
-  An \emph{antihole} is a subgraph of $G$ whose complement is a hole in $G$.
+  An \emph{antihole} is a graph $G$ such that $\overline{G}$ is a hole.
 \end{defn}

### 2020-09-17 paper/experiments.tex
Fixes

@@
 All of our algorithms search for an odd hole or an odd antihole and stop when find one, or a evidence of one.
-Therefore, their running times are greatest with perfect graphs on the input and we decided to use\todo{run some smart nonperfect tests} perfect graphs for our performance benchmarks.
-For every test, the vertex number were shuffled.
+Therefore, their running times are greatest with perfect graphs on the input and we decided to use perfect graphs for our performance benchmarks.
+For every test, the vertex numbers were shuffled.
 For every randomly generated graph class and for each size, we ran the tests on 10 graphs generated with different seeds and took their average running time.
+% \todo{run some smart nonperfect tests}
 
-Below, we first present our data sets then overall time results on them and lastly a plot breaking down what parts of CCLSV and GPU CCLSV constitute their overall running time.
+Below, we first present our data sets then overall time results on them and lastly a plot breaking down what parts of CCLSV and GPU CCLSV implementations constitute their overall running times.
 
@@
 
-\todo{generate perfect Erdos--Renyi graphs}
+% \todo{generate perfect Erdos--Renyi graphs}
 
@@
 \todo{implement generating perfect graphs by removing long cycles} This method of generating perfect graphs is very inefficient and we couldn't generate any graphs with $|V| \geq 20$.
-Second, those graphs favour the na\"ive algortihm, because there is very low probability of long paths to appear.
+Second, those graphs favor the na\"ive algorithm, because there is very low probability of long paths to appear.
 
-We generate random bipartite graphs by creating two equal-sized sets of vertices, and then added every possible edge between them with a probability of $p = 0.5$.
+We generate random bipartite graphs by creating two equal-sized sets of vertices, and then adding every possible edge between them with a probability of $p = 0.5$.
 In this way we can also generate line graphs of random bipartite graphs.
-This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
+This gives us graphs of varying $|V|$, so we repeated the process until we had sufficient number of graphs for each $|V|$.
 
-There are also a few interesting classes of perfect graphs that appear on a grid, or a checker board.
+There are also a few interesting classes of perfect graphs that appear on a grid, or a chessboard.
 In lattice graph, each vertex is connected to vertices that are above, below, to the left and to the right of it, if such vertices exist.
@@
 
-First, let us take a look at the performance of CCLSV algorithm.
-If we limit runtime to about two minutes, we can run it on graphs of sizes up to 40-70, depending on the type of the graph we test.
-Worth noting is the fact that there isn't that much of a variance of the running time depending on the type of graph we test on.
+First, let us take a look at the performance of the CCLSV algorithm.
+If we limit the runtime to about two minutes, we can run it on graphs of sizes up to 40-70, depending on the type of the graph we test.
+Worth noting is the fact that the CCLSV algorithm usually grows slower than the na\"ive algorithm.
+Oftentimes this is mitigated by the fact that the na\"ive algorithm works very well on smaller graphs, but it is not always the case.
+For example, for larger instances of lattice graphs and hypercube graphs the CCLSV works better than na\"ive algorithm.
+If we would want to test graphs larger than presented here, the GPU CCLSV seems to be the best solution.
+For every type of graph we tested, it finished within two minutes for graphs of $|V|$ up to about 50.
+The na\"ive algorithm is very fast for some graphs, like split graphs or random bipartite graphs, but GPU CCLSV still seems to be the best solution for larger graphs of unknown structure.
+  % there isn't that much of a variance of the running time depending on the type of graph we test on.
 This is a big advantage of CCLSV over the na\"ive algorithm, which is highly dependent on the type of input.
-On some graphs, it works almost instantenously, what is to be expected, given its method of enumerating paths.
+On some graphs, it works almost instantaneously, what is to be expected, given its method of enumerating paths.
 But on some graphs, e.g.
@@
 
-Let us turn our attention to the GPU CCLSV's results.
+Let us try to understand where the speedup of GPU CCLSV comes from.
 \Cref{plot:perfDetailed} shows breakdown of each implementation running times on a single graph of each class.
-We can clearly see that in most cases testing possible near-cleaners takes most of the running time, so the speedup by the GPU is significant.
+We can clearly see that in most cases testing possible near-cleaners takes most of the running time, so the speedup achieved by utilizing the GPU is significant.
 
@@
 When running GPU CCLSV on split graphs, quite a lot of time is spent checking simple structures.
-The biggest challange we can see is in an attempt to parallelise this is spreading work evenly across CUDA threads.
+The biggest challenge we can see is in an attempt to parallelize this is spreading work evenly across CUDA threads.
 
 % When looking at the results (\Cref{plot:perfLines}), while na\"ive algorithm's time is almost zero, we see the CCLSV running time climbing with the growth of $|V|$, with only moderate improvement by GPU CCLSV.
-Slight GPU improvement is explained by anylysis of the components of the overall time (\Cref{plot:perfDet}).
+Slight GPU improvement is explained by analysis of the components of the overall time (\Cref{plot:perfDet}).
 Testing all near cleaners takes up around half of total time, so we cannot speed up the overall time by much.
@@
 % Next, we generated a random bipartite graphs (see paragraph above) and then calculated their line graphs.
-This gives us graphs of varying $|V|$, so we repeated the process until we had sufficieng number of graphs for each $|V|$.
+This gives us graphs of varying $|V|$, so we repeated the process until we had sufficient number of graphs for each $|V|$.
 On \cref{plot:perf2Lines} we can see na\"ive algorithm being much faster on the majority of the tests, although its faster growth allows GPU CCLSV to be faster on the biggest tests.
@@
 One thing of note is, that by specifying the precision of $\vartheta$ we want to calculate to be $1/3$ the algorithm sped up  by 20-40\%.
-Also, we cache results of calculatin $\vartheta$, meaning that throught whole execution of our coloring algorithm, we only calculate $\vartheta$ for each graph once.
+Also, we cache results of calculating $\vartheta$, meaning that through whole execution of our coloring algorithm, we only calculate $\vartheta$ for each graph once.
 Our main goal of the implementation was to check if this method is still impractical, even on modern equipment.
@@
 
-We ran our tests on the data sets generated in the same way as for perfect graph recognition. We only adjusted grah sizes to get the running times of up to a couple of minutes.
+We ran our tests on the data sets generated in the same way as for perfect graph recognition. We only adjusted graph sizes to get the running times of up to a couple of minutes.
 
@@
 First, we present overall running times of the coloring algorithm (\Cref{fig:CSDPLines}) and then breakdown the running time in two parts: calculating $\vartheta$ by the CSDP library and graphs manipulations which constitute the rest of the coloring algorithm (\Cref{fig:CSDPDet}).
-We note that $\vartheta$ calculation is highly dependent on the type of the graph.
+We note that $\vartheta$ calculation is very dependent on the type of the graph.
 For our biggest tested cases of $|V| = 48$, all required calculations of $\vartheta$ take almost 7 minutes in bipartite graphs, but only 12 seconds in line graphs of bipartite graphs.
 Because CSDP library is highly optimized, it is expected that it would run much faster on some graphs.
-However, it is not clear what could we do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs or lattice graphs.
+However, it is not clear what we could do to speedup the running times on tests that CSDP is slow on, such as bipartite graphs or lattice graphs.
 A potential improvement would be to again use CUDA, this time for $\vartheta$ calculations, possibly utilizing the cuSOLVER library \cite{cusolver}.
@@
 We implemented and benchmarked two different approaches for recognizing perfect graphs.
-Both have their positives and drawbacks -- CCLSV's running times are more predictable, but on many graphs it is noticeably slower than the na\"ive algorithm.
-On the other hand, running na\"ive algorithm on a graph we don't know any properties of can lead to unbearably slow performance.
-
+Both have their positives and drawbacks -- testing big graph of unknown structure is probably better done with the CCLSV algorithm, while the na\"ive algorithm is much faster on some cases.
 The GPU CCLSV implementation shows that using parallel computation can be very profitable for this task.
-A further research can be done to see if further progress could be made, however there is no obvious improvement we can see.
+An additional research could be done to see if further progress can be made, however there is no obvious improvement we can see.
 Generating all possible near-cleaners makes a heavy use of sets (our tests indicated that if we simply list all combinations of sets $X_i$ and $N_j$, the resulting list $\mathcal{R}$ would be much bigger than necessary).
@@
 
-A GPU implementation of na\"ive algorithm could also be considered for future work.
-We have created one, but after all path-enumaration optimizations of the CPU implementation we didn't manage to achieve any noticeable speedup.
-The reason again was, that we could't spread the work evenly between CUDA threads.
+A GPU implementation of the na\"ive algorithm could also be considered for future work.
+We have created one, but after all path-enumeration optimizations of the CPU implementation we didn't manage to achieve any noticeable speedup.
+The reason again was, that we couldn't spread the work evenly between CUDA threads.
 Because some prefixes of paths require much more processing than others, this is not a trivial task and a careful study would be needed.
@@
 Maybe a better way of calculating $\vartheta$ could be found, or the GPU could again be usable for this task.
-We point to Nvidia's cuSOLVER  cite{cusolver} as a possible starting point.
+We point to Nvidia's cuSOLVER  \cite{cusolver} as a possible starting point.

### 2020-09-17 paper/implementation.tex
Fixes

@@
 A repository containing the discussed source code and tests is available under the link: \href{https://github.com/AdrianSiwiec/Perfect-Graphs}{\texttt{https://github.com/AdrianSiwiec/Perfect-Graphs}}
-\todo{make repo public and add readme on howto run, some script creating and running default tests}
 
@@
 When implementing an algorithm with the running time of $O(|V|^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is at all usable.
-We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.\todo{well..
-there's this java impl} So, to test the usability of CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm.
+We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.
+So, to test the usability of CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm.
 Let us describe it briefly.
@@
 In short: we take a path on a input, increment its last vertex until it is a neighbor of the vertex one before last.
-Then we check if generated sequence is a path.
+Then we check if generated sequence is a path -- all of its vertices are unique and there are edges only consecutive vertices share an edge.
 If it is we return it and if we run out of vertices before a path is found, we increment one before last vertex until it is a neighbor of one vertex before it, set last vertex to first and continue the process.
@@
 
-We have an array $first$ in which for each vertex is written its first neighbor on its neighbors list, and an array $next$ of size $|V(G)|^2$ where for each pair of vertices $a, b$ if $a$ and $b$ are connected, there is written a neighbor of $a$ that is next after $b$ in a neighbors list of $a$ (or a flag indicating $b$ is $a$'s last neighbor).
+We have an array $first$ in which for each vertex is written its first neighbor on its neighbors list, and an array $next$ of size $|V(G)|^2$ where for each pair of connected vertices $a, b$, there is written a neighbor of $a$ that is next after $b$ in a neighbors list of $a$ (or a flag indicating $b$ is $a$'s last neighbor).
 Then, say our input is a path $v = v_1, \ldots v_k$.
@@
 
-This simple change in data structure design gave us a speedup of overall running time of our na\"ive algorithm in the range of about 5x.
+This simple change in the data structure design gave us a speedup of overall running time of our na\"ive algorithm in the range of about 5x.
 
@@
 A theoretically optimal solution in general would be to have a hashing set of vertices.
-For each vertex in a path candidate, we check if it is already in a set.
+For each vertex in a path candidate, we check if it is already in the set.
 If it is, return that not all vertices are unique, else add it to the set.
@@
 First, we don't need a hashing set.
-We can have an array of bools, of size $|V(G)|$ and mark vertices of a path there.
+We can have an array of bools, of size $|V(G)|$ and mark vertices of the path there.
 Paths are usually much shorter than $|V(G)|$, but we operate on small graphs, so we can afford this.
@@
 We use the same algorithm for generating starting vertices for a possible $\T_2$ and $\T_3$.
-Before optimizing path enumeration algorithm, all calls of $areUnique$ alone took abour 70\% of total running time of the CCLSV algorithm.
+Before optimizing path enumeration algorithm, all calls of $areUnique$ alone took about 70\% of total running time of the CCLSV algorithm.
 After optimizing $areUnique$, path enumeration still took more than 50\% of total running time.
-After all optimizations it is almost unnoticable.
+After all optimizations it is almost unnoticeable.
 
@@
 Callgrind is a profiling tool that records the call history and event counts (data reads, cache misses etc.) of a program and presents it as a call-graph.
-It is then possible to visualise this, we used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
+It is then possible to visualize this, we used a tool \emph{gprof2dot} \cite{gprof2dot} to generate visual call graphs from callgrind's output.
 
-Before any optimizatios, a major part of Berge recognition algorithm was being spent on enumerating all possible paths of given length -- this is done either to find a simple structure or check a possible near cleaner for an amenable odd hole.
-Therefore optimizations of the path enumerating algorithm were also helpful in speeding up CCLSV implementation.
+Before any optimizations, a major part of Berge recognition algorithm was being spent on enumerating all possible paths of given length -- this is done either to find a simple forbidden structure or to check a possible near cleaner for an amenable odd hole.
+Therefore optimizations of the path enumerating algorithm were also helpful in speeding up the CCLSV implementation.
 
@@
 It is a data structure to represent a set of bits, that also allows for fast bitwise operators that one can apply to builtin integers.
-At the very end of \Cref{alg:listNearCleaners} a set $\mathcal{R}$ is constructed, which is an union of all possible unions of pairs $X_i$ and $N_j$.
+At the very end of \Cref{alg:listNearCleaners} a set $\mathcal{R}$ is constructed, which is a set of all possible unions of pairs $X_i$ and $N_j$.
 We used \texttt{dynamic\_bitset} to represent each of the sets $X_i$ and $N_j$, and the elements of the set $\mathcal{R}$.
-This significantly speeds up the operation of union of two sets (line \ref{line:listNCcalcR}).
+This significantly speeds up the calculation of $\mathcal{R}$ (line \ref{line:listNCcalcR}).
 With this modification, the speedup of \Cref{alg:listNearCleaners} was about 20\%.
@@
 After these optimizations, checking each potential near-cleaner by \Cref{alg:testNearCleaner} is by far the biggest bottleneck of the CCLSV algorithm.
-We didn't find any major optimizations there, but the \Cref{alg:testNearCleaner} has a good potential for parrallelization, which we explore in \Cref{sec:CUDA}.
+We didn't find any major optimizations there, but the \Cref{alg:testNearCleaner} has a good potential for parallelization, which we explore in \Cref{sec:CUDA}.
 
@@
 
-CUDA is a parrallel computing platform model created by Nvidia and executed on Nvidia GPUs.
+CUDA is a parallel computing platform model created by Nvidia and executed on Nvidia GPUs.
 It allows to run a program  by many CUDA threads at once.
-Although usually described by the the PRAM models, implementing PRAM algorithm in CUDA architecture is not as straightforward as implementing a RAM algorith on a CPU.
+Although usually described by the the PRAM models, implementing PRAM algorithms in CUDA architecture is not as straightforward as implementing RAM algorithms on a CPU.
 Some of the causes are: synchronization between threads is very costly, there are multiple memory models to choose from, threads run divided in blocks and it is possible to efficiently share memory within blocks and copying memory from and back to CPU suffers from a large latency.
@@
 On one hand the graphs we are working on are small and our time complexity so large that a speedup from massively parallel architecture could be profitable.
-On the other hand, the algorithm is complex and not easy to parallelise.
-Therefore we decided to analyze the  CCLSV algorithm and parrallelize parts that would benefit from it the most.
+On the other hand, the algorithm is complex and not easy to parallelize.
+Therefore we decided to analyze the  CCLSV algorithm and parallelize parts that would benefit from it the most.
 
@@
 It calculates array $R$ of shortest paths, then for each 3-vertex path and an additional vertex it does $O(1)$ checks to see if they along with two paths from $R$ give us an odd hole.
-We will parallelise the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd}.
+We will parallelize the work after calculating $R$, that is, lines \ref{line:cudaStart}-\ref{line:cudaEnd}.
 Let us notice, that for all $X$s, all 3-vertex paths enumerated in line \ref{line:3vertex} are the same.
-We calculate them beforehand, then each CUDA thread receives one 3-vertex path $x_1 - x_2 - x_3$ and an additional vertex $y_1$ and performs the required checks in lines \ref{line:cudaWorkStard}-\ref{line:cudaWorkEnd}.
-This is almost perfect scenario for the GPU -- we do a simple SIMD work in parallel, without a lot scattered memory access.
+We calculate them beforehand, then each CUDA thread receives one 3-vertex path $x_1$-$x_2$-$x_3$ and an additional vertex $y_1$ and performs the required checks in lines \ref{line:cudaWorkStard}-\ref{line:cudaWorkEnd}.
+This is almost perfect scenario for the GPU -- we do a simple SIMD\footnote{Single Instruction Multiple Data, meaning performing same operations on multiple data points in parallel} work in parallel, without a lot scattered memory access.
 
-The part of the CCLSV implemented on the GPU achieved speedup of up to 15x. Which gave us a speedup of up to 9x for overall CCLSV algorithm, depending on a class of graph we benchmark on.
+The part of the CCLSV implemented on the GPU achieved speedup of up to 15x. This gave us a speedup of up to 9x for overall CCLSV algorithm, depending on a class of graph we benchmark on.

### 2020-09-17 paper/perfectGraphs.tex
Fixes

@@
 Bipartite graphs are perfect, since we can color them with two colors.
-From the theorem of König we get that line graphs of bipartite graphs are also perfect \cite{Knig1916, GC03}.
+From the theorem of König \cite{Knig1916} we get that line graphs of bipartite graphs are also perfect \cite{GC03}.
 From the perfect graph theorem (\Cref{thm:pgt}) it follows that complements of bipartite graphs and complement of line graphs of bipartite graphs are also perfect.
@@
 \subsubsection{2-join, Homogeneous Pair and Skew Partition}
-A graph $G$ has a \emph{2-join} if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$.
+A graph $G$ has a \emph{2-join} if and only if its vertices can be partitioned into sets $V_1$, $V_2$, each of size at least three, and there are nonempty disjoint subsets $A_1, B_1 \subseteq V_1$ and $A_2, B_2 \subseteq V_2$, such that all vertices of $A_1$ are adjacent to all vertices of $A_2$, all vertices of $B_1$ are adjacent to all vertices of $B_2$, and these are the only edges between $V_1$ and $V_2$.
 When a graph $G$ has a 2-join, it can be decomposed onto two smaller graphs $G_1$, $G_2$, so that $G$ is perfect if and only if $G_1$ and $G_2$ are perfect \cite{Cornujols1985}.
@@
 The proof of \Cref{thm:spgt} is a consequence of the \emph{Decomposition theorem}:
+
 \begin{theorem}[Decomposition theorem, stated as Theorem 4.2 of \cite{GC03}]
@@
 
-The following is based on the paper by \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}. We will not provide full proof of its correctness, but we will aim to show the intuition behind the algorithm.
+The following section is based on the paper by \citeauthor{MC05} \citetitle*[]{MC05} \cite{MC05}.
+We will not provide full proof of its correctness, but we will aim to show the intuition behind the algorithm.
 
@@
 Else, we check if there is a near-cleaner for a shortest odd hole or for shortest odd antihole (\Cref{AmenableHoles}).
+If we find no such near-cleaners, then, as we will see, the graph is Berge.
 
@@
 
-\begin{alg}[Test if $G$ contains a Pyramid]
+\begin{alg}[Test if $G$ contains a pyramid]
 	\label{alg:testPyramid}
@@
 					\mIf{$s_1 = b_1$ \label{line:ShortestPathsStart}} \Comment{calculate all possible $P_1$ paths}
-						\ls $P_1(b_1) \gets$ the one-vertex path with vertex $b_1$
+						\ls $P_1(b_1) \gets$ the one-vertex path $b_1$
 						\ls \algorithmicforeach ~$m \in M$ \algorithmicdo~ $P_1(m) \gets$ \textsc{undefined}
@@
 							}
-								\ls $P_1(m) \gets s_1-S_1(m)-m-T_1(m)-b_1$
+								\ls $P_1(m) \gets s_1$-$S_1(m)$-$m$-$T_1(m)$-$b_1$
 							\mElse
@@
 						\lsx $P_1(m_1)$ or have a neighbor in $P_1(m_1)$
-						\lsx color all other vertices white.
+						\ls color all other vertices white.
 						\mForEach{$m_2 \in M \cup \{b_2\}$}
@@
 				\mForEach{triple $m_1, m_2, m_3$ such that $m_i \in M \cup \{b_i\}$} \label{line:m1m2m3}
-					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j)$ is a good $(i, j)$-pair}
+					\mIf{$\forall_{1\leq i < j \leq 3}$: $(m_i, m_j) \in good\_pairs_{i, 2}$}
 						\ls \RETURN \TRUE \label{line:pyramidTrue}
@@
 
-Now we will proove the time complexity.
+Now we will prove the time complexity.
 
@@
 This gives us a time of $O(|V|^7)$.
-We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole Berge recognition algorithm takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
+We could speed it up to $O(|V|^6)$ with more careful algorithm (see Algorithm 3.1 of \cite{MC05}), but since whole Berge recognition algorithm takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
 
@@
 
+When graphs $G$ and $\overline{G}$ contain no pyramids, no jewels and no configurations of type $\T_1, \T_2$ or $\T_3$, we will say that graph $G$ contains no \emph{simple forbidden structures}.
+
 \subsection{Amenable holes.}
 \label{AmenableHoles}
-As we will see (\Cref{thm:amenableHoles}), if graphs $G$ and $\overline{G}$ contain no jewels, pyramids or configurations of type $\T_1, \T_2$ or $\T_3$, then every shortest odd hole in $G$ or $\overline{G}$ will have a special structure and we will call it amenable.
+As we will see (\Cref{thm:amenableHoles}), if graph $G$ contains no simple forbidden structures, then every shortest odd hole in $G$ or $\overline{G}$ will have a special structure and we will call it amenable.
 This fact will help us determine if $G$ or $\overline{G}$ contain an odd hole.
@@
 
-Let us notice, that if $X$ is a cleaner for $C$, then $C$ is a clean hole in $G \setminus X$.
+\noindent Let us notice, that if $X$ is a cleaner for $C$, then $C$ is a clean hole in $G \setminus X$.
 
@@
 \Cref{fig:amenableOddHole} shows an example of an amenable odd hole $C = v_1$-$\ldots$-$v_7$-$v_1$.
-It is not a clean hole -- vertices $v_8$ and $v_9$ are $C$-major, and $\{v_8, v_9, v_1, v_2, v_3\}$ is an axample of a near-cleaner for $C$.
+It is not a clean hole -- vertices $v_8$ and $v_9$ are $C$-major, and $\{v_8, v_9, v_1, v_2, v_3\}$ is an example of a near-cleaner for $C$.
 \Cref{fig:notAmenableHole} shows an odd hole $C = v_1$-$\ldots$-$v_7$-$v_1$ that is not amenable, because there is no $\{v_8, v_9\}$-complete edge in $C$.
@@
 	\label{thm:amenableHoles}
-	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest odd hole in $G$ is amenable.
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no pyramids, no jewels and no configurations of types $\T_1, \T_2$ or $\T_3$. Then every shortest odd hole in $G$ is amenable.
 	% \TODO{Any ideas on what else to say here? List all 9 steps?}
@@
 	\label{alg:listNearCleaners}
-	Input: A graph $G$.
+	Input: A graph $G$ containing no simple forbidden structures.
 
@@
 	\label{thm:92}
-	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no pyramids, no jewels and no configurations of types $\T_1, \T_2$ or $\T_3$.
 Then the result of the \Cref{alg:listNearCleaners} on the graph $G$ is a set $\mathcal{R}$, such that for every shortest amenable hole $C$, there is a near-cleaner for $C$ in $\mathcal{R}$.
@@
 	\label{alg:testNearCleaner}
-	Input: A graph $G$ containing no simple forbidden structure, and a subset $X \subseteq V(G)$.
+	Input: A graph $G$ containing no simple forbidden structures, and a subset $X \subseteq V(G)$.
 
@@
 			\mForEach{$y_1 \in V(G) \setminus X$} \label{line:cudaStart}
-				\mForEach{3-vertex path $x_1-x_2-x_3$ of $G\setminus y_1$} \label{line:3vertex}
+				\mForEach{3-vertex path $x_1$-$x_2$-$x_3$ of $G\setminus y_1$} \label{line:3vertex}
 					\mIf{$R(x_1, y_1), R(x_2, y_2)$ both exist} \label{line:cudaWorkStard}
@@
 	\label{thm:testNCWorks}
-	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$.
+	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no pyramids, no jewels and no configurations of types $\T_1, \T_2$ or $\T_3$.
 Let $X$ be a subset of $V(G)$.
@@
 In lines \ref{line:testXStart}-\ref{line:testXEnd} we test each $X \in \mathcal{R}$ and if an odd hole is reported, then by \Cref{thm:testNCWorks} $G$ is not Berge.
-If for all $X \in \mathcal{R}$ an odd hole is not reported, then by \Cref{thm:amenableHoles}, \Cref{thm:92} and \Cref{thm:testNCWorks} there is no odd hole in $G$.
+If for all $X \in \mathcal{R}$ no odd holes are reported, then by \Cref{thm:amenableHoles}, \Cref{thm:92} and \Cref{thm:testNCWorks} there are no odd holes in $G$.
 We run the same checks on $\overline{G}$ and if again we do not detect an odd hole, then $G$ is Berge and by \Cref{thm:spgt} $G$ is perfect.

### 2020-09-17 paper/coloringBergeGraphs.tex
Fixes

@@
 $$\sum\limits_{i\in S}(e_1^\intercal v_i)^2 \leq \sum\limits_{i \in S'}(e_1^\intercal v_i)^2 \leq |e_1|^2 = 1$$
-\todo{todo}
 Each term on the left hand side is equal to $5^{-k/4}$, so the left hand side is equal to $|S|5^{-k/2}$, and so $|S| \leq 5^{k/2}$.

### 2020-09-17 code/Java2/test/src/main/java/hello/HelloJGraphT.java
Java JGraphT test

@@ -1,0 +1,148 @@
+/*
+ * (C) Copyright 2003-2020, by Barak Naveh and Contributors.
+ *
+ * JGraphT : a free Java graph-theory library
+ *
+ * See the CONTRIBUTORS.md file distributed with this work for additional
+ * information regarding copyright ownership.
+ *
+ * This program and the accompanying materials are made available under the
+ * terms of the Eclipse Public License 2.0 which is available at
+ * http://www.eclipse.org/legal/epl-2.0, or the
+ * GNU Lesser General Public License v2.1 or later
+ * which is available at
+ * http://www.gnu.org/licenses/old-licenses/lgpl-2.1-standalone.html.
+ *
+ * SPDX-License-Identifier: EPL-2.0 OR LGPL-2.1-or-later
+ */
+package hello;
+
+
+import org.jgrapht.*;
+import org.jgrapht.alg.cycle.BergeGraphInspector;
+import org.jgrapht.graph.*;
+//import org.jgrapht.nio.*;
+//import org.jgrapht.nio.dot.*;
+import org.jgrapht.traverse.*;
+
+import java.io.*;
+import java.net.*;
+import java.rmi.server.ExportException;
+import java.util.*;
+
+
+/**
+ * A simple introduction to using JGraphT.
+ *
+ * @author Barak Naveh
+ */
+public final class HelloJGraphT {
+    private HelloJGraphT() {
+    } // ensure non-instantiability.
+
+    /**
+     * The starting point for the demo.
+     *
+     * @param args ignored.
+     * @throws URISyntaxException if invalid URI is constructed.
+     * @throws ExportException    if graph cannot be exported.
+     */
+    public static void main(String[] args)
+            throws URISyntaxException,
+            IOException {
+        BufferedReader reader;
+        ArrayList<Graph> graphs = new ArrayList<>();
+        String filePath = "/home/pierre/Documents/Studia/Magisterium/code/test/cuPerfTest/tests/java.t.in";
+        reader = new BufferedReader(new FileReader(filePath));
+        String line = reader.readLine();
+
+        System.out.println("Hello!");
+
+        while (line != null) {
+            if (line.trim().length() == 0) {
+                line = reader.readLine();
+                continue;
+            }
+            int n = Integer.parseInt(line);
+            String s = "";
+            for (int i = 0; i < n; i++) {
+                line = reader.readLine();
+                s = s + line;
+            }
[…]

### 2020-09-17 code/test/generate/generate.cpp

@@ -10,11 +10,11 @@
 int main() {
   srand(time(0));
 
-  int minN = 18;
-  int maxN = 36;
-  int step = 6;
+  int minN = 10;
+  int maxN = 16;
+  int step = 1;
 
-  for (int i = 0; i < 1; i++) {
+  for (int i = 0; i < 10; i++) {
     set<int> done;
 
     while (done.size() < (maxN - minN + step) / step) {

### 2020-09-17 code/test/plot.py
Java plot

@@ -88,6 +88,7 @@ algo_colors = {
     "CUDA Naive": "#ff0000",
     "Naive": "#00ff00",
     "CSDP Color": "#377eb8",
+    "JAVA": "#d62728",
 }
 algo_markers = {
     "Cuda Perfect": ".",
@@ -95,6 +96,7 @@ algo_markers = {
     "CUDA Naive": "o",
     "Naive": "+",
     "CSDP Color": ".",
+    "JAVA": ".",
 }
 
 algo_labels = {
@@ -103,6 +105,7 @@ algo_labels = {
     "CUDA Naive": 'GPU Na"ive',
     "Naive": "Naïve",
     "CSDP Color": "Color",
+    "JAVA": "JGraphT"
 }
 
 algo_field_labels = {
@@ -140,6 +143,7 @@ sizes_in_inches = {
     "allGraphs": (10, 25),
     "wideDetailed": (4.77, 7.1),
     "regular_small": (2.38, 1.5),
+    # "regular_small": (3, 2),
     "wideDetailed_small": (2.38, 1.5),
 }
 # sizes_in_inches = {"regular": (5, 3), "wide": (8, 3)}
@@ -453,6 +457,22 @@ experiments = [
         "out_prefix": "color",
         # "ylim": (0, 1),
     },
+    {
+        "restrictions": [(csv_algo, "JAVA")],
+        "x_param": csv_N,
+        "x_show": csv_N,
+        "type": "lines",
+        "size": sizes_in_inches["regular_small"],
+        "y_param": csv_overall,
+        "ylog": True,
+        "yformatter": func_formatter,
+        "x_label": label_lca_N,
+        # "x_ticks": [18, 24, 30, 36, 42, 48],
+        # "x_ticks_labels": ["$6\\times 3$", "", "$6\\times 5$", "", "$6\\times 7$", ""],
+        "y_label": label_time_overall_s,
+        "out_prefix": "java",
+        "ylim": (1, 250),
+    },
 ]
 
 if len(sys.argv) < 2:
@@ -498,12 +518,8 @@ for i_exp, experiment in enumerate(experiments):
     # Filter data we should plot in current image
     for row in csv_file:
         isOk = True
-        for res_name, res_val in experiment[
-            "restrictions"
-        ]:  # process restrictions to plot only what we want
-            if isinstance(
-                res_val, str
-            ):  # for a string, restriction should be a substring of a field in a row
+        for res_name, res_val in experiment["restrictions"]:
+            if isinstance(res_val, str):
[…]

### 2020-09-17 paper/experiments.tex
Add paragraph on JgraphT

@@
 
+\subsubsection{JGraphT implementation}
+
+% \begin{wrapfigure}{r}{0.5\textwidth}
+%   \centering\
+%   \input{plots/java.java.t.in.out.csv.lines.pgf}
+%   \caption{JGraphT Berge recognition performance}
+%   \label{plot:jgrapht}
+% \end{wrapfigure}
+\begin{figure}
+  \centering
+  \input{plots/java.java.t.in.out.csv.lines.pgf}
+  \caption{JGraphT Berge recognition performance}
+  \label{plot:jgrapht}
+\end{figure}
+
+JGraphT \cite{jgrapht} is an open-source Java library of graph data structures and algorithms.
+It provides many graph algorithms, such as bipartite and general matchings, flows and colorings.
+In a research paper about it \cite{jgraphtPaper}, the library is described as a robust and performance-driven graph library.
+It is used in many commercial and open-source projects, including Apache Cassandra database, Apache Storm and Graal JVM.
+
+The Berge recognition algorithm implemented there is exactly the CCLSV algorithm, but during our tests the performance was much worse when compared to our implementations.
+See \Cref{plot:jgrapht} for a overall running times on line graphs of random bipartite graphs.
+After looking at the source code of the Berge recognition algorithm, we think that the poor performance may be caused by the lack of optimizations we talked about in Sections \ref{sec:secnaive} and \ref{sec:Optimizations} -- the implementation is rather straightforward and unoptimized.
+For example in many places it uses HashSets when arrays would suffice.
+
 \section{Coloring Berge graphs}
@@
 
+All of our implementations are significantly faster than the only other perfect graph recognition implementation we found.
+
 We also implemented algorithm for coloring perfect graphs.

### 2020-09-17 paper/implementation.tex
Add paragraph on JgraphT

@@
 \section{Berge graphs recognition: na\"ive approach}
+\label{sec:secnaive}
 When implementing an algorithm with the running time of $O(|V|^9)$ (especially one as complex as CCLSV), one of the first questions that pop up is whether this algorithm is at all usable.
-We couldn't find any existing programs that test whether the graph is perfect, be it an implementation of CCLSV, or a na\"ive approach.
-So, to test the usability of CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm.
+We found only one existing attempt at implementing a perfect graph recognition algorithm, but it suffers from a very poor performance (see \Cref{plot:jgrapht}).
+So, to test the usability of the CCLSV implementation, we measured it against our own na\"ive perfect recognition algorithm.
 Let us describe it briefly.

### 2020-09-17 code/test/plot.py

@@ -143,6 +143,7 @@ sizes_in_inches = {
     "allGraphs": (10, 25),
     "wideDetailed": (4.77, 7.1),
     "regular_small": (2.38, 1.5),
+    "regular_small2": (3.17, 2),
     # "regular_small": (3, 2),
     "wideDetailed_small": (2.38, 1.5),
 }
@@ -462,7 +463,7 @@ experiments = [
         "x_param": csv_N,
         "x_show": csv_N,
         "type": "lines",
-        "size": sizes_in_inches["regular_small"],
+        "size": sizes_in_inches["regular_small2"],
         "y_param": csv_overall,
         "ylog": True,
         "yformatter": func_formatter,

### 2020-09-21 paper/appendA.tex
Overweekend fixes

@@
 The work is not intended to be self-contained and will be impossible to fully understand without \cite{coloringSquareFree} at hand.
-But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a major step required before an attempt to implement it would be made.
-For some, looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.
+But when reading \cite{coloringSquareFree}, one may pose a question of what sort of an algorithm emerges from it, and we believe the pseudocode below gives a first overview and is a step required before an attempt to implement it would be made.
+Looking at the pseudocode could provide a better way to analyze and possibly simplify the algorithm.
 
@@
 
-Recall, that a prism (\cref{def:prism}) is a graph consisting of two disjoint triangles and two disjoint paths between them.
+\begin{defnTwo}[prism]
+  A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
+\end{defnTwo}
+
+Notice that for a graph to contain no odd holes, all three paths in a prism must have the same parity.
+A prism with all three paths odd is called an \emph{odd prism} and a prism with all three paths even is called an \emph{even prism}.
 
 \begin{defnTwo}[Artemis graph]
-  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd hole, no antihole of length at least five, and no prism.
+  A graph $G$ is an \emph{Artemis graph} if and only if it contains no odd holes, no antiholes of length at least five, and no prisms.
 \end{defnTwo}
@@
   In a graph $G$, subdividing an edge $uv \in E(G)$ means removing the edge $uv$ and adding a new vertex $w$ and two new edges $uw, wv$.
-Starting with a graph $G$, the effect of repeatedly subdividing edges prioduces a graph $H$ called a \emph{subdivision of $G$}.
+Starting with a graph $G$, the effect of repeatedly subdividing edges produces a graph $H$ called a \emph{subdivision of $G$}.
 Note that $V(G) \subseteq V(H)$.
@@
 
-The algorithm we present is derived from contructive proof of the following two theorems.
+The algorithm we present is derived from a constructive proof of the following two theorems.
 
@@
 \begin{defnTwo}[major neighbor of a prism]
-  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of pritm $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
+  A vertex $v \in V(G) \setminus K$ is a \emph{major neighbor} of prism $K$ is and only if it has at least two neighbors in $\{a_1, a_2, a_3\}$ and at least two neighbors in $\{b_1, b_2, b_3\}$.
   \label{def:majorNeiOfPrism}
@@
 \begin{theorem}[Lemma 3.3 of \cite{coloringSquareFree}]
-  Let $G$ be a berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$.
+  Let $G$ be a Berge graph, let $H$ be a hyperprism in $G$ and let $M$ be the set of major neighbors of $H$ in $G$.
 Let $F$ be a component of $V(G) \setminus(V(H) \cup M)$, such that the set of attachments of $F$ in $H$ is not local.
@@
 
-\begin{defnTwo}[major vertex w.r.t. a strip system]
+\begin{defnTwo}[major vertex w.r.t.~a strip system]
   A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) the strip system if and only if the set of its neighbors saturates the strip system.
@@
 
-\begin{defnTwo}[major vertex w.r.t. some choice of rungs]
+\begin{defnTwo}[major vertex w.r.t.~some choice of rungs]
   A vertex $v \in V(G) \setminus V(S, N)$  is \emph{major} with respect to (w.r.t.) some choice of rungs if and only if the $J$-strip system defined by this choice of rungs is saturated by the set of neighbors of $v$.
@@
 
-\begin{defnTwo}[subset local w.r.t. a strip system]
+\begin{defnTwo}[subset local w.r.t.~a strip system]
   A subset $X \subseteq V(S, N)$ is \emph{local} with respect to (w.r.t.) the strip system, if and only if either $X \subseteq N_v$ for some $v \in V(J)$ or $X \subseteq S_{uv}$ for some $uv \in E(J)$.
@@
 	\item $a \ntriangleleft X$, when $a$ is a vertex and $X$ is a set of vertices -- $a$ is anticomplete to $X$,
-	\item $X \setComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is complete to $Y$,
-	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of vertices -- $X$ is anticomplete to $Y$,
+	\item $X \setComplete Y$, when $X$ and $Y$ are sets of vertices -- $X$ is complete to $Y$,
+	\item $X \setAntiComplete Y$, when $X$ and $Y$ are sets of vertices -- $X$ is anticomplete to $Y$,
 	\item $[n]$  -- $\{1, \ldots, n\}$,

### 2020-09-21 paper/coloringAppendix/algI.tex
Style fixes
Overweekend fixes

@@
   $H \gets$ an induced prism of $G$ \tcp*{\Cref{thm:getPrism}}
-  \TODO{do we get $H$ ready from A.1.1?}
 
@@
       $M \gets \{v: v$ is a major neighbor of H$\}$\;
-      \TODO{how do we get M?}
 
@@
         $(S, N) \gets$ a $J$-strip system\;
-        \TODO{how?}
       }\Else{
@@
       $J', (S', N') \gets$ \textsc{Growing-J-Strip}$(G, J, (S, N))$\;
-      $M \gets$ a set of major vertives w.r.t. $(S, N)$\;
+      $M \gets$ a set of major vertices w.r.t. $(S, N)$\;
       \If{$J', (S', N')$ is a special $K_4$ system}{
@@
   \Return \textsc{Color-Good-Partition}$(G, P)$\;
+  \vspace{-5cm}
 \end{mynameforalgorithm}

### 2020-09-21 paper/coloringAppendix/algVII.tex
Overweekend fixes

@@
     $(S, N)$ -- a $J$-strip system \newline
-    $m \in G \setminus (S, N)$ that is major w.r.t. some choice of rungs of $(S, N)$ but not w.r.t. $(S, N)$
+    $m \in G \setminus (S, N)$ that is major w.r.t.~some choice of rungs of $(S, N)$ but not w.r.t. $(S, N)$
   }
@@
   $X \gets N(m)$\;
-  $M \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. $(S,N)$\;
-  $M^* \gets$ vertices of $G\setminus V(S,N)$ major w.r.t. some choice of rungs\;
-  \Assert[SPGT 8.4]{$J = K_4$}
+  $M \gets$ vertices of $G\setminus V(S,N)$ major w.r.t.~$(S,N)$\;
+  $M^* \gets$ vertices of $G\setminus V(S,N)$ major w.r.t.~some choice of rungs\;
+  \Assert[\cite{MC06} 8.4]{$J = K_4$}
   $V(J) \gets [4]$\;
@@
   \Assert[6.3.(7)]{Every $34$-rung has non-zero even length}
-  $\forall_{i \neq j \in [4]} O_{ij} \gets$ set of vertices that are not major w.r.t $L(H')$ and
+  $\forall_{i \neq j \in [4]} O_{ij} \gets$ set of vertices that are not major w.r.t~$L(H')$ and
   are complete to $(T'_i \cup T'_j) \setminus R'_{ij}$\;

### 2020-09-21 paper/coloringAppendix/algVIa.tex
Algos and KT fixes
Style fixes
Overweekend fixes

@@
-\subsubsection{Notes}
-\begin{itemize}
-	\item $T_{uv} := N_u \cap N_v$
-	\item Strip $S_{uv}$ is \emph{rich} iff $S_{uv} \setminus T_{uv} \neq \emptyset$
-\end{itemize}
-
-\begin{algorithm}
+\begin{mynameforalgorithm}
 	\SetKwFunction{GoodPartitionJStrip}{\textsc{Good-Partition-From-J-Strip-System}}
@@
 		$(S, N)$ -- a maximal $J$-strip system \newline
-		$M$ -- a set of major vertices w.r.t. $(S, N)$
+		$M$ -- a set of major vertices w.r.t.~$(S, N)$
 	}
@@
 	\Assert{$M \cup T_{uv}$ is a clique}
+	Strip $S_{uv}$ is \emph{rich} if and only if $S_{uv} \setminus T_{uv} \neq \emptyset$\;
 	\If{$\exists S_{uv}$ -- a rich strip in $(S,N)$} {
@@
 	}
-\end{algorithm}
+\vspace{-1cm}
+\end{mynameforalgorithm}

### 2020-09-21 paper/coloringBergeGraphs.tex
Overweekend fixes

@@
 
-There has been much progress on the quest of finding an algorithm coloring perfect graphs, without the use of ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
+There has been much progress on the quest of finding an algorithm coloring perfect graphs, without the use of the ellipsoid method (see \Cref{sec:classicalColoring}), however there is still no known polynomial combinatorial algorithm to do this.
 
@@
 
-From (\ref{en:ei2}) it follows that diagonal entries of any positive semidefinite matrix are nonnegative and the sum of two positive semidefinite matrices is positive semidefinite.
+From (\ref{en:ei2}) it follows that diagonal entries of any positive semidefinite matrix are nonnegative and that the sum of two positive semidefinite matrices is positive semidefinite.
 
@@
 
-Now, we can define a \emph{semidefinite program} to be an optimization problem of the following form:
-
+\begin{defn}[semidefinite program]
+  Let $A_1, \ldots, A_n, B$ be given symmetric $m \times m$ matrices and be $c \in \mathbb{R}^n$ a given vector. A \emph{semidefinite program} is an optimization problem of the following form:
   \begin{equation*}
@@
   \end{equation*}
-Here $A_1, \ldots, A_n, B$ are given symmetric $m \times m$ matrices and $c \in \mathbb{R}^n$ is a given vector.
   Any choice of the values $x_i$ that satisfies the given constraint is called a \emph{feasible solution}.
+\end{defn}
 
@@
 Let us recall, that an orthogonal representation of a graph $G = (V, E)$ is a labeling $u: V \rightarrow \mathbb{R}^d$ for some $d$, such that $u_i^\intercal u_j = 0$ for all anticonnected vertices $i, j$.
-An \emph{orthonormal} representation is an orthogonal representation with $|u_i| = 1$ for all $i$.
 The \emph{angle} of an orthogonal representation is the smallest half-angle of a rotational cone containing the representing vectors.
@@
   \begin{equation*}
-    \begin{array}{ll@{}ll}
-      \text{minimize}   & t      &                                              \\
-      \text{subject to} & Y      & \succeq 0                                    \\
-                        & Y_{ij} & = -1      & (\forall~ij \in E(\overline{G})) \\
-                        & Y_{ii} & = t - 1                                      \\
+    \begin{array}{l@{}rlll}
+      \text{minimize~~}   & t      &                                              \\
+      \text{subject to~~} & Y      & \succeq & 0                                    \\
+                        & Y_{ij} & = & -1      & (\forall~ij \in E(\overline{G})) \\
+                        & Y_{ii} & = & t - 1                                      \\
     \end{array}
@@
 
-\section{Coloring perfect graphs using ellipsoid method}
+\section{Coloring perfect graphs using an ellipsoid method}
 \label{sec:coloringEllipsoid}
@@
 published an ellipsoid-method-based polynomial algorithm for coloring perfect graphs, a combinatorial algorithm for doing the same has been sought.
-As of yet, it is not known, although there is much progress in the field.
+As of yet, there isn't one, although there is much progress in the field.
 
-\begin{defn}[prism]
 A \emph{prism} is a graph consisting of two disjoint triangles and two disjoint paths between them.
 Notice that for a graph to contain no odd holes, all three paths in a prism must have the same parity.
-  \label{def:prism}
-\end{defn}
-
 A prism with all three paths odd is called an \emph{odd prism} and a prism with all three paths even is called an \emph{even prism}.
@@
 \cite{Conforti2004}.
-During one of her lectures, Maria Chudnovsky expressed hope that discovery of full algorithm for coloring Berge graphs might follow a similar pattern.
+During one of her lectures, Maria Chudnovsky expressed hope that discovery of a full algorithm for coloring Berge graphs might follow a similar pattern.
 
@@
 We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.
-The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper is far from straightforward.
+The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper isn't straightforward.
 We provide its pseudocode in the Appendix A.

### 2020-09-21 paper/definitions.tex
Overweekend fixes

@@
 We will only consider finite graphs, that is, $V$ and $E$ are always finite.
-If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set}.
+If $G$ is a graph, then $V = V(G)$ is the \emph{vertex set} of $G$, and $E = E(G)$ is the \emph{edge set} of $G$.
 When the context of $G$ is clear we will use $V$ and $E$ to denote its vertex and edge set.
@@
 
-Given a graph $G = (V, E)$ and a set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.
+Given a graph $G = (V, E)$ and a set $X \subseteq V$ by $G\setminus X$ we will denote the induced subgraph $G[V\setminus X]$.
 
@@
 
-Our graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we  added any edge to $G_0$ it would stop being a path.
+Our graph $G_0$ is a path of length 3, with the inside $G_0^* = \{v_2, v_3\}$. If we added any edge to the $G_0$ it would stop being a path.
 
@@
 \begin{defn}[clique]
-  A \emph{complete graph} or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is, every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
+  A \emph{complete graph} or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is, every two vertices are connected.
 \end{defn}
 
+We will denote the clique on $n$ vertices as $K_n$.
+
 \begin{defn}[clique number]
-  A \emph{clique number} of a graph $G$, denoted as $\omega(G)$, is a cardinality of its largest induced clique.
+  The \emph{clique number} of a graph $G$, denoted as $\omega(G)$, is a cardinality of its largest induced clique.
 \end{defn}
@@
 \begin{defn}[stability number]
-  A \emph{stability number} of a graph $G$, denoted as $\alpha(G)$, is a cardinality of its largest induced stable set.
+  The \emph{stability number} of a graph $G$, denoted as $\alpha(G)$, is a cardinality of its largest induced stable set.
 \end{defn}
@@
 \begin{defn}[chromatic number]
-  A \emph{chromatic number} of a graph $G$, denoted as $\chi(G)$, is a smallest natural number $k$, for which there exists a $k$-coloring of $G$.
+  The \emph{chromatic number} of a graph $G$, denoted as $\chi(G)$, is a smallest natural number $k$, for which there exists a $k$-coloring of $G$.
 \end{defn}

### 2020-09-21 paper/experiments.tex
Overweekend fixes

@@
 When running GPU CCLSV on split graphs, quite a lot of time is spent checking simple structures.
-The biggest challenge we can see is in an attempt to parallelize this is spreading work evenly across CUDA threads.
+The biggest challenge we can see is in an attempt to parallelize this is spreading the work evenly across CUDA threads.
 
@@
 In most of our tests, the majority of running time was consumed on calculating $\vartheta$ of various graphs.
-As it was done by an external library, there isn't much optimization potential for us.
+So, there isn't much optimization potential for us.
 One thing of note is, that by specifying the precision of $\vartheta$ we want to calculate to be $1/3$ the algorithm sped up  by 20-40\%.
@@
 
-A GPU implementation of the na\"ive algorithm could also be considered for future work.
+A GPU implementation of the na\"ive algorithm could also be considered for a future work.
 We have created one, but after all path-enumeration optimizations of the CPU implementation we didn't manage to achieve any noticeable speedup.

### 2020-09-21 paper/implementation.tex
Overweekend fixes

@@
 
-We try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd hole is found we report that the graph is perfect, else that it is not.
+We try find an odd hole directly, then, we run the same algorithm on $\overline{G}$, and if no odd holes are found we report that the graph is perfect, else that it is not.
 
@@
 
-Another crucial optimization is to eliminate partial solutions that have edges between not consecutive vertices right away.
+Another crucial optimization is to eliminate partial solutions that have edges between nonconsecutive vertices right away.
 Also, when we look for an odd hole specifically, we can assume that its first vertex we enumerate is the lowest.

### 2020-09-21 paper/perfectGraphs.tex
Overweekend fixes

@@
 If $G$ contains a clique $K$ as a subgraph, we must use at least $|V(K)|$ colors to color it.
-This gives us a lower bound for a chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$.
+This gives us a lower bound for the chromatic number $\chi(G)$ -- it is always greater or equal to the cardinality of the largest clique $\omega(G)$.
 The reverse is not always true, in fact we can construct a graph with no triangles and requiring arbitrarily large numbers of colors (e.g.
@@
 	\label{def:bergeGraph}
-	A graph $G$ is \emph{Berge} if and only if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph.
+	A graph $G$ is \emph{Berge} if and only if both $G$ and $\overline{G}$ have no odd holes as induced subgraphs.
 \end{defn}
@@
 Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2.
-It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
-A graph with no odd hole and no odd antihole is called \emph{Berge} (\Cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
+It is also easy to see, that an odd antihole of size $n$ has the chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$.
+A graph with no odd holes and no odd antiholes is called \emph{Berge} (\Cref{def:bergeGraph}) after Claude Berge who studied perfect graphs.
 
-In 1961 Berge conjured that a graph is perfect if and only if it contains no odd hole and no odd antihole in what has become known as a strong perfect graph conjecture.
+In 1961 Berge conjured that a graph is perfect if and only if it contains no odd holes and no odd antiholes in what has become known as a strong perfect graph conjecture.
 In 2001 Chudnovsky et al.
@@
 
-\section{Recognizing berge graphs}
+\section{Recognizing perfect graphs}
 \label{sec:recognizingBerge}
@@
 
-Most obvious way to find a jewel is to enumerate all (possibly chordal) cycles of length 5 as $v_1, \ldots v_5$, check if it has all required nonedges and if it does, try to find a path $P$ as required.
+The most obvious way to find a jewel is to enumerate all (possibly chordal) cycles of length 5 as $v_1, \ldots v_5$, check if it has all required nonedges and if it does, try to find a path $P$ as required.
 This gives us a time of $O(|V|^7)$.
-We could speed it up to $O(|V|^6)$ with more careful algorithm (see Algorithm 3.1 of \cite{MC05}), but since whole Berge recognition algorithm takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
+We could speed it up to $O(|V|^6)$ with a more careful algorithm (see Algorithm 3.1 of \cite{MC05}), but since whole Berge recognition algorithm takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.
 
@@
 	\item $X$ is an anticomponent of the set of all $\{v_1, v_2, v_5\}$-complete vertices, and $v_3$, $v_4$ are not $X$-complete,
-	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$,
+	\item $P$ is a path of $G \setminus ( X \cup \{v_1, v_2, v_3, v_4\} )$ between $v_5$ and $v_6$ and no vertex in $P^*$ is $X$-complete or adjacent to $v_1$ or adjacent to $v_2$,
 	\item If $v_5v_6$ is an edge, then $v_6$ is not $X$-complete.
@@
 Each is checked in $O(1)$ time.
-If we find the correct one, we calculate a path $P$, but return right away, so we calculate $P$ at most once in whole algorithm.
+If we find the correct one, we calculate a path $P$, but return right away, so we calculate $P$ at most once in the whole algorithm.
 \end{proof}
@@
 		\mEndFor
-		\ls \RETURN no odd hole found
+		\ls \RETURN no odd holes found
 	\mEndProcedure
@@
 
-	The overall running time is $O(|V|^9)$ with testing for pyramids and testing all possible near-cleaners being parts with biggest time complexity.
+	The overall running time is $O(|V|^9)$ with testing for pyramids and testing all possible near-cleaners being parts with the biggest time complexity.
 \end{proof}

### 2020-09-22 paper/coloringBergeGraphs.tex
Final pdf to check

@@
 
-\Cref{sec:InformationTheory} and \Cref{sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.
+\Cref{sec:InformationTheory,sec:computingTheta} are based on lecture notes by Lovász \cite{Lovasz95}.
 
@@
 However, each value of $i$ when sent across the channel can be confused with value $(i \pm 1)$ mod $5$.
-This situation can be modeled by a graph $C_5$ (\cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if the values they represent can be confused.
+This situation can be modeled by a graph $C_5$ (\Cref{fig:c5}) in which vertices correspond to signal values and two vertices are connected if and only if the values they represent can be confused.
 
@@
 
-For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to $\alpha(G)$.
+For $k = 1$, maximum number of messages we can send without confusion in a single step is equal to the stability number $\alpha(G)$.
 To describe longer messages we use \emph{strong product} $G \cdot H$ of two graphs $G = (V, E)$, $H = (W, F)$ as the graph with $V(G \cdot H) = V \times W$, with $(i, u)(j, v) \in E(G \cdot H)$ if and only if $ij \in E$ and $uv \in F$, or $ij \in E$ and $u = v$, or $i = j$ and $uv \in F$.
@@
 \begin{defn}[semidefinite program]
-  Let $A_1, \ldots, A_n, B$ be given symmetric $m \times m$ matrices and be $c \in \mathbb{R}^n$ a given vector. A \emph{semidefinite program} is an optimization problem of the following form:
+  Let $A_1, \ldots, A_n, B$ be given symmetric $m \times m$ matrices and be $c \in \mathbb{R}^n$ be a given vector. A \emph{semidefinite program} is an optimization problem of the following form:
   \begin{equation*}
@@
 
-\section{Classical algorithms}
+\section{Combinatorial algorithms}
 \label{sec:classicalColoring}
@@
 
+\subsubsection{Coloring square-free Berge graphs}
+
 A most recent advancement (2018) is an algorithm by Chudnovsky et al.
@@
 
-The algorithm for coloring square-free Berge graphs is much more complex than CCLSV algorithm for Berge graphs recognition and would be much harder to implement.
-The main idea is that, if square-free Berge graph $G$ is not a member of class that is simple to recognize and color (Artemis graphs), then it must have an induced prism.
-We find it and grow it until it is maximal and then we can create a partition of $G$, that we color recursively.
+The algorithm for coloring square-free Berge graphs is much more complex than the CCLSV algorithm for Berge graphs recognition and would be much harder to implement.  
+The main idea is that, if square-free Berge graph $G$ is not an Artemis graph, then it must have an induced prism.
+We find it and grow it into a structure called a hyperprism, which is a generalization of a prism.
+Then, we grow it further either to find a maximal induced hyperprism, or encounter an induced subgraph that is the line graph of a bipartite subdivision of $K_4$.
+If the latter outcome happens, we can grow it in turn into a rather complex structure called a $J$-strip system and then into a maximal $J$-strip system.
+When we have found a maximal induced hyperprism or a maximal $J$-strip system, we can find a partition of graph $G$ that we can color recursively.
+
 The paper in which the algorithm is presented \cite{coloringSquareFree} is of much more mathematical ''flavor'' than \cite{MC05} -- there is a proof that a $O(|V|^9)$ algorithm exists, but actually deducing it from the paper isn't straightforward.
 We provide its pseudocode in the Appendix A.
+We believe that the work done there is a structurization of the algorithm that is a required step for a possible future work of implementing it.

### 2020-09-22 paper/definitions.tex
Final pdf to check

@@
 
-\begin{defn}[anticlique]
-  An \emph{independent set} or an \emph{anticlique} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
+\begin{defn}[independent set]
+  An \emph{independent set} or a \emph{stable set} is a graph of the form $G = (V, \emptyset)$, that is no vertices are connected.
 \end{defn}
-In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an anticlique.
+In a similar fashion, given a graph $G = (V, E)$, a subset of its vertices $V' \subseteq V$ will be called \emph{independent} (in the context of $G$) if and only if $G[V']$ is an independent set.
 

### 2020-09-22 paper/main.tex
Fixes
Final pdf to check

@@
 	Perfect graphs are a subject of intense study since their introduction in 1961.
-Only in 2001 the famous Perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found.
+Only in 2001 the famous perfect graph conjecture was proven to be true and in 2005 a polynomial method of determining if a graph is perfect was found.
 Since 1988 an algorithm is known for coloring perfect graphs, but it uses an ellipsoid method which is said to be complicated and impractical.
-As recently as in 2018 a polynomial algorithm for coloring perfect graphs without squares was published, that uses a combinatorial approach.
+As recently as in 2018 a polynomial algorithm that uses a combinatorial approach for coloring perfect graphs without squares was published.
 
@@
 \renewcommand{\listtheoremname}{List of algorithms}
+\makeatletter
+\renewcommand\thmt@listnumwidth{2.6em}
+\makeatother
 \listoftheorems[ignoreall,show={alg}]

### 2020-09-22 paper/perfectGraphs.tex
Final pdf to check

@@
 
-The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjured by Berge in 1961~\cite{CB61} and then proven by Lovász in 1972~\cite{LL72}.
+The first step to solve the problem of recognizing perfect graphs was the \emph{(weak) perfect graph theorem} first conjectured by Berge in 1961~\cite{CB61} and then proven by Lovász in 1972~\cite{LL72}.
 
@@
 
-In 1961 Berge conjured that a graph is perfect if and only if it contains no odd holes and no odd antiholes in what has become known as a strong perfect graph conjecture.
+In 1961 Berge conjectured that a graph is perfect if and only if it contains no odd holes and no odd antiholes in what has become known as a strong perfect graph conjecture.
 In 2001 Chudnovsky et al.

### 2020-09-22 code/test/plot.py

@@ -459,11 +459,11 @@ experiments = [
         # "ylim": (0, 1),
     },
     {
-        "restrictions": [(csv_algo, "JAVA")],
+        "restrictions": [],
         "x_param": csv_N,
         "x_show": csv_N,
         "type": "lines",
-        "size": sizes_in_inches["regular_small2"],
+        "size": sizes_in_inches["regular"],
         "y_param": csv_overall,
         "ylog": True,
         "yformatter": func_formatter,
@@ -472,7 +472,7 @@ experiments = [
         # "x_ticks_labels": ["$6\\times 3$", "", "$6\\times 5$", "", "$6\\times 7$", ""],
         "y_label": label_time_overall_s,
         "out_prefix": "java",
-        "ylim": (1, 250),
+        # "ylim": (1, 250),
     },
 ]
 
